### 2017-06-06 paper/article.tex
Code update + Article v1

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{hyperref}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Applied Acoustics}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{An efficient audio coding scheme for large scale monitoring of soundscapes}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{Felix Gontier, Mathieu Lagrange, Arnaud Can, Catherine Lavandier}

\address{felix.gontier@reseau.eseo.fr\\mathieu.lagrange@cnrs.fr}

\begin{abstract}
%% Text of abstract
The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc (wp.nyu.edu/sonyc) and cense (cense.ifsttar.fr) projects.

Together with the estimation of acoustic indicators (LAeq, ...), one important aspect of those networks is their ability to detect the presence of sound sources of interest ( bird calls, sirens, explosion, ...) in order to better assess soundscapes. This detection step can be operated online (on the sensors) or offline (on the data servers).

The former is efficient in terms of data storage as only the detection events are transmitted. Though, it requires the availability of computing resources on the sensors in order to perform the detection step, and the detection is done once and cannot be recomputed.

The latter scheme has several benefits. First, the sensor is much simpler and can thus be autonomous in terms of energy, easing the deployment of the network. Second, it allows researchers to gather large amount of data that can be post processed and studied further offline. Data can be re analysed following newer classification schemes or using new indicators.

But, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way. Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.

The coding scheme described in this paper has the following features. It is of low bitrate but still allows the computation of most of the standard acoustics indicators with high precision. As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data. Finally, according to preliminary perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.

In order to promote reproducible research, the coder as well as the experiments needed to generate the figures will be made available to the community.

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% \linenumbers
\clearpage
%% main text
\section{Introduction}
%\label{}

\section{Method}

\subsection{Signal Representation}
As audio signals in the time domain offers very few, often inefficient processing possibilities to reduce data size, a common practice is to prefer the frequency domain which in many cases provides a better information representation. Therefore, we first apply a short-term Fourier transform (STFT) to the arbitrary-length signal (sampled continously in our application). The phase is then discarded, being mostly retrievable under certain conditions \cite{nawab1983}, as well as resulting negative frequency components which are redundant due to the real nature of studied signals. However, these operations do not induce a significant gain in data size compared to the raw audio. A solution is the implementation of auditory filterbanks to concentrate relevant information into a fixed number of values in the same way the human cochlea does, that is, grouping frequency coefficients around critical bands in a logarithmic scale. This technique offers an important advantage beyond the information-dimensionality ratio improvement: in the Fourier squared magnitude domain, it only amounts to a single matrix multiplication which can be reversed to some degree. In this work, we study two different filterbanks and propose a set of analysis parameters for each.\\

We first use the widely known Mel scale as implemented by the \textit{rastamat} library \cite{ellis2005}. STFT analysis frames are obtained by applying a Hann window on 23.2~ms of signal with 50\% (11.6~ms) overlap to allow for phase recovery.\\

Another studied auditory transformation is the calculation of third-octave bands, generally used to compute the equivalent sound level $L_{eq}$ when acoustic measurements are needed. While the related filters are usually applied in the time domain, \cite{antoni2010} presents a frequency weights matrix design procedure that complies with both ANSI S1.1-1986 and IEC 61260-1:2014 standards, while respecting the partition of unity principle over all frequency bins in the relevant range. We implement this method for third-octave bands -17 to 13, ie. 20~Hz - 20kHz range, although with a minor change: inverting the use of sines and cosines is found to be a more intuitively correct approach, as we believe was the author's original intention. The STFT is computed for 125~ms audio windows, zero-padded to maximize FFT performance after the application of a rectangular function. No overlap is used to maximize the efficiency of the process as it is not needed to match the concept of "fast" acoustical measurements (8 per second). The rectangular window choice is made to ensure energy conservation in a given analysis frame. Results are compared with Couvreur's implementation \cite{couvreur} and observe similar results and a better handling of sidemost bands: low frequencies where resolution is poor and higher frequencies where cutoff frequencies are superior than Nyquist's frequency rendering most time-domain filter designs difficult.\\

\subsection{Data Encoding}
We finally use Huffman coding to further reduce data dimensionality. As in most entropy coding algorithms, the efficiency of this technique depends on two major factors: a reduced amount of symbols and a low data entropy. The first is generally obtained by applying a quantization process to the signal, whereas the second is directly linked with the probability density function (PDF) of these symbols, with entropy decreasing when very few symbols have a very high probability of appearance. Considering an estimated PDF for our data as shown in Figure~\ref{fig:pdf}a, immediately applying a linear quantization clearly results in most of the information being lost. We therefore spread the PDF by taking the logarithm (natural or base 10) of the signal, then apply a linear quantization with $2^{q-1}-1$ output values to obtain Figure~\ref{fig:pdf}b. Finally, we use a simple $\Delta$-encoding algorithm along the time dimension to eliminate redundancies and effectively concentrate higher probabilities on symbols around zero (Figure~\ref{fig:pdf}c). This yields a higher amount of symbols at $2^q-1$ but a nevertheless smaller entropy (in the example shown here, the former is $H_{log} = 6.24~sh$ and the latter $H_{\Delta} = 3.54~sh$). Huffman encoding is then computed for large texture frames of several minutes with a frame-specific symbol-code dictionnary, as we found using a single dictionnary generated with an entire dataset was not beneficial in terms of efficiency or computation time. Alternatively, analysis frames can be encoded and sent separately for continous transfers using one general dictionnary.\\

\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.8\textwidth]{pdf.eps}
	\caption{Example of estimated probability density functions of the data throughout the encoding step. (left) Unchanged output of the representation step, concentrated towards very low values. (middle) PSD "flattening" effect induced by logarithm application. Here values are mapped to the range $[0, 2^7-1]$ and rounded to perform quantization. (right) Output of the $\Delta$ compression, with desirable probabilities as the input to a Huffman algorithm.}
	\label{fig:pdf}
\end{figure}
6.24 before
3.54 after

\subsection{Decoding and Signal Retrieval}

The decoding process is quite straightforward, as both Huffman and $\Delta$ compression are lossless and directly reversible. Recovering a linearly-scaled spectrogram can be achieved by scaling the transpose of the forward transformation matrix, although a loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}. Signal phase is approximated by either white noise spectrogram scaling or a Griffin\& Lim algorithm \cite{griffin1984}, and the signal is retrieved using overlap-add. When using overlap while computing third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.\\

\begin{figure}[htbp]
	\centering
		\includegraphics[width=0.8\textwidth]{freq.png}
	\caption{Third-octave bands analysis and approximate inverse transformation effects on energy location. This process yields an important and heterogeneous loss in resolution, particularly at higher frequency points.}
	\label{fig:freq}
\end{figure}

The entire coder process is summarized in Figure~\ref{fig:scheme}.

\begin{figure}[htbp]
	\centering
		\includegraphics[width=1\textwidth]{scheme.pdf}
	\caption{Overview of the coder process.}
	\label{fig:scheme}
\end{figure}

\subsection{Evaluation}
A set of metrics is computed to assess the efficiency of the proposed coder scheme and determine the impact of the algorithm's parameters, which are as follow: the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, and only for Mel bands the number of coefficients between 10 and 40. We also study the effect of time averaging analysis frames: to force a fixed amount of frames per second lesser than the average speech rate in phonemes per second is a possible way to alter intelligibility at the cost of temporal information resolution.\\

The UrbanSound8k dataset\cite{salamon2014} features about 9 hours of urban environmental sounds recordings separated in 8732 wave files ranging from 1 to 4 seconds each. The recordings are labeled in 10 classes (air conditioner, car horn, children playing, dog bark, drilling, enginge idling, gun shot, jackhammer, siren, street music), and distributed in 10 independant folds. A method and baseline results are also provided for the classification task. It is used in all the following experiments with the exception of intelligibility computation for which a small dataset of high-quality voice recordings is preferred. Audio files are resampled 44.1 samples per second, normalized and reduced to a single channel.\\

We first evaluate the global loss of information by implementing the four classification models proposed in \cite{salamon2014}: a support vector machine with a radial basis function kernel, a random forest classifier with 500 trees, a decision tree and a k-nearest neighbors classifier with $k = 5$. Values for the SVM parameter $C$ and RBF kernel variance $\sigma^2$ are found with a grid search. We apply a discrete cosine transform to the critical band signal representation to obtain cepstra (known as Mel Frequency Cepstrum Coefficients or MFCC in the first case) of which we conserve the 25 first coefficients, and summarize along time with the mean, variance, skewness, kurtosis, minimum, maximum, median, derivative mean and variance, second order derivative mean and variance. The feature vector is thus comprised of 275 values to reproduce available results and compare with our own. Models are trained for each setup using the 10-fold method, that is, every combination of testing one fold on models trained with the other nine.\\

Intelligibility in decoded and reconstructed audio is also one of the main concerns of this study. We conduct preliminary perceptive tests to ensure that a clean speech recording is made unintelligible, implying the same results in usually noisier urban soundscapes. We also provide the computation of two objective metrics: the Coherence Speech Intelligibility Index\cite{kates2005} (CSII) and frequency-eighted segmental SNR\cite{hu2008} (fwSNRseg) by comparing original unaltered samples and recovered audio. These two indicators have been shown to correlate well with perceptual tests\cite{ma2009}, although results are only available for lesser degradations and distortions.\\

The coder's output bitrate as well as additional measurement error is computed for both data representations, it is expressed in dB and compared to the IEC 61672-1:2013 standard on sound level meter tolerance. This is to verify that the quantization step yields a maximum absolute error inferior to the precision of the recording device. To provide relevant statistics, these quantities are estimated for a total of 53 10-minutes texture frames.\\

\section{Results}

\section{Conclusion}

\clearpage
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-harv} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.
\section{References}
\begin{thebibliography}{09}

\bibitem{nawab1983}
Nawab, H. and Quatieri, T. and Lim, J. (1983). Signal reconstruction from short-time Fourier transform magnitude. \textit{IEEE Transactions on Acoustics, Speech, and Signal Processing}, 31(4)

\bibitem{ellis2005}
Ellis, D. (2005). \textit{{PLP} and {RASTA} (and {MFCC}, and inversion) in {M}atlab}. Available at: \url{http://www.ee.columbia.edu/~dpwe/resources/matlab/rastamat/}

\bibitem{antoni2010}
Antoni, J. (2010). Orthogonal-like fractional-octave-band filters. \textit{J. Ac. Soc. Am.}, 127(2)

\bibitem{couvreur}
Couvreur, C. \textit{Implementation of a one-third-octave filter bank in Matlab}. Available at: \url{http://citeseer.ist.psu.edu/24150.html}

\bibitem{griffin1984}
Griffin, D. and Lim, J. (1984). Signal Estimation from Modified Short-Time Fourier Transform. \textit{IEEE Transactions on Acoustics, Speech, and Signal Processing}, 32(2)

\bibitem{salamon2014}
Salamon, J. and Jacoby, C. and Bello, J. (2014). A Dataset and Taxonomy for Urban Sound Research. \textit{Proceedings of the 22nd ACM international conference on Multimedia}

\bibitem{kates2005}
Kates, J. and Arehart, K. (2005). Coherence and the Speech Intelligibility Index. \textit{J. Ac. Soc. Am.}, 115(5)

\bibitem{hu2008}
Hu, Y. and Loizou, P. (2008). Evaluation of objective quality measures for speech enhancement. \textit{IEEE Transactions on Audio, Speech, and Language Processing}, 16(1)

\bibitem{ma2009}
Ma, J. and Hu, Y. and Loizou, P. (2009). Objective measures for predicting speech intelligibility in noisy conditions based on new band-importance functions. \textit{J. Ac. Soc. Am.}, 125(5)

\end{thebibliography}
\end{document}

\endinput
%%
%% End of file `elsarticle-template-harv.tex'.

### 2017-06-06 censeCoder/ceco1representation.m

@@ -28,7 +28,7 @@ if strcmp(setting.desc, 'mel')
     end
 elseif strcmp(setting.desc, 'tob')
     l_frame = (round(0.125*sr)-mod(round(0.125*sr), 2)); % Approximately 125ms, "fast" Leq
-    l_hop = 0.5*l_frame; % No overlap
+    l_hop = setting.tobhop*l_frame;
     %% Filterbank calculation, can be replaced with constant matrix
     N = 2^13;
     N_filt = 2^17; % Design with a much greater precision
@@ -119,6 +119,9 @@ for ind_fold = 1:length(file_path)
             n_frames{ind_fold}{ind_file} = size(X, 2); % Number of STFT windows before averaging, needed for reconstruction
             Xi{ind_fold}{ind_file} = H*(abs(X).^2);
             Xi{ind_fold}{ind_file} = 10*log10(Xi{ind_fold}{ind_file}/N);
+            if ~isempty(find(isnan(Xi{ind_fold}{ind_file}), 1)) || ~isempty(find(isnan(Xi{ind_fold}{ind_file}), 1))
+                disp(['NaN or Inf found at file ' num2str(ind_file) ' in fold ' num2str(ind_fold) '.']);
+            end
             %% Quantization
             if setting.quant ~= 0
                 q_norm{ind_fold}{ind_file} = zeros(2, 1);

### 2017-06-06 censeCoder/ceco2coder.m

@@ -37,7 +37,7 @@ if strcmp(setting.desc, 'mel')
     end
 elseif strcmp(setting.desc, 'tob')
     l_frame = (round(0.125*sr)-mod(round(0.125*sr), 2)); % Approximately 125ms, "fast" Leq
-    l_hop = 0.5*l_frame; % No overlap
+    l_hop = setting.tobhop*l_frame;
     n_fps = 1+(sr-l_frame)/l_hop;
 end
 
@@ -53,7 +53,7 @@ end
 l_frame = ceil(60*setting.textframe*n_fps); % length of a texture frame in windows
 n_frames = ceil(size(X_desc_mat, 2)/l_frame);
 for ind_frame = 1:n_frames
-    disp(['Processing frame ' num2str(ind_frame) ' of ' num2str(n_frames) '...']);
+    disp(['Encoding: Processing frame ' num2str(ind_frame) ' of ' num2str(n_frames) '...']);
     %% Frames
     X_frame = X_desc_mat(:, (ind_frame-1)*l_frame+1:min(ind_frame*l_frame, end))'; % Transpose to group by features rather than time windows when reshaping to vector
     X_frame = X_frame(:); % Vector reformatting
@@ -85,7 +85,9 @@ for ind_frame = 1:n_frames
     end
     X_huff{ind_frame} = bin2dec(reshape(num2str([X_huff{ind_frame}(1:end-mod(end, 8)); X_huff{ind_frame}(end-mod(end, 8)+1:end); zeros(8-mod(length(X_huff{ind_frame}), 8), 1)]), 8, [])');
 end
-bitrate = sum(code_len)/length(X_huff)/setting.textframe/60;
+% bitrate = sum(code_len)/length(X_huff)/setting.textframe/60;
+bitrate = code_len/setting.textframe/60;
+if strcmp(setting.dataset, 'urbansound8k'); bitrate = bitrate(1:end-1); end % Last frame is incomplete and adds a bias
 
 %% Outputs
 % Store

### 2017-06-06 censeCoder/ceco3decoder.m

@@ -27,7 +27,7 @@ if strcmp(setting.desc, 'mel')
     end
 elseif strcmp(setting.desc, 'tob')
     l_frame = (round(0.125*sr)-mod(round(0.125*sr), 2)); % Approximately 125ms, "fast" Leq
-    l_hop = 0.5*l_frame; % No overlap
+    l_hop = setting.tobhop*l_frame;
     %% Filterbank calculation, can be replaced with constant matrix
     N = 2^13;
     N_filt = 2^17; % Design with a much greater precision
@@ -41,14 +41,15 @@ end
 
 if setting.quant
     X_desc_mat = [];
-    for indframe = 1:numel(data.X_huff)
+    for ind_frame = 1:numel(data.X_huff)
+        disp(['Decoding: Processing frame ' num2str(ind_frame) ' of ' num2str(numel(data.X_huff)) '...']);
         %% Matlab needs binary vectors
-        X_huff = str2num(reshape(dec2bin(data.X_huff{indframe})', [], 1));
-        X_huff = X_huff(1:data.huff_len(indframe));
+        X_huff = str2num(reshape(dec2bin(data.X_huff{ind_frame})', [], 1));
+        X_huff = X_huff(1:data.huff_len(ind_frame));
         %% Huffman decoding
         switch setting.dictgen
             case 'local'
-                X_delta = huffmandeco(X_huff, data.dict{indframe});
+                X_delta = huffmandeco(X_huff, data.dict{ind_frame});
             case 'global'
                 X_delta = huffmandeco(X_huff, data.dict);
         end
@@ -163,7 +164,7 @@ end
 if strcmp(setting.desc, 'mel')
     audiowrite(['..\..\decoded_samples\Sample_mel_fps' num2str(setting.fps) '_mel' num2str(setting.mel) '_quant' num2str(setting.quant) '_' setting.phaserec '.wav'], x{1}{1}./max(abs(x{1}{1})), sr);
 elseif strcmp(setting.desc, 'tob')
-    audiowrite(['..\..\decoded_samples\Sample_th_oct_quant' num2str(setting.quant) '.wav'], x{1}{1}./max(abs(x{1}{1})), sr);
+    audiowrite(['..\..\decoded_samples\Sample_th_oct_quant' num2str(setting.quant) '_' setting.phaserec '.wav'], x{1}{1}./max(abs(x{1}{1})), sr);
 end
 %% Outputs
 % Store

### 2017-06-06 censeCoder/ceco4metrics.m

@@ -68,12 +68,6 @@ switch setting.dataset
                 end
                 t_csii = (snr_csii+15)/30; % normalisation
                 csii(ind_file) = mean(mean(t_csii, 2));
-
-%                 P = sum(msc{ind_file}.*(abs(y_spec)).^2, 2);
-%                 N = sum((1-msc{ind_file}).*(abs(y_spec)).^2, 2);
-%                 snr_csii = 10*log10((sum(w.*repmat(P, [1 size(w, 2)])))./(sum(w.*repmat(N, [1 size(w, 2)]))));
-%                 t_csii = (snr_csii+15)/30; % normalisation
-%                 csii{ind_file} = mean(t_csii);
             elseif strcmp(setting.intelind, 'fwSNRseg')
                 X = [];
                 Y = [];
@@ -82,7 +76,7 @@ switch setting.dataset
                     Y(ind_band, :) = sum(repmat(w(:, ind_band), 1, size(y_spec, 2)).*abs(y_spec), 1);
                 end
                 fwSNRseg(ind_file) = (10/size(y_spec, 2))*sum(sum(log10((X.^2)./((X-Y).^2)), 1)/size(w, 2), 2);
-            end            
+            end
         end
         if strcmp(setting.intelind, 'CSII')
             obs.msc_mat = msc_mat;
@@ -98,12 +92,12 @@ switch setting.dataset
         load_data = expLoad(config, [], 1);
         x_desc = cell(length(load_data.X_desc), 1);
         for ind_fold = 1:length(load_data.X_desc)
-            disp(['Processing fold ' num2str(ind_fold) ' of ' num2str(length(load_data.X_desc)) '...']);
+            disp(['Feature extraction: Processing fold ' num2str(ind_fold) ' of ' num2str(length(load_data.X_desc)) '...']);
 %             x_desc{ind_fold} = zeros(275, 1);
             for ind_file = 1:length(load_data.X_desc{ind_fold})
                 if strcmp(setting.desc, 'mel')
                     if setting.quant ~= 0
-                        X_mel{ind_fold}{ind_file} = double(load_data.X_desc{ind_fold}{ind_file}).*load_data.x_mel_max{ind_fold}{ind_file}./(2^(setting.quant-1)-1); % Datatype size minus 1 for the delta-comp
[…]

### 2017-06-06 censeCoder/cecoReport.m

@@ -8,6 +8,8 @@ function config = cecoReport(config)
                                                             
 if nargin==0, censeCoder('report', 'r'); return; end%censeCoder('report', 'rhv'); return; end      
 
+% {fps, mel, quant, dictgen, htreealg, textframe, dataset, classmethod, phaserec, desc, intelind, tobhop}
+
 %% KNN
 % config = expExpose(config, 'p', 'mask', {0, 0, 6, 1, 2, 10, 2, 4, 2}, 'obs', 'cv_acc', 'save', 'knn_fps_mel_8', 'step', 4, 'expand', 1, 'color', {'b', 'g', 'r', 'black'}); % KNN accuracy as f(mel,fps)
 % config = expExpose(config, 't', 'mask', {7, 4, 1, 1, 2, 10, 2, 4, 2}, 'obs', 'cv_acc', 'save', 'knn_base', 'step', 4); % Baseline KNN accuracy

### 2017-06-06 censeCoder/run_script.m

@@ -3,6 +3,18 @@ clear all, close all, clc;
 %% 8 bit quant, varying fps/mel
 % censeCoder('do', [1 2 4], 'mask', {0, 0, 6, 1, 2, 10, 2, 4, 2, 1, 2});
 % censeCoder('do', [1 2 3 4], 'mask', {0, 0, 6, 1, 2, 10, 1, 4, 1, 1, 2});
-censeCoder('do', [4], 'mask', {0, 0, 6, 1, 2, 10, 1, 4, 1, 2, 1});
+%censeCoder('do', [3], 'mask', {0, 0, 6, 1, 2, 10, 1, 4, 1, 2, 1});
 % %% Baseline
-% censeCoder('do', [1 4], 'mask', {7, 4, 1, 1, 2, 10, 0, 4, 2, 1, 2});
+% censeCoder('do', [1 4], 'mask', {7, 3, 1, 1, 2, 10, 2, 1, 2, 1, 2});
+
+%% Global run
+%%% censeCoder('do', [step], 'mask', {fps, mel, quant, dictgen, htreealg, textframe, dataset, classmethod, phaserec, desc, intelind, tobhop});
+% censeCoder('do', [1], 'mask', {-1, -1, 0, -1, -1, -1, 0, -1, -1, 2, -1, 2}); % Third-octave bands
+% censeCoder('do', [2], 'mask', {-1, -1, 0, 1, 2, 10, 2, -1, -1, 2, -1, 2});
+% censeCoder('do', [4], 'mask', {-1, -1, 0, -1, -1, -1, 2, 1, -1, 2, -1, 2});
+
+% censeCoder('do', [1 4], 'mask', {7, 3, 1, -1, -1, -1, 2, 0, -1, 1, -1, -1});
+% censeCoder('do', [1 2 4], 'mask', {0, 0, 6, 1, 2, 10, 2, 4, -1, 1, -1, -1});
+% censeCoder('do', [1 2 3 4], 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, 0, -1});
+% censeCoder('do', [4], 'mask', {0, 0, 6, 1, 2, 10, 2, 1:3, -1, 1, -1, -1});
+censeCoder('do', [1 2 4], 'mask', {7, 3, 2:6, 1, 2, 10, 2, 0, -1, 1, -1, -1});

### 2017-06-06 paper/article.tex
new layout
ml comments

@@
 
-\documentclass[preprint,12pt]{elsarticle}
+\documentclass[final,3p,times,twocolumn]{elsarticle}
 
@@
 \usepackage{hyperref}
+\usepackage{color}
+
 %% The amsthm package provides extended theorem environments
@@
 \journal{Applied Acoustics}
+
+\newcommand{\ml}[1]{\textcolor{blue}{ Mathieu: #1}}
 
@@
 
-\title{An efficient audio coding scheme for large scale monitoring of soundscapes}
+\title{An efficient audio coding scheme for large scale acoustic monitoring}
 
@@
 
-\section{Method}
+\section{Background}
 
-\subsection{Signal Representation}
+\ml{decrit ici les besoins avec une biblio}
+
+\subsection{acoustic monitoring}
+
+db spl, tiers d'octave, etc
+
+10 refs
+
+et dire que a partir de tiers d'ocatve 125 on peut retrouver tout les autres
+
+\subsection{event detection}
+
+15 refs
+
+\section{Encoding scheme}
+
 As audio signals in the time domain offers very few, often inefficient processing possibilities to reduce data size, a common practice is to prefer the frequency domain which in many cases provides a better information representation.
@@
 In this work, we study two different filterbanks and propose a set of analysis parameters for each.\\
+
+\ml{ce n'est pas vraiment ca.
+On a une contrainte qui est que l'on veut coder des données utilissables pour le monitoring acoustique et la reco d'evenements qui considère des représentations spécifiques.
+Je te propose donc de passer en revue les deux côtés dans la section ci dessus (background) et dire que nos choix sont raisonnables.}
 
@@
 The rectangular window choice is made to ensure energy conservation in a given analysis frame.
-Results are compared with Couvreur's implementation \cite{couvreur} and observe similar results and a better handling of sidemost bands: low frequencies where resolution is poor and higher frequencies where cutoff frequencies are superior than Nyquist's frequency rendering most time-domain filter designs difficult.\\
+Results are compared with Couvreur's implementation \cite{couvreur}.
+We observe similar results and a better handling of sidemost bands: low frequencies where resolution is poor and higher frequencies where cutoff frequencies are superior than Nyquist's frequency rendering most time-domain filter designs difficult.
+\ml{pas clair}
+
+\ml{mettre des chiffres ou une figure pour motiver ton choix dans la section dédiée et faire ici une ref}
 
 \subsection{Data Encoding}
-We finally use Huffman coding to further reduce data dimensionality.
-As in most entropy coding algorithms, the efficiency of this technique depends on two major factors: a reduced amount of symbols and a low data entropy.
+
+\ml{en general tes phrases sont trop longues. Coupe en deux des que tu peux et pas de paranthèses !!}
+
+A Huffman coding scheme \cite{} is then used to further reduce data dimensionality.
+As in most entropy coding algorithms, the efficiency of this technique depends on two important factors: a reduced amount of symbols \ml{in the dictionnary ?} and a low data entropy \ml{explique ce dernier point}.
 The first is generally obtained by applying a quantization process to the signal, whereas the second is directly linked with the probability density function (PDF) of these symbols, with entropy decreasing when very few symbols have a very high probability of appearance.
@@
 We therefore spread the PDF by taking the logarithm (natural or base 10) of the signal, then apply a linear quantization with $2^{q-1}-1$ output values to obtain Figure~\ref{fig:pdf}b.
-Finally, we use a simple $\Delta$-encoding algorithm along the time dimension to eliminate redundancies and effectively concentrate higher probabilities on symbols around zero (Figure~\ref{fig:pdf}c).
-This yields a higher amount of symbols at $2^q-1$ but a nevertheless smaller entropy (in the example shown here, the former is $H_{log} = 6.24~sh$ and the latter $H_{\Delta} = 3.54~sh$).
-Huffman encoding is then computed for large texture frames of several minutes with a frame-specific symbol-code dictionnary, as we found using a single dictionnary generated with an entire dataset was not beneficial in terms of efficiency or computation time.
-Alternatively, analysis frames can be encoded and sent separately for continous transfers using one general dictionnary.\\
+Finally, we use a $\Delta$-encoding algorithm \cite{} along the time dimension to reduce redundancies and effectively concentrate higher probabilities on symbols around zero (Figure~\ref{fig:pdf}c).
+This yields a higher amount of symbols at $2^q-1$ but a nevertheless smaller entropy.
+In the example shown here, the former is $H_{log} = 6.24~sh$ and the latter $H_{\Delta} = 3.54~sh$.
+Huffman encoding is then computed for texture frames of several minutes with a frame-specific symbol-code dictionnary.
+Indeed, we found that using a single dictionnary generated with an entire dataset was not beneficial in terms of efficiency or computation time.
+Alternatively, analysis frames can be encoded and sent separately for continous transfers using one general dictionnary.
 
-\begin{figure}[htbp]
+\ml{a discuter. Pourquoi ne pas avoir un dic fixe, ce doit etre couteux de faire huffman a chaque fois ?}
+
+\ml{ici encore, il faut mettre des chiffres pour motiver ce choix. plutot faire des refs a la subsection dediée}
+
+\begin{figure*}[htbp]
 	\centering
@@
 	\label{fig:pdf}
-\end{figure}
+\end{figure*}
 6.24 before
@@
 
-\subsection{Decoding and Signal Retrieval}
-
 The decoding process is quite straightforward, as both Huffman and $\Delta$ compression are lossless and directly reversible.
-Recovering a linearly-scaled spectrogram can be achieved by scaling the transpose of the forward transformation matrix, although a loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
-Signal phase is approximated by either white noise spectrogram scaling or a Griffin\& Lim algorithm \cite{griffin1984}, and the signal is retrieved using overlap-add.
-When using overlap while computing third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.\\
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=0.8\textwidth]{freq.png}
-	\caption{Third-octave bands analysis and approximate inverse transformation effects on energy location.
-This process yields an important and heterogeneous loss in resolution, particularly at higher frequency points.}
-	\label{fig:freq}
-\end{figure}
 
@@
 
-\begin{figure}[htbp]
+\begin{figure*}[htbp]
 	\centering
@@
 	\label{fig:scheme}
-\end{figure}
+\end{figure*}
 
-\subsection{Evaluation}
+\section{Evaluation}
 A set of metrics is computed to assess the efficiency of the proposed coder scheme and determine the impact of the algorithm's parameters, which are as follow: the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, and only for Mel bands the number of coefficients between 10 and 40.
 We also study the effect of time averaging analysis frames: to force a fixed amount of frames per second lesser than the average speech rate in phonemes per second is a possible way to alter intelligibility at the cost of temporal information resolution.\\
+
+\subsection{efficiency}
+
+detaille les resulats pour l'efficacité de codage
+
+\subsection{recognition}
 
@@
 
+\subsection{Inintelligibility}
+
 Intelligibility in decoded and reconstructed audio is also one of the main concerns of this study.
@@
 These two indicators have been shown to correlate well with perceptual tests\cite{ma2009}, although results are only available for lesser degradations and distortions.\\
+
+	\ml{j'ai mis le paragraphe en dessous pour des raisons de clarté car cela ne fait pas parti du codeur. A reformuler}
+
+ Recovering a linearly-scaled spectrogram can be achieved by scaling the transpose of the forward transformation matrix, although a loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
+Signal phase is approximated by either white noise spectrogram scaling or a Griffin\& Lim algorithm \cite{griffin1984}, and the signal is retrieved using overlap-add.
+When using overlap while computing third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.\\
+
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\columnwidth]{freq.png}
+	\caption{Third-octave bands analysis and approximate inverse transformation effects on energy location.
+This process yields an important and heterogeneous loss in resolution, particularly at higher frequency points.}
+	\label{fig:freq}
+\end{figure}
 

### 2017-06-11 paper/article.tex
Paper update + TOB filters fix

@@
 
-\ml{decrit ici les besoins avec une biblio}
+The present work is constrained to allow both acoustic monitoring and sound event recognition in urban soundscapes.
+Here we briefly review state-of-the-art methods in both subjects to guide our choices.
 
-\subsection{acoustic monitoring}
+\subsection{Acoustic monitoring}
 
-db spl, tiers d'octave, etc
+The considered sensor network primarily aims at monitoring urban soundscapes, that is, continously assessing their content and impact on the population.
+This is typically enabled by measuring energetic acoustic indicators such as the equivalent sound pressure level $L_{eq}$ in dB SPL or its A-weighted equivalent $L_{Aeq}$ in dBA.
+However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they fail to fully describe soundscapes \cite{rychtarikova2013}.
+Many other variables can be derived to better account for previously implicit properties \cite{can2016} including percentile values or time evolution.
+Studies have been conducted to select relevant subsets of descriptors in sound environment characterization \cite{can2015, brocolini2013, nilsson2007}.\\
 
-10 refs
+All the mentionned indicators are measured at periods ranging from 0.125~ms or 1~s (resp.
+fast and slow) to longer periods of several minutes.
+Therefore, sound frequency information remains unused despite being closely related with subjective evaluations \cite{ishiyama2000}.
+A simple solution is the calculation of energetic indicators for the 31 third-octave bands within the human audition range 20~Hz - 20~kHz.\\
 
-et dire que a partir de tiers d'ocatve 125 on peut retrouver tout les autres
+This measurement appears well-suited for this work's purpose: in addition to being an efficient descriptor \cite{torija2013}, it allows for the computation of most cited indicators while representing reasonably small, fixed amounts of data to be transmitted.
 
-\subsection{event detection}
+\subsection{Event detection}
 
-15 refs
+Another major interest of this work is sound event recognition.
+This problem has been the subject of extensive research in the past on speech \cite{anusuya2009}, music \cite{tzanetakis2002}, and lately more complex scenes in which the current work falls.
+Studied classification methods are diverse, ranging from time-dependant modeling with HMMs \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}.
+Common architectures include learning-based classifiers such as support vector machines (SVM) \cite{kumar2016}, gaussian mixture models (GMM) \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}.
+However, the selection of relevant features is still an open debate.
+The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal.
+Among them, mel spectrograms and their cepstral-domain derivation, the mel-frequency cepstrum coefficients (MFCC), are the most recurrent.
+These representations effectively try to model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale, thus bearing important physical significance.
+They may also be exploited together with features computed in other domains to better model signal properties.
+For instance, \cite{cai2006} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domaid features.
+Another promising solution is feature engineering via unsupervised learning, which \cite{salamon2015-2} implements with a k-means clustering technique.
+Alternative data representations such as the scattering transform \cite{bauge2013} show good results in environmental sound classification tasks \cite{salamon2015}.\\
+A more detailed review of used methods is available in \cite{chachada2013}.
 
@@
 
-As audio signals in the time domain offers very few, often inefficient processing possibilities to reduce data size, a common practice is to prefer the frequency domain which in many cases provides a better information representation.
-Therefore, we first apply a short-term Fourier transform (STFT) to the arbitrary-length signal (sampled continously in our application).
-The phase is then discarded, being mostly retrievable under certain conditions \cite{nawab1983}, as well as resulting negative frequency components which are redundant due to the real nature of studied signals.
-However, these operations do not induce a significant gain in data size compared to the raw audio.
-A solution is the implementation of auditory filterbanks to concentrate relevant information into a fixed number of values in the same way the human cochlea does, that is, grouping frequency coefficients around critical bands in a logarithmic scale.
-This technique offers an important advantage beyond the information-dimensionality ratio improvement: in the Fourier squared magnitude domain, it only amounts to a single matrix multiplication which can be reversed to some degree.
-In this work, we study two different filterbanks and propose a set of analysis parameters for each.\\
+The technical constraints of size inherent to the studied setup make it impossible to transmit raw audio recordings.
+Following the considerations briefly exposed in the previous section, we conclude that third-octave bands are a reasonable choice.
+As mentionned, they provide advantages in both acoustic monitoring and data volume per measurement period.
+The physical content is also close to that of mel spectrograms, being just another filterbank transform with logarithmic frequency scaling.\\
 
-\ml{ce n'est pas vraiment ca.
-On a une contrainte qui est que l'on veut coder des données utilissables pour le monitoring acoustique et la reco d'evenements qui considère des représentations spécifiques.
-Je te propose donc de passer en revue les deux côtés dans la section ci dessus (background) et dire que nos choix sont raisonnables.}
+A common way to implement third-octave analysis is to first design the highest octave three filters, and use them on progressively time-decimated versions of the input signal \cite{davis1986}.
+In practice, however, this technique presents multiple issues.
+\cite{antoni2010} presents an alternative analysis method based on direct frequency weighting.
+The weights matrix design procedure complies with both ANSI S1.1-1986 and IEC 61260-1:2014 standards.
+It also respects the partition of unity principle over all frequency bins in the relevant range.
+Resulting filters for different parameter $l$ values are compared with Couvreur's implementation \cite{couvreur} of the time-domain filtering, as shown in Figure~\ref{fig:freq_filt}.
+The major difference is that gains at cutoff frequencies are fixed at the optimal -3dB by design.\\
 
-We first use the widely known Mel scale as implemented by the \textit{rastamat} library \cite{ellis2005}.
-STFT analysis frames are obtained by applying a Hann window on 23.2~ms of signal with 50\% (11.6~ms) overlap to allow for phase recovery.\\
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\columnwidth]{tob_imp.eps}
+	\caption{Comparison of Couvreur's and Antoni's implementations of third-octave filters. Frequency-weighting allows for arbitrary transfer functions and thus more accurate gains as standards impose.}
+	\label{fig:freq_filt}
+\end{figure}
 
-Another studied auditory transformation is the calculation of third-octave bands, generally used to compute the equivalent sound level $L_{eq}$ when acoustic measurements are needed.
-While the related filters are usually applied in the time domain, \cite{antoni2010} presents a frequency weights matrix design procedure that complies with both ANSI S1.1-1986 and IEC 61260-1:2014 standards, while respecting the partition of unity principle over all frequency bins in the relevant range.
-We implement this method for third-octave bands -17 to 13, ie.
-20~Hz - 20kHz range, although with a minor change: inverting the use of sines and cosines is found to be a more intuitively correct approach, as we believe was the author's original intention.
-The STFT is computed for 125~ms audio windows, zero-padded to maximize FFT performance after the application of a rectangular function.
-No overlap is used to maximize the efficiency of the process as it is not needed to match the concept of "fast" acoustical measurements (8 per second).
-The rectangular window choice is made to ensure energy conservation in a given analysis frame.
-Results are compared with Couvreur's implementation \cite{couvreur}.
-We observe similar results and a better handling of sidemost bands: low frequencies where resolution is poor and higher frequencies where cutoff frequencies are superior than Nyquist's frequency rendering most time-domain filter designs difficult.
-\ml{pas clair}
+The first step is to represent the signal in the frequency domain using a short-term Fourier transform (STFT).
+The continuously sampled audio is segmented into 125~ms frames to provide "fast" acoustic measurements.
+The data is zero-passed to the next power of two to allow best fft performances.
+No overlap is used as it doubles both computational and memory costs and is not required for our application.
+A rectangular window is applied to ensure energy conservation in a given analysis frame.
+The phase is unimportant to third-octave analysis, thus it is discarded.
+Similarly, negative frequency components contain the same information as positive ones because the base signal is real.
+We then compute third-octave bands from the squared spectral magnitude by matrix multiplication with the frequency weights proposed in \cite{antoni2010} for $l = 2$\footnote{When implementing said method, we found that squaring the $\phi_l(p), l \geq 1$ intermediate function (p.
+887) was the correct approach to meet cutoff frequencies requirements, and we believe this was the author's original intention.}.
+We include analysis for bands $i$ from -17 to 13, ie.
+center frequencies $f_i$ ranging from $20~Hz$ to $20~kHz$ with $f_0 = 1~kHz$.
+This means the main representation is composed of 31 values sampled every 125~ms.\\
 
-\ml{mettre des chiffres ou une figure pour motiver ton choix dans la section dédiée et faire ici une ref}
+Alternatively, we also implement the mel filterbank for testing purposes.
+Mel spectrograms can be used as a baseline method to evaluate the relative performance of third-octave bands in sound event recognition.
+Furthermore, this representation is not bound by constraints such as conservation of energy, specific framing parameters or fixed resolution.
+It offers a more flexible tool to study intelligibility alteration and coder performance, both of which we take interest in.
+Mel spectrograms are computed with the \textit{rastamat} library \cite{ellis2005}.
+STFT analysis frames are obtained by applying a Hann window on 23.2~ms of signal with 50\% (11.6~ms) overlap to allow for efficient phase recovery in further tests.
 
@@
 
-\ml{en general tes phrases sont trop longues. Coupe en deux des que tu peux et pas de paranthèses !!}
-
-A Huffman coding scheme \cite{} is then used to further reduce data dimensionality.
-As in most entropy coding algorithms, the efficiency of this technique depends on two important factors: a reduced amount of symbols \ml{in the dictionnary ?} and a low data entropy \ml{explique ce dernier point}.
-The first is generally obtained by applying a quantization process to the signal, whereas the second is directly linked with the probability density function (PDF) of these symbols, with entropy decreasing when very few symbols have a very high probability of appearance.
+A Huffman coding scheme \cite{huffman1952} is then used to further reduce data dimensionality.
+As in most entropy coding algorithms, the efficiency of this technique depends on two important factors.
+A reduced amount of symbols in the dictionnary yields smaller code size on lower probability symbols.
+Lower data entropy, ie.
+lower average information content of the signal distribution, also increases performance.
+The first is generally obtained by applying a quantization process to the signal, whereas the second is directly linked with the probability density function (PDF) of these symbols.
+It is defined as $H = -\sum\limits_i p_ilog_n(p_i)$, where $p_i$ is the probability of appearance of a given symbol and $n$ the numerical base in which information is represented.
+As such, entropy decreases when very few symbols have a very high probability of appearance and is maximum for a uniform distribution.
 Considering an estimated PDF for our data as shown in Figure~\ref{fig:pdf}a, immediately applying a linear quantization clearly results in most of the information being lost.
-We therefore spread the PDF by taking the logarithm (natural or base 10) of the signal, then apply a linear quantization with $2^{q-1}-1$ output values to obtain Figure~\ref{fig:pdf}b.
-Finally, we use a $\Delta$-encoding algorithm \cite{} along the time dimension to reduce redundancies and effectively concentrate higher probabilities on symbols around zero (Figure~\ref{fig:pdf}c).
+We therefore spread the PDF by taking the logarithm of the representation.
+A linear quantization is then applied with $2^{q-1}-1$ output values to obtain Figure~\ref{fig:pdf}b.
+Finally, we use a $\Delta$-encoding algorithm along the time dimension to reduce redundancies.
+This also effectively concentrates higher probabilities on symbols around zero (Figure~\ref{fig:pdf}c).
 This yields a higher amount of symbols at $2^q-1$ but a nevertheless smaller entropy.
 In the example shown here, the former is $H_{log} = 6.24~sh$ and the latter $H_{\Delta} = 3.54~sh$.
-Huffman encoding is then computed for texture frames of several minutes with a frame-specific symbol-code dictionnary.
-Indeed, we found that using a single dictionnary generated with an entire dataset was not beneficial in terms of efficiency or computation time.
-Alternatively, analysis frames can be encoded and sent separately for continous transfers using one general dictionnary.
+Huffman encoding is then computed with either a frame-specific symbol-code dictionnary or a constant one generated from an entire dataset.
+A comparison of both methods is shown in Figure~\ref{fig:dict_comp}.
+For most short texture frame durations, we found the local Huffman algorithm to be much faster.
+In fact, encoding complexity is function of the amount of dictionnary elements.
+If it is specific to a given data packet, then it does not need to contain every possible value.
+This gain seem to outweight the additional complexity induced by the tree generation algorithm.
+Alternatively, short texture frames or single analysis windows can be encoded using one general dictionnary to improve bitrate.
+This choice depends on which of the size and complexity parameters must be reduced most.\\
 
-\ml{a discuter. Pourquoi ne pas avoir un dic fixe, ce doit etre couteux de faire huffman a chaque fois ?}
-
-\ml{ici encore, il faut mettre des chiffres pour motiver ce choix. plutot faire des refs a la subsection dediée}
-
-\begin{figure*}[htbp]
+\begin{figure}[htbp]
 	\centering
-		\includegraphics[width=0.8\textwidth]{pdf.eps}
+		\includegraphics[width=0.5\textwidth]{pdf.eps}
 	\caption{Example of estimated probability density functions of the data throughout the encoding step.
 (left) Unchanged output of the representation step, concentrated towards very low values.
-(middle) PSD "flattening" effect induced by logarithm application.
+(middle) PDF "flattening" effect induced by logarithm application.
 Here values are mapped to the range $[0, 2^7-1]$ and rounded to perform quantization.
@@
 	\label{fig:pdf}
-\end{figure*}
-6.24 before
-3.54 after
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\columnwidth]{dict_comp.eps}
+	\caption{Performance comparison of locally and globally generated Huffman dictionnaries.
+(top) The mean execution time ratio favors the use of frame-specific dictionnaries for tested texture frame lengths.
+(bottom) The mean output bitrate is close for both algorithms, showing that the necessity of sending symbol-code pairs mostly compensates for their optimality.}
+	\label{fig:dict_comp}
+\end{figure}
 
@@
 
-The entire coder process is summarized in Figure~\ref{fig:scheme}.
+The entire coder scheme is summarized in Figure~\ref{fig:scheme}.
 
@@
 A set of metrics is computed to assess the efficiency of the proposed coder scheme and determine the impact of the algorithm's parameters, which are as follow: the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, and only for Mel bands the number of coefficients between 10 and 40.
-We also study the effect of time averaging analysis frames: to force a fixed amount of frames per second lesser than the average speech rate in phonemes per second is a possible way to alter intelligibility at the cost of temporal information resolution.\\
+We also study the effect of time averaging analysis frames: to force a fixed amount of frames per second lesser than the average speech rate in phonemes per second is a possible way to alter intelligibility at the cost of temporal information resolution.
 
-\subsection{efficiency}
+\subsection{Efficiency}
 
-detaille les resulats pour l'efficacité de codage
+The coder's output bitrate as well as additional measurement error is computed for both data representations, it is expressed in dB and compared to the IEC 61672-1:2013 standard on sound level meter tolerance.
+This is to verify that the quantization step yields a maximum absolute error inferior to the precision of the recording device.
+To provide relevant statistics, these quantities are estimated for a total of 53 10-minutes texture frames.
 
-\subsection{recognition}
+\subsection{Event recognition}
 
@@
 The feature vector is thus comprised of 275 values to reproduce available results and compare with our own.
-Models are trained for each setup using the 10-fold method, that is, every combination of testing one fold on models trained with the other nine.\\
+Models are trained for each setup using the 10-fold method, that is, every combination of testing one fold on models trained with the other nine.
 
@@
 
-	\ml{j'ai mis le paragraphe en dessous pour des raisons de clarté car cela ne fait pas parti du codeur. A reformuler}
-
- Recovering a linearly-scaled spectrogram can be achieved by scaling the transpose of the forward transformation matrix, although a loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
+These metrics require a recovery of the time-domain signal.
+We must first recover a linearly-scaled spectrogram from the band-focused representations.
+This can be achieved by multiplying by the scaled transpose of the forward transformation matrix.
+A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
 Signal phase is approximated by either white noise spectrogram scaling or a Griffin\& Lim algorithm \cite{griffin1984}, and the signal is retrieved using overlap-add.
@@
 \end{figure}
-
-The coder's output bitrate as well as additional measurement error is computed for both data representations, it is expressed in dB and compared to the IEC 61672-1:2013 standard on sound level meter tolerance.
-This is to verify that the quantization step yields a maximum absolute error inferior to the precision of the recording device.
-To provide relevant statistics, these quantities are estimated for a total of 53 10-minutes texture frames.\\
 
@@
 
-\bibitem{nawab1983}
-Nawab, H. and Quatieri, T. and Lim, J. (1983). Signal reconstruction from short-time Fourier transform magnitude. \textit{IEEE Transactions on Acoustics, Speech, and Signal Processing}, 31(4)
+\bibitem{gozalo2015}
+Rey Gozalo, G.
+and Trujillo Carmona, J.
+and Barrigon Morillas, J.M.
+and Gomez Escobar, V.
+(2015).
+Relationship between objective acoustic indices and subjective assessments for the quality of soundscapes.
+\textit{Applied Acoustics}, 97, pp.
+1-10
+
+\bibitem{rychtarikova2013}
+Rychtarikova, M. and Vermeir, G. (2013). Soundscape categorization on the basis of objective acoustical parameters. \textit{Applied Acoustics}, 74(2), pp. 240-247
+
+\bibitem{can2016}
+Can, A.
+and Aumond, P.
+and Michel, S.
+and De Coensel, B.
+and Ribeiro, C.
+and Botteldooren, D.
+and Lavandier, C.
+(2016).
+Comparison of noise indicators in an urban context.
+In: \textit{Proceedings of the 45th International Congress and Exposition on Noise Control Engineering}, pp.
+5678-5686
+
+\bibitem{can2015}
+Can, A. and Gauvreau, B. (2015). Describing and classifying urban sound environments with a relevant set of physical indicators. \textit{J. Ac. Soc. Am.}, 137(1), pp. 208-218
+
+\bibitem{brocolini2013}
+Brocolini, L.
+and Lavandier, C.
+and Quoy, M.
+and Ribeiro, C.
+(2013).
+Measurements of acoustic environments for urban soundscapes: Choice of homogeneous periods, optimization of durations, and selection of indicators.
+\textit{J.
+Ac.
+Soc.
+Am.}, 134(1), pp.
+813-821
+
+\bibitem{nilsson2007}
+Nilsson, M.
+and Botteldooren, D.
+and De Coensel, B.
+(2007).
+Acoustic indicators of soundscape quality and noise annoyance in outdoor urban areas.
+In: \textit{Proceedings of the 19th International Congress on Acoustics}
+
+\bibitem{ishiyama2000}
+Ishiyama, T. and Hashimoto, T. (2000). The impact of sound quality on annoyance caused by road traffc noise: an influence of frequency spectra on annoyance. \textit{JSAE Review}, 21(2), pp. 225-230
+
+\bibitem{torija2013}
+Torija, A.
+and Ruiz, D.
+and Ramos-Ridao, A.
+(2013).
+Application of a methodology for categorizing and differentiating urban soundscapes using acoustical descriptors and semantic-differential attributes.
+\textit{J.
+Ac.
+Soc.
+Am.}, 134(1), pp.
+791-802
+
+\bibitem{anusuya2009}
+Anusuya, M. and Katty, S. (2009).  Speech recognition by machine, a review. \textit{International Journal of Computer Science and Information Security}, 6(3), pp. 181-205
+
+\bibitem{tzanetakis2002}
+Tzanztakis, G. and Essl, G. and Cook, P. (2002). Automatic musical genre classification of audio signals. \textit{IEEE Transactions on Speech and Audio Processing}, 10(5), pp. 293-302
+
+\bibitem{ntalampiras2014}
+Ntalampiras, S. (2014). Universal background modeling for acoustic surveillance of urban traffic. \textit{Digital Signal Processing}, 31, pp. 69-78
+
+\bibitem{aucouturier2007}
+Aucouturier, J.
+and Defreville, B.
+and Pachet, F.
+(2007).
+The bag-of-frames approach to audio pattern recognition: A sufficient model for urban soundscapes but not for polyphonic music.
+\textit{J.
+Ac.
+Soc.
+Am.}, 122(2), pp.
+881-891
+
+\bibitem{foggia2015}
+Foggia, P.
+and Petkov, N.
+and Saggese, A.
+and Strisciuglio, N.
+and Vento, M.
+(2015).
+Reliable detection of audio events in highly noisy environments.
+\textit{Pattern Recognition Letters}, 65, pp.
+22-28
+
+\bibitem{kumar2016}
+Kumar, A. and Raj, B. (2016). Features and Kernels for Audio Event Recognition. \textit{arXiv Preprint}, Available at: \url{https://arxiv.org/abs/1607.05765}
+
+\bibitem{radhakrishnan2005}
+Radhakrishnan, R. and Divakaran, A. and Smaragdis, P. (2005). Audio analysis for surveillance applications. In: \textit{IEEE Workshop on Applications of Signal Processing to Audio and Acoustics}
+
+\bibitem{salamon2017}
+Salamon, J. and Bello, J. (2017). Deep convolutional neural networks and data augmentation for environmental sound classification. \textit{IEEE Signal Processing Letters}, 24(3), pp. 279-283
+
+\bibitem{piczak2015}
+Piczak, K. (2015). Environmental sound classification with convolutional neural networks. In: \textit{IEEE 25th International Workshop on Machine Learning for Signal Processing}
+
+\bibitem{khunarsal2013}
+Khunarsal, P. and Lursinsap, C. and Raicharoen, T. (2013). Very short time environmental sound classification based on spectrogram pattern matching. \textit{Information Sciences}, 243, pp. 57-74
+
+\bibitem{couvreur2004}
+Couvreur, L.
+and Laniray, M.
+(2004).
+Automatic noise recognition in urban environments based on artificial neural networks and hidden markov models.
+In: \textit{The 33rd International Congress and Exposition on Noise Control Engineering}
+
+\bibitem{cai2006}
+Cai, R.
+and Lu, L.
+and Hanjalic, A.
+and Zhang, H.
+and Cai, L.
+(2006).
+A flexible framewok for key audio effects detection and auditory context inference.
+\textit{IEEE Transactions on Audio, Speech, and Language Processing}, 14(3), pp.
+1026-1039
+
+\bibitem{chu2009}
+Chu, S.
+and Narayanan, S.
+and Kuo, C.
+(2009).
+Environmental sound recognition with time-frequency audio features.
+\textit{IEEE Transactions on Audio, Speech, and Language Processing}, 17(6), pp.
+1142-1158
+
+\bibitem{salamon2015-2}
+Salamon, J. and Bello, J. (2015). Unsupervised feature learning for urman sound classification. In: \textit{2015 IEEE International Conference on Acoustics, Speech and Signal Processing}
+
+\bibitem{bauge2013}
+Baugé, C.
+and Lagrange, M.
+and Andén, J.
+and Mallat, S.
+(2013).
+Representing environmental sounds using the separable scattering transform.
+In: \textit{2013 IEEE International Conference on Acoustics, Speech and Signal Processing}
+
+\bibitem{salamon2015}
+Salamon, J. and Bello, J. (2015). Feature learning with deep scattering for urban sound analysis. In: \textit{23rd European Signal Processing Conference}
+
+\bibitem{chachada2013}
+Chachada, S. and Kuo, C. (2013). Environmental sound recognition: A survey. In: \textit{2013 Asia-Pacific Signal and Information Processing Association Annual Summit and Conference}
+
+\bibitem{davis1986}
+Davis, S. (1986). Octave and fractional-octave band digital filtering based on the proposed ANSI standard. In: \textit{1986 IEEE International Conference on Acoustics, Speech and Signal Processing}
 
@@
 Ellis, D. (2005). \textit{{PLP} and {RASTA} (and {MFCC}, and inversion) in {M}atlab}. Available at: \url{http://www.ee.columbia.edu/~dpwe/resources/matlab/rastamat/}
+
+\bibitem{huffman1952}
+Huffman, D. (1952). A method for the construction of minimum-redundancy codes. \textit{Proceedings of the IRE}, 40(9), pp. 1098-1101
 

### 2017-06-11 censeCoder/run_script.m

@@ -16,5 +16,5 @@ clear all, close all, clc;
 % censeCoder('do', [1 4], 'mask', {7, 3, 1, -1, -1, -1, 2, 0, -1, 1, -1, -1});
 % censeCoder('do', [1 2 4], 'mask', {0, 0, 6, 1, 2, 10, 2, 4, -1, 1, -1, -1});
 % censeCoder('do', [1 2 3 4], 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, 0, -1});
-% censeCoder('do', [4], 'mask', {0, 0, 6, 1, 2, 10, 2, 1:3, -1, 1, -1, -1});
-censeCoder('do', [1 2 4], 'mask', {7, 3, 2:6, 1, 2, 10, 2, 0, -1, 1, -1, -1});
+censeCoder('do', [4], 'mask', {0, 0, 6, 1, 2, 10, 2, 1:3, -1, 1, -1, -1});
+% censeCoder('do', [1 2 4], 'mask', {7, 3, 2:6, 1, 2, 10, 2, 0, -1, 1, -1, -1});

### 2017-06-11 censeCoder/util/third_octave_filterbank.m

@@ -33,11 +33,11 @@ for ind_wm = 1:length(wm)
         phi = .5*(p./P+1);
         % We found that inverting cos and sin seemed better
         for ind_l = 1:l
-            phi = cos(pi/2*phi);
+            phi = sin(pi/2*phi).^2;
         end
-        G(ind_wm, k_i(ind_wm)+p(1):k_i(ind_wm)+p(end)) = cos(pi/2*phi);
+        G(ind_wm, k_i(ind_wm)+p(1):k_i(ind_wm)+p(end)) = sin(pi/2*phi);
         if ind_wm>1
-            G(ind_wm-1, k_i(ind_wm)+p(1):k_i(ind_wm)+p(end)) = sin(pi/2*phi);
+            G(ind_wm-1, k_i(ind_wm)+p(1):k_i(ind_wm)+p(end)) = cos(pi/2*phi);
         end
     end
 end

### 2017-06-12 paper/article.tex
second ml pass

@@
 \newcommand{\ml}[1]{\textcolor{blue}{ Mathieu: #1}}
+\newcommand{\fg}[1]{\textcolor{red}{ Felix: #1}}
 
@@
 The present work is constrained to allow both acoustic monitoring and sound event recognition in urban soundscapes.
-Here we briefly review state-of-the-art methods in both subjects to guide our choices.
+Here we briefly review state-of-the-art methods in both subjects in order to better motivate our choices.
 
@@
 The considered sensor network primarily aims at monitoring urban soundscapes, that is, continously assessing their content and impact on the population.
-This is typically enabled by measuring energetic acoustic indicators such as the equivalent sound pressure level $L_{eq}$ in dB SPL or its A-weighted equivalent $L_{Aeq}$ in dBA.
-However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they fail to fully describe soundscapes \cite{rychtarikova2013}.
+In the literature, this is typically enabled by measuring energetic acoustic indicators such as the equivalent sound pressure level $L_{eq}$ in dB SPL or its A-weighted equivalent $L_{Aeq}$ in dBA.
+However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe soundscapes \cite{rychtarikova2013}.
 Many other variables can be derived to better account for previously implicit properties \cite{can2016} including percentile values or time evolution.
@@
 
-Another major interest of this work is sound event recognition.
-This problem has been the subject of extensive research in the past on speech \cite{anusuya2009}, music \cite{tzanetakis2002}, and lately more complex scenes in which the current work falls.
+Eventhough the above discussed indicators provide more richness than $L_{eq}$, recent studies show that abstract statistics are still not sufficient to fully model the human perception of soundscapes.
+The recognition of sources of interest is thus of importance.
+As far as the encoding scheme is concerned, it is thus important that the encoded data allows the computation of the above cited indicators but also the recognition of sources of interest with state of the art methods.
+
+The recognition of sources of interest from audio streams has been the subject of extensive research in the past on speech \cite{anusuya2009}, music \cite{tzanetakis2002}, and lately more complex scenes in which the current work falls.
 Studied classification methods are diverse, ranging from time-dependant modeling with HMMs \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}.
@@
 Following the considerations briefly exposed in the previous section, we conclude that third-octave bands are a reasonable choice.
-As mentionned, they provide advantages in both acoustic monitoring and data volume per measurement period.
+As mentionned, they provide advantages in both acoustic monitoring quality and reduced data volume per measurement period.
 The physical content is also close to that of mel spectrograms, being just another filterbank transform with logarithmic frequency scaling.\\
@@
 The continuously sampled audio is segmented into 125~ms frames to provide "fast" acoustic measurements.
-The data is zero-passed to the next power of two to allow best fft performances.
+The data is zero-padded to the next power of two to allow best fft performances.
 No overlap is used as it doubles both computational and memory costs and is not required for our application.
-A rectangular window is applied to ensure energy conservation in a given analysis frame.
+A rectangular window is thus applied to ensure energy conservation in a given analysis frame.
 The phase is unimportant to third-octave analysis, thus it is discarded.
@@
 
-Alternatively, we also implement the mel filterbank for testing purposes.
-Mel spectrograms can be used as a baseline method to evaluate the relative performance of third-octave bands in sound event recognition.
-Furthermore, this representation is not bound by constraints such as conservation of energy, specific framing parameters or fixed resolution.
-It offers a more flexible tool to study intelligibility alteration and coder performance, both of which we take interest in.
+Alternatively, we also implement the mel filterbank for comparison purposes, as the mel filterbank is the root representation of many state of the art classification algorithms.
+Mel spectrograms can thus be used as a baseline method to evaluate the relative performance of third-octave bands in sound event recognition.
+
+As the Mel representation is not bounded by constraints such as conservation of energy, specific framing parameters or fixed resolution, it also offers a more flexible tool to study intelligibility alteration and coder performance, both of which we take interest in.
+
 Mel spectrograms are computed with the \textit{rastamat} library \cite{ellis2005}.
@@
 It is defined as $H = -\sum\limits_i p_ilog_n(p_i)$, where $p_i$ is the probability of appearance of a given symbol and $n$ the numerical base in which information is represented.
+
 As such, entropy decreases when very few symbols have a very high probability of appearance and is maximum for a uniform distribution.
@@
 This yields a higher amount of symbols at $2^q-1$ but a nevertheless smaller entropy.
+
 In the example shown here, the former is $H_{log} = 6.24~sh$ and the latter $H_{\Delta} = 3.54~sh$.
@@
 
-The decoding process is quite straightforward, as both Huffman and $\Delta$ compression are lossless and directly reversible.
-
-The entire coder scheme is summarized in Figure~\ref{fig:scheme}.
+The decoding process is quite straightforward, as both Huffman and $\Delta$ compression are lossless and directly reversible. The entire coder scheme is summarized in Figure~\ref{fig:scheme}.
 
@@
 
-The coder's output bitrate as well as additional measurement error is computed for both data representations, it is expressed in dB and compared to the IEC 61672-1:2013 standard on sound level meter tolerance.
-This is to verify that the quantization step yields a maximum absolute error inferior to the precision of the recording device.
-To provide relevant statistics, these quantities are estimated for a total of 53 10-minutes texture frames.
+The coder's output bitrate as well as additional measurement error is computed for both data representations : third-octave and Mel.
+It is expressed in dB and compared to the IEC 61672-1:2013 standard on sound level meter tolerance.
+This is to verify that the quantization step yields a maximum absolute error inferior to the precision of the target recording device.
+To provide relevant statistics, these quantities are estimated for a total of 53 10-minutes texture frames \ml{describe dataset, etc}.
 
@@
 
-The UrbanSound8k dataset\cite{salamon2014} features about 9 hours of urban environmental sounds recordings separated in 8732 wave files ranging from 1 to 4 seconds each.
+In order to ensure that the proposed scheme allows the recognition of events using state of the art methods, we consider the UrbanSound8k dataset\cite{salamon2014}.
+It features about 9 hours of urban environmental sounds recordings separated in 8732 wave files ranging from 1 to 4 seconds each.
 The recordings are labeled in 10 classes (air conditioner, car horn, children playing, dog bark, drilling, enginge idling, gun shot, jackhammer, siren, street music), and distributed in 10 independant folds.
@@
 The feature vector is thus comprised of 275 values to reproduce available results and compare with our own.
-Models are trained for each setup using the 10-fold method, that is, every combination of testing one fold on models trained with the other nine.
+Models are trained for each setup using a 10-fold cross validation method \ml{provided by the authors of \cite{salamon2014} ?}, that is, every combination of testing one fold on models trained with the other nine.
 
@@
 
-Intelligibility in decoded and reconstructed audio is also one of the main concerns of this study.
-We conduct preliminary perceptive tests to ensure that a clean speech recording is made unintelligible, implying the same results in usually noisier urban soundscapes.
-We also provide the computation of two objective metrics: the Coherence Speech Intelligibility Index\cite{kates2005} (CSII) and frequency-eighted segmental SNR\cite{hu2008} (fwSNRseg) by comparing original unaltered samples and recovered audio.
-These two indicators have been shown to correlate well with perceptual tests\cite{ma2009}, although results are only available for lesser degradations and distortions.\\
+Intelligibility in decoded and reconstructed audio is also oan concerns of this study.
+It is indeed important that the produced scheme maintains a high level of recognition of acoustic events but, as the dat is transmitted over the network and potentially stored, the level of intelligibility of the decoded stream should be as low as possible.
+
+%conduct thus preliminary perceptive tests to ensure that a clean speech recording is made unintelligible, implying the same results in usually noisier urban soundscapes. We also
+
+We thus provide the computation of two objective metrics: the Coherence Speech Intelligibility Index\cite{kates2005} (CSII) and frequency-weighted segmental SNR\cite{hu2008} (fwSNRseg) by comparing original unaltered samples and recovered audio.
+These two indicators have been shown to correlate well with perceptual tests\cite{ma2009}, although results are only available for lesser degradations and distortions than the ones we consider in this study.\\
 
 These metrics require a recovery of the time-domain signal.
-We must first recover a linearly-scaled spectrogram from the band-focused representations.
-This can be achieved by multiplying by the scaled transpose of the forward transformation matrix.
+To do so, a linearly-scaled spectrogram from the band-focused representations is estimated.
+This estimation can be achieved by multiplying by the scaled transpose of the forward transformation matrix.
 A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
-Signal phase is approximated by either white noise spectrogram scaling or a Griffin\& Lim algorithm \cite{griffin1984}, and the signal is retrieved using overlap-add.
-When using overlap while computing third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.\\
+Signal phase is approximated by either white noise spectrogram scaling or a Griffin\& Lim algorithm \cite{griffin1984}, and the signal is retrieved using concatenation or overlap-add.
+When using overlap to compute third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.\\
 

### 2017-06-14 paper/article.tex
scketching intro

@@
 
-\title{An efficient audio coding scheme for large scale acoustic monitoring}
+\title{An effective sensor grid approach for large scale acoustic monitoring}
 
@@
 %\label{}
+
+As such, there is a strong need for the development of the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} for the monitoring of the acoustic environment, be it from urban, rural or wilderness areas.
+
+The sensor grid approach put the focus on a) a distributed system of data acquisition with a large set of sensors, b) the production and storage of a large dataset, and c) its availability for intensive and open data analysis computation.
+
+requirements
+
+scalability:
+power managment:
+security and privacy:
+data richness:
+
+low consumption computation (processing and transmission) of the sensor node
+
+low bitrate of the transmitted data for efficient transmission and storage
+
+proposed approach
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figures/censeCoder}
+\vspace{-0.15in}
+\caption{}
+\label{fig:codingScheme}
+\end{figure}
 

### 2017-06-16 paper/article.tex
Paper update + mel bands fix

--- 2017-06-12 paper/article.tex
@@
 \usepackage{amssymb}
+\usepackage{amsmath}
 \usepackage{epstopdf}
@@
 \usepackage{color}
+\usepackage{multirow}
 
@@
 This is to verify that the quantization step yields a maximum absolute error inferior to the precision of the target recording device.
-To provide relevant statistics, these quantities are estimated for a total of 53 10-minutes texture frames \ml{describe dataset, etc}.
+To provide relevant statistics, these quantities are estimated for a total of 53 10-minutes texture frames.
+They are obtained from the UrbanSound8k dataset presented in the next section.
 
@@
 It is used in all the following experiments with the exception of intelligibility computation for which a small dataset of high-quality voice recordings is preferred.
-Audio files are resampled 44.1 samples per second, normalized and reduced to a single channel.\\
+Audio files are resampled 44.1~kHz, normalized and reduced to a single channel.\\
 
-We first evaluate the global loss of information by implementing the four classification models proposed in \cite{salamon2014}: a support vector machine with a radial basis function kernel, a random forest classifier with 500 trees, a decision tree and a k-nearest neighbors classifier with $k = 5$.
+We evaluate the global loss of information by implementing the four classification models proposed in \cite{salamon2014}: a support vector machine with a radial basis function kernel, a random forest classifier with 500 trees, a decision tree and a k-nearest neighbors classifier with $k = 5$.
 Values for the SVM parameter $C$ and RBF kernel variance $\sigma^2$ are found with a grid search.
@@
 The feature vector is thus comprised of 275 values to reproduce available results and compare with our own.
-Models are trained for each setup using a 10-fold cross validation method \ml{provided by the authors of \cite{salamon2014} ?}, that is, every combination of testing one fold on models trained with the other nine.
+Models are trained for each setup using a 10-fold cross validation method provided by the authors of \cite{salamon2014}, that is, every combination of testing one fold on models trained with the other nine.
 
@@
 A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
-Signal phase is approximated by either white noise spectrogram scaling or a Griffin\& Lim algorithm \cite{griffin1984}, and the signal is retrieved using concatenation or overlap-add.
+Signal phase is approximated by either white noise spectrogram scaling or a Griffin \& Lim algorithm \cite{griffin1984}, and the signal is retrieved using concatenation or overlap-add.
 When using overlap to compute third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.\\
@@
 
+\subsection{Coder efficiency}
+The main indicator of performance is the bitrate obtained at the output of the coder.
+The three varying factors studied are the data word size $q$, the number of bands and the effect of reducing time-resolution by averaging analysis frames.
+Figure~\ref{fig:bitrate_q} shows estimations of the output bitrate for different values of $q$.
+To match third-octave bands computation principle where a 125~ms analysis is mandatory, we averaged mel frames over time.
+Because we use the most common parameters, namely 23.2~ms window with 50\% overlap, the closest achievable rate considering simple averaging is 7.74 frames per second.
+Third-octave representation on 31 bands yielded an overall higher size than their mel equivalent, here estimated for 30 bands.
+It however compares with the 40-mel bands representation which is the most used in litterature.
+This occurence is likely due to the distribution observed by the data prior to Huffman encoding.
+
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\columnwidth]{bitrate_qall.eps}
+	\caption{Coder output bitrate as a function of quantization for third-octave and mel bands with 8 frames per second.}
+	\label{fig:bitrate_q}
+\end{figure}
+
+A second set of parameters influences directly the time-frequency resolution of the analysis.
+By choosing a frame rate and number of bands, one can effectively control the size of periodically transmitted data.
+We evaluate the bitrate for 10 to 40 mel bands and a frame rate from 2 to 10 per second, with fixed $q = 8$.
+Results are exposed in Figure~\ref{fig:bitrate_mel_avg}.
+As intuitively expected, the bitrate for a given word size $q$ can be modeled as a linear function of the representation dimensions for one second of analysis.
+Small variations are induced by data distributions on a per-frame level and their effect on the Huffman algorithm.
+
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\columnwidth]{bitrate_mel_avg.eps}
+	\caption{Impact of representation resolution on the encoded data bitrate.}
+	\label{fig:bitrate_mel_avg}
+\end{figure}
+
+While this experiment may seem trivial, it aims at assessing potential tradeoffs between bitrate and information. As such, it will be further discussed in the \textit{Event recognition} subsection.\\
+
+We also examine the additionnal error caused by encoding steps after obtaining the desired data representation.
+The only lossy operation applied is quantization, which is defined by an output word size $q$ in bits.
+However, it corresponds to the word size \textit{after} $\Delta$-compression, meaning that the data is in fact quantized on $2^{q-1}$ values.
+Since these measurements are already expressed in dB, the error $\varepsilon$ is:
+\begin{equation*}
+	\varepsilon = |x_q-x|
+\end{equation*}
+where $x_q$ and $x$ are the quantized and clean representations repectively. $x_q$ is given by:
+\begin{equation*}
+x_q(n) = \frac{\Delta_x}{2^{q-1}-1}\textrm{round}\left(\frac{(2^{q-1}-1)x(n)}{\Delta_x}\right), x\in \left[0, \Delta_x\right]
+\end{equation*}
+Figure~\ref{fig:error_q} shows an estimation of $\varepsilon$ as a function of $q$ for third-octave and mel bands.
+In both cases, the mean and standard deviation seem to decrease by a factor of 2 as $q$ increases.
+To explain this phenomenon, let us model $x$ as a uniform distribution such as $x\sim \textit{U}\{0, \Delta_x\}$.
+While this is not exact it matches our objective when using a logarithm to flatten given PDFs.
+The error $\varepsilon$ will follow a uniform distribution $U\sim \{0, \frac{\Delta_x}{2\times (2^{q-1}-1)}\}$.
+Therefore, the mean and standard deviation are:
+\[
+\begin{cases}
+	\mu_\epsilon = \frac{\Delta_x}{4\times (2^{q-1}-1)}\\
+	\sigma_\epsilon = \frac{1}{12}\frac{\Delta_x}{2\times (2^{q-1}-1)}
+\end{cases}
+\]
+justifying the decaying ratio as $q$ increases. In practice, we assume that $\varepsilon = f(\Delta_x, \frac{1}{2^{q-1}-1})$ with the heterogeneity of the data's PDF inducing small variations.\\
+
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\columnwidth]{error_qall.eps}
+	\caption{Measurement error induced by encoding for different quantization resolutions.}
+	\label{fig:error_q}
+\end{figure}
+
+Because in our implementation $\Delta_x$ is sampled for each analysis frame, the error has the same statistics across all bands.
+We compare the observed values against those specified in the IEC 61672-1:2013 for $f = 1~kHz$ as it is where the most accurate measurements are expected.
+For class 1 and 2 sound level meters, the tolerance is set at about $\pm 1~dB$ and $\pm 1.5~dB$ respectively.
+Results for 6, 7 or 8-bit words lie within the shorter range and are therefore compliant with the standard's measurement tolerance.
+
+\subsection{Event recognition}
+
+The same set of parameters as in bitrate evaluation is used to study sound event recognition.
+We aim at finding possibilities to further reduce the encoded data size without affecting performance in a significant way.
+Results of the four presented classification methods are provided for completeness.\\
+
+First, we observe the impact of quantization on classification accuracy.
+The models are trained on the most complete implemented representation, ie.
+40 mel bands and no time averaging (85 frames per second).
+Figure~\ref{fig:class_mel_q} shows that this process yields equivalent accuracy for higher resolutions.\\
+
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\columnwidth]{class_mel_q.eps}
+	\caption{Classification accuracy as a function of word size before encoding. The baseline on the right is computed without quantizing the representation.}
+	\label{fig:class_mel_q}
+\end{figure}
+
+The effect of changing representation time-frequency resolution is presented in Table~\ref{T1}.
+Similarly to baseline results, the random forest and SVM classifiers are the most performant at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively.
+However, we find that given our setup, diminishing the number of analysis bands to an extent generally does not cause the classification task to fail.
+The decision tree is a flagrant example of this, with best performances for 10 mel bands only and a 4\% lower accuracy for 40.
+Even if the difference is insignificant, all other models perform best with 30 or 40 mel bands as a representation base.
+Time decimation is also possible, as in most cases the original data can be averaged consistently and yield a good classification accuracy.
+The loss of information can be considered negligible for FPS values as low as 8 or 10 depending on the method.
+This means that we can effectively divide the data size by a factor of at most 10 without affecting sound event recognition.
+It also provides us with a preliminary confirmation of the possibility for "fast"-sampled third-octave bands cepstra to match  MFCC performances.\fg{Highlight best/ok values once per class.
+method, not per fps}\\
+
+\begin{table*}[h]
+\centering
+\caption{Classification accuracy for varying representation resolutions}
+\label{T1}
+\begin{tabular}{ll|c|c|c|c|c|c|c|} 
+\cline{3-9}
+\multicolumn{2}{c}{\multirow{2}{*}{SVM}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
+ & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9} 
+\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
+ & \multicolumn{1}{|c|}{10} & 0.55$\pm$0.03 & 0.60$\pm$0.03 & \textbf{0.61$\pm$0.04} & \textbf{0.62$\pm$0.03} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.06} & \textbf{0.65$\pm$0.06} \\ \cline{2-9}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{20} & \textbf{0.58$\pm$0.04} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.65$\pm$0.05} & \textbf{0.67$\pm$0.06} \\ \cline{2-9}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{30} & \textbf{\textcolor{red}{0.60$\pm$0.03}} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.65$\pm$0.04}} & \textbf{\textcolor{red}{0.65$\pm$0.03}} & \textbf{\textcolor{red}{0.67$\pm$0.04}} & \textbf{\textcolor{red}{0.68$\pm$0.04}} \\ \cline{2-9}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{40} & \textbf{0.60$\pm$0.03} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.66$\pm$0.04} & \textbf{0.68$\pm$0.05} \\ \cline{1-9}
+\end{tabular}
+
+\begin{tabular}{ll|c|c|c|c|c|c|c|} 
+\cline{3-9}
+\multicolumn{2}{c}{\multirow{2}{*}{RF-500}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
+ & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9} 
+\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
+ & \multicolumn{1}{|c|}{10} & \textbf{0.60$\pm$0.03} & \textbf{0.62$\pm$0.03} & \textbf{0.62$\pm$0.03} & \textbf{0.63$\pm$0.03} & \textbf{0.63$\pm$0.03} & \textbf{0.65$\pm$0.04} & \textbf{0.67$\pm$0.05} \\ \cline{2-9}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{20} & \textbf{0.61$\pm$0.04} & \textbf{0.63$\pm$0.03} & \textbf{0.64$\pm$0.03} & \textbf{\textcolor{red}{0.64$\pm$0.03}} & \textbf{0.64$\pm$0.04} & \textbf{0.66$\pm$0.06} & \textbf{0.69$\pm$0.06} \\ \cline{2-9}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{30} & \textbf{\textcolor{red}{0.62$\pm$0.03}} & \textbf{\textcolor{red}{0.63$\pm$0.03}} & \textbf{\textcolor{red}{0.64$\pm$0.03}} & \textbf{0.64$\pm$0.03} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.67$\pm$0.05}} & \textbf{\textcolor{red}{0.69$\pm$0.06}} \\ \cline{2-9}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{40} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.67$\pm$0.06} & \textbf{0.68$\pm$0.06} \\ \cline{1-9}
+\end{tabular}
+
+\begin{tabular}{ll|c|c|c|c|c|c|c|} 
+\cline{3-9}
+\multicolumn{2}{c}{\multirow{2}{*}{DT}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
+ & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9} 
+\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
+ & \multicolumn{1}{|c|}{10} & \textbf{0.42$\pm$0.03} & \textbf{\textcolor{red}{0.46$\pm$0.04}} & \textbf{\textcolor{red}{0.46$\pm$0.02}} & \textbf{0.44$\pm$0.03} & \textbf{\textcolor{red}{0.45$\pm$0.03}} & \textbf{\textcolor{red}{0.46$\pm$0.05}} & \textbf{\textcolor{red}{0.49$\pm$0.03}} \\ \cline{2-9}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{20} & \textbf{\textcolor{red}{0.43$\pm$0.05}} & \textbf{0.43$\pm$0.03} & 0.43$\pm$0.02 & \textbf{0.44$\pm$0.03} & \textbf{0.45$\pm$0.03} & \textbf{0.45$\pm$0.05} & \textbf{0.47$\pm$0.05} \\ \cline{2-9}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{30} & \textbf{0.42$\pm$0.04} & \textbf{0.43$\pm$0.02} & \textbf{0.44$\pm$0.03} & \textbf{\textcolor{red}{0.45$\pm$0.05}} & \textbf{0.43$\pm$0.03} & \textbf{0.43$\pm$0.04} & \textbf{0.45$\pm$0.05} \\ \cline{2-9}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{40} & \textbf{0.42$\pm$0.06} & 0.43$\pm$0.03 & 0.43$\pm$0.03 & \textbf{0.42$\pm$0.03} & \textbf{0.44$\pm$0.03} & \textbf{0.46$\pm$0.03} & 0.45$\pm$0.04 \\ \cline{1-9} 
+\end{tabular}
+
+\begin{tabular}{ll|c|c|c|c|c|c|c|} 
+\cline{3-9}
+\multicolumn{2}{c}{\multirow{2}{*}{KNN-5}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
+ & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9} 
+\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
+ & \multicolumn{1}{|c|}{10} & \textbf{0.43$\pm$0.02} & \textbf{0.51$\pm$0.04} & \textbf{0.53$\pm$0.04} & \textbf{0.53$\pm$0.05} & \textbf{0.53$\pm$0.04} & \textbf{0.54$\pm$0.04} & \textbf{0.56$\pm$0.03} \\ \cline{2-9}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{20} & \textbf{0.44$\pm$0.03} & \textbf{0.52$\pm$0.04} & \textbf{0.53$\pm$0.03} & \textbf{0.54$\pm$0.04} & \textbf{0.54$\pm$0.04} & \textbf{0.55$\pm$0.04} & \textbf{\textcolor{red}{0.58$\pm$0.04}} \\ \cline{2-9}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{30} & \textbf{0.45$\pm$0.04} & \textbf{\textcolor{red}{0.54$\pm$0.05}} & \textbf{\textcolor{red}{0.55$\pm$0.05}} & \textbf{0.55$\pm$0.04} & \textbf{\textcolor{red}{0.55$\pm$0.04}} & \textbf{0.56$\pm$0.04} & \textbf{0.56$\pm$0.04} \\ \cline{2-9}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{40} & \textbf{\textcolor{red}{0.46$\pm$0.03}} & \textbf{0.53$\pm$0.05} & \textbf{0.55$\pm$0.05} & \textbf{\textcolor{red}{0.55$\pm$0.04}} & \textbf{0.55$\pm$0.05} & \textbf{\textcolor{red}{0.57$\pm$0.04}} & \textbf{0.57$\pm$0.03} \\ \cline{1-9}
+\end{tabular} 
+\end{table*}
+
+\subsection{Third-octave bands as base descriptors}
+
+We now compare the efficiency of third-octave bands at characterizing urban soundscapes to that of mel spectrograms.
+Following the previous discussions, the classification task is run on corresponding cepstra with a fixed 8 frames per second and 31 bands.
+Figure~\ref{fig:tob_mel_q} displays \fg{fig to be added} similar results to 40 bands, 8 fps mel spectrograms.\\
+
+To further analyze both representations advantages, the confusion matrix is a reliable tool.
+It aims at providing information regarding class-by-class accuracy and misclassification rates.
+We thus compute these metrics for the SVM classifier, with predictions cumulated over the ten folds in test configuration.
+Results are visible in Figure~\ref{fig:tob_conf} and Figure~\ref{fig:mel_conf}
+
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\columnwidth]{tob_conf.eps}
+	\caption{Confusion matrix of the SVM classification on third-octave bands with $q = 8$.}
+	\label{fig:tob_conf}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\columnwidth]{mel_conf.eps}
+	\caption{Confusion matrix for the same setup with 40 mel bands.}
+	\label{fig:mel_conf}
+\end{figure}
+\fg{Ici je pensais pouvoir trouver et expliquer les differences dues au contenu des descripteurs, mais apparemment les résultats sont proches. TODO: creuser un peu plus, et conclure}
+
+\subsection{Inintelligibility}
+
+Finally, objective intelligibility metrics are estimated for the studied parameters and compared to perceptual tests.
+Figure~\ref{fig:int_mel_avg} shows both the CSII and fwSNRseg indicators for varying representation dimensions.
+Figure~\ref{fig:percint_mel_avg} presents the results of the preliminar perceptual test for the same setup.
+We acknowledge that it is surely biased by a reduced number of participants and lack of tested audio material.
+However, it is sufficient to judge the relevance of objective indicators in our conditions.
+We may at first observe a resemblance between the three measurements.
+
+The CSII accounts for the whole spectrogram distance between clean and distorted audio at each point in time and frequency.
+This includes the phase, which we discard early in the representation step.
+The error induced by forward and inverse mel bands transformation as well as operations reducing data dimensionality further contribute to very high distances.
+In fact, the signal is too distorted for the proposed SNR normalization to ensure CSII values in the 0-1 range.
+The indicator differs from perceptual evaluations for middle-valued frame rates, with for example the 9.5 fps curve being lower than expected.
+Values are also very close for multiple parameter combinations where a threshold between intelligibility and inintelligibility could be found.
+This is therefore not an adequate indicator for this application.\\
+
+Alternatively, the frequency-weighted segmental SNR considers only spectrogram magnitudes.
+As a result, distance is generally lower and a more accurate representation of the reality.
+Nevertheless, the fwSNRseg still uses point-wise comparison.
+A shape seems to appear where the influences of frame rate and mel bands on output are decorrelated, ie.
+almost the same curve is offset as a function of frame rate.
+While the values are still concentrated around the critical threshold location at about -5~dB, this metric is likely a better indicator due to its approach of the clean-reconstructed signal distance.
+
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\columnwidth]{int_mel_avg.eps}
+	\caption{The two objective indicators computed for intelligibility assessment.
+Negative CSII values indicate a signal-to-noise ratio too low for the recommended normalization, thus severe disparities between the original and reconstructed signal.}
+	\label{fig:int_mel_avg}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\columnwidth]{percint_mel_avg.eps}
+	\caption{Results of a very small perceptual intelligibility test.}
+	\label{fig:percint_mel_avg}
+\end{figure}
+
+\fg{figures a refaire}
 \section{Conclusion}

### 2017-06-16 censeCoder/ceco1representation.m

@@ -99,15 +99,28 @@ for ind_fold = 1:length(file_path)
             end
             %% FFT bins to MEL bins
             Xm{ind_fold}{ind_file} = audspec(X, sr, setting.mel, 'mel', 0, sr/2, 1, 1);
-            Xm{ind_fold}{ind_file} = log(Xm{ind_fold}{ind_file});
+            Xm{ind_fold}{ind_file} = 10*log10(Xm{ind_fold}{ind_file});
             %% Quantization
-            if setting.quant ~= 0
+%             if setting.quant ~= 0
+%                 Xm_clean = Xm{ind_fold}{ind_file};
+%                 q_norm{ind_fold}{ind_file} = max(max(Xm{ind_fold}{ind_file})); % Needed for reconstruction
+%                 Xm{ind_fold}{ind_file} = int16((2^(setting.quant-1)-1)*Xm{ind_fold}{ind_file}./q_norm{ind_fold}{ind_file}); % Datatype size minus 1 for the delta-comp
+%                 Xm{ind_fold}{ind_file}(Xm{ind_fold}{ind_file}<0) = 0; % Low values elimination
+%                 % q_loss(end+1) = 10*log10(mean(mean(abs(exp(double(Xm{ind_fold}{ind_file}).*q_norm{ind_fold}{ind_file}./(2^(setting.quant-1)-1))-exp(Xm_clean)))));
+%                 q_loss(end+1) = mean(mean(abs(10*log10(exp(double(Xm{ind_fold}{ind_file}).*q_norm{ind_fold}{ind_file}./(2^(setting.quant-1)-1)))-10*log10(exp(Xm_clean)))));
+%                 if isnan(q_loss(end)) || isinf(q_loss(end))
+%                     disp(['NaN or Inf found at file ' num2str(ind_file) ' in fold ' num2str(ind_fold) '.']);
+%                     q_loss = q_loss(1:end-1);
+%                 end
+%             end
+            if setting.quant ~= 0                
+                q_norm{ind_fold}{ind_file} = zeros(2, 1);
                 Xm_clean = Xm{ind_fold}{ind_file};
-                q_norm{ind_fold}{ind_file} = max(max(Xm{ind_fold}{ind_file})); % Needed for reconstruction
[…]

### 2017-06-16 censeCoder/ceco2coder.m

@@ -30,8 +30,10 @@ sr = 44100;
 if strcmp(setting.desc, 'mel')
     l_frame = 1024;
     l_hop = 0.5*l_frame;
+    n_fps = 1+(sr-l_frame)/l_hop; % Number of frames per second with base settings
     if setting.fps % 0 means none
-        n_fps = setting.fps; % Number of frames per second with custom settings
+        n_avg = round(n_fps/setting.fps); % Number of consecutive frames to average into one
+        n_fps = n_fps/n_avg; % Number of frames per second with custom settings
     else
         n_fps = 1+(sr-l_frame)/l_hop; % Number of frames per second with base settings
     end
@@ -86,7 +88,7 @@ for ind_frame = 1:n_frames
     X_huff{ind_frame} = bin2dec(reshape(num2str([X_huff{ind_frame}(1:end-mod(end, 8)); X_huff{ind_frame}(end-mod(end, 8)+1:end); zeros(8-mod(length(X_huff{ind_frame}), 8), 1)]), 8, [])');
 end
 % bitrate = sum(code_len)/length(X_huff)/setting.textframe/60;
-bitrate = code_len/setting.textframe/60;
+bitrate = code_len*n_fps/l_frame;
 if strcmp(setting.dataset, 'urbansound8k'); bitrate = bitrate(1:end-1); end % Last frame is incomplete and adds a bias
 
 %% Outputs

### 2017-06-16 censeCoder/ceco3decoder.m

@@ -85,9 +85,9 @@ for ind_fold = 1:length(X_desc)
         if strcmp(setting.desc, 'mel')
             %% Normalisation
             if setting.quant ~= 0
-                X_desc{ind_fold}{ind_file} = data.q_norm{ind_fold}{ind_file}*double(X_desc{ind_fold}{ind_file})/(2^(setting.quant-1)-1);
+                X_desc{ind_fold}{ind_file} = (double(X_desc{ind_fold}{ind_file}).*data.q_norm{ind_fold}{ind_file}(2)./(2^(setting.quant-1)-1))+data.q_norm{ind_fold}{ind_file}(1);
             end
-            X_desc{ind_fold}{ind_file} = exp(X_desc{ind_fold}{ind_file});
+            X_desc{ind_fold}{ind_file} = 10.^(X_desc{ind_fold}{ind_file}/10);
 
             %% Reconstruction of the linearly-scaled spectrogram
             X = invaudspec(X_desc{ind_fold}{ind_file}, sr, l_frame, 'mel', 0, sr/2, 1, 1);

### 2017-06-16 censeCoder/ceco4metrics.m

@@ -97,12 +97,12 @@ switch setting.dataset
             for ind_file = 1:length(load_data.X_desc{ind_fold})
                 if strcmp(setting.desc, 'mel')
                     if setting.quant ~= 0
-                        X_mel{ind_fold}{ind_file} = double(load_data.X_desc{ind_fold}{ind_file}).*load_data.q_norm{ind_fold}{ind_file}./(2^(setting.quant-1)-1); % Datatype size minus 1 for the delta-comp
+                        X_mel{ind_fold}{ind_file} = (double(load_data.X_desc{ind_fold}{ind_file}).*load_data.q_norm{ind_fold}{ind_file}(2)./(2^(setting.quant-1)-1))+load_data.q_norm{ind_fold}{ind_file}(1);
                     else
                         X_mel{ind_fold}{ind_file} = load_data.X_desc{ind_fold}{ind_file};
                     end
                     X_mel{ind_fold}{ind_file}(X_mel{ind_fold}{ind_file} == 0) = eps;
-                    X_cep = spec2cep(exp(X_mel{ind_fold}{ind_file}), 25, 2);
+                    X_cep = spec2cep(10.^(X_mel{ind_fold}{ind_file}/10), 25, 2);
                     if size(X_cep, 2)>1
                         x_desc{ind_fold}(:, ind_file) = [min(X_cep')'; max(X_cep')'; median(X_cep, 2); mean(X_cep, 2); var(X_cep, 0, 2); skewness(X_cep, 1, 2); kurtosis(X_cep, 1, 2); mean(diff(X_cep, 1, 2), 2); var(diff(X_cep, 1, 2), 0, 2); mean(diff(X_cep, 2, 2), 2); var(diff(X_cep, 2, 2), 0, 2)];
                     else

### 2017-06-16 censeCoder/cecoReport.m

@@ -10,21 +10,89 @@ if nargin==0, censeCoder('report', 'r'); return; end%censeCoder('report', 'rhv')
 
 % {fps, mel, quant, dictgen, htreealg, textframe, dataset, classmethod, phaserec, desc, intelind, tobhop}
 
-%% KNN
-% config = expExpose(config, 'p', 'mask', {0, 0, 6, 1, 2, 10, 2, 4, 2}, 'obs', 'cv_acc', 'save', 'knn_fps_mel_8', 'step', 4, 'expand', 1, 'color', {'b', 'g', 'r', 'black'}); % KNN accuracy as f(mel,fps)
-% config = expExpose(config, 't', 'mask', {7, 4, 1, 1, 2, 10, 2, 4, 2}, 'obs', 'cv_acc', 'save', 'knn_base', 'step', 4); % Baseline KNN accuracy
+%%% censeCoder('do', [step], 'mask', {fps, mel, quant, dictgen, htreealg, textframe, dataset, classmethod, phaserec, desc, intelind, tobhop});
+%%% Error - All quant
+% censeCoder('do', [1], 'mask', {-1, -1, 0, -1, -1, -1, 0, -1, -1, 2, -1, 2}); % Third-octave bands
+%%% Bitrate - All quant
+% censeCoder('do', [2], 'mask', {-1, -1, 0, 1, 2, 10, 2, -1, -1, 2, -1, 2});
+%%% Class - All quant
+% censeCoder('do', [4], 'mask', {-1, -1, 0, -1, -1, -1, 2, 1, -1, 2, -1, 2});
+% censeCoder('do', [4], 'mask', {-1, -1, 0, -1, -1, -1, 2, 2:4, -1, 2, -1, 2});
+%%% Intel indicators - All quant
+% censeCoder('do', [2 3 4], 'mask', {-1, -1, 2:6, 1, 2, 10, 1, -1, 1, 2, 0, 2});
 
-%% CSII
-% config = expExpose(config, 'p', 'mask', {0, 0, 6, 1, 2, 10, 1, 4, 2}, 'obs', 'csii', 'save', 'csii_fps_mel_8', 'step', 4, 'expand', 2, 'color', 'k'); % CSII indicator as f(mel,fps)
[…]

### 2017-06-16 censeCoder/run_script.m

@@ -1,20 +1,29 @@
 clear all, close all, clc;
 
-%% 8 bit quant, varying fps/mel
-% censeCoder('do', [1 2 4], 'mask', {0, 0, 6, 1, 2, 10, 2, 4, 2, 1, 2});
-% censeCoder('do', [1 2 3 4], 'mask', {0, 0, 6, 1, 2, 10, 1, 4, 1, 1, 2});
-%censeCoder('do', [3], 'mask', {0, 0, 6, 1, 2, 10, 1, 4, 1, 2, 1});
-% %% Baseline
-% censeCoder('do', [1 4], 'mask', {7, 3, 1, 1, 2, 10, 2, 1, 2, 1, 2});
-
 %% Global run
 %%% censeCoder('do', [step], 'mask', {fps, mel, quant, dictgen, htreealg, textframe, dataset, classmethod, phaserec, desc, intelind, tobhop});
+%%% Error - All quant
 % censeCoder('do', [1], 'mask', {-1, -1, 0, -1, -1, -1, 0, -1, -1, 2, -1, 2}); % Third-octave bands
+%%% Bitrate - All quant
 % censeCoder('do', [2], 'mask', {-1, -1, 0, 1, 2, 10, 2, -1, -1, 2, -1, 2});
+%%% Class - All quant
 % censeCoder('do', [4], 'mask', {-1, -1, 0, -1, -1, -1, 2, 1, -1, 2, -1, 2});
+% censeCoder('do', [4], 'mask', {-1, -1, 0, -1, -1, -1, 2, 2:4, -1, 2, -1, 2});
+%%% Intel indicators - All quant
+% censeCoder('do', [2 3 4], 'mask', {-1, -1, 2:6, 1, 2, 10, 1, -1, 1, 2, 0, 2});
 
+%%% Error/Class - No averaging, 30 bands, no quant
 % censeCoder('do', [1 4], 'mask', {7, 3, 1, -1, -1, -1, 2, 0, -1, 1, -1, -1});
-% censeCoder('do', [1 2 4], 'mask', {0, 0, 6, 1, 2, 10, 2, 4, -1, 1, -1, -1});
+%%% Error/Bitrate/Class - 8 fps, 40 bands, all quant
+% censeCoder('do', [1 2], 'mask', {4, 4, 2:6, 1, 2, 10, 2, -1, -1, 1, -1, -1});
[…]

### 2017-06-16 paper/article.tex
some comments to results

@@
 \subsection{Coder efficiency}
+
 The main indicator of performance is the bitrate obtained at the output of the coder.
@@
 This occurence is likely due to the distribution observed by the data prior to Huffman encoding.
+
+\ml{pourquoi parler d'overlap ici, alors que le codeur ne doit en utiliser ?}
 
@@
 Results are exposed in Figure~\ref{fig:bitrate_mel_avg}.
-As intuitively expected, the bitrate for a given word size $q$ can be modeled as a linear function of the representation dimensions for one second of analysis.
+As expected, the bitrate for a given word size $q$ can be modeled as a linear function of the representation dimensions for one second of analysis.
 Small variations are induced by data distributions on a per-frame level and their effect on the Huffman algorithm.
@@
 
-While this experiment may seem trivial, it aims at assessing potential tradeoffs between bitrate and information. As such, it will be further discussed in the \textit{Event recognition} subsection.\\
+This experiment aims at assessing potential tradeoffs between bitrate and information. As such, it will be further discussed in the \textit{Event recognition} subsection.\\
 
-We also examine the additionnal error caused by encoding steps after obtaining the desired data representation.
+We also examine the additionnal error caused by the encoding steps after obtaining the desired data representation.
 The only lossy operation applied is quantization, which is defined by an output word size $q$ in bits.
@@
 
-Because in our implementation $\Delta_x$ is sampled for each analysis frame, the error has the same statistics across all bands.
-We compare the observed values against those specified in the IEC 61672-1:2013 for $f = 1~kHz$ as it is where the most accurate measurements are expected.
+As $\Delta_x$ is sampled for each analysis frame in our implementation, the error has the same statistics across all bands.
+We compare the observed values against those specified in the IEC 61672-1:2013 \ml{norm ?
+please cite} for $f = 1~kHz$ as it is where the most accurate measurements are expected.
 For class 1 and 2 sound level meters, the tolerance is set at about $\pm 1~dB$ and $\pm 1.5~dB$ respectively.
-Results for 6, 7 or 8-bit words lie within the shorter range and are therefore compliant with the standard's measurement tolerance.
+Results for 6, 7 or 8-bit words lie within the shorter range and are therefore compliant with those standard's measurement tolerance.
 
@@
 
-The same set of parameters as in bitrate evaluation is used to study sound event recognition.
-We aim at finding possibilities to further reduce the encoded data size without affecting performance in a significant way.
-Results of the four presented classification methods are provided for completeness.\\
+The same set of parameters as in bitrate evaluation is used to study the impact of their tuing to the sound event recognition performance.
+We thus aim at finding ways to further reduce the encoded data size without strongly affecting recognition performance.
+Results of the four presented classification methods are provided for the sake of completeness.\\
 
@@
 The effect of changing representation time-frequency resolution is presented in Table~\ref{T1}.
-Similarly to baseline results, the random forest and SVM classifiers are the most performant at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively.
-However, we find that given our setup, diminishing the number of analysis bands to an extent generally does not cause the classification task to fail.
-The decision tree is a flagrant example of this, with best performances for 10 mel bands only and a 4\% lower accuracy for 40.
-Even if the difference is insignificant, all other models perform best with 30 or 40 mel bands as a representation base.
-Time decimation is also possible, as in most cases the original data can be averaged consistently and yield a good classification accuracy.
+Similarly to baseline results, the random forest and SVM classifiers are the higher performing systems at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively.
+However, we find that given our setup, diminishing the number of analysis bands to some extent most often does notinduces a strong drop of performance.
+The performance of the decision tree classifier is a good example of this behavior, with best performances for 10 mel bands only and a 4\% lower accuracy for 40.
+Even if the difference is small, all other models perform best with 30 or 40 mel bands as a representation.
+Time decimation is also possible, as in most cases the original data can be averaged \ml{consistently ?} and yield a good classification accuracy.
 The loss of information can be considered negligible for FPS values as low as 8 or 10 depending on the method.
-This means that we can effectively divide the data size by a factor of at most 10 without affecting sound event recognition.
+This means that we can effectively divide the data size by a factor of at most 10 without affecting sound event recognition performance.
 It also provides us with a preliminary confirmation of the possibility for "fast"-sampled third-octave bands cepstra to match  MFCC performances.\fg{Highlight best/ok values once per class.
@@
 
-Finally, objective intelligibility metrics are estimated for the studied parameters and compared to perceptual tests.
+Finally, objective intelligibility metrics are estimated for the studied parameters and compared to an informal perceptual evaluation \footnote{Decoded speech utterances for various conditions can be listened to at \url{http://}}.
 Figure~\ref{fig:int_mel_avg} shows both the CSII and fwSNRseg indicators for varying representation dimensions.
-Figure~\ref{fig:percint_mel_avg} presents the results of the preliminar perceptual test for the same setup.
+Figure~\ref{fig:percint_mel_avg} presents the results of the preliminar perceptual test \ml{comment tu as fait le test ?} for the same setup.
 We acknowledge that it is surely biased by a reduced number of participants and lack of tested audio material.
-However, it is sufficient to judge the relevance of objective indicators in our conditions.
-We may at first observe a resemblance between the three measurements.
+However, it is sufficient to judge the relevance of objective indicators in our conditions as we can observe a correlation between the three metrics.
 
@@
 Values are also very close for multiple parameter combinations where a threshold between intelligibility and inintelligibility could be found.
-This is therefore not an adequate indicator for this application.\\
+This is therefore not an adequate indicator for our purpose.\\
 
 Alternatively, the frequency-weighted segmental SNR considers only spectrogram magnitudes.
-As a result, distance is generally lower and a more accurate representation of the reality.
+As a result, distance is generally lower and a more representative of the induced perceptual distortion.
 Nevertheless, the fwSNRseg still uses point-wise comparison.
@@
 While the values are still concentrated around the critical threshold location at about -5~dB, this metric is likely a better indicator due to its approach of the clean-reconstructed signal distance.
+\ml{incrompehnsible}
 

### 2017-06-16 paper/article.tex
new intro

--- 2017-06-16 paper/article.tex
@@
 \usepackage{amssymb}
-\usepackage{amsmath}
 \usepackage{epstopdf}
@@
 \usepackage{color}
-\usepackage{multirow}
 
@@
 %% Text of abstract
-The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc (wp.nyu.edu/sonyc) and cense (cense.ifsttar.fr) projects.
-
-Together with the estimation of acoustic indicators (LAeq, ...), one important aspect of those networks is their ability to detect the presence of sound sources of interest ( bird calls, sirens, explosion, ...) in order to better assess soundscapes.
-This detection step can be operated online (on the sensors) or offline (on the data servers).
-
-The former is efficient in terms of data storage as only the detection events are transmitted.
-Though, it requires the availability of computing resources on the sensors in order to perform the detection step, and the detection is done once and cannot be recomputed.
-
-The latter scheme has several benefits.
-First, the sensor is much simpler and can thus be autonomous in terms of energy, easing the deployment of the network.
-Second, it allows researchers to gather large amount of data that can be post processed and studied further offline.
-Data can be re analysed following newer classification schemes or using new indicators.
-
-But, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way.
-Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.
-
-The coding scheme described in this paper has the following features.
-It is of low bitrate but still allows the computation of most of the standard acoustics indicators with high precision.
-As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data.
-Finally, according to preliminary perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
-
-In order to promote reproducible research, the coder as well as the experiments needed to generate the figures will be made available to the community.
 
@@
 
-As such, there is a strong need for the development of the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} for the monitoring of the acoustic environment, be it from urban, rural or wilderness areas.
+The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc (wp.nyu.edu/sonyc) and cense (cense.ifsttar.fr) projects.
 
+To do so, considering the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} has several advantages.
 The sensor grid approach put the focus on a) a distributed system of data acquisition with a large set of sensors, b) the production and storage of a large dataset, and c) its availability for intensive and open data analysis computation.
 
-requirements
+In our application setting, the requirements are the following.
+First,  the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, \textit{i.e.} the approach shall be scalable.
+Second, the nodes shall be energy efficient in order ot ease the deployment of the sensors grid to the desired topology, ideally autonomous.
+Third, the data transfer used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to ensure the privacy of the citizen.
+Lastly, the data stored shall be as rich as possible while retaining a low bitrate for efficient transmission and storage
 
-scalability:
-power managment:
-security and privacy:
-data richness:
+The data of interest is first acoustic indicators (LAeq, ...) and second the presence of sound sources of interest (bird calls, sirens, explosion, ...).
+The latter allow us to better assess soundscapes in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}.
+This detection step can respectively be operated online (on the sensors) or offline (on the data servers).
 
-low consumption computation (processing and transmission) of the sensor node
+The former is efficient in terms of data storage as only the detection events are transmitted and is thus currently considered in several approaches \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
+Though, it requires the availability of computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware d not allow them to be autonomous using power sources like decent size solar panels.
+Furthermore, the detection is done once and cannot be recomputed during posterior analyses.
 
-low bitrate of the transmitted data for efficient transmission and storage
+The latter scheme has several benefits.
+First, the sensor is much simpler and can thus be autonomous in terms of energy, easing the deployment of the network.
+Second, it allows researchers to gather large amount of data that can be post processed and studied further offline.
+Data can be re analysed following newer classification schemes or using new indicators.
 
-proposed approach
+However, transmitting the raw audio through the network has several disavantages, in terms of required bandwidth, storage capabilities and privacy.Thus, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way.
+Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.
+
+We thus propose in this paper a audio coding scheme specifically tailored for use in a sensor grid which has the following features.
+It is of low bitrate but still allows the computation of most of the standard acoustics indicators with high precision.
+As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data.
+Finally, according to preliminary perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
+
+In order to promote reproducible research, the coder as well as the experiments needed to generate the figures will be made available to the community.
+The remaining of the paper is organized as follows: Section \ref{sec:background} reviews the types of data that needs to be estimated using the transmitted data and Section \ref{sec:coder} describes the proposed encoding schemeSection.
+the experimental protocol designed to validate the proposed approach is described in Section \ref{sec:protocol} and results are discussed in Section \ref{sec:results}.
 
@@
 \vspace{-0.15in}
-\caption{}
+\caption{Alternative implementations of the sensor grid approach for the monitoring of the acoustic environnment.
+In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation.
+Thickness of arrows indicate bandwidth and thickness of boxes indicates the level of computation or storage required.}
 \label{fig:codingScheme}
@@
 
-\section{Background}
+\section{Background} \label{sec:background}
 
@@
 
-\section{Encoding scheme}
+\section{Encoding scheme} \label{sec:coder}
 
@@
 
-\section{Evaluation}
+\section{Validation protocol} \label{sec:protocol}
+
 A set of metrics is computed to assess the efficiency of the proposed coder scheme and determine the impact of the algorithm's parameters, which are as follow: the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, and only for Mel bands the number of coefficients between 10 and 40.
@@
 This is to verify that the quantization step yields a maximum absolute error inferior to the precision of the target recording device.
-To provide relevant statistics, these quantities are estimated for a total of 53 10-minutes texture frames.
-They are obtained from the UrbanSound8k dataset presented in the next section.
+To provide relevant statistics, these quantities are estimated for a total of 53 10-minutes texture frames \ml{describe dataset, etc}.
 
@@
 It is used in all the following experiments with the exception of intelligibility computation for which a small dataset of high-quality voice recordings is preferred.
-Audio files are resampled 44.1~kHz, normalized and reduced to a single channel.\\
+Audio files are resampled 44.1 samples per second, normalized and reduced to a single channel.\\
 
-We evaluate the global loss of information by implementing the four classification models proposed in \cite{salamon2014}: a support vector machine with a radial basis function kernel, a random forest classifier with 500 trees, a decision tree and a k-nearest neighbors classifier with $k = 5$.
+We first evaluate the global loss of information by implementing the four classification models proposed in \cite{salamon2014}: a support vector machine with a radial basis function kernel, a random forest classifier with 500 trees, a decision tree and a k-nearest neighbors classifier with $k = 5$.
 Values for the SVM parameter $C$ and RBF kernel variance $\sigma^2$ are found with a grid search.
@@
 The feature vector is thus comprised of 275 values to reproduce available results and compare with our own.
-Models are trained for each setup using a 10-fold cross validation method provided by the authors of \cite{salamon2014}, that is, every combination of testing one fold on models trained with the other nine.
+Models are trained for each setup using a 10-fold cross validation method \ml{provided by the authors of \cite{salamon2014} ?}, that is, every combination of testing one fold on models trained with the other nine.
 
@@
 A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
-Signal phase is approximated by either white noise spectrogram scaling or a Griffin \& Lim algorithm \cite{griffin1984}, and the signal is retrieved using concatenation or overlap-add.
+Signal phase is approximated by either white noise spectrogram scaling or a Griffin\& Lim algorithm \cite{griffin1984}, and the signal is retrieved using concatenation or overlap-add.
 When using overlap to compute third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.\\
@@
 
-\section{Results}
+\section{Results} \label{sec:results}
 
-\subsection{Coder efficiency}
-The main indicator of performance is the bitrate obtained at the output of the coder.
-The three varying factors studied are the data word size $q$, the number of bands and the effect of reducing time-resolution by averaging analysis frames.
-Figure~\ref{fig:bitrate_q} shows estimations of the output bitrate for different values of $q$.
-To match third-octave bands computation principle where a 125~ms analysis is mandatory, we averaged mel frames over time.
-Because we use the most common parameters, namely 23.2~ms window with 50\% overlap, the closest achievable rate considering simple averaging is 7.74 frames per second.
-Third-octave representation on 31 bands yielded an overall higher size than their mel equivalent, here estimated for 30 bands.
-It however compares with the 40-mel bands representation which is the most used in litterature.
-This occurence is likely due to the distribution observed by the data prior to Huffman encoding.
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=\columnwidth]{bitrate_qall.eps}
-	\caption{Coder output bitrate as a function of quantization for third-octave and mel bands with 8 frames per second.}
-	\label{fig:bitrate_q}
-\end{figure}
-
-A second set of parameters influences directly the time-frequency resolution of the analysis.
-By choosing a frame rate and number of bands, one can effectively control the size of periodically transmitted data.
-We evaluate the bitrate for 10 to 40 mel bands and a frame rate from 2 to 10 per second, with fixed $q = 8$.
-Results are exposed in Figure~\ref{fig:bitrate_mel_avg}.
-As intuitively expected, the bitrate for a given word size $q$ can be modeled as a linear function of the representation dimensions for one second of analysis.
-Small variations are induced by data distributions on a per-frame level and their effect on the Huffman algorithm.
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=\columnwidth]{bitrate_mel_avg.eps}
-	\caption{Impact of representation resolution on the encoded data bitrate.}
-	\label{fig:bitrate_mel_avg}
-\end{figure}
-
-While this experiment may seem trivial, it aims at assessing potential tradeoffs between bitrate and information. As such, it will be further discussed in the \textit{Event recognition} subsection.\\
-
-We also examine the additionnal error caused by encoding steps after obtaining the desired data representation.
-The only lossy operation applied is quantization, which is defined by an output word size $q$ in bits.
-However, it corresponds to the word size \textit{after} $\Delta$-compression, meaning that the data is in fact quantized on $2^{q-1}$ values.
-Since these measurements are already expressed in dB, the error $\varepsilon$ is:
-\begin{equation*}
-	\varepsilon = |x_q-x|
-\end{equation*}
-where $x_q$ and $x$ are the quantized and clean representations repectively. $x_q$ is given by:
-\begin{equation*}
-x_q(n) = \frac{\Delta_x}{2^{q-1}-1}\textrm{round}\left(\frac{(2^{q-1}-1)x(n)}{\Delta_x}\right), x\in \left[0, \Delta_x\right]
-\end{equation*}
-Figure~\ref{fig:error_q} shows an estimation of $\varepsilon$ as a function of $q$ for third-octave and mel bands.
-In both cases, the mean and standard deviation seem to decrease by a factor of 2 as $q$ increases.
-To explain this phenomenon, let us model $x$ as a uniform distribution such as $x\sim \textit{U}\{0, \Delta_x\}$.
-While this is not exact it matches our objective when using a logarithm to flatten given PDFs.
-The error $\varepsilon$ will follow a uniform distribution $U\sim \{0, \frac{\Delta_x}{2\times (2^{q-1}-1)}\}$.
-Therefore, the mean and standard deviation are:
-\[
-\begin{cases}
-	\mu_\epsilon = \frac{\Delta_x}{4\times (2^{q-1}-1)}\\
-	\sigma_\epsilon = \frac{1}{12}\frac{\Delta_x}{2\times (2^{q-1}-1)}
-\end{cases}
-\]
-justifying the decaying ratio as $q$ increases. In practice, we assume that $\varepsilon = f(\Delta_x, \frac{1}{2^{q-1}-1})$ with the heterogeneity of the data's PDF inducing small variations.\\
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=\columnwidth]{error_qall.eps}
-	\caption{Measurement error induced by encoding for different quantization resolutions.}
-	\label{fig:error_q}
-\end{figure}
-
-Because in our implementation $\Delta_x$ is sampled for each analysis frame, the error has the same statistics across all bands.
-We compare the observed values against those specified in the IEC 61672-1:2013 for $f = 1~kHz$ as it is where the most accurate measurements are expected.
-For class 1 and 2 sound level meters, the tolerance is set at about $\pm 1~dB$ and $\pm 1.5~dB$ respectively.
-Results for 6, 7 or 8-bit words lie within the shorter range and are therefore compliant with the standard's measurement tolerance.
-
-\subsection{Event recognition}
-
-The same set of parameters as in bitrate evaluation is used to study sound event recognition.
-We aim at finding possibilities to further reduce the encoded data size without affecting performance in a significant way.
-Results of the four presented classification methods are provided for completeness.\\
-
-First, we observe the impact of quantization on classification accuracy.
-The models are trained on the most complete implemented representation, ie.
-40 mel bands and no time averaging (85 frames per second).
-Figure~\ref{fig:class_mel_q} shows that this process yields equivalent accuracy for higher resolutions.\\
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=\columnwidth]{class_mel_q.eps}
-	\caption{Classification accuracy as a function of word size before encoding. The baseline on the right is computed without quantizing the representation.}
-	\label{fig:class_mel_q}
-\end{figure}
-
-The effect of changing representation time-frequency resolution is presented in Table~\ref{T1}.
-Similarly to baseline results, the random forest and SVM classifiers are the most performant at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively.
-However, we find that given our setup, diminishing the number of analysis bands to an extent generally does not cause the classification task to fail.
-The decision tree is a flagrant example of this, with best performances for 10 mel bands only and a 4\% lower accuracy for 40.
-Even if the difference is insignificant, all other models perform best with 30 or 40 mel bands as a representation base.
-Time decimation is also possible, as in most cases the original data can be averaged consistently and yield a good classification accuracy.
-The loss of information can be considered negligible for FPS values as low as 8 or 10 depending on the method.
-This means that we can effectively divide the data size by a factor of at most 10 without affecting sound event recognition.
-It also provides us with a preliminary confirmation of the possibility for "fast"-sampled third-octave bands cepstra to match  MFCC performances.\fg{Highlight best/ok values once per class.
-method, not per fps}\\
-
-\begin{table*}[h]
-\centering
-\caption{Classification accuracy for varying representation resolutions}
-\label{T1}
-\begin{tabular}{ll|c|c|c|c|c|c|c|} 
-\cline{3-9}
-\multicolumn{2}{c}{\multirow{2}{*}{SVM}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
- & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9} 
-\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} & 0.55$\pm$0.03 & 0.60$\pm$0.03 & \textbf{0.61$\pm$0.04} & \textbf{0.62$\pm$0.03} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.06} & \textbf{0.65$\pm$0.06} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & \textbf{0.58$\pm$0.04} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.65$\pm$0.05} & \textbf{0.67$\pm$0.06} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & \textbf{\textcolor{red}{0.60$\pm$0.03}} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.65$\pm$0.04}} & \textbf{\textcolor{red}{0.65$\pm$0.03}} & \textbf{\textcolor{red}{0.67$\pm$0.04}} & \textbf{\textcolor{red}{0.68$\pm$0.04}} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & \textbf{0.60$\pm$0.03} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.66$\pm$0.04} & \textbf{0.68$\pm$0.05} \\ \cline{1-9}
-\end{tabular}
-
-\begin{tabular}{ll|c|c|c|c|c|c|c|} 
-\cline{3-9}
-\multicolumn{2}{c}{\multirow{2}{*}{RF-500}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
- & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9} 
-\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} & \textbf{0.60$\pm$0.03} & \textbf{0.62$\pm$0.03} & \textbf{0.62$\pm$0.03} & \textbf{0.63$\pm$0.03} & \textbf{0.63$\pm$0.03} & \textbf{0.65$\pm$0.04} & \textbf{0.67$\pm$0.05} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & \textbf{0.61$\pm$0.04} & \textbf{0.63$\pm$0.03} & \textbf{0.64$\pm$0.03} & \textbf{\textcolor{red}{0.64$\pm$0.03}} & \textbf{0.64$\pm$0.04} & \textbf{0.66$\pm$0.06} & \textbf{0.69$\pm$0.06} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & \textbf{\textcolor{red}{0.62$\pm$0.03}} & \textbf{\textcolor{red}{0.63$\pm$0.03}} & \textbf{\textcolor{red}{0.64$\pm$0.03}} & \textbf{0.64$\pm$0.03} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.67$\pm$0.05}} & \textbf{\textcolor{red}{0.69$\pm$0.06}} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.67$\pm$0.06} & \textbf{0.68$\pm$0.06} \\ \cline{1-9}
-\end{tabular}
-
-\begin{tabular}{ll|c|c|c|c|c|c|c|} 
-\cline{3-9}
-\multicolumn{2}{c}{\multirow{2}{*}{DT}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
- & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9} 
-\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} & \textbf{0.42$\pm$0.03} & \textbf{\textcolor{red}{0.46$\pm$0.04}} & \textbf{\textcolor{red}{0.46$\pm$0.02}} & \textbf{0.44$\pm$0.03} & \textbf{\textcolor{red}{0.45$\pm$0.03}} & \textbf{\textcolor{red}{0.46$\pm$0.05}} & \textbf{\textcolor{red}{0.49$\pm$0.03}} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & \textbf{\textcolor{red}{0.43$\pm$0.05}} & \textbf{0.43$\pm$0.03} & 0.43$\pm$0.02 & \textbf{0.44$\pm$0.03} & \textbf{0.45$\pm$0.03} & \textbf{0.45$\pm$0.05} & \textbf{0.47$\pm$0.05} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & \textbf{0.42$\pm$0.04} & \textbf{0.43$\pm$0.02} & \textbf{0.44$\pm$0.03} & \textbf{\textcolor{red}{0.45$\pm$0.05}} & \textbf{0.43$\pm$0.03} & \textbf{0.43$\pm$0.04} & \textbf{0.45$\pm$0.05} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & \textbf{0.42$\pm$0.06} & 0.43$\pm$0.03 & 0.43$\pm$0.03 & \textbf{0.42$\pm$0.03} & \textbf{0.44$\pm$0.03} & \textbf{0.46$\pm$0.03} & 0.45$\pm$0.04 \\ \cline{1-9} 
-\end{tabular}
-
-\begin{tabular}{ll|c|c|c|c|c|c|c|} 
-\cline{3-9}
-\multicolumn{2}{c}{\multirow{2}{*}{KNN-5}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
- & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9} 
-\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} & \textbf{0.43$\pm$0.02} & \textbf{0.51$\pm$0.04} & \textbf{0.53$\pm$0.04} & \textbf{0.53$\pm$0.05} & \textbf{0.53$\pm$0.04} & \textbf{0.54$\pm$0.04} & \textbf{0.56$\pm$0.03} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & \textbf{0.44$\pm$0.03} & \textbf{0.52$\pm$0.04} & \textbf{0.53$\pm$0.03} & \textbf{0.54$\pm$0.04} & \textbf{0.54$\pm$0.04} & \textbf{0.55$\pm$0.04} & \textbf{\textcolor{red}{0.58$\pm$0.04}} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & \textbf{0.45$\pm$0.04} & \textbf{\textcolor{red}{0.54$\pm$0.05}} & \textbf{\textcolor{red}{0.55$\pm$0.05}} & \textbf{0.55$\pm$0.04} & \textbf{\textcolor{red}{0.55$\pm$0.04}} & \textbf{0.56$\pm$0.04} & \textbf{0.56$\pm$0.04} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & \textbf{\textcolor{red}{0.46$\pm$0.03}} & \textbf{0.53$\pm$0.05} & \textbf{0.55$\pm$0.05} & \textbf{\textcolor{red}{0.55$\pm$0.04}} & \textbf{0.55$\pm$0.05} & \textbf{\textcolor{red}{0.57$\pm$0.04}} & \textbf{0.57$\pm$0.03} \\ \cline{1-9}
-\end{tabular} 
-\end{table*}
-
-\subsection{Third-octave bands as base descriptors}
-
-We now compare the efficiency of third-octave bands at characterizing urban soundscapes to that of mel spectrograms.
-Following the previous discussions, the classification task is run on corresponding cepstra with a fixed 8 frames per second and 31 bands.
-Figure~\ref{fig:tob_mel_q} displays \fg{fig to be added} similar results to 40 bands, 8 fps mel spectrograms.\\
-
-To further analyze both representations advantages, the confusion matrix is a reliable tool.
-It aims at providing information regarding class-by-class accuracy and misclassification rates.
-We thus compute these metrics for the SVM classifier, with predictions cumulated over the ten folds in test configuration.
-Results are visible in Figure~\ref{fig:tob_conf} and Figure~\ref{fig:mel_conf}
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=\columnwidth]{tob_conf.eps}
-	\caption{Confusion matrix of the SVM classification on third-octave bands with $q = 8$.}
-	\label{fig:tob_conf}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=\columnwidth]{mel_conf.eps}
-	\caption{Confusion matrix for the same setup with 40 mel bands.}
-	\label{fig:mel_conf}
-\end{figure}
-\fg{Ici je pensais pouvoir trouver et expliquer les differences dues au contenu des descripteurs, mais apparemment les résultats sont proches. TODO: creuser un peu plus, et conclure}
-
-\subsection{Inintelligibility}
-
-Finally, objective intelligibility metrics are estimated for the studied parameters and compared to perceptual tests.
-Figure~\ref{fig:int_mel_avg} shows both the CSII and fwSNRseg indicators for varying representation dimensions.
-Figure~\ref{fig:percint_mel_avg} presents the results of the preliminar perceptual test for the same setup.
-We acknowledge that it is surely biased by a reduced number of participants and lack of tested audio material.
-However, it is sufficient to judge the relevance of objective indicators in our conditions.
-We may at first observe a resemblance between the three measurements.
-
-The CSII accounts for the whole spectrogram distance between clean and distorted audio at each point in time and frequency.
-This includes the phase, which we discard early in the representation step.
-The error induced by forward and inverse mel bands transformation as well as operations reducing data dimensionality further contribute to very high distances.
-In fact, the signal is too distorted for the proposed SNR normalization to ensure CSII values in the 0-1 range.
-The indicator differs from perceptual evaluations for middle-valued frame rates, with for example the 9.5 fps curve being lower than expected.
-Values are also very close for multiple parameter combinations where a threshold between intelligibility and inintelligibility could be found.
-This is therefore not an adequate indicator for this application.\\
-
-Alternatively, the frequency-weighted segmental SNR considers only spectrogram magnitudes.
-As a result, distance is generally lower and a more accurate representation of the reality.
-Nevertheless, the fwSNRseg still uses point-wise comparison.
-A shape seems to appear where the influences of frame rate and mel bands on output are decorrelated, ie.
-almost the same curve is offset as a function of frame rate.
-While the values are still concentrated around the critical threshold location at about -5~dB, this metric is likely a better indicator due to its approach of the clean-reconstructed signal distance.
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=\columnwidth]{int_mel_avg.eps}
-	\caption{The two objective indicators computed for intelligibility assessment.
-Negative CSII values indicate a signal-to-noise ratio too low for the recommended normalization, thus severe disparities between the original and reconstructed signal.}
-	\label{fig:int_mel_avg}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=\columnwidth]{percint_mel_avg.eps}
-	\caption{Results of a very small perceptual intelligibility test.}
-	\label{fig:percint_mel_avg}
-\end{figure}
-
-\fg{figures a refaire}
 \section{Conclusion}
@@
 \section{References}
+
+\bibliographystyle{plain}
+\bibliography{biblio}
+
+\ml{USE BIBTEX !!}
+
 \begin{thebibliography}{09}

### 2017-06-16 paper/article.tex

--- 2017-06-16 paper/article.tex
@@
 
-\section{Results}
+\section{Results} \label{sec:results}
 

### 2017-06-16 paper/article.tex
new comments

@@
 
-\title{An effective sensor grid approach for large scale acoustic monitoring}
+\title{A sensor grid approach for large scale acoustic monitoring}
 
@@
 		\includegraphics[width=\columnwidth]{class_mel_q.eps}
-	\caption{Classification accuracy as a function of word size before encoding. The baseline on the right is computed without quantizing the representation.}
+	\caption{Classification accuracy as a function of word size before encoding.
+The baseline on the right is computed without quantizing the representation.
+\ml{cette figure pose probleme, car la baseline n'a pas de word size, je mettrai un tick "no quant".
+Pourquoi les lignes continues jqa la baseline ?}}
 	\label{fig:class_mel_q}
@@
 \begin{table*}[h]
+	\ml{percentage}
 \centering
@@
 Figure~\ref{fig:int_mel_avg} shows both the CSII and fwSNRseg indicators for varying representation dimensions.
-Figure~\ref{fig:percint_mel_avg} presents the results of the preliminar perceptual test \ml{comment tu as fait le test ?} for the same setup.
+Figure~\ref{fig:percint_mel_avg} presents the results of the preliminar perceptual test \ml{soit on fait un test avec 5-10 personnes soit on en parle pas} for the same setup.
 We acknowledge that it is surely biased by a reduced number of participants and lack of tested audio material.

### 2017-06-16 paper/article.tex
sketch abstract

@@
 
-\address{felix.gontier@reseau.eseo.fr\\mathieu.lagrange@cnrs.fr}
+\address{felix.gontier@reseau.eseo.fr \\ mathieu.lagrange@cnrs.fr}
 
@@
 
+The acoustic environment represents both societal and environmental concerns, in particular for cities that are subjected to a multitude of noise sources and that count de facto numerous exposed people.
+
+In this context, monitoring the acoustic environnment in urban but also rural or wilderness areas is an important matter.
+Fostering on the recent development of low cost hardware acoustic sensors, we propose to using a sensor grid approach.
+
+audio sensing
+
+audio encoding
+
 \end{abstract}
@@
 \begin{keyword}
+
+acoustic monitoring \sep soundscape assessment \sep
 %% keywords here, in the form: keyword \sep keyword

### 2017-06-19 paper/article.tex
Paper update

--- 2017-06-16 paper/article.tex
@@
 %% Text of abstract
+The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc (wp.nyu.edu/sonyc) and cense (cense.ifsttar.fr) projects.
+
+Together with the estimation of acoustic indicators (LAeq, ...), one important aspect of those networks is their ability to detect the presence of sound sources of interest ( bird calls, sirens, explosion, ...) in order to better assess soundscapes.
+This detection step can be operated online (on the sensors) or offline (on the data servers).
+
+The former is efficient in terms of data storage as only the detection events are transmitted.
+Though, it requires the availability of computing resources on the sensors in order to perform the detection step, and the detection is done once and cannot be recomputed.
+
+The latter scheme has several benefits.
+First, the sensor is much simpler and can thus be autonomous in terms of energy, easing the deployment of the network.
+Second, it allows researchers to gather large amount of data that can be post processed and studied further offline.
+Data can be re analysed following newer classification schemes or using new indicators.
+
+But, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way.
+Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.
+
+The coding scheme described in this paper has the following features.
+It is of low bitrate but still allows the computation of most of the standard acoustics indicators with high precision.
+As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data.
+Finally, according to preliminary perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
+
+In order to promote reproducible research, the coder as well as the experiments needed to generate the figures will be made available to the community.
 
@@
 
-The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc (wp.nyu.edu/sonyc) and cense (cense.ifsttar.fr) projects.
+As such, there is a strong need for the development of the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} for the monitoring of the acoustic environment, be it from urban, rural or wilderness areas.
 
-To do so, considering the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} has several advantages.
 The sensor grid approach put the focus on a) a distributed system of data acquisition with a large set of sensors, b) the production and storage of a large dataset, and c) its availability for intensive and open data analysis computation.
 
-In our application setting, the requirements are the following.
-First,  the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, \textit{i.e.} the approach shall be scalable.
-Second, the nodes shall be energy efficient in order ot ease the deployment of the sensors grid to the desired topology, ideally autonomous.
-Third, the data transfer used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to ensure the privacy of the citizen.
-Lastly, the data stored shall be as rich as possible while retaining a low bitrate for efficient transmission and storage
+requirements
 
-The data of interest is first acoustic indicators (LAeq, ...) and second the presence of sound sources of interest (bird calls, sirens, explosion, ...).
-The latter allow us to better assess soundscapes in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}.
-This detection step can respectively be operated online (on the sensors) or offline (on the data servers).
+scalability:
+power managment:
+security and privacy:
+data richness:
 
-The former is efficient in terms of data storage as only the detection events are transmitted and is thus currently considered in several approaches \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
-Though, it requires the availability of computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware d not allow them to be autonomous using power sources like decent size solar panels.
-Furthermore, the detection is done once and cannot be recomputed during posterior analyses.
+low consumption computation (processing and transmission) of the sensor node
 
-The latter scheme has several benefits.
-First, the sensor is much simpler and can thus be autonomous in terms of energy, easing the deployment of the network.
-Second, it allows researchers to gather large amount of data that can be post processed and studied further offline.
-Data can be re analysed following newer classification schemes or using new indicators.
+low bitrate of the transmitted data for efficient transmission and storage
 
-However, transmitting the raw audio through the network has several disavantages, in terms of required bandwidth, storage capabilities and privacy.Thus, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way.
-Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.
+proposed approach
 
-We thus propose in this paper a audio coding scheme specifically tailored for use in a sensor grid which has the following features.
-It is of low bitrate but still allows the computation of most of the standard acoustics indicators with high precision.
-As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data.
-Finally, according to preliminary perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
+%\begin{figure}[t]
+%\includegraphics[width=\columnwidth]{figures/censeCoder}
+%\vspace{-0.15in}
+%\caption{}
+%\label{fig:codingScheme}
+%\end{figure}
 
-In order to promote reproducible research, the coder as well as the experiments needed to generate the figures will be made available to the community.
-The remaining of the paper is organized as follows: Section \ref{sec:background} reviews the types of data that needs to be estimated using the transmitted data and Section \ref{sec:coder} describes the proposed encoding schemeSection.
-the experimental protocol designed to validate the proposed approach is described in Section \ref{sec:protocol} and results are discussed in Section \ref{sec:results}.
-
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{figures/censeCoder}
-\vspace{-0.15in}
-\caption{Alternative implementations of the sensor grid approach for the monitoring of the acoustic environnment.
-In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation.
-Thickness of arrows indicate bandwidth and thickness of boxes indicates the level of computation or storage required.}
-\label{fig:codingScheme}
-\end{figure}
-
-\section{Background} \label{sec:background}
+\section{Background}
 
@@
 
-\section{Encoding scheme} \label{sec:coder}
+\section{Encoding scheme}
 
@@
 
-\section{Validation protocol} \label{sec:protocol}
-
+\section{Evaluation}
 A set of metrics is computed to assess the efficiency of the proposed coder scheme and determine the impact of the algorithm's parameters, which are as follow: the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, and only for Mel bands the number of coefficients between 10 and 40.
@@
 
-\section{Results} \label{sec:results}
+\section{Results}
 
@@
 
-The same set of parameters as in bitrate evaluation is used to study the impact of their tuing to the sound event recognition performance.
+The same set of parameters as in bitrate evaluation is used to study the impact of their tuning to the sound event recognition performance.
 We thus aim at finding ways to further reduce the encoded data size without strongly affecting recognition performance.
@@
 Similarly to baseline results, the random forest and SVM classifiers are the higher performing systems at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively.
-However, we find that given our setup, diminishing the number of analysis bands to some extent most often does notinduces a strong drop of performance.
+However, we find that given our setup, diminishing the number of analysis bands to some extent most often does not induce a strong drop of performance.
 The performance of the decision tree classifier is a good example of this behavior, with best performances for 10 mel bands only and a 4\% lower accuracy for 40.
 Even if the difference is small, all other models perform best with 30 or 40 mel bands as a representation.
-Time decimation is also possible, as in most cases the original data can be averaged \ml{consistently ?} and yield a good classification accuracy.
-The loss of information can be considered negligible for FPS values as low as 8 or 10 depending on the method.
+Time decimation is also possible, as the original representation can be averaged and consistently yield a good classification accuracy.
+The loss of information can be considered negligible for FPS values as low as 20 or 10 depending on the method.
+Even below, classification accuracy only drops by one or a few percents.
 This means that we can effectively divide the data size by a factor of at most 10 without affecting sound event recognition performance.
-It also provides us with a preliminary confirmation of the possibility for "fast"-sampled third-octave bands cepstra to match  MFCC performances.\fg{Highlight best/ok values once per class.
-method, not per fps}\\
+It also provides us with a preliminary confirmation of the possibility for "fast"-sampled third-octave bands cepstra to match  MFCC performances.\\
 
@@
 \multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} & 0.55$\pm$0.03 & 0.60$\pm$0.03 & \textbf{0.61$\pm$0.04} & \textbf{0.62$\pm$0.03} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.06} & \textbf{0.65$\pm$0.06} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{10} & 0.55$\pm$0.03 & 0.60$\pm$0.03 & 0.61$\pm$0.04 & 0.62$\pm$0.03 & 0.62$\pm$0.04 & \textbf{0.63$\pm$0.06} & \textbf{0.65$\pm$0.06} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & \textbf{0.58$\pm$0.04} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.65$\pm$0.05} & \textbf{0.67$\pm$0.06} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{20} & 0.58$\pm$0.04 & 0.62$\pm$0.04 & 0.63$\pm$0.04 & 0.64$\pm$0.04 & 0.63$\pm$0.04 & \textbf{0.65$\pm$0.05} & \textbf{0.67$\pm$0.06} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & \textbf{\textcolor{red}{0.60$\pm$0.03}} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.65$\pm$0.04}} & \textbf{\textcolor{red}{0.65$\pm$0.03}} & \textbf{\textcolor{red}{0.67$\pm$0.04}} & \textbf{\textcolor{red}{0.68$\pm$0.04}} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{30} & 0.60$\pm$0.03 & 0.64$\pm$0.04 & 0.64$\pm$0.04 & \textbf{0.65$\pm$0.04} & \textbf{0.65$\pm$0.03} & \textbf{0.67$\pm$0.04} & \textbf{\textcolor{red}{0.68$\pm$0.04}} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & \textbf{0.60$\pm$0.03} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.66$\pm$0.04} & \textbf{0.68$\pm$0.05} \\ \cline{1-9}
+ & \multicolumn{1}{|c|}{40} & 0.60$\pm$0.03 & 0.63$\pm$0.04 & \textbf{0.64$\pm$0.04} & 0.64$\pm$0.04 & \textbf{0.64$\pm$0.04} & \textbf{0.66$\pm$0.04} & \textbf{0.68$\pm$0.05} \\ \cline{1-9}
 \end{tabular}
@@
 \multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} & \textbf{0.60$\pm$0.03} & \textbf{0.62$\pm$0.03} & \textbf{0.62$\pm$0.03} & \textbf{0.63$\pm$0.03} & \textbf{0.63$\pm$0.03} & \textbf{0.65$\pm$0.04} & \textbf{0.67$\pm$0.05} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{10} & 0.60$\pm$0.03 & 0.62$\pm$0.03 & 0.62$\pm$0.03 & 0.63$\pm$0.03 & 0.63$\pm$0.03 & \textbf{0.65$\pm$0.04} & \textbf{0.67$\pm$0.05} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & \textbf{0.61$\pm$0.04} & \textbf{0.63$\pm$0.03} & \textbf{0.64$\pm$0.03} & \textbf{\textcolor{red}{0.64$\pm$0.03}} & \textbf{0.64$\pm$0.04} & \textbf{0.66$\pm$0.06} & \textbf{0.69$\pm$0.06} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{20} & 0.61$\pm$0.04 & 0.63$\pm$0.03 & 0.64$\pm$0.03 & 0.64$\pm$0.03 & 0.64$\pm$0.04 & \textbf{0.66$\pm$0.06} & \textbf{0.69$\pm$0.06} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & \textbf{\textcolor{red}{0.62$\pm$0.03}} & \textbf{\textcolor{red}{0.63$\pm$0.03}} & \textbf{\textcolor{red}{0.64$\pm$0.03}} & \textbf{0.64$\pm$0.03} & \textbf{\textcolor{red}{0.64$\pm$0.04}} & \textbf{\textcolor{red}{0.67$\pm$0.05}} & \textbf{\textcolor{red}{0.69$\pm$0.06}} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{30} & 0.62$\pm$0.03 & 0.63$\pm$0.03 & 0.64$\pm$0.03 & 0.64$\pm$0.03 & 0.64$\pm$0.04 & \textbf{0.67$\pm$0.05} & \textbf{\textcolor{red}{0.69$\pm$0.06}} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & \textbf{0.62$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.64$\pm$0.04} & \textbf{0.63$\pm$0.04} & \textbf{0.67$\pm$0.06} & \textbf{0.68$\pm$0.06} \\ \cline{1-9}
+ & \multicolumn{1}{|c|}{40} & 0.62$\pm$0.04 & 0.63$\pm$0.04 & 0.63$\pm$0.04 & 0.64$\pm$0.04 & 0.63$\pm$0.04 & \textbf{0.67$\pm$0.06} & \textbf{0.68$\pm$0.06} \\ \cline{1-9}
 \end{tabular}
@@
 \multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} & \textbf{0.42$\pm$0.03} & \textbf{\textcolor{red}{0.46$\pm$0.04}} & \textbf{\textcolor{red}{0.46$\pm$0.02}} & \textbf{0.44$\pm$0.03} & \textbf{\textcolor{red}{0.45$\pm$0.03}} & \textbf{\textcolor{red}{0.46$\pm$0.05}} & \textbf{\textcolor{red}{0.49$\pm$0.03}} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{10} & 0.42$\pm$0.03 & \textbf{0.46$\pm$0.04} & 0.46$\pm$0.02 & 0.44$\pm$0.03 & 0.45$\pm$0.03 & \textbf{0.46$\pm$0.05} & \textbf{\textcolor{red}{0.49$\pm$0.03}} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & \textbf{\textcolor{red}{0.43$\pm$0.05}} & \textbf{0.43$\pm$0.03} & 0.43$\pm$0.02 & \textbf{0.44$\pm$0.03} & \textbf{0.45$\pm$0.03} & \textbf{0.45$\pm$0.05} & \textbf{0.47$\pm$0.05} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{20} & 0.43$\pm$0.05 & 0.43$\pm$0.03 & 0.43$\pm$0.02 & 0.44$\pm$0.03 & 0.45$\pm$0.03 & 0.45$\pm$0.05 & \textbf{0.47$\pm$0.05} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & \textbf{0.42$\pm$0.04} & \textbf{0.43$\pm$0.02} & \textbf{0.44$\pm$0.03} & \textbf{\textcolor{red}{0.45$\pm$0.05}} & \textbf{0.43$\pm$0.03} & \textbf{0.43$\pm$0.04} & \textbf{0.45$\pm$0.05} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{30} & 0.42$\pm$0.04 & 0.43$\pm$0.02 & 0.44$\pm$0.03 & 0.45$\pm$0.05 & 0.43$\pm$0.03 & 0.43$\pm$0.04 & \textbf{0.45$\pm$0.05} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & \textbf{0.42$\pm$0.06} & 0.43$\pm$0.03 & 0.43$\pm$0.03 & \textbf{0.42$\pm$0.03} & \textbf{0.44$\pm$0.03} & \textbf{0.46$\pm$0.03} & 0.45$\pm$0.04 \\ \cline{1-9}
+ & \multicolumn{1}{|c|}{40} & 0.42$\pm$0.06 & 0.43$\pm$0.03 & 0.43$\pm$0.03 & 0.42$\pm$0.03 & 0.44$\pm$0.03 & 0.46$\pm$0.03 & \textbf{0.46$\pm$0.04} \\ \cline{1-9}
 \end{tabular}
@@
 \multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} & \textbf{0.43$\pm$0.02} & \textbf{0.51$\pm$0.04} & \textbf{0.53$\pm$0.04} & \textbf{0.53$\pm$0.05} & \textbf{0.53$\pm$0.04} & \textbf{0.54$\pm$0.04} & \textbf{0.56$\pm$0.03} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{10} &0.43$\pm$0.02 & 0.51$\pm$0.04 & 0.53$\pm$0.04 & 0.53$\pm$0.05 & 0.53$\pm$0.04 & 0.54$\pm$0.04 & \textbf{0.56$\pm$0.03} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & \textbf{0.44$\pm$0.03} & \textbf{0.52$\pm$0.04} & \textbf{0.53$\pm$0.03} & \textbf{0.54$\pm$0.04} & \textbf{0.54$\pm$0.04} & \textbf{0.55$\pm$0.04} & \textbf{\textcolor{red}{0.58$\pm$0.04}} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{20} & 0.44$\pm$0.03 & 0.52$\pm$0.04 & 0.53$\pm$0.03 & 0.54$\pm$0.04 & \textbf{0.54$\pm$0.04} & \textbf{0.55$\pm$0.04} & \textbf{\textcolor{red}{0.58$\pm$0.04}} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & \textbf{0.45$\pm$0.04} & \textbf{\textcolor{red}{0.54$\pm$0.05}} & \textbf{\textcolor{red}{0.55$\pm$0.05}} & \textbf{0.55$\pm$0.04} & \textbf{\textcolor{red}{0.55$\pm$0.04}} & \textbf{0.56$\pm$0.04} & \textbf{0.56$\pm$0.04} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{30} & 0.45$\pm$0.04 & 0.54$\pm$0.05 & \textbf{0.55$\pm$0.05} & \textbf{0.55$\pm$0.04} & \textbf{0.55$\pm$0.04} & \textbf{0.56$\pm$0.04} & \textbf{0.56$\pm$0.04} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & \textbf{\textcolor{red}{0.46$\pm$0.03}} & \textbf{0.53$\pm$0.05} & \textbf{0.55$\pm$0.05} & \textbf{\textcolor{red}{0.55$\pm$0.04}} & \textbf{0.55$\pm$0.05} & \textbf{\textcolor{red}{0.57$\pm$0.04}} & \textbf{0.57$\pm$0.03} \\ \cline{1-9}
+ & \multicolumn{1}{|c|}{40} & 0.46$\pm$0.03 & 0.53$\pm$0.05 & \textbf{0.55$\pm$0.05} & \textbf{0.55$\pm$0.04} & \textbf{0.55$\pm$0.05} & \textbf{0.57$\pm$0.04} & \textbf{0.57$\pm$0.03} \\ \cline{1-9}
 \end{tabular}
@@
 Following the previous discussions, the classification task is run on corresponding cepstra with a fixed 8 frames per second and 31 bands.
-Figure~\ref{fig:tob_mel_q} displays \fg{fig to be added} similar results to 40 bands, 8 fps mel spectrograms.\\
+Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps mel spectrograms seen in Table~\ref{T1} for all classification schemes.\\
+
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\columnwidth]{class_tob_q.eps}
+	\caption{Classification accuracy with third-octave bands and varying word size.}
+	\label{fig:class_tob_q}
+\end{figure}
 
@@
 We thus compute these metrics for the SVM classifier, with predictions cumulated over the ten folds in test configuration.
-Results are visible in Figure~\ref{fig:tob_conf} and Figure~\ref{fig:mel_conf}
+Results are visible in Figure~\ref{fig:tob_conf} and Figure~\ref{fig:mel_conf}.
+The analogous natures of the two descriptors is highlighted by close one-versus-one differentiation performances, with a slightly lower accuracy for third-octave bands on average.
+A noticeable difference is that on the log-frequency scale the bandwidth of mel filters narrows as frequency increases while third-octave are evenly distributed.
+The effect of this can be seen between classes 5 and 8 (resp.
+\textit{Drilling} and \textit{Jackhammer}).
+These sounds involve important low-frequency information which can generally differentiate them, leading third-octave descriptors to perform better.
+Conversely this improves globally class 1 (\textit{Air conditioning}) recognition as most of its defining components are situated in higher frequencies.\\
+
+Each descriptor is thus found to have similar representational capabilities despite minor construction differences.
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}[h!]
 	\centering
@@
 \end{figure}
-\fg{Ici je pensais pouvoir trouver et expliquer les differences dues au contenu des descripteurs, mais apparemment les résultats sont proches. TODO: creuser un peu plus, et conclure}
 
@@
 Finally, objective intelligibility metrics are estimated for the studied parameters and compared to an informal perceptual evaluation \footnote{Decoded speech utterances for various conditions can be listened to at \url{http://}}.
-Figure~\ref{fig:int_mel_avg} shows both the CSII and fwSNRseg indicators for varying representation dimensions.
-Figure~\ref{fig:percint_mel_avg} presents the results of the preliminar perceptual test \ml{comment tu as fait le test ?} for the same setup.
+Figures~\ref{fig:csii_mel_avg} and \ref{fig:fwsnrseg_mel_avg} shows both the CSII and fwSNRseg indicators for varying representation dimensions.
+Figure~\ref{fig:percint_mel_avg} presents the results of the preliminar perceptual test for the same setup.
+For this test, subjects were asked to blindly listen to recovered speech audio with different representation and coding parameters.
+They had to rate each extract between 0 ans 5, respectively inintelligible and perfectly comprehensible.
 We acknowledge that it is surely biased by a reduced number of participants and lack of tested audio material.
@@
 	\centering
-		\includegraphics[width=\columnwidth]{int_mel_avg.eps}
-	\caption{The two objective indicators computed for intelligibility assessment.
+		\includegraphics[width=\columnwidth]{csii_mel_avg.eps}
+	\caption{The Coherence SII objective indicator computed for intelligibility assessment.
 Negative CSII values indicate a signal-to-noise ratio too low for the recommended normalization, thus severe disparities between the original and reconstructed signal.}
-	\label{fig:int_mel_avg}
+	\label{fig:csii_mel_avg}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+		\includegraphics[width=\columnwidth]{fwsnrseg_mel_avg.eps}
+	\caption{Frequency-weighted segmental SNR for the same parameters.}
+	\label{fig:fwsnrseg_mel_avg}
 \end{figure}
@@
 		\includegraphics[width=\columnwidth]{percint_mel_avg.eps}
-	\caption{Results of a very small perceptual intelligibility test.}
+	\caption{Results of the perceptual intelligibility test.}
 	\label{fig:percint_mel_avg}
@@
 \section{References}
-
-\bibliographystyle{plain}
-\bibliography{biblio}
-
-\ml{USE BIBTEX !!}
-
 \begin{thebibliography}{09}

### 2017-06-19 censeCoder/cecoReport.m

@@ -49,7 +49,7 @@ if nargin==0, censeCoder('report', 'r'); return; end%censeCoder('report', 'rhv')
 %%% Class
 % Fixed: -
 % Varying: Quant - All
-config = expExpose(config, 'p', 'mask', {-1, -1, 0, -1, -1, -1, 2, 0, -1, 2, -1, 2}, 'obs', 'cv_acc', 'save', 'tob_class', 'step', 4, 'expand', 'quant');
+% config = expExpose(config, 'p', 'mask', {-1, -1, 0, -1, -1, -1, 2, 0, -1, 2, -1, 2}, 'obs', 'cv_acc', 'save', 'tob_class', 'step', 4, 'expand', 'quant');
 
 %%% Intel
 % Fixed: -
@@ -85,7 +85,7 @@ config = expExpose(config, 'p', 'mask', {-1, -1, 0, -1, -1, -1, 2, 0, -1, 2, -1,
 % config = expExpose(config, 'p', 'mask', {7, 4, 1, -1, -1, -1, 2, 0, -1, 1, -1, -1}, 'obs', 'cv_acc', 'save', 'mel_class_mel30_avg0_q0', 'step', 4);
 % Fixed: Quant - 8
 % Varying: Mel - All, Avg - All
-%config = expExpose(config, 't', 'mask', {0, 0, 6, 1, 2, 10, 2, 4, -1, 1, -1, -1}, 'obs', 'cv_acc', 'save', 'mel_class_melall_avgall_q8', 'step', 4, 'expand', 'fps');
+config = expExpose(config, 't', 'mask', {0, 0, 6, 1, 2, 10, 2, 1, -1, 1, -1, -1}, 'obs', 'cv_acc', 'save', 'mel_class_melall_avgall_q8', 'step', 4);
 
 %%% Intel
 % Fixed: Quant - 8

### 2017-06-19 censeCoder/report_figs.m

@@ -108,22 +108,22 @@ end
 % errorbar(11:10:41, data_csii.meanData(5, :), data_csii.stdData(5, :))
 % errorbar(12:10:42, data_csii.meanData(6, :), data_csii.stdData(6, :))
 % errorbar(13:10:43, data_csii.meanData(7, :), data_csii.stdData(7, :))
-% axis([0 50 -0.7 0.2]), grid on, legend(fps_lgd, 'location', 'northwest'), xlabel('Mel bands'); ylabel('CSII')
-% 
-% load('report/figures/mel_fwSNRseg_melall_avgall_q8.mat');
-% data_fwSNRseg = data;
-% clear data;
-% figure(1), clf
-% 
-% errorbar(10:10:40, data_fwSNRseg.meanData(1, :), data_fwSNRseg.stdData(1, :))
-% hold on,
-% errorbar(10:10:40, data_fwSNRseg.meanData(2, :), data_fwSNRseg.stdData(2, :))
-% errorbar(10:10:40, data_fwSNRseg.meanData(3, :), data_fwSNRseg.stdData(3, :))
-% errorbar(10:10:40, data_fwSNRseg.meanData(4, :), data_fwSNRseg.stdData(4, :))
-% errorbar(10:10:40, data_fwSNRseg.meanData(5, :), data_fwSNRseg.stdData(5, :))
-% errorbar(10:10:40, data_fwSNRseg.meanData(6, :), data_fwSNRseg.stdData(6, :))
-% errorbar(10:10:40, data_fwSNRseg.meanData(7, :), data_fwSNRseg.stdData(7, :))
-% axis([0 50 -15 5]), grid on, xlabel('Mel bands'); ylabel('fwSNRseg (dB)')
+% axis([-10 45 -0.7 -0.1]), grid on, legend(fps_lgd, 'location', 'northwest'), xlabel('Mel bands'); ylabel('CSII')
+
+load('report/figures/mel_fwSNRseg_melall_avgall_q8.mat');
+data_fwSNRseg = data;
+clear data;
+figure(1), clf
+
+errorbar(10:10:40, data_fwSNRseg.meanData(1, :), data_fwSNRseg.stdData(1, :))
+hold on,
+errorbar(10:10:40, data_fwSNRseg.meanData(2, :), data_fwSNRseg.stdData(2, :))
+errorbar(10:10:40, data_fwSNRseg.meanData(3, :), data_fwSNRseg.stdData(3, :))
[…]

### 2017-06-19 censeCoder/run_script.m

@@ -25,5 +25,6 @@ clear all, close all, clc;
 % censeCoder('do', [1 2 4], 'mask', {0, 0, 6, 1, 2, 10, 2, 0, -1, 1, -1, -1});
 %%% Intel indicators - All mel settings, 8 bit
 % censeCoder('do', [1 2 3 4], 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, 0, -1});
-
-censeCoder('do', [4], 'mask', {4, 4, 6, 1, 2, 10, 2, 1, -1, 0, -1, 2});
+% censeCoder('do', [4], 'mask', {4, 4, 6, 1, 2, 10, 2, 1, -1, 0, -1, 2});
+ 
+censeCoder('do', [1 2 3], 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, -1, -1});

### 2017-06-19 paper/article.tex
fie fixes

@@
 %% Text of abstract
-The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc (wp.nyu.edu/sonyc) and cense (cense.ifsttar.fr) projects.
 
-Together with the estimation of acoustic indicators (LAeq, ...), one important aspect of those networks is their ability to detect the presence of sound sources of interest ( bird calls, sirens, explosion, ...) in order to better assess soundscapes.
-This detection step can be operated online (on the sensors) or offline (on the data servers).
+The acoustic environment represents both societal and environmental concerns, in particular for cities that are subjected to a multitude of noise sources and that count de facto numerous exposed people.
 
-The former is efficient in terms of data storage as only the detection events are transmitted.
-Though, it requires the availability of computing resources on the sensors in order to perform the detection step, and the detection is done once and cannot be recomputed.
+In this context, monitoring the acoustic environnment in urban but also rural or wilderness areas is an important matter.
+Fostering on the recent development of low cost hardware acoustic sensors, we propose to using a sensor grid approach.
 
-The latter scheme has several benefits.
-First, the sensor is much simpler and can thus be autonomous in terms of energy, easing the deployment of the network.
-Second, it allows researchers to gather large amount of data that can be post processed and studied further offline.
-Data can be re analysed following newer classification schemes or using new indicators.
+audio sensing
 
-But, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way.
-Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.
-
-The coding scheme described in this paper has the following features.
-It is of low bitrate but still allows the computation of most of the standard acoustics indicators with high precision.
-As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data.
-Finally, according to preliminary perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
-
-In order to promote reproducible research, the coder as well as the experiments needed to generate the figures will be made available to the community.
+audio encoding
 
@@
 
-As such, there is a strong need for the development of the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} for the monitoring of the acoustic environment, be it from urban, rural or wilderness areas.
+The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc (wp.nyu.edu/sonyc) and cense (cense.ifsttar.fr) projects.
 
+To do so, considering the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} has several advantages.
 The sensor grid approach put the focus on a) a distributed system of data acquisition with a large set of sensors, b) the production and storage of a large dataset, and c) its availability for intensive and open data analysis computation.
 
-requirements
+In our application setting, the requirements are the following.
+First,  the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, \textit{i.e.} the approach shall be scalable.
+Second, the nodes shall be energy efficient in order ot ease the deployment of the sensors grid to the desired topology, ideally autonomous.
+Third, the data transfer used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to ensure the privacy of the citizen.
+Lastly, the data stored shall be as rich as possible while retaining a low bitrate for efficient transmission and storage
 
-scalability:
-power managment:
-security and privacy:
-data richness:
+The data of interest is first acoustic indicators (LAeq, ...) and second the presence of sound sources of interest (bird calls, sirens, explosion, ...).
+The latter allow us to better assess soundscapes in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}.
+This detection step can respectively be operated online (on the sensors) or offline (on the data servers).
 
-low consumption computation (processing and transmission) of the sensor node
+The former is efficient in terms of data storage as only the detection events are transmitted and is thus currently considered in several approaches \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
+Though, it requires the availability of computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware d not allow them to be autonomous using power sources like decent size solar panels.
+Furthermore, the detection is done once and cannot be recomputed during posterior analyses.
 
-low bitrate of the transmitted data for efficient transmission and storage
+The latter scheme has several benefits.
+First, the sensor is much simpler and can thus be autonomous in terms of energy, easing the deployment of the network.
+Second, it allows researchers to gather large amount of data that can be post processed and studied further offline.
+Data can be re analysed following newer classification schemes or using new indicators.
 
-proposed approach
+However, transmitting the raw audio through the network has several disavantages, in terms of required bandwidth, storage capabilities and privacy.Thus, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way.
+Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.
 
-%\begin{figure}[t]
-%\includegraphics[width=\columnwidth]{figures/censeCoder}
-%\vspace{-0.15in}
-%\caption{}
-%\label{fig:codingScheme}
-%\end{figure}
+We thus propose in this paper a audio coding scheme specifically tailored for use in a sensor grid which has the following features.
+It is of low bitrate but still allows the computation of most of the standard acoustics indicators with high precision.
+As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data.
+Finally, according to preliminary perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
 
-\section{Background}
+In order to promote reproducible research, the coder as well as the experiments needed to generate the figures will be made available to the community.
+The remaining of the paper is organized as follows: Section \ref{sec:background} reviews the types of data that needs to be estimated using the transmitted data and Section \ref{sec:coder} describes the proposed encoding schemeSection.
+the experimental protocol designed to validate the proposed approach is described in Section \ref{sec:protocol} and results are discussed in Section \ref{sec:results}.
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{figures/censeCoder}
+\vspace{-0.15in}
+\caption{Alternative implementations of the sensor grid approach for the monitoring of the acoustic environnment.
+In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation.
+Thickness of arrows indicate bandwidth and thickness of boxes indicates the level of computation or storage required.}
+\label{fig:codingScheme}
+\end{figure}
+
+\section{Background} \label{sec:background}
 
@@
 \cite{antoni2010} presents an alternative analysis method based on direct frequency weighting.
-The weights matrix design procedure complies with both ANSI S1.1-1986 and IEC 61260-1:2014 standards.
+The weights matrix design procedure complies with both ANSI S1.1-1986 \cite{citeulike:9580295} and IEC 61260-1:2014 \cite{iec-norm} standards.
 It also respects the partition of unity principle over all frequency bins in the relevant range.
@@
 This occurence is likely due to the distribution observed by the data prior to Huffman encoding.
-
-\ml{pourquoi parler d'overlap ici, alors que le codeur ne doit en utiliser ?}
 
@@
 \end{figure}
-
-\fg{figures a refaire}
 \section{Conclusion}

### 2017-06-19 paper/article.tex
abstract done

@@
 
-\author{Felix Gontier, Mathieu Lagrange, Arnaud Can, Catherine Lavandier}
+\author{F\'elix Gontier, Mathieu Lagrange, Pierre Aumond, Arnaud Can, Catherine Lavandier}
 
-\address{felix.gontier@reseau.eseo.fr \\ mathieu.lagrange@cnrs.fr}
+\address{felix.gontier@reseau.eseo.fr}
 
@@
 
-The acoustic environment represents both societal and environmental concerns, in particular for cities that are subjected to a multitude of noise sources and that count de facto numerous exposed people.
+The acoustic environment represents both societal and environmental concerns.
+Monitoring the acoustic environnment in urban but also rural or wilderness areas is therefore an important matter.
+Fostering on the recent development of low cost hardware acoustic sensors, we propose to consider a sensor grid approach to tackle this issue.
 
-In this context, monitoring the acoustic environnment in urban but also rural or wilderness areas is an important matter.
-Fostering on the recent development of low cost hardware acoustic sensors, we propose to using a sensor grid approach.
+In this kind of approach, the crucial question is the nature of the data that is transmitted from the sensors to the processing and archival servers.
+To this end, we propose an efficient audio coding scheme based on third octave band spectral representation that allows 1) the estimation of most acousitc indicators and 2) the recognition of acoustic events at state of the art performance rate.
+The former is useful to provide quantitative information about the acoustic environment, while the latter is useful to gather more qualitative information and build perceptually motivated indicators using for example some emergence of a given sound source.
 
-audio sensing
-
-audio encoding
+The coding scheme is also demonstrated to transmit spectrally encoded data that, reverted to the time domain using state of the art techniques, is not intelligible, thus protecting the privacy of citizens.
 

### 2017-06-22 paper/article.tex
Paper update

@@
 The former is efficient in terms of data storage as only the detection events are transmitted and is thus currently considered in several approaches \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
-Though, it requires the availability of computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware d not allow them to be autonomous using power sources like decent size solar panels.
+Though, it requires the availability of computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware do not allow them to be autonomous using power sources like decent size solar panels.
 Furthermore, the detection is done once and cannot be recomputed during posterior analyses.
@@
 
-However, transmitting the raw audio through the network has several disavantages, in terms of required bandwidth, storage capabilities and privacy.Thus, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way.
+However, transmitting the raw audio through the network has several disavantages, in terms of required bandwidth, storage capabilities and privacy.
+Thus, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way.
 Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.
@@
 In order to promote reproducible research, the coder as well as the experiments needed to generate the figures will be made available to the community.
-The remaining of the paper is organized as follows: Section \ref{sec:background} reviews the types of data that needs to be estimated using the transmitted data and Section \ref{sec:coder} describes the proposed encoding schemeSection.
-the experimental protocol designed to validate the proposed approach is described in Section \ref{sec:protocol} and results are discussed in Section \ref{sec:results}.
+The remaining of the paper is organized as follows: Section \ref{sec:background} reviews the types of data that needs to be estimated using the transmitted data and Section \ref{sec:coder} describes the proposed encoding scheme.
+The experimental protocol designed to validate the proposed approach is described in Section \ref{sec:protocol} and results are discussed in Section \ref{sec:results}.
 
@@
 	\centering
-		\includegraphics[width=\columnwidth]{tob_imp.eps}
+		\includegraphics[width=\columnwidth]{figures/tob_imp.eps}
 	\caption{Comparison of Couvreur's and Antoni's implementations of third-octave filters. Frequency-weighting allows for arbitrary transfer functions and thus more accurate gains as standards impose.}
@@
 	\centering
-		\includegraphics[width=0.5\textwidth]{pdf.eps}
+		\includegraphics[width=0.5\textwidth]{figures/pdf.eps}
 	\caption{Example of estimated probability density functions of the data throughout the encoding step.
@@
 	\centering
-		\includegraphics[width=\columnwidth]{dict_comp.eps}
+		\includegraphics[width=\columnwidth]{figures/dict_comp.eps}
 	\caption{Performance comparison of locally and globally generated Huffman dictionnaries.
@@
 	\centering
-		\includegraphics[width=1\textwidth]{scheme.pdf}
+		\includegraphics[width=1\textwidth]{figures/scheme.pdf}
 	\caption{Overview of the coder process.}
@@
 The coder's output bitrate as well as additional measurement error is computed for both data representations : third-octave and Mel.
-It is expressed in dB and compared to the IEC 61672-1:2013 standard on sound level meter tolerance.
+It is expressed in dB and compared to the IEC 61672-1:2013 standard \cite{iec-norm2} on sound level meter tolerance.
 This is to verify that the quantization step yields a maximum absolute error inferior to the precision of the target recording device.
@@
 	\centering
-		\includegraphics[width=\columnwidth]{freq.png}
+		\includegraphics[width=\columnwidth]{figures/freq.png}
 	\caption{Third-octave bands analysis and approximate inverse transformation effects on energy location.
@@
 	\centering
-		\includegraphics[width=\columnwidth]{bitrate_qall.eps}
+		\includegraphics[width=\columnwidth]{figures/bitrate_qall.eps}
 	\caption{Coder output bitrate as a function of quantization for third-octave and mel bands with 8 frames per second.}
@@
 	\centering
-		\includegraphics[width=\columnwidth]{bitrate_mel_avg.eps}
+		\includegraphics[width=\columnwidth]{figures/bitrate_mel_avg.eps}
 	\caption{Impact of representation resolution on the encoded data bitrate.}
@@
 	\centering
-		\includegraphics[width=\columnwidth]{error_qall.eps}
+		\includegraphics[width=\columnwidth]{figures/error_qall.eps}
 	\caption{Measurement error induced by encoding for different quantization resolutions.}
@@
 As $\Delta_x$ is sampled for each analysis frame in our implementation, the error has the same statistics across all bands.
-We compare the observed values against those specified in the IEC 61672-1:2013 \ml{norm ?
-please cite} for $f = 1~kHz$ as it is where the most accurate measurements are expected.
+We compare the observed values against those specified in the IEC 61672-1:2013 \cite{iec-norm2} for $f = 1~kHz$ as it is where the most accurate measurements are expected.
 For class 1 and 2 sound level meters, the tolerance is set at about $\pm 1~dB$ and $\pm 1.5~dB$ respectively.
@@
 	\centering
-		\includegraphics[width=\columnwidth]{class_mel_q.eps}
+		\includegraphics[width=\columnwidth]{figures/class_mel_q.eps}
 	\caption{Classification accuracy as a function of word size before encoding. The baseline on the right is computed without quantizing the representation.}
@@
 \centering
-\caption{Classification accuracy for varying representation resolutions}
+\caption{Classification accuracy for varying representation resolutions, in percentages for clarity}
 \label{T1}
@@
 \multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} & 0.55$\pm$0.03 & 0.60$\pm$0.03 & 0.61$\pm$0.04 & 0.62$\pm$0.03 & 0.62$\pm$0.04 & \textbf{0.63$\pm$0.06} & \textbf{0.65$\pm$0.06} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{10} & 55$\pm$3 & 60$\pm$3 & 61$\pm$4 & 62$\pm$3 & 62$\pm$4 & \textbf{63$\pm$6} & \textbf{65$\pm$6} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & 0.58$\pm$0.04 & 0.62$\pm$0.04 & 0.63$\pm$0.04 & 0.64$\pm$0.04 & 0.63$\pm$0.04 & \textbf{0.65$\pm$0.05} & \textbf{0.67$\pm$0.06} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{20} & 58$\pm$4 & 62$\pm$4 & 63$\pm$4 & 64$\pm$4 & 63$\pm$4 & \textbf{65$\pm$0.05} & \textbf{67$\pm$6} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & 0.60$\pm$0.03 & 0.64$\pm$0.04 & 0.64$\pm$0.04 & \textbf{0.65$\pm$0.04} & \textbf{0.65$\pm$0.03} & \textbf{0.67$\pm$0.04} & \textbf{\textcolor{red}{0.68$\pm$0.04}} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{30} & 60$\pm$3 & 64$\pm$4 & 64$\pm$4 & \textbf{65$\pm$4} & \textbf{65$\pm$3} & \textbf{67$\pm$4} & \textbf{\textcolor{red}{68$\pm$4}} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & 0.60$\pm$0.03 & 0.63$\pm$0.04 & \textbf{0.64$\pm$0.04} & 0.64$\pm$0.04 & \textbf{0.64$\pm$0.04} & \textbf{0.66$\pm$0.04} & \textbf{0.68$\pm$0.05} \\ \cline{1-9}
+ & \multicolumn{1}{|c|}{40} & 60$\pm$3 & 63$\pm$4 & \textbf{64$\pm$4} & 64$\pm$4 & \textbf{64$\pm$4} & \textbf{66$\pm$4} & \textbf{68$\pm$5} \\ \cline{1-9}
 \end{tabular}
@@
 \multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} & 0.60$\pm$0.03 & 0.62$\pm$0.03 & 0.62$\pm$0.03 & 0.63$\pm$0.03 & 0.63$\pm$0.03 & \textbf{0.65$\pm$0.04} & \textbf{0.67$\pm$0.05} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{10} & 60$\pm$3 & 62$\pm$3 & 62$\pm$3 & 63$\pm$3 & 63$\pm$3 & \textbf{65$\pm$4} & \textbf{67$\pm$5} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & 0.61$\pm$0.04 & 0.63$\pm$0.03 & 0.64$\pm$0.03 & 0.64$\pm$0.03 & 0.64$\pm$0.04 & \textbf{0.66$\pm$0.06} & \textbf{0.69$\pm$0.06} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{20} & 61$\pm$4 & 63$\pm$3 & 64$\pm$3 & 64$\pm$3 & 64$\pm$4 & \textbf{66$\pm$6} & \textbf{69$\pm$6} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & 0.62$\pm$0.03 & 0.63$\pm$0.03 & 0.64$\pm$0.03 & 0.64$\pm$0.03 & 0.64$\pm$0.04 & \textbf{0.67$\pm$0.05} & \textbf{\textcolor{red}{0.69$\pm$0.06}} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{30} & 62$\pm$3 & 63$\pm$3 & 64$\pm$3 & 64$\pm$3 & 64$\pm$4 & \textbf{67$\pm$5} & \textbf{\textcolor{red}{69$\pm$6}} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & 0.62$\pm$0.04 & 0.63$\pm$0.04 & 0.63$\pm$0.04 & 0.64$\pm$0.04 & 0.63$\pm$0.04 & \textbf{0.67$\pm$0.06} & \textbf{0.68$\pm$0.06} \\ \cline{1-9}
+ & \multicolumn{1}{|c|}{40} & 62$\pm$4 & 63$\pm$4 & 63$\pm$4 & 64$\pm$4 & 63$\pm$4 & \textbf{67$\pm$6} & \textbf{68$\pm$6} \\ \cline{1-9}
 \end{tabular}
@@
 	\centering
-		\includegraphics[width=\columnwidth]{class_tob_q.eps}
+		\includegraphics[width=\columnwidth]{figures/class_tob_q.eps}
 	\caption{Classification accuracy with third-octave bands and varying word size.}
@@
 We thus compute these metrics for the SVM classifier, with predictions cumulated over the ten folds in test configuration.
-Results are visible in Figure~\ref{fig:tob_conf} and Figure~\ref{fig:mel_conf}.
 The analogous natures of the two descriptors is highlighted by close one-versus-one differentiation performances, with a slightly lower accuracy for third-octave bands on average.
-A noticeable difference is that on the log-frequency scale the bandwidth of mel filters narrows as frequency increases while third-octave are evenly distributed.
-The effect of this can be seen between classes 5 and 8 (resp.
-\textit{Drilling} and \textit{Jackhammer}).
+Both representations yield best results for the \textit{Gun shot} class with 88.2\% for third-octave cepstra and 86.6\% for mel cepstra.
+Their poorest accuracy is on the \textit{Air conditioning} class with 32.0\% and 38.1\% respectively.
+However, a noticeable difference between them is that on the log-frequency scale the bandwidth of mel filters narrows as frequency increases, while third-octave are evenly distributed.
+The effect of this can be seen between classes \textit{Drilling} and \textit{Jackhammer}.
 These sounds involve important low-frequency information which can generally differentiate them, leading third-octave descriptors to perform better.
-Conversely this improves globally class 1 (\textit{Air conditioning}) recognition as most of its defining components are situated in higher frequencies.\\
+Conversely, using mel-based cepstra improves globally \textit{Air conditioning} recognition as most of its defining components are situated in higher frequencies.\\
 
-Each descriptor is thus found to have similar representational capabilities despite minor construction differences.
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=\columnwidth]{tob_conf.eps}
-	\caption{Confusion matrix of the SVM classification on third-octave bands with $q = 8$.}
-	\label{fig:tob_conf}
-\end{figure}
-
-\begin{figure}[h!]
-	\centering
-		\includegraphics[width=\columnwidth]{mel_conf.eps}
-	\caption{Confusion matrix for the same setup with 40 mel bands.}
-	\label{fig:mel_conf}
-\end{figure}
+Both descriptor are thus found to have similar representational capabilities despite minor construction differences.
 
@@
 Figure~\ref{fig:percint_mel_avg} presents the results of the preliminar perceptual test for the same setup.
-For this test, subjects were asked to blindly listen to recovered speech audio with different representation and coding parameters.
+%For this test, subjects were asked to blindly listen to recovered speech audio with different representation and coding parameters.
 They had to rate each extract between 0 ans 5, respectively inintelligible and perfectly comprehensible.
@@
 
-The CSII accounts for the whole spectrogram distance between clean and distorted audio at each point in time and frequency.
+%The CSII accounts for the whole spectrogram distance between clean and distorted audio at each point in time and frequency.
 This includes the phase, which we discard early in the representation step.
@@
 
-Alternatively, the frequency-weighted segmental SNR considers only spectrogram magnitudes.
+%Alternatively, the frequency-weighted segmental SNR considers only spectrogram magnitudes.
 As a result, distance is generally lower and a more representative of the induced perceptual distortion.
@@
 	\centering
-		\includegraphics[width=\columnwidth]{csii_mel_avg.eps}
+		\includegraphics[width=\columnwidth]{figures/csii_mel_avg.eps}
 	\caption{The Coherence SII objective indicator computed for intelligibility assessment.
@@
 	\centering
-		\includegraphics[width=\columnwidth]{fwsnrseg_mel_avg.eps}
+		\includegraphics[width=\columnwidth]{figures/fwsnrseg_mel_avg.eps}
 	\caption{Frequency-weighted segmental SNR for the same parameters.}
@@
 	\centering
-		\includegraphics[width=\columnwidth]{percint_mel_avg.eps}
+		\includegraphics[width=\columnwidth]{figures/percint_mel_avg.eps}
 	\caption{Results of the perceptual intelligibility test.}
@@
 %% TeX file.
-\section{References}
 
@@
 
-\ml{USE BIBTEX !!}
-
-\begin{thebibliography}{09}
-
-\bibitem{gozalo2015}
-Rey Gozalo, G.
+%\ml{USE BIBTEX !!}
+%\bibliography{mybib}{}
+%
+%
+%\begin{thebibliography}{09}
+%
+%\bibitem{gozalo2015}
+%Rey Gozalo, G.
 and Trujillo Carmona, J.
@@
 1-10
-
-\bibitem{rychtarikova2013}
-Rychtarikova, M. and Vermeir, G. (2013). Soundscape categorization on the basis of objective acoustical parameters. \textit{Applied Acoustics}, 74(2), pp. 240-247
-
-\bibitem{can2016}
-Can, A.
+%
+%\bibitem{rychtarikova2013}
+%Rychtarikova, M. and Vermeir, G. (2013). Soundscape categorization on the basis of objective acoustical parameters. \textit{Applied Acoustics}, 74(2), pp. 240-247
+%
+%\bibitem{can2016}
+%Can, A.
 and Aumond, P.
@@
 5678-5686
-
-\bibitem{can2015}
-Can, A. and Gauvreau, B. (2015). Describing and classifying urban sound environments with a relevant set of physical indicators. \textit{J. Ac. Soc. Am.}, 137(1), pp. 208-218
-
-\bibitem{brocolini2013}
-Brocolini, L.
+%
+%\bibitem{can2015}
+%Can, A. and Gauvreau, B. (2015). Describing and classifying urban sound environments with a relevant set of physical indicators. \textit{J. Ac. Soc. Am.}, 137(1), pp. 208-218
+%
+%\bibitem{brocolini2013}
+%Brocolini, L.
 and Lavandier, C.
@@
 813-821
-
-\bibitem{nilsson2007}
-Nilsson, M.
+%
+%\bibitem{nilsson2007}
+%Nilsson, M.
 and Botteldooren, D.
@@
 In: \textit{Proceedings of the 19th International Congress on Acoustics}
-
-\bibitem{ishiyama2000}
-Ishiyama, T. and Hashimoto, T. (2000). The impact of sound quality on annoyance caused by road traffc noise: an influence of frequency spectra on annoyance. \textit{JSAE Review}, 21(2), pp. 225-230
-
-\bibitem{torija2013}
-Torija, A.
+%
+%\bibitem{ishiyama2000}
+%Ishiyama, T. and Hashimoto, T. (2000). The impact of sound quality on annoyance caused by road traffc noise: an influence of frequency spectra on annoyance. \textit{JSAE Review}, 21(2), pp. 225-230
+%
+%\bibitem{torija2013}
+%Torija, A.
 and Ruiz, D.
@@
 791-802
-
-\bibitem{anusuya2009}
-Anusuya, M. and Katty, S. (2009).  Speech recognition by machine, a review. \textit{International Journal of Computer Science and Information Security}, 6(3), pp. 181-205
-
-\bibitem{tzanetakis2002}
-Tzanztakis, G. and Essl, G. and Cook, P. (2002). Automatic musical genre classification of audio signals. \textit{IEEE Transactions on Speech and Audio Processing}, 10(5), pp. 293-302
-
-\bibitem{ntalampiras2014}
-Ntalampiras, S. (2014). Universal background modeling for acoustic surveillance of urban traffic. \textit{Digital Signal Processing}, 31, pp. 69-78
-
-\bibitem{aucouturier2007}
-Aucouturier, J.
+%
+%\bibitem{anusuya2009}
+%Anusuya, M. and Katty, S. (2009). Speech recognition by machine, a review. \textit{International Journal of Computer Science and Information Security}, 6(3), pp. 181-205
+%
+%\bibitem{tzanetakis2002}
+%Tzanztakis, G. and Essl, G. and Cook, P. (2002). Automatic musical genre classification of audio signals. \textit{IEEE Transactions on Speech and Audio Processing}, 10(5), pp. 293-302
+%
+%\bibitem{ntalampiras2014}
+%Ntalampiras, S. (2014). Universal background modeling for acoustic surveillance of urban traffic. \textit{Digital Signal Processing}, 31, pp. 69-78
+%
+%\bibitem{aucouturier2007}
+%Aucouturier, J.
 and Defreville, B.
@@
 881-891
-
-\bibitem{foggia2015}
-Foggia, P.
+%
+%\bibitem{foggia2015}
+%Foggia, P.
 and Petkov, N.
@@
 22-28
-
-\bibitem{kumar2016}
-Kumar, A. and Raj, B. (2016). Features and Kernels for Audio Event Recognition. \textit{arXiv Preprint}, Available at: \url{https://arxiv.org/abs/1607.05765}
-
-\bibitem{radhakrishnan2005}
-Radhakrishnan, R. and Divakaran, A. and Smaragdis, P. (2005). Audio analysis for surveillance applications. In: \textit{IEEE Workshop on Applications of Signal Processing to Audio and Acoustics}
-
-\bibitem{salamon2017}
-Salamon, J. and Bello, J. (2017). Deep convolutional neural networks and data augmentation for environmental sound classification. \textit{IEEE Signal Processing Letters}, 24(3), pp. 279-283
-
-\bibitem{piczak2015}
-Piczak, K. (2015). Environmental sound classification with convolutional neural networks. In: \textit{IEEE 25th International Workshop on Machine Learning for Signal Processing}
-
-\bibitem{khunarsal2013}
-Khunarsal, P. and Lursinsap, C. and Raicharoen, T. (2013). Very short time environmental sound classification based on spectrogram pattern matching. \textit{Information Sciences}, 243, pp. 57-74
-
-\bibitem{couvreur2004}
-Couvreur, L.
+%
+%\bibitem{kumar2016}
+%Kumar, A. and Raj, B. (2016). Features and Kernels for Audio Event Recognition. \textit{arXiv Preprint}, Available at: \url{https://arxiv.org/abs/1607.05765}
+%
+%\bibitem{radhakrishnan2005}
+%Radhakrishnan, R. and Divakaran, A. and Smaragdis, P. (2005). Audio analysis for surveillance applications. In: \textit{IEEE Workshop on Applications of Signal Processing to Audio and Acoustics}
+%
+%\bibitem{salamon2017}
+%Salamon, J. and Bello, J. (2017). Deep convolutional neural networks and data augmentation for environmental sound classification. \textit{IEEE Signal Processing Letters}, 24(3), pp. 279-283
+%
+%\bibitem{piczak2015}
+%Piczak, K. (2015). Environmental sound classification with convolutional neural networks. In: \textit{IEEE 25th International Workshop on Machine Learning for Signal Processing}
+%
+%\bibitem{khunarsal2013}
+%Khunarsal, P. and Lursinsap, C. and Raicharoen, T. (2013). Very short time environmental sound classification based on spectrogram pattern matching. \textit{Information Sciences}, 243, pp. 57-74
+%
+%\bibitem{couvreur2004}
+%Couvreur, L.
 and Laniray, M.
@@
 In: \textit{The 33rd International Congress and Exposition on Noise Control Engineering}
-
-\bibitem{cai2006}
-Cai, R.
+%
+%\bibitem{cai2006}
+%Cai, R.
 and Lu, L.
@@
 1026-1039
-
-\bibitem{chu2009}
-Chu, S.
+%
+%\bibitem{chu2009}
+%Chu, S.
 and Narayanan, S.
@@
 1142-1158
-
-\bibitem{salamon2015-2}
-Salamon, J. and Bello, J. (2015). Unsupervised feature learning for urman sound classification. In: \textit{2015 IEEE International Conference on Acoustics, Speech and Signal Processing}
-
-\bibitem{bauge2013}
-Baugé, C.
+%
+%\bibitem{salamon2015-2}
+%Salamon, J. and Bello, J. (2015). Unsupervised feature learning for urman sound classification. In: \textit{2015 IEEE International Conference on Acoustics, Speech and Signal Processing}
+%
+%\bibitem{bauge2013}
+%Baugé, C.
 and Lagrange, M.
@@
 In: \textit{2013 IEEE International Conference on Acoustics, Speech and Signal Processing}
-
-\bibitem{salamon2015}
-Salamon, J. and Bello, J. (2015). Feature learning with deep scattering for urban sound analysis. In: \textit{23rd European Signal Processing Conference}
-
-\bibitem{chachada2013}
-Chachada, S. and Kuo, C. (2013). Environmental sound recognition: A survey. In: \textit{2013 Asia-Pacific Signal and Information Processing Association Annual Summit and Conference}
-
-\bibitem{davis1986}
-Davis, S. (1986). Octave and fractional-octave band digital filtering based on the proposed ANSI standard. In: \textit{1986 IEEE International Conference on Acoustics, Speech and Signal Processing}
-
-\bibitem{ellis2005}
-Ellis, D. (2005). \textit{{PLP} and {RASTA} (and {MFCC}, and inversion) in {M}atlab}. Available at: \url{http://www.ee.columbia.edu/~dpwe/resources/matlab/rastamat/}
-
-\bibitem{huffman1952}
-Huffman, D. (1952). A method for the construction of minimum-redundancy codes. \textit{Proceedings of the IRE}, 40(9), pp. 1098-1101
-
-\bibitem{antoni2010}
-Antoni, J. (2010). Orthogonal-like fractional-octave-band filters. \textit{J. Ac. Soc. Am.}, 127(2)
-
-\bibitem{couvreur}
-Couvreur, C. \textit{Implementation of a one-third-octave filter bank in Matlab}. Available at: \url{http://citeseer.ist.psu.edu/24150.html}
-
-\bibitem{griffin1984}
-Griffin, D. and Lim, J. (1984). Signal Estimation from Modified Short-Time Fourier Transform. \textit{IEEE Transactions on Acoustics, Speech, and Signal Processing}, 32(2)
-
-\bibitem{salamon2014}
-Salamon, J. and Jacoby, C. and Bello, J. (2014). A Dataset and Taxonomy for Urban Sound Research. \textit{Proceedings of the 22nd ACM international conference on Multimedia}
-
-\bibitem{kates2005}
-Kates, J. and Arehart, K. (2005). Coherence and the Speech Intelligibility Index. \textit{J. Ac. Soc. Am.}, 115(5)
-
-\bibitem{hu2008}
-Hu, Y. and Loizou, P. (2008). Evaluation of objective quality measures for speech enhancement. \textit{IEEE Transactions on Audio, Speech, and Language Processing}, 16(1)
-
-\bibitem{ma2009}
-Ma, J. and Hu, Y. and Loizou, P. (2009). Objective measures for predicting speech intelligibility in noisy conditions based on new band-importance functions. \textit{J. Ac. Soc. Am.}, 125(5)
-
-\end{thebibliography}
+%
+%\bibitem{salamon2015}
+%Salamon, J. and Bello, J. (2015). Feature learning with deep scattering for urban sound analysis. In: \textit{23rd European Signal Processing Conference}
+%
+%\bibitem{chachada2013}
+%Chachada, S. and Kuo, C. (2013). Environmental sound recognition: A survey. In: \textit{2013 Asia-Pacific Signal and Information Processing Association Annual Summit and Conference}
+%
+%\bibitem{davis1986}
+%Davis, S. (1986). Octave and fractional-octave band digital filtering based on the proposed ANSI standard. In: \textit{1986 IEEE International Conference on Acoustics, Speech and Signal Processing}
+%
+%\bibitem{ellis2005}
+%Ellis, D. (2005). \textit{{PLP} and {RASTA} (and {MFCC}, and inversion) in {M}atlab}. Available at: \url{http://www.ee.columbia.edu/~dpwe/resources/matlab/rastamat/}
+%
+%\bibitem{huffman1952}
+%Huffman, D. (1952). A method for the construction of minimum-redundancy codes. \textit{Proceedings of the IRE}, 40(9), pp. 1098-1101
+%
+%\bibitem{antoni2010}
+%Antoni, J. (2010). Orthogonal-like fractional-octave-band filters. \textit{J. Ac. Soc. Am.}, 127(2), pp. 884–895
+%
+%\bibitem{couvreur}
+%Couvreur, C. \textit{Implementation of a one-third-octave filter bank in Matlab}. Available at: \url{http://citeseer.ist.psu.edu/24150.html}
+%
+%\bibitem{griffin1984}
+%Griffin, D. and Lim, J. (1984). Signal Estimation from Modified Short-Time Fourier Transform. \textit{IEEE Transactions on Acoustics, Speech, and Signal Processing}, 32(2), pp. 236-243
+%
+%\bibitem{salamon2014}
+%Salamon, J. and Jacoby, C. and Bello, J. (2014). A Dataset and Taxonomy for Urban Sound Research. \textit{Proceedings of the 22nd ACM international conference on Multimedia}
+%
+%\bibitem{kates2005}
+%Kates, J. and Arehart, K. (2005). Coherence and the Speech Intelligibility Index. \textit{J. Ac. Soc. Am.}, 115(5), pp. 2224–2237
+%
+%\bibitem{hu2008}
+%Hu, Y. and Loizou, P. (2008). Evaluation of objective quality measures for speech enhancement. \textit{IEEE Transactions on Audio, Speech, and Language Processing}, 16(1), pp. 229–238
+%
+%\bibitem{ma2009}
+%Ma, J.
+and Hu, Y.
+and Loizou, P.
+(2009).
+Objective measures for predicting speech intelligibility in noisy conditions based on new band-importance functions.
+\textit{J.
+Ac.
+Soc.
+Am.}, 125(5), pp.
+3387–3405
+%
+%
+%\end{thebibliography}
 \end{document}

### 2017-06-22 censeCoder/ceco3decoder.m

@@ -118,6 +118,7 @@ for ind_fold = 1:length(X_desc)
                     end
                     x{ind_fold}{ind_file} = x_temp;
             end
+            audiowrite(['..\..\decoded_samples\Sample_mel_fps' num2str(setting.fps) '_mel' num2str(setting.mel) '_quant' num2str(setting.quant) '_' setting.phaserec '_' num2str(ind_file) '.wav'], x{ind_fold}{ind_file}./max(abs(x{ind_fold}{ind_file})), sr);
         elseif strcmp(setting.desc, 'tob')
             %% Normalisation
             if setting.quant ~= 0
@@ -158,14 +159,11 @@ for ind_fold = 1:length(X_desc)
                     end
                     x{ind_fold}{ind_file} = x_temp;
             end
+            audiowrite(['..\..\decoded_samples\Sample_th_oct_quant' num2str(setting.quant) '_hop' num2str(setting.tobhop) '_' setting.phaserec '_' num2str(ind_file) '.wav'], x{ind_fold}{ind_file}./max(abs(x{ind_fold}{ind_file})), sr);
         end
     end
 end
-if strcmp(setting.desc, 'mel')
-    audiowrite(['..\..\decoded_samples\Sample_mel_fps' num2str(setting.fps) '_mel' num2str(setting.mel) '_quant' num2str(setting.quant) '_' setting.phaserec '.wav'], x{1}{1}./max(abs(x{1}{1})), sr);
-elseif strcmp(setting.desc, 'tob')
-    audiowrite(['..\..\decoded_samples\Sample_th_oct_quant' num2str(setting.quant) '_' setting.phaserec '.wav'], x{1}{1}./max(abs(x{1}{1})), sr);
-end
+
 %% Outputs
 % Store
 store.x_rec = x;

### 2017-06-22 censeCoder/cecoReport.m

@@ -79,13 +79,13 @@ if nargin==0, censeCoder('report', 'r'); return; end%censeCoder('report', 'rhv')
 %%% Class
 % Fixed: Mel - 30, Avg - None
 % Varying: Quant - All>0
-% config = expExpose(config, 'p', 'mask', {7, 4, 2:6, 1, 2, 10, 2, 0, -1, 1, -1, -1}, 'obs', 'cv_acc', 'save', 'mel_class_mel30_avg0_qall', 'step', 4, 'expand', 'quant');
+config = expExpose(config, 'p', 'mask', {7, 4, 2:6, 1, 2, 10, 2, 0, -1, 1, -1, -1}, 'obs', 'cv_acc', 'save', 'mel_class_mel40_avg0_qall', 'step', 4, 'expand', 'quant');
 % Fixed: Mel - 30, Avg - None, Quant - None
 % Varying: -
-% config = expExpose(config, 'p', 'mask', {7, 4, 1, -1, -1, -1, 2, 0, -1, 1, -1, -1}, 'obs', 'cv_acc', 'save', 'mel_class_mel30_avg0_q0', 'step', 4);
+config = expExpose(config, 'p', 'mask', {7, 4, 1, -1, -1, -1, 2, 0, -1, 1, -1, -1}, 'obs', 'cv_acc', 'save', 'mel_class_mel40_avg0_q0', 'step', 4);
 % Fixed: Quant - 8
 % Varying: Mel - All, Avg - All
-config = expExpose(config, 't', 'mask', {0, 0, 6, 1, 2, 10, 2, 1, -1, 1, -1, -1}, 'obs', 'cv_acc', 'save', 'mel_class_melall_avgall_q8', 'step', 4);
+% config = expExpose(config, 't', 'mask', {0, 0, 6, 1, 2, 10, 2, 1, -1, 1, -1, -1}, 'obs', 'cv_acc', 'save', 'mel_class_melall_avgall_q8', 'step', 4);
 
 %%% Intel
 % Fixed: Quant - 8

### 2017-06-22 censeCoder/report_figs.m

@@ -110,35 +110,35 @@ end
 % errorbar(13:10:43, data_csii.meanData(7, :), data_csii.stdData(7, :))
 % axis([-10 45 -0.7 -0.1]), grid on, legend(fps_lgd, 'location', 'northwest'), xlabel('Mel bands'); ylabel('CSII')
 
-load('report/figures/mel_fwSNRseg_melall_avgall_q8.mat');
-data_fwSNRseg = data;
-clear data;
-figure(1), clf
-
-errorbar(10:10:40, data_fwSNRseg.meanData(1, :), data_fwSNRseg.stdData(1, :))
-hold on,
-errorbar(10:10:40, data_fwSNRseg.meanData(2, :), data_fwSNRseg.stdData(2, :))
-errorbar(10:10:40, data_fwSNRseg.meanData(3, :), data_fwSNRseg.stdData(3, :))
-errorbar(10:10:40, data_fwSNRseg.meanData(4, :), data_fwSNRseg.stdData(4, :))
-errorbar(10:10:40, data_fwSNRseg.meanData(5, :), data_fwSNRseg.stdData(5, :))
-errorbar(10:10:40, data_fwSNRseg.meanData(6, :), data_fwSNRseg.stdData(6, :))
-errorbar(10:10:40, data_fwSNRseg.meanData(7, :), data_fwSNRseg.stdData(7, :))
-axis([-10 45 -15 5]), grid on, legend(fps_lgd, 'location', 'northwest'), xlabel('Mel bands'); ylabel('fwSNRseg (dB)')
-
-%% Mel_class_q
-% load('report/figures/mel_class_mel30_avg0_qall.mat');
-% data_qall = data;
-% load('report/figures/mel_class_mel30_avg0_q0.mat');
+% load('report/figures/mel_fwSNRseg_melall_avgall_q8.mat');
+% data_fwSNRseg = data;
+% clear data;
 % figure(1), clf
 % 
-% errorbar([8.44 8.48 8.52 8.56], data.meanData, data.stdData, 'xk', 'Linewidth', 1.5)
+% errorbar(10:10:40, data_fwSNRseg.meanData(1, :), data_fwSNRseg.stdData(1, :))
 % hold on,
-% errorbar([3.94:7.94 8.44], [data_qall.meanData(1, :) data.meanData(1)], [data_qall.stdData(1, :) data.stdData(1)])
[…]

### 2017-06-22 censeCoder/run_script.m

@@ -27,4 +27,7 @@ clear all, close all, clc;
 % censeCoder('do', [1 2 3 4], 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, 0, -1});
 % censeCoder('do', [4], 'mask', {4, 4, 6, 1, 2, 10, 2, 1, -1, 0, -1, 2});
  
-censeCoder('do', [1 2 3], 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, -1, -1});
+% censeCoder('do', [1 2 3], 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, -1, -1});
+% censeCoder('do', [3], 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, -1, -1});
+censeCoder('do', [1 2 3], 'mask', {-1, -1, 0, 1, 2, 10, 1, -1, 1, 2, -1, 1});
+censeCoder('do', [1 2 3], 'mask', {-1, -1, 0, 1, 2, 10, 1, -1, 1, 2, -1, 2});

### 2017-06-22 paper/article.tex
addition in intro

@@
 Second, the nodes shall be energy efficient in order ot ease the deployment of the sensors grid to the desired topology, ideally autonomous.
-Third, the data transfer used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to ensure the privacy of the citizen.
-Lastly, the data stored shall be as rich as possible while retaining a low bitrate for efficient transmission and storage
+Third, the encoding scheme used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to ensure the privacy of the citizen.
+Lastly, the data stored shall be as rich as possible while remaining a low bitrate for efficient transmission and storage.
 
@@
 However, transmitting the raw audio through the network has several disavantages, in terms of required bandwidth, storage capabilities and privacy.
-Thus, for transmission from the sensors to the storage unit, the data needs to be encoded in an efficient way.
+Thus, for transmission from the sensors to the storage unit, the data can be encoded in a more efficient way than lossy audio encoding standards \cite{pan1995tutorial} as the audio signal is not mandatory for the computation of the acoustic indicators and the features needed for event recognition.
 Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.

### 2017-06-22 paper/article.tex
Paper update

@@
 \centering
-\caption{Classification accuracy for varying representation resolutions, in percentages for clarity}
+\caption{Classification accuracy in percentage for different classifiers: SVMs (a), Random Forests (b), Decision Trees (c), and Nearest Neigbors (d) with respect to varying representation resolutions.
+Numbers in red indicate best performance and numbers in bold indicate statistical equivalent results compared to teh best performing setting.}
 \label{T1}
+(a)\\
 \begin{tabular}{ll|c|c|c|c|c|c|c|}
@@
 \end{tabular}
-
+\\(b)\\
 \begin{tabular}{ll|c|c|c|c|c|c|c|}
@@
 \end{tabular}
-
+\\(c)\\
 \begin{tabular}{ll|c|c|c|c|c|c|c|}
@@
 \multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} & 0.42$\pm$0.03 & \textbf{0.46$\pm$0.04} & 0.46$\pm$0.02 & 0.44$\pm$0.03 & 0.45$\pm$0.03 & \textbf{0.46$\pm$0.05} & \textbf{\textcolor{red}{0.49$\pm$0.03}} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{10} & 42$\pm$3 & \textbf{46$\pm$4} & 46$\pm$2 & 44$\pm$3 & 45$\pm$3 & \textbf{46$\pm$5} & \textbf{\textcolor{red}{49$\pm$3}} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & 0.43$\pm$0.05 & 0.43$\pm$0.03 & 0.43$\pm$0.02 & 0.44$\pm$0.03 & 0.45$\pm$0.03 & 0.45$\pm$0.05 & \textbf{0.47$\pm$0.05} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{20} & 43$\pm$5 & 43$\pm$3 & 43$\pm$2 & 44$\pm$3 & 45$\pm$3 & 45$\pm$5 & \textbf{47$\pm$5} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & 0.42$\pm$0.04 & 0.43$\pm$0.02 & 0.44$\pm$0.03 & 0.45$\pm$0.05 & 0.43$\pm$0.03 & 0.43$\pm$0.04 & \textbf{0.45$\pm$0.05} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{30} & 42$\pm$4 & 43$\pm$2 & 44$\pm$3 & 45$\pm$5 & 43$\pm$3 & 43$\pm$4 & \textbf{45$\pm$5} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & 0.42$\pm$0.06 & 0.43$\pm$0.03 & 0.43$\pm$0.03 & 0.42$\pm$0.03 & 0.44$\pm$0.03 & 0.46$\pm$0.03 & \textbf{0.46$\pm$0.04} \\ \cline{1-9}
+ & \multicolumn{1}{|c|}{40} & 42$\pm$6 & 43$\pm$3 & 43$\pm$3 & 42$\pm$3 & 44$\pm$3 & 46$\pm$3 & \textbf{46$\pm$4} \\ \cline{1-9}
 \end{tabular}
-
+\\(d)\\
 \begin{tabular}{ll|c|c|c|c|c|c|c|}
@@
 \multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} &0.43$\pm$0.02 & 0.51$\pm$0.04 & 0.53$\pm$0.04 & 0.53$\pm$0.05 & 0.53$\pm$0.04 & 0.54$\pm$0.04 & \textbf{0.56$\pm$0.03} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{10} &43$\pm$2 & 51$\pm$4 & 53$\pm$4 & 53$\pm$5 & 53$\pm$4 & 54$\pm$4 & \textbf{56$\pm$3} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & 0.44$\pm$0.03 & 0.52$\pm$0.04 & 0.53$\pm$0.03 & 0.54$\pm$0.04 & \textbf{0.54$\pm$0.04} & \textbf{0.55$\pm$0.04} & \textbf{\textcolor{red}{0.58$\pm$0.04}} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{20} & 44$\pm$3 & 52$\pm$4 & 53$\pm$3 & 54$\pm$4 & \textbf{54$\pm$4} & \textbf{55$\pm$4} & \textbf{\textcolor{red}{58$\pm$4}} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & 0.45$\pm$0.04 & 0.54$\pm$0.05 & \textbf{0.55$\pm$0.05} & \textbf{0.55$\pm$0.04} & \textbf{0.55$\pm$0.04} & \textbf{0.56$\pm$0.04} & \textbf{0.56$\pm$0.04} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{30} & 45$\pm$4 & 54$\pm$5 & \textbf{55$\pm$5} & \textbf{55$\pm$4} & \textbf{55$\pm$4} & \textbf{56$\pm$4} & \textbf{56$\pm$4} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & 0.46$\pm$0.03 & 0.53$\pm$0.05 & \textbf{0.55$\pm$0.05} & \textbf{0.55$\pm$0.04} & \textbf{0.55$\pm$0.05} & \textbf{0.57$\pm$0.04} & \textbf{0.57$\pm$0.03} \\ \cline{1-9}
+ & \multicolumn{1}{|c|}{40} & 46$\pm$3 & 53$\pm$5 & \textbf{55$\pm$5} & \textbf{55$\pm$4} & \textbf{55$\pm$5} & \textbf{57$\pm$4} & \textbf{57$\pm$3} \\ \cline{1-9}
 \end{tabular}
+
 \end{table*}
@@
 Following the previous discussions, the classification task is run on corresponding cepstra with a fixed 8 frames per second and 31 bands.
-Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps mel spectrograms seen in Table~\ref{T1} for all classification schemes.\\
+Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps mel spectrograms seen in Table~\ref{T1} for all classification schemes.
+In this table, equivalence of performance with respect to the best performing setting (in red) is evaluated using the following procedure.
+We evaluate the null hypothesis that the substraction of the two compared distribution (the distribution of the setting we consider minus the distribution of the best performing one) comes from a normal distribution with mean equal to zero and unknown variance, using the paired-sample t-test at the 0.05 significance level.
+If the null hypothesis is not rejected, the setting is considered as equivalent in terms of performance to the best performing one.
+\\
 

### 2017-06-22 censeCoder/report_figs.m
Commit clean

@@ -131,17 +131,14 @@ data_qall = data;
 load('report/figures/mel_class_mel40_avg0_q0.mat');
 figure(1), clf
 
-errorbar([0 8.94], [NaN data.meanData(1)], [NaN data.stdData(1)], 'x', 'Color', [0 0.4470 0.7410], 'Linewidth', 1.5)
+% errorbar([8.44 8.48 8.52 8.56], data.meanData, data.stdData, 'xk', 'Linewidth', 1.5)
 hold on,
-errorbar([0 8.98], [NaN data.meanData(2)], [NaN data.stdData(2)], '-x', 'Color', [0.9290 0.6940 0.1250], 'Linewidth', 1.5)
-errorbar([0 9.02], [NaN data.meanData(3)], [NaN data.stdData(3)], '-x', 'Color', [0.4940 0.1840 0.5560], 'Linewidth', 1.5)
-errorbar([0 9.06], [NaN data.meanData(4)], [NaN data.stdData(4)], '-x', 'Color', [0.4660 0.6740 0.1880], 'Linewidth', 1.5)
-errorbar([3.94:7.94], [data_qall.meanData(1, :)], [data_qall.stdData(1, :)], '-x', 'Color', [0 0.4470 0.7410])
-errorbar([3.98:7.98], [data_qall.meanData(2, :)], [data_qall.stdData(2, :)], '-x', 'Color', [0.9290 0.6940 0.1250])
-errorbar([4.02:8.02], [data_qall.meanData(3, :)], [data_qall.stdData(3, :)], '-x', 'Color', [0.4940 0.1840 0.5560])
-errorbar([4.06:8.06], [data_qall.meanData(4, :)], [data_qall.stdData(4, :)], '-x', 'Color', [0.4660 0.6740 0.1880])
+errorbar([3.94:7.94 8.44 8.94], [data_qall.meanData(1, :) NaN data.meanData(1)], [data_qall.stdData(1, :) NaN data.stdData(1)], '-x')
+errorbar([3.98:7.98 8.48 8.98], [data_qall.meanData(2, :) NaN data.meanData(2)], [data_qall.stdData(2, :) NaN data.stdData(2)], '-x')
+errorbar([4.02:8.02 8.52 9.02], [data_qall.meanData(3, :) NaN data.meanData(3)], [data_qall.stdData(3, :) NaN data.stdData(3)], '-x')
[…]

### 2017-06-22 censeCoder/report_figs.m
Figure/table update

@@ -131,14 +131,17 @@ data_qall = data;
 load('report/figures/mel_class_mel40_avg0_q0.mat');
 figure(1), clf
 
-% errorbar([8.44 8.48 8.52 8.56], data.meanData, data.stdData, 'xk', 'Linewidth', 1.5)
+errorbar([3.94:7.94], [data_qall.meanData(1, :)], [data_qall.stdData(1, :)], '-x', 'Color', [0 0.4470 0.7410])
 hold on,
-errorbar([3.94:7.94 8.44 8.94], [data_qall.meanData(1, :) NaN data.meanData(1)], [data_qall.stdData(1, :) NaN data.stdData(1)], '-x')
-errorbar([3.98:7.98 8.48 8.98], [data_qall.meanData(2, :) NaN data.meanData(2)], [data_qall.stdData(2, :) NaN data.stdData(2)], '-x')
-errorbar([4.02:8.02 8.52 9.02], [data_qall.meanData(3, :) NaN data.meanData(3)], [data_qall.stdData(3, :) NaN data.stdData(3)], '-x')
-errorbar([4.06:8.06 8.56 9.06], [data_qall.meanData(4, :) NaN data.meanData(4)], [data_qall.stdData(4, :) NaN data.stdData(4)], '-x')
+errorbar([3.98:7.98], [data_qall.meanData(2, :)], [data_qall.stdData(2, :)], '-x', 'Color', [0.8500 0.3250 0.0980])
+errorbar([4.02:8.02], [data_qall.meanData(3, :)], [data_qall.stdData(3, :)], '-x', 'Color', [0.9290 0.6940 0.1250])
+errorbar([4.06:8.06], [data_qall.meanData(4, :)], [data_qall.stdData(4, :)], '-x', 'Color', [0.4940 0.1840 0.5560])
+errorbar([8.44 8.94], [NaN data.meanData(1)], [NaN data.stdData(1)], 'x', 'Linewidth', 1.5, 'Color', [0 0.4470 0.7410])
+errorbar([8.44 8.98], [NaN data.meanData(2)], [NaN data.stdData(2)], 'x', 'Linewidth', 1.5, 'Color', [0.8500 0.3250 0.0980])
+errorbar([8.48 9.02], [NaN data.meanData(3)], [NaN data.stdData(3)], 'x', 'Linewidth', 1.5, 'Color', [0.9290 0.6940 0.1250])
[…]

### 2017-06-22 paper/article.tex
Commit clean
inteligibility

@@
 
-Intelligibility in decoded and reconstructed audio is also oan concerns of this study.
-It is indeed important that the produced scheme maintains a high level of recognition of acoustic events but, as the dat is transmitted over the network and potentially stored, the level of intelligibility of the decoded stream should be as low as possible.
+Intelligibility in decoded and reconstructed audio is also an important concern in this study.
+It is indeed important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data is transmitted over the network and potentially stored, the level of intelligibility of the decoded stream should be as low as possible.
+
+Forensic phonetics \cite{baldwin1990forensic}
+
+indice biométrique faible \cite{boe2000forensic}
+
+In order to decrease the intelligibility, several approaches can be considered.
+First,  a speech versus non speech detector can be implemented on the sensor.
+If some speech is detected, the data is not transmitted.
+This approach is prone to failure of the detector and will lead to unavailibility of data whcih might compromise the computation of some indicators.
+Second, as the speech is mostly concentrated at a given frequency region, a band pass filter from 1 kHz to $~$4-5 kHz could be considered in order to remove the formant information \cite{kent1992acoustic}.
+However, as some frequency bands are no longer available, the computation of the acoustic indicators is no longer possible.
+A third approach is to wisely choose the frame rate.
+Since a phoneme is about 100ms to 200ms long \cite{kuwabara1996acoustic} \cite{rosen1992temporal} a frame rate lower than 4 Hz should dramatically reduce intelligibility.
 
@@
 
-We thus provide the computation of two objective metrics: the Coherence Speech Intelligibility Index\cite{kates2005} (CSII) and frequency-weighted segmental SNR\cite{hu2008} (fwSNRseg) by comparing original unaltered samples and recovered audio.
+To evaluate the impact of the frame rate on intelligibility two objective metrics are considered: the Coherence Speech Intelligibility Index\cite{kates2005} (CSII) and frequency-weighted segmental SNR\cite{hu2008} (fwSNRseg) by comparing original unaltered samples and recovered audio.
 These two indicators have been shown to correlate well with perceptual tests\cite{ma2009}, although results are only available for lesser degradations and distortions than the ones we consider in this study.\\

### 2017-06-26 paper/article.tex
inteligibility
Intelligibility

@@
 To evaluate the impact of the frame rate on intelligibility two objective metrics are considered: the Coherence Speech Intelligibility Index\cite{kates2005} (CSII) and frequency-weighted segmental SNR\cite{hu2008} (fwSNRseg) by comparing original unaltered samples and recovered audio.
-These two indicators have been shown to correlate well with perceptual tests\cite{ma2009}, although results are only available for lesser degradations and distortions than the ones we consider in this study.\\
+These two indicators have been shown to correlate well with perceptual tests\cite{ma2009}, although results are only available for lesser degradations and distortions than the ones we consider in this study.
+For this reason, a small-scale perceptual test is also conducted.
+We use a dataset of clean speech recordings comprised of 9 french sentences enunciated by 3 male and 3 female speakers.
+The recordings are encoded with analysis frame rates of 50~Hz, 16~Hz, 8~Hz and 4~Hz for a total of 216 audio excerpts.
+At each test iteration, a listener is presented with sentences and asked both to transcribe the utterances and rate the global intelligibility between 1 and 5.
+Each sentence is tested twice in order to palliate the reduced number of participants.
+The listening bias induced is attenuated by using the 9 sentences only once for the two lower and higher frame rates.
+Furthermore, the global order of examples as well as speakers are randomized.
+Nine subjects of ages ranging from 17 to 60 and with normal hearing capacity participated.\\
 
@@
 Finally, objective intelligibility metrics are estimated for the studied parameters and compared to an informal perceptual evaluation \footnote{Decoded speech utterances for various conditions can be listened to at \url{http://}}.
-Figures~\ref{fig:csii_mel_avg} and \ref{fig:fwsnrseg_mel_avg} shows both the CSII and fwSNRseg indicators for varying representation dimensions.
-Figure~\ref{fig:percint_mel_avg} presents the results of the preliminar perceptual test for the same setup.
-%For this test, subjects were asked to blindly listen to recovered speech audio with different representation and coding parameters.
-They had to rate each extract between 0 ans 5, respectively inintelligible and perfectly comprehensible.
-We acknowledge that it is surely biased by a reduced number of participants and lack of tested audio material.
-However, it is sufficient to judge the relevance of objective indicators in our conditions as we can observe a correlation between the three metrics.
+Figures~\ref{fig:csii_tob_fps} and \ref{fig:fwsnrseg_tob_fps} shows both the CSII and fwSNRseg indicators for varying frames per second in analysis.
+Figure~\ref{fig:subj_int} presents the results of the preliminar perceptual test for the same setup.
+We acknowledge that it is surely biased by the reduced number of participants and scarcity of tested audio material.
+However, it is sufficient to judge the relevance of objective indicators in our conditions and study the intelligibility of fast acoustical measurements.\\
 
-%The CSII accounts for the whole spectrogram distance between clean and distorted audio at each point in time and frequency.
+Perceptual test results are in accordance with the formulated concerns.
+First, phonems separation is mandatory in order to ensure intelligibility.
+This implies an analysis frame rate significantly larger than that of phonems in the considered language.
+Here we observe a limit of about 10~Hz corresponding to a duration of 100~ms, rendering the studied 8~Hz measurements inintelligible.
+Few words were understood correctly as a result of coincidentally adequate frame timings, ie.
+analysis frames matching phonem utterances for a short duration.
+Similarly, framing effects induced by the proposed processing scheme yielded errors for higher fps transcriptions and a globally lower comprehension as perceived by the subjects.\\
+
+The CSII accounts for the spectrogram distance between clean and distorted audio at each point in time and frequency.
 This includes the phase, which we discard early in the representation step.
-The error induced by forward and inverse mel bands transformation as well as operations reducing data dimensionality further contribute to very high distances.
+The error induced by forward and inverse third-octave bands transformation as well as operations reducing data dimensionality further contribute to very high point-wise disparities.
 In fact, the signal is too distorted for the proposed SNR normalization to ensure CSII values in the 0-1 range.
-The indicator differs from perceptual evaluations for middle-valued frame rates, with for example the 9.5 fps curve being lower than expected.
-Values are also very close for multiple parameter combinations where a threshold between intelligibility and inintelligibility could be found.
-This is therefore not an adequate indicator for our purpose.\\
+When compared to perceptual test results, the CSII shows no clear separation in the 10 frames per second neighbourhood.
+It is therefore not a good indicator in our conditions.\\
 
-%Alternatively, the frequency-weighted segmental SNR considers only spectrogram magnitudes.
+Alternatively, the frequency-weighted segmental SNR considers only spectrogram magnitudes.
 As a result, distance is generally lower and a more representative of the induced perceptual distortion.
-Nevertheless, the fwSNRseg still uses point-wise comparison.
-A shape seems to appear where the influences of frame rate and mel bands on output are decorrelated, ie.
-almost the same curve is offset as a function of frame rate.
-While the values are still concentrated around the critical threshold location at about -5~dB, this metric is likely a better indicator due to its approach of the clean-reconstructed signal distance.
-\ml{incrompehnsible}
+Nevertheless, the fwSNRseg still uses a point-wise comparison which is certainly too precise for the studied degradations.
+Its shape seems more accurate at higher frame rates where intelligibility is almost constant.
+The previously observed threshold is however absent as the curve present a smoother increase trend, and the difference between 8~Hz and 16~Hz is not significant enough to correlate with subjective measurements.\\
 
@@
 	\centering
-		\includegraphics[width=\columnwidth]{figures/csii_mel_avg.eps}
+		\includegraphics[width=\columnwidth]{figures/csii_tob_fps.eps}
 	\caption{The Coherence SII objective indicator computed for intelligibility assessment.
 Negative CSII values indicate a signal-to-noise ratio too low for the recommended normalization, thus severe disparities between the original and reconstructed signal.}
-	\label{fig:csii_mel_avg}
+	\label{fig:csii_tob_fps}
 \end{figure}
@@
 	\centering
-		\includegraphics[width=\columnwidth]{figures/fwsnrseg_mel_avg.eps}
-	\caption{Frequency-weighted segmental SNR for the same parameters.}
-	\label{fig:fwsnrseg_mel_avg}
+		\includegraphics[width=\columnwidth]{figures/fwsnrseg_tob_fps.eps}
+	\caption{Frequency-weighted segmental SNR with varying analysis frame rates around the considered 8~Hz value.
+This indicator shows a better correlation with subjective tests but lacks an inintelligibility threshold.}
+	\label{fig:fwsnrseg_tob_fps}
 \end{figure}
@@
 	\centering
-		\includegraphics[width=\columnwidth]{figures/percint_mel_avg.eps}
-	\caption{Results of the perceptual intelligibility test.}
-	\label{fig:percint_mel_avg}
+		\includegraphics[width=\columnwidth]{figures/subj_int.eps}
+	\caption{Results of the perceptual intelligibility test with subjective normalized for visibility.
+A limit for intelligibility appears at around 10~Hz, corresponding to the average duration of a phonem.}
+	\label{fig:subj_int}
 \end{figure}
 \section{Conclusion}
+
+\section{Acknowlegments}
+
+The authors would like to thank Christophe d'Alessandro for fruitful discussion on speech intelligibilty.
 

### 2017-06-26 censeCoder/ceco1representation.m

@@ -27,10 +27,10 @@ if strcmp(setting.desc, 'mel')
         disp(['Chosen FPS is ' num2str(setting.fps) ', actual one is ' num2str(n_fps/n_avg) '.']);
     end
 elseif strcmp(setting.desc, 'tob')
-    l_frame = (round(0.125*sr)-mod(round(0.125*sr), 2)); % Approximately 125ms, "fast" Leq
+    l_frame = (round(setting.toblen*sr)-mod(round(setting.toblen*sr), 2)); % Approximately 125ms, "fast" Leq
     l_hop = setting.tobhop*l_frame;
     %% Filterbank calculation, can be replaced with constant matrix
-    N = 2^13;
+    N = 2^(ceil(log2(l_frame)));
     N_filt = 2^17; % Design with a much greater precision
     G = third_octave_filterbank(sr, N_filt, -17:13);
     G = G(:, 1:round(N_filt/N):end); % Only take the resolution needed
@@ -51,6 +51,18 @@ switch setting.dataset
             if length(rush_names{ind_file}) > 4 && strcmp(rush_names{ind_file}(end-3:end), '.wav')
                 ind_wav = ind_wav+1;
                 file_path{1}{ind_wav} = [datapath rush_names{ind_file}];
+            end
+        end
+    case 'speech_mod'
+        if ispc; datapath = [config.inputPath 'rush_mod\']; else datapath = [config.inputPath 'rush_mod/']; end
+        rush_dir = dir(datapath);
+        rush_names = {rush_dir.name};
+        ind_wav = 0; % Real number of .wav files
+        for ind_file = 1:numel(rush_names)
+            if length(rush_names{ind_file}) > 4 && strcmp(rush_names{ind_file}(end-3:end), '.wav')
+                ind_wav = ind_wav+1;
+                file_path{1}{ind_wav} = [datapath rush_names{ind_file}];
+                wav_name{1}{ind_wav} = rush_names{ind_file};
             end
         end
     case 'urbansound8k'
@@ -131,6 +143,7 @@ for ind_fold = 1:length(file_path)
             X = stft(x, l_frame, l_hop, 'rect', 1)/sqrt(l_frame/2+1); % Energy conservation (Parseval theorem)
             n_frames{ind_fold}{ind_file} = size(X, 2); % Number of STFT windows before averaging, needed for reconstruction
[…]

### 2017-06-26 censeCoder/ceco2coder.m

@@ -38,7 +38,7 @@ if strcmp(setting.desc, 'mel')
         n_fps = 1+(sr-l_frame)/l_hop; % Number of frames per second with base settings
     end
 elseif strcmp(setting.desc, 'tob')
-    l_frame = (round(0.125*sr)-mod(round(0.125*sr), 2)); % Approximately 125ms, "fast" Leq
+    l_frame = (round(setting.toblen*sr)-mod(round(setting.toblen*sr), 2)); % Approximately 125ms, "fast" Leq
     l_hop = setting.tobhop*l_frame;
     n_fps = 1+(sr-l_frame)/l_hop;
 end
@@ -101,6 +101,7 @@ if strcmp(setting.desc, 'mel')
 end
 if setting.quant; store.q_norm = data.q_norm; end
 store.n_frames = data.n_frames;
+if strcmp(setting.dataset, 'speech_mod'); store.wav_name = data.wav_name; end
 
 % Observations
 obs.code_len = code_len;

### 2017-06-26 censeCoder/ceco3decoder.m

@@ -26,10 +26,10 @@ if strcmp(setting.desc, 'mel')
         n_avg = round(n_fps/setting.fps); % Number of consecutive frames to average into one
     end
 elseif strcmp(setting.desc, 'tob')
-    l_frame = (round(0.125*sr)-mod(round(0.125*sr), 2)); % Approximately 125ms, "fast" Leq
+    l_frame = (round(setting.toblen*sr)-mod(round(setting.toblen*sr), 2)); % Approximately 125ms, "fast" Leq
     l_hop = setting.tobhop*l_frame;
     %% Filterbank calculation, can be replaced with constant matrix
-    N = 2^13;
+    N = 2^(ceil(log2(l_frame)));
     N_filt = 2^17; % Design with a much greater precision
     G = third_octave_filterbank(sr, N_filt, -17:13);
     G = G(:, 1:round(N_filt/N):end); % Only take the resolution needed
@@ -155,11 +155,15 @@ for ind_fold = 1:length(X_desc)
                         x_stft = stft(x_temp, l_frame, l_hop, 'hamming', 1);
                         b = sqrt(sum(win(1:end/2+1)))*sqrt(Xw).*x_stft./abs(x_stft); % As described in G&L paper
                         % b = (sqrt(x_spec)/32768).*exp(1i*angle(x_stft)); % Also works
-                        x_temp = istft(b, l_frame, l_hop, 'hanning');
+                        x_temp = istft(b, l_frame, l_hop, 'hamming');
                     end
                     x{ind_fold}{ind_file} = x_temp;
             end
-            audiowrite(['..\..\decoded_samples\Sample_th_oct_quant' num2str(setting.quant) '_hop' num2str(setting.tobhop) '_' setting.phaserec '_' num2str(ind_file) '.wav'], x{ind_fold}{ind_file}./max(abs(x{ind_fold}{ind_file})), sr);
+            if ~strcmp(setting.dataset, 'speech_mod')
+                audiowrite(['..\..\decoded_samples\Sample_th_oct_quant' num2str(setting.quant) '_hop' num2str(setting.tobhop) '_' setting.phaserec '_len' num2str(setting.toblen) '_file' num2str(ind_file) '.wav'], x{ind_fold}{ind_file}./max(abs(x{ind_fold}{ind_file})), sr);
+            else
[…]

### 2017-06-26 censeCoder/cecoReport.m

@@ -79,10 +79,10 @@ if nargin==0, censeCoder('report', 'r'); return; end%censeCoder('report', 'rhv')
 %%% Class
 % Fixed: Mel - 30, Avg - None
 % Varying: Quant - All>0
-config = expExpose(config, 'p', 'mask', {7, 4, 2:6, 1, 2, 10, 2, 0, -1, 1, -1, -1}, 'obs', 'cv_acc', 'save', 'mel_class_mel40_avg0_qall', 'step', 4, 'expand', 'quant');
+% config = expExpose(config, 'p', 'mask', {7, 4, 2:6, 1, 2, 10, 2, 0, -1, 1, -1, -1}, 'obs', 'cv_acc', 'save', 'mel_class_mel40_avg0_qall', 'step', 4, 'expand', 'quant');
 % Fixed: Mel - 30, Avg - None, Quant - None
 % Varying: -
-config = expExpose(config, 'p', 'mask', {7, 4, 1, -1, -1, -1, 2, 0, -1, 1, -1, -1}, 'obs', 'cv_acc', 'save', 'mel_class_mel40_avg0_q0', 'step', 4);
+% config = expExpose(config, 'p', 'mask', {7, 4, 1, -1, -1, -1, 2, 0, -1, 1, -1, -1}, 'obs', 'cv_acc', 'save', 'mel_class_mel40_avg0_q0', 'step', 4);
 % Fixed: Quant - 8
 % Varying: Mel - All, Avg - All
 % config = expExpose(config, 't', 'mask', {0, 0, 6, 1, 2, 10, 2, 1, -1, 1, -1, -1}, 'obs', 'cv_acc', 'save', 'mel_class_melall_avgall_q8', 'step', 4);
@@ -92,7 +92,8 @@ config = expExpose(config, 'p', 'mask', {7, 4, 1, -1, -1, -1, 2, 0, -1, 1, -1, -
 % Varying: Mel - All, Avg - All
 % config = expExpose(config, 'p', 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, 1, -1}, 'obs', 'csii', 'save', 'mel_csii_melall_avgall_q8', 'step', 4, 'expand', 'mel');
[…]

### 2017-06-26 censeCoder/perc_int.m

@@ -1,81 +1,136 @@
 function perc_int(act)
 
+if ~nargin; act = 'disp'; end;
+
 switch act
     case 'test'
         if exist('subj_notes.mat', 'file')
             load('subj_notes.mat');
-            ind_test = size(subj_notes, 3)+1;
+            ind_test = length(subj_notes)+1;
         else
-            fps = [2 4 6 8 10 20 0];
-            mel = [10 20 30 40];
+            q = 8;
+            toblen = 1000*[0.02 0.06 0.125 0.25];
             ind_test = 1;
         end
-        subj_notes(:,:,ind_test) = zeros(length(fps), length(mel))-1;
+        n_sen = 9;
+        sen_sfx = {'_C_1', '_C_2', '_F_1', '_F_2', '_Q_1', '_Q_2', '_S_1', '_S_2', '_S_3'};
+        subj_notes{ind_test} = zeros(2*n_sen, 1)-1;
+        sentences_tr{ind_test} = cell(2*n_sen, 1);
+        sp_cnt = zeros(6, 1); % Speaker test count
+        
+        
+        
+        % High fps
+        sen = randperm(n_sen);
+        set_cnt = round(rand(1, 1))+4;
+        setting{ind_test}(:, 1:n_sen) = [sen; [ones(1, set_cnt) 2*ones(1, n_sen-set_cnt)]];
+        
+        % Low fps
+        sen = randperm(n_sen);
+        set_cnt = round(rand(1, 1))+4;
+        setting{ind_test}(:, n_sen+1:2*n_sen) = [sen; [3*ones(1, set_cnt) 4*ones(1, n_sen-set_cnt)]];
+        
+        rp = randperm(size(setting{ind_test}, 2));
+        setting{ind_test} = setting{ind_test}(:, rp);
 
-        disp('----- Perceptive test on intelligibility -----');
-        disp(['Test number ' num2str(ind_test) '.']);
-
-        fps_mel = combvec(fps, mel);
-        rp = randperm(length(fps)*length(mel));
-        fps_mel = fps_mel(:, rp);
-
-        for ind_setting = 1:size(fps_mel, 2)
-            disp(['Setting ' num2str(ind_setting) ' of ' num2str(size(fps_mel, 2)) '.']);
[…]

### 2017-06-26 censeCoder/report_figs.m

@@ -126,22 +126,22 @@ end
 % axis([-10 45 -15 5]), grid on, legend(fps_lgd, 'location', 'northwest'), xlabel('Mel bands'); ylabel('fwSNRseg (dB)')
 
 %% Mel_class_q
-load('report/figures/mel_class_mel40_avg0_qall.mat');
-data_qall = data;
-load('report/figures/mel_class_mel40_avg0_q0.mat');
-figure(1), clf
-
-errorbar([3.94:7.94], [data_qall.meanData(1, :)], [data_qall.stdData(1, :)], '-x', 'Color', [0 0.4470 0.7410])
-hold on,
-errorbar([3.98:7.98], [data_qall.meanData(2, :)], [data_qall.stdData(2, :)], '-x', 'Color', [0.8500 0.3250 0.0980])
-errorbar([4.02:8.02], [data_qall.meanData(3, :)], [data_qall.stdData(3, :)], '-x', 'Color', [0.9290 0.6940 0.1250])
-errorbar([4.06:8.06], [data_qall.meanData(4, :)], [data_qall.stdData(4, :)], '-x', 'Color', [0.4940 0.1840 0.5560])
-errorbar([8.44 8.94], [NaN data.meanData(1)], [NaN data.stdData(1)], 'x', 'Linewidth', 1.5, 'Color', [0 0.4470 0.7410])
-errorbar([8.44 8.98], [NaN data.meanData(2)], [NaN data.stdData(2)], 'x', 'Linewidth', 1.5, 'Color', [0.8500 0.3250 0.0980])
-errorbar([8.48 9.02], [NaN data.meanData(3)], [NaN data.stdData(3)], 'x', 'Linewidth', 1.5, 'Color', [0.9290 0.6940 0.1250])
-errorbar([8.52 9.06], [NaN data.meanData(4)], [NaN data.stdData(4)], 'x', 'Linewidth', 1.5, 'Color', [0.4940 0.1840 0.5560])
-axis([3 9.5 0.4 0.8]), grid on, xlabel('Word size (bits)'); ylabel('Classification accuracy'); legend('SVM', 'RF', 'DT', 'KNN', 'location', 'northwest', 'orientation', 'horizontal');
-set(gca, 'xticklabels', {'3','4','5','6','7','8','No quant.'})
+% load('report/figures/mel_class_mel40_avg0_qall.mat');
+% data_qall = data;
+% load('report/figures/mel_class_mel40_avg0_q0.mat');
[…]

### 2017-06-26 censeCoder/run_script.m

@@ -1,7 +1,7 @@
 clear all, close all, clc;
 
 %% Global run
-%%% censeCoder('do', [step], 'mask', {fps, mel, quant, dictgen, htreealg, textframe, dataset, classmethod, phaserec, desc, intelind, tobhop});
+%%% censeCoder('do', [step], 'mask', {fps, mel, quant, dictgen, htreealg, textframe, dataset, classmethod, phaserec, desc, intelind, tobhop, toblen});
 %%% Error - All quant
 % censeCoder('do', [1], 'mask', {-1, -1, 0, -1, -1, -1, 0, -1, -1, 2, -1, 2}); % Third-octave bands
 %%% Bitrate - All quant
@@ -29,5 +29,6 @@ clear all, close all, clc;
  
 % censeCoder('do', [1 2 3], 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, -1, -1});
 % censeCoder('do', [3], 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, -1, -1});
-censeCoder('do', [1 2 3], 'mask', {-1, -1, 0, 1, 2, 10, 1, -1, 1, 2, -1, 1});
-censeCoder('do', [1 2 3], 'mask', {-1, -1, 0, 1, 2, 10, 1, -1, 1, 2, -1, 2});
+% censeCoder('do', [1 2 3], 'mask', {-1, -1, 0, 1, 2, 10, 1, -1, 1, 2, -1, 1});
+% censeCoder('do', [1 2 3], 'mask', {-1, -1, 0, 1, 2, 10, 1, -1, 1, 2, -1, 2});
+censeCoder('do', [1 2 3 4], 'mask', {-1, -1, 6, 1, 2, 10, 1, -1, 1, 2, 0, 2, 1:4});

### 2017-06-26 paper/article.tex
more int results

@@
 
-\subsection{Inintelligibility}
+\subsection{Inintelligibility} \label{sec:inintelligibility}
 
@@
 
-To evaluate the impact of the frame rate on intelligibility two objective metrics are considered: the Coherence Speech Intelligibility Index\cite{kates2005} (CSII) and frequency-weighted segmental SNR\cite{hu2008} (fwSNRseg) by comparing original unaltered samples and recovered audio.
-These two indicators have been shown to correlate well with perceptual tests\cite{ma2009}, although results are only available for lesser degradations and distortions than the ones we consider in this study.
-For this reason, a small-scale perceptual test is also conducted.
-We use a dataset of clean speech recordings comprised of 9 french sentences enunciated by 3 male and 3 female speakers.
-The recordings are encoded with analysis frame rates of 50~Hz, 16~Hz, 8~Hz and 4~Hz for a total of 216 audio excerpts.
-At each test iteration, a listener is presented with sentences and asked both to transcribe the utterances and rate the global intelligibility between 1 and 5.
-Each sentence is tested twice in order to palliate the reduced number of participants.
-The listening bias induced is attenuated by using the 9 sentences only once for the two lower and higher frame rates.
-Furthermore, the global order of examples as well as speakers are randomized.
-Nine subjects of ages ranging from 17 to 60 and with normal hearing capacity participated.\\
+To evaluate the impact of the frame rate on intelligibility a perceptual test and the evolution of two objective measures are considered.
+For the evaluation, a dataset of clean speech recordings made of 9 french sentences enunciated by 3 male and 3 female speakers.
+The recorded sentences are encoded using the proposed approach with analysis frame rates of 50~Hz, 16~Hz, 8~Hz and 4~Hz for a total of 216 audio excerpts.
+For the perceptual test, each subject is presented with sentences and asked both to transcribe the utterances and rate the global intelligibility between 1 and 5.
+Due to the low number of sentences, each sentence is tested twice for the same subject but under different encoding setting and speaker identity.
+8 subjects of age ranging from 17 to 60 which reported normal hearing  participated to the listening test.
+The test was conducted using a Matlab interface displayed with a desktop computer and audio was played through Beyerdynamics DT 770 headphones.
+The output level was set by the experimenter at the same level for all subjects.
 
-These metrics require a recovery of the time-domain signal.
+Concerning the objective measures, we computed the Coherence Speech Intelligibility Index \cite{kates2005} (CSII) and the frequency-weighted segmental SNR \cite{hu2008} (fwSNRseg) by comparing original unaltered samples and recovered audio as those two indicators have been shown to correlate well with perceptual tests \cite{ma2009}, although results are only available for lesser degradations and distortions than the ones we consider in this study.
+\\
+
+These metrics require an estimate of the time-domain signal.
 To do so, a linearly-scaled spectrogram from the band-focused representations is estimated.
@@
 A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
-Signal phase is approximated by either white noise spectrogram scaling or a Griffin \& Lim algorithm \cite{griffin1984}, and the signal is retrieved using concatenation or overlap-add.
+Signal phase is approximated by either white noise spectrogram scaling or the Griffin \& Lim algorithm \cite{griffin1984}.
+The signal is then retrieved using concatenation or overlap-add.
 When using overlap to compute third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.\\
@@
 
-Finally, objective intelligibility metrics are estimated for the studied parameters and compared to an informal perceptual evaluation \footnote{Decoded speech utterances for various conditions can be listened to at \url{http://}}.
-Figures~\ref{fig:csii_tob_fps} and \ref{fig:fwsnrseg_tob_fps} shows both the CSII and fwSNRseg indicators for varying frames per second in analysis.
-Figure~\ref{fig:subj_int} presents the results of the preliminar perceptual test for the same setup.
-We acknowledge that it is surely biased by the reduced number of participants and scarcity of tested audio material.
-However, it is sufficient to judge the relevance of objective indicators in our conditions and study the intelligibility of fast acoustical measurements.\\
+Objective intelligibility metrics are then computed for the encoder's settings under evaluation and compared to the results of the perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{http://}}.
+Figures~\ref{fig:csii_tob_fps} and \ref{fig:fwsnrseg_tob_fps} shows both the CSII and fwSNRseg indicators for varying encoding frames per second.
+Figure~\ref{fig:subj_int} presents the results of the perceptual test for the same encoder's settings.
 
-Perceptual test results are in accordance with the formulated concerns.
-First, phonems separation is mandatory in order to ensure intelligibility.
-This implies an analysis frame rate significantly larger than that of phonems in the considered language.
-Here we observe a limit of about 10~Hz corresponding to a duration of 100~ms, rendering the studied 8~Hz measurements inintelligible.
-Few words were understood correctly as a result of coincidentally adequate frame timings, ie.
-analysis frames matching phonem utterances for a short duration.
-Similarly, framing effects induced by the proposed processing scheme yielded errors for higher fps transcriptions and a globally lower comprehension as perceived by the subjects.\\
+Perceptual test results confirm the qualitative evaluation of speech properties discussed in Section \ref{sec:inintelligibility}.
+Phonemes separation is indeed mandatory in order to ensure good intelligibility of speech.
+This implies an analysis frame rate significantly larger than the phonemes rate the considered language.
+A limit of about 10~Hz corresponding to a frame duration of 100~ms is observed, as the studied 8~Hz setting is found to be almost completely inintelligible.
+Very few words are understood correctly.
+And we assume that the correctly identified words are a result of coincidentally adequate frame timings, \textit{i.e.} analysis frames matching the location of phoneme utterances for a short duration.
+Similarly, framing effects induced by the proposed processing scheme yielded errors for higher frame rates transcriptions and a globally lower perceptual intelligibility.\\
 
@@
 In fact, the signal is too distorted for the proposed SNR normalization to ensure CSII values in the 0-1 range.
-When compared to perceptual test results, the CSII shows no clear separation in the 10 frames per second neighbourhood.
+When compared to perceptual test results, the CSII shows no clear separation around 10 frames per second.
 It is therefore not a good indicator in our conditions.\\
 
-Alternatively, the frequency-weighted segmental SNR considers only spectrogram magnitudes.
-As a result, distance is generally lower and a more representative of the induced perceptual distortion.
-Nevertheless, the fwSNRseg still uses a point-wise comparison which is certainly too precise for the studied degradations.
-Its shape seems more accurate at higher frame rates where intelligibility is almost constant.
-The previously observed threshold is however absent as the curve present a smoother increase trend, and the difference between 8~Hz and 16~Hz is not significant enough to correlate with subjective measurements.\\
+More interestingly, the frequency-weighted segmental SNR considers only spectrogram magnitudes.
+As a result, distance is generally lower and more representative of the induced perceptual distortion.
+Nevertheless, the fwSNRseg still uses a point-wise comparison which is certainly too precise for the level of degradations considered in this study.
+Indeed, it seems more accurate at higher frame rates compared to the results achieved using the perceptual test.
+Though, the threshold observed in the results of the perceptual test is not measured using the fwSNRseg metric and the difference between 8~Hz and 16~Hz is not large enough to match subjective measurements.\\
 
@@
 	\caption{Results of the perceptual intelligibility test with subjective normalized for visibility.
-A limit for intelligibility appears at around 10~Hz, corresponding to the average duration of a phonem.}
+A limit for intelligibility appears at around 10~Hz, corresponding to the average duration of a phoneme.}
 	\label{fig:subj_int}
 \end{figure}
+
 \section{Conclusion}

### 2017-06-26 paper/article.tex
done with ininti...

@@
 
-Intelligibility in decoded and reconstructed audio is also an important concern in this study.
+Intelligibility in decoded and reconstructed audio is also an important concernof this study.
 It is indeed important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data is transmitted over the network and potentially stored, the level of intelligibility of the decoded stream should be as low as possible.
 
-Forensic phonetics \cite{baldwin1990forensic}
-
-indice biométrique faible \cite{boe2000forensic}
+The use of an audio recording as an evidence is considered by the forensic phonetics \cite{baldwin1990forensic} domain.
+It shall be remebered that even recorded with a good quality, such recording remains a weak biometrical indicator \cite{boe2000forensic}.
+Still, even if the identity of the speaker cannot be asserted, one can attempt to transcribe the spoken utterances.
+As such, we believe that it is important to demonstrate that the proposed encoding scheme do not allow such thing.
 
@@
 If some speech is detected, the data is not transmitted.
-This approach is prone to failure of the detector and will lead to unavailibility of data whcih might compromise the computation of some indicators.
+This approach is however prone to failure of the detector and will lead to unavailibility of data during speech time periods which might compromise the computation of some indicators.
+
 Second, as the speech is mostly concentrated at a given frequency region, a band pass filter from 1 kHz to $~$4-5 kHz could be considered in order to remove the formant information \cite{kent1992acoustic}.
 However, as some frequency bands are no longer available, the computation of the acoustic indicators is no longer possible.
+
 A third approach is to wisely choose the frame rate.
-Since a phoneme is about 100ms to 200ms long \cite{kuwabara1996acoustic} \cite{rosen1992temporal} a frame rate lower than 4 Hz should dramatically reduce intelligibility.
+Since a phoneme is about 100ms to 200ms long \cite{kuwabara1996acoustic} \cite{rosen1992temporal} a frame rate lower than 4 Hz should therefore dramatically reduce intelligibility.
 

### 2017-07-16 paper/article.tex
Paper update - Error

@@
 A common way to implement third-octave analysis is to first design the highest octave three filters, and use them on progressively time-decimated versions of the input signal \cite{davis1986}.
-In practice, however, this technique presents multiple issues.
-\cite{antoni2010} presents an alternative analysis method based on direct frequency weighting.
+\cite{antoni2010} presents an alternative analysis method based on direct frequency weighting, which yields a lower computational complexity as opposed to time filtering.
 The weights matrix design procedure complies with both ANSI S1.1-1986 \cite{citeulike:9580295} and IEC 61260-1:2014 \cite{iec-norm} standards.
@@
 No overlap is used as it doubles both computational and memory costs and is not required for our application.
-A rectangular window is thus applied to ensure energy conservation in a given analysis frame.
+A windowing function can be applied, for instance a rectangular window to ensure energy conservation in a given analysis frame.
 The phase is unimportant to third-octave analysis, thus it is discarded.
@@
 center frequencies $f_i$ ranging from $20~Hz$ to $20~kHz$ with $f_0 = 1~kHz$.
-This means the main representation is composed of 31 values sampled every 125~ms.\\
+This means the main representation is composed of 31 values sampled every 125~ms.
 
@@
 
-The coder's output bitrate as well as additional measurement error is computed for both data representations : third-octave and Mel.
-It is expressed in dB and compared to the IEC 61672-1:2013 standard \cite{iec-norm2} on sound level meter tolerance.
-This is to verify that the quantization step yields a maximum absolute error inferior to the precision of the target recording device.
-To provide relevant statistics, these quantities are estimated for a total of 53 10-minutes texture frames.
-They are obtained from the UrbanSound8k dataset presented in the next section.
+The coder's output bitrate as well as measurement error is computed for both data representations.
+This metric is composed of band analysis error and the additional loss yielded by quantization before the encoding process.
+To this aim, third-octave bands are computed with the proposed method, then averaged and compared with the Matlab \textit{ita\_ toolbox}\cite{itatoolbox2017} implementation for the whole signal.
+We study both "fast" computation with 125~ms windows and no overlap and "slow" 1~s, 50\% overlap analysis to assess the impact of time integration.
+In both cases the reference is composed of 2~s extracts.
+The experiment is run for white noise as well as urban environmental recordings.
+As the analysis frames are of short duration, poor frequency resolution and spectral leakage are important, particularly in lower studied frequencies.
+For this reason we evaluate the effect of different windowing functions on each band measurement error.
+The toolbox's implementation shows less than 0.1~dB error when compared with a class 1 sound level meter and as such is considered a sufficient reference.
+To provide relevant statistics, these quantities are estimated for about 4500 extracts obtained from the UrbanSound8k dataset which we discuss in the next section.
 
@@
 It is used in all the following experiments with the exception of intelligibility computation for which a small dataset of high-quality voice recordings is preferred.
-Audio files are resampled 44.1~kHz, normalized and reduced to a single channel.\\
+Audio files are resampled 44.1~kHz, normalized and reduced to a single channel.
 
@@
 
-Intelligibility in decoded and reconstructed audio is also an important concernof this study.
+Intelligibility in decoded and reconstructed audio is also an important concern of this study.
 It is indeed important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data is transmitted over the network and potentially stored, the level of intelligibility of the decoded stream should be as low as possible.
@@
 
-%conduct thus preliminary perceptive tests to ensure that a clean speech recording is made unintelligible, implying the same results in usually noisier urban soundscapes. We also
-
 To evaluate the impact of the frame rate on intelligibility a perceptual test and the evolution of two objective measures are considered.
@@
 Due to the low number of sentences, each sentence is tested twice for the same subject but under different encoding setting and speaker identity.
-8 subjects of age ranging from 17 to 60 which reported normal hearing  participated to the listening test.
+12 subjects of age ranging from 17 to 60 which reported normal hearing participated to the listening test.
 The test was conducted using a Matlab interface displayed with a desktop computer and audio was played through Beyerdynamics DT 770 headphones.
@@
 Concerning the objective measures, we computed the Coherence Speech Intelligibility Index \cite{kates2005} (CSII) and the frequency-weighted segmental SNR \cite{hu2008} (fwSNRseg) by comparing original unaltered samples and recovered audio as those two indicators have been shown to correlate well with perceptual tests \cite{ma2009}, although results are only available for lesser degradations and distortions than the ones we consider in this study.
-\\
 
@@
 The signal is then retrieved using concatenation or overlap-add.
-When using overlap to compute third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.\\
+When using overlap to compute third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.
 
@@
 
+The measurement error is computed for third-octave bands and different windowing functions.
+Results are displayed in Table~\ref{T1}.
+The error was found to be decreasing with frequency increasing.
+The study is thus focused on the 20~Hz and 1~kHz bands, respectively the lowest and reference frequencies.
+The first observation is that using 1~s analysis over 125~ms yields better estimations at 20~Hz.
+This is expected as it provides a globally better resolution and therefore reduces the impact of spectral leakage effects in this region.
+When considering white noise the error is low on the whole spectrum, although this effectiveness does not translate to environmental sounds analysis.
+A factor of this phenomenon is found to be the sound level disparities absent in the first case but omnipresent in the second.
+For each frame, we computed the difference between the maximum and studied band levels in the reference, and compared it with the observed estimation error.
+The results show a correlation between the two quantities: when the sound level is low with respect to the peak, the error tends to increase.
+Furthermore, the closer a significantly higher level is to the studied frequency band, the larger the error is.
+This is due to framing and as such is particularly important in lower frequencies that suffer the most from it.
+The window function choice impact is closely related to these concerns.
+As the bitrate constraint prioritizes no overlap use for a fast analysis, the rectangular window seems a reasonable choice at first with its energy conservation qualities.
+While it yields the lowest error in high frequency bands, its high spectral leakage effect makes it unprecise in lower frequencies.
+Non-flat windows better account for this issue but require assuming that the signal is stationnary in a given frame and are thus biased.
+For slow measurements, the rectangular window impact is less harmful to band analysis due to an increased frequency resolution.\\
+
+\begin{table*}[h]
+\centering
+\caption{Third-octave bands measurement absolute error in dB for fast and slow computations and four window functions.
+The proposed method is here compared with evaluations by the \textit{ITA-toolbox} for 2-seconds extracts.
+}
+\label{T1}
+\begin{tabular}{|c|c|c|c|c|c|}
+\cline{1-6}
+\multirow{2}{*}{Analysis} & \multirow{2}{*}{Window} & \multicolumn{2}{|c|}{White noise} & \multicolumn{2}{|c|}{Environmental recordings}\\ \cline{3-6}
+ & & 20~Hz & 1~kHz & 20~Hz & 1~kHz\\ \cline{1-6}
+\multicolumn{1}{|c}{\multirow{4}{*}{Fast - 125~ms, 0$\%$ overlap}}
+ & \multicolumn{1}{|c|}{Rectangular} & 0.94$\pm$0.75 & 0.07$\pm$0.02 & 5.59$\pm$5.64 & 0.21$\pm$0.76\\ \cline{2-6}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{Hamming} & 1.02$\pm$0.71\newline & 0.16$\pm$0.14 & 3.34$\pm$3.41 & 0.44$\pm$0.76\\ \cline{2-6}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{Gaussian} & 1.04$\pm$0.71 & 0.17$\pm$0.15 & 3.56$\pm$3.63 & 0.48$\pm$0.83\\ \cline{2-6}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{Tukey ($\alpha = 0.5$)} & 0.97$\pm$0.75 & 0.11$\pm$0.09 & 4.16$\pm$5.58 & 0.32$\pm$0.80\\ \cline{1-6}
+ \multicolumn{1}{|c}{\multirow{4}{*}{Slow - 1~s, 50$\%$ overlap}}
+ & \multicolumn{1}{|c|}{Rectangular} & 0.48$\pm$0.36 & 0.08$\pm$0.05 & 1.86$\pm$3.13 & 0.40$\pm$0.55\\ \cline{2-6}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{Hamming} & 0.57$\pm$0.56 & 0.09$\pm$0.07 & 2.23$\pm$3.58 & 0.74$\pm$1.61\\ \cline{2-6}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{Gaussian} & 0.62$\pm$0.61 & 0.10$\pm$0.08 & 2.48$\pm$4.16 & 0.80$\pm$1.75\\ \cline{2-6}
+\multicolumn{1}{|c}{}
+ & \multicolumn{1}{|c|}{Tukey ($\alpha = 0.5$)} & 0.53$\pm$0.48 & 0.09$\pm$0.07 & 2.82$\pm$6.64 & 0.61$\pm$1.40\\ \cline{1-6}
+\end{tabular}
+\end{table*}
+
 We also examine the additionnal error caused by the encoding steps after obtaining the desired data representation.
@@
 \]
-justifying the decaying ratio as $q$ increases. In practice, we assume that $\varepsilon = f(\Delta_x, \frac{1}{2^{q-1}-1})$ with the heterogeneity of the data's PDF inducing small variations.\\
+justifying the decaying ratio as $q$ increases. In practice, we assume that $\varepsilon = f(\Delta_x, \frac{1}{2^{q-1}-1})$ with the heterogeneity of the data's PDF inducing small variations.
 
@@
 As $\Delta_x$ is sampled for each analysis frame in our implementation, the error has the same statistics across all bands.
-We compare the observed values against those specified in the IEC 61672-1:2013 \cite{iec-norm2} for $f = 1~kHz$ as it is where the most accurate measurements are expected.
-For class 1 and 2 sound level meters, the tolerance is set at about $\pm 1~dB$ and $\pm 1.5~dB$ respectively.
-Results for 6, 7 or 8-bit words lie within the shorter range and are therefore compliant with those standard's measurement tolerance.
+It is to be added to the measurement error discussed in the same section before comparing to the values specified in the IEC 61672-1:2013 \cite{iec-norm2} standard on class 1 and 2 sound level meters.
 
@@
 
-The effect of changing representation time-frequency resolution is presented in Table~\ref{T1}.
+The effect of changing representation time-frequency resolution is presented in Table~\ref{T2}.
 Similarly to baseline results, the random forest and SVM classifiers are the higher performing systems at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively.
@@
 \caption{Classification accuracy in percentage for different classifiers: SVMs (a), Random Forests (b), Decision Trees (c), and Nearest Neigbors (d) with respect to varying representation resolutions.
-Numbers in red indicate best performance and numbers in bold indicate statistical equivalent results compared to teh best performing setting.}
-\label{T1}
+Numbers in red indicate best performance and numbers in bold indicate statistical equivalent results compared to the best performing setting.}
+\label{T2}
 (a)\\
@@
 \multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & 58$\pm$4 & 62$\pm$4 & 63$\pm$4 & 64$\pm$4 & 63$\pm$4 & \textbf{65$\pm$0.05} & \textbf{67$\pm$6} \\ \cline{2-9}
+ & \multicolumn{1}{|c|}{20} & 58$\pm$4 & 62$\pm$4 & 63$\pm$4 & 64$\pm$4 & 63$\pm$4 & \textbf{65$\pm$5} & \textbf{67$\pm$6} \\ \cline{2-9}
 \multicolumn{1}{|c}{}
@@
 Following the previous discussions, the classification task is run on corresponding cepstra with a fixed 8 frames per second and 31 bands.
-Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps mel spectrograms seen in Table~\ref{T1} for all classification schemes.
+Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps mel spectrograms seen in Table~\ref{T2} for all classification schemes.
 In this table, equivalence of performance with respect to the best performing setting (in red) is evaluated using the following procedure.
@@
 Very few words are understood correctly.
-And we assume that the correctly identified words are a result of coincidentally adequate frame timings, \textit{i.e.} analysis frames matching the location of phoneme utterances for a short duration.
+We assume that the correctly identified words are a result of coincidentally adequate frame timings, \textit{i.e.} analysis frames matching the location of phoneme utterances for a short duration.
 Similarly, framing effects induced by the proposed processing scheme yielded errors for higher frame rates transcriptions and a globally lower perceptual intelligibility.\\

### 2017-07-16 censeCoder/ceco1representation.m

@@ -28,11 +28,11 @@ if strcmp(setting.desc, 'mel')
     end
 elseif strcmp(setting.desc, 'tob')
     l_frame = (round(setting.toblen*sr)-mod(round(setting.toblen*sr), 2)); % Approximately 125ms, "fast" Leq
-    l_hop = setting.tobhop*l_frame;
+    l_hop = round(setting.tobhop*l_frame);
     %% Filterbank calculation, can be replaced with constant matrix
     N = 2^(ceil(log2(l_frame)));
     N_filt = 2^17; % Design with a much greater precision
-    G = third_octave_filterbank(sr, N_filt, -17:13);
+    G = third_octave_filterbank(sr, N_filt, -17:13, 3);
     G = G(:, 1:round(N_filt/N):end); % Only take the resolution needed
     H = G.^2; % Frequency weights matrix
 %     HH = H'*H;

### 2017-07-16 censeCoder/ceco2coder.m

@@ -79,6 +79,7 @@ for ind_frame = 1:n_frames
                 X_delta_all = delta_enc(X_desc_all);
                 [symbol, prob] = huff_dict(X_delta_all, 'unique', setting.quant); % DdP
                 dict = huffmandict(symbol, prob, 2, setting.htreealg); % Tree generation
+                save('../embedded/matlab/dict.mat', 'dict');
                 clear X_desc_all X_delta_all;
             end
             X_huff{ind_frame} = huffmanenco(X_delta, dict);

### 2017-07-16 censeCoder/ceco3decoder.m

@@ -31,7 +31,7 @@ elseif strcmp(setting.desc, 'tob')
     %% Filterbank calculation, can be replaced with constant matrix
     N = 2^(ceil(log2(l_frame)));
     N_filt = 2^17; % Design with a much greater precision
-    G = third_octave_filterbank(sr, N_filt, -17:13);
+    G = third_octave_filterbank(sr, N_filt, -17:13, 3);
     G = G(:, 1:round(N_filt/N):end); % Only take the resolution needed
     H = G.^2; % Frequency weights matrix
     HH = H'*H;

### 2017-07-16 censeCoder/cecoReport.m

@@ -92,8 +92,9 @@ if nargin==0, censeCoder('report', 'r'); return; end%censeCoder('report', 'rhv')
 % Varying: Mel - All, Avg - All
 % config = expExpose(config, 'p', 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, 1, -1}, 'obs', 'csii', 'save', 'mel_csii_melall_avgall_q8', 'step', 4, 'expand', 'mel');
 % config = expExpose(config, 'p', 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, 2, -1}, 'obs', 'fwSNRseg', 'save', 'mel_fwSNRseg_melall_avgall_q8', 'step', 4, 'expand', 'mel');
-config = expExpose(config, 'p', 'mask', {-1, -1, 6, 1, 2, 10, 1, -1, 1, 2, 1, 2, 1:4}, 'obs', 'csii', 'save', 'tob_csii_len', 'step', 4);
-config = expExpose(config, 'p', 'mask', {-1, -1, 6, 1, 2, 10, 1, -1, 1, 2, 2, 2, 1:4}, 'obs', 'fwSNRseg', 'save', 'tob_fwSNRseg_len', 'step', 4);
+% config = expExpose(config, 'p', 'mask', {-1, -1, 6, 1, 2, 10, 1, -1, 1, 2, 1, 2, 1:4}, 'obs', 'csii', 'save', 'tob_csii_len', 'step', 4);
+% config = expExpose(config, 'p', 'mask', {-1, -1, 6, 1, 2, 10, 1, -1, 1, 2, 2, 2, 1:4}, 'obs', 'fwSNRseg', 'save', 'tob_fwSNRseg_len', 'step', 4);
 
+config = expExpose(config, 'p', 'mask', {-1, -1, 6, 1, 2, 10, 2, 0, -1, 2, -1, 1, 6}, 'obs', 'fwSNRseg', 'save', 'tob_fwSNRseg_len', 'step', 4);
 
 

### 2017-07-16 censeCoder/run_script.m

@@ -31,4 +31,7 @@ clear all, close all, clc;
 % censeCoder('do', [3], 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, -1, -1});
 % censeCoder('do', [1 2 3], 'mask', {-1, -1, 0, 1, 2, 10, 1, -1, 1, 2, -1, 1});
 % censeCoder('do', [1 2 3], 'mask', {-1, -1, 0, 1, 2, 10, 1, -1, 1, 2, -1, 2});
-censeCoder('do', [1 2 3], 'mask', {-1, -1, 6, 1, 2, 10, 3, -1, 2, 2, -1, 1, 1:4});
+% censeCoder('do', [1 2 3], 'mask', {-1, -1, 6, 1, 2, 10, 3, -1, 2, 2, -1, 1, 1:4});
+% censeCoder('do', [1 2], 'mask', {-1, -1, 6, 2, 2, 10, 2, -1, -1, 2, -1, 2, 3});
+censeCoder('do', [1 4], 'mask', {-1, -1, 6, 1, 2, 10, 2, 4, -1, 2, -1, 3, 6});
+

### 2017-07-16 censeCoder/util/delta_enc.m

@@ -1,12 +1,20 @@
 function x_c = delta_enc(x)
 
-assert(isvector(x));
-
-x_c = zeros(size(x));
-prev = 0;
-for indel = 1:length(x)
-    x_c(indel) = x(indel) - prev;
-    prev = x(indel);
+if isvector(x)
+    x_c = zeros(size(x));
+    prev = 0;
+    for indel = 1:length(x)
+        x_c(indel) = x(indel) - prev;
+        prev = x(indel);
+    end
+else
+    assert(ndims(x)<=2);
+    x_c = zeros(size(x));
+    prev = 0;
+    for indel = 1:size(x, 2)
+        x_c(:, indel) = x(:, indel) - prev;
+        prev = x(:, indel);
+    end
 end
 
 end

### 2017-07-16 tobError/run_script.m

@@ -1,0 +1,33 @@
+%clear all, close all, clc;
+
+%% Noise
+% tobError('do', 1:3, 'mask', {0, 1, 1, 4});
+% tobError('do', 1:3, 'mask', {12, 1, 1, 0});
+
+%% Speech
+% tobError('do', 1:3, 'mask', {0, 2, 1, 4, 2});
+% tobError('do', 1:3, 'mask', {12, 2, 1, 0, 2});
+
+%% US8k
+% tobError('do', 1:3, 'mask', {0, 3, 1, 4});
+% tobError('do', 1:3, 'mask', {12, 3, 1, 0});
+
+%% Noise
+% tobError('do', 1:3, 'mask', {0, 1, 2, 4});
+% tobError('do', 1:3, 'mask', {12, 1, 2, 4:10});
+
+%% Speech
+% tobError('do', 1:3, 'mask', {0, 2, 2, 4});
+% tobError('do', 1:3, 'mask', {12, 2, 2, 4:10});
+
+%% US8k
+% tobError('do', 1:3, 'mask', {0, 3, 2, 4});
+% tobError('do', 1:3, 'mask', {12, 3, 2, 4:10});
+
+%% Noise
+% tobError('do', [1 2 3], 'mask', {12, 1, 1, 4, 2});
+% tobError('do', [3], 'mask', {12, 1, 1, 4, 2});
+% [1 6 12 17]
+% tobError('do', [1 3], 'mask', {12, 1, 2, 6, 2});
+tobError('do', [3], 'mask', {17, 3, 0, 6, 2});
+

### 2017-07-16 tobError/toer3error.m

@@ -1,0 +1,59 @@
+function [config, store, obs] = toer3error(config, setting, data)              
+% toer3error ERROR step of the expLanes experiment tobError                    
+%    [config, store, obs] = toer3error(config, setting, data)                  
+%      - config : expLanes configuration state                                 
+%      - setting   : set of factors to be evaluated                            
+%      - data   : processing data stored during the previous step              
+%      -- store  : processing data to be saved for the other steps             
+%      -- obs    : observations to be saved for analysis                       
+                                                                               
+% Copyright: felix                                                             
+% Date: 12-Jul-2017                                                            
+                                                                               
+% Set behavior for debug mode                                                  
+if nargin==0, tobError('do', 3, 'mask', {}); return; else store=[]; obs=[]; end
+                                                                               
+data_cen = expLoad(config, [], 1);
+
+assert(setting.reflen>=setting.framelen);
+err_cen_ref = [];
+r_level = [];
+for ind_wav = 1:length(data.X_tob_ref)
+    if setting.framelen == 0.125
+        X_tob_cen = [];
+        if strcmp(setting.dataset, 'noise'); n_ref = 1; else n_ref = size(data.X_tob_ref{ind_wav}, 2)-1; end
+        if n_ref > 0
+            for ind_ref = 1:n_ref
+                n_avg = round(setting.reflen/setting.framelen);
+                X_tob_cen(:, ind_ref) = mean(data_cen.X_tob_cen{ind_wav}(:, (ind_ref-1)*n_avg+1:min(ind_ref*n_avg, end))/4096, 2);
+                X_tob_cen(X_tob_cen == 0) = eps;
+            end
+            err_cen_ref = [err_cen_ref 10*log10(X_tob_cen)-10*log10(data.X_tob_ref{ind_wav}(:, 1:n_ref))];
+%             r_level = [r_level max(10*log10(data.X_tob_ref{ind_wav}(:, 1:n_ref)))-10*log10(data.X_tob_ref{ind_wav}(18, 1:n_ref))];
+        end
+    else
+        X_tob_cen = [];
[…]

### 2017-07-16 tobError/toerInit.m

@@ -1,0 +1,10 @@
+function [config, store] = toerInit(config)                        
+% toerInit INITIALIZATION of the expLanes experiment tobError      
+%    [config, store] = toerInit(config)                            
+%      - config : expLanes configuration state                     
+%      -- store  : processing data to be saved for the other steps 
+                                                                   
+% Copyright: felix                                                 
+% Date: 12-Jul-2017                                                
+                                                                   
+if nargin==0, tobError(); return; else store=[];  end              

### 2017-07-18 paper/article.tex
ml proof read starts and conclusion

@@
 \newcommand{\fg}[1]{\textcolor{red}{ Felix: #1}}
+\newcommand{\ac}[1]{\textcolor{red}{ Arnaud: #1}}
+\newcommand{\pa}[1]{\textcolor{red}{ Pierre: #1}}
+\newcommand{\cl}[1]{\textcolor{red}{ Catherine: #1}}
 
@@
 
-The acoustic environment represents both societal and environmental concerns.
-Monitoring the acoustic environnment in urban but also rural or wilderness areas is therefore an important matter.
-Fostering on the recent development of low cost hardware acoustic sensors, we propose to consider a sensor grid approach to tackle this issue.
+The spreading of urban areas and the growth of human population worldwide raised societal and environmental concerns.
+To better address those, the monitoring the acoustic environnment in urban but also rural or wilderness areas is among other monitoring efforts an important matter.
+Fostering on the recent development of low cost hardware acoustic sensors, we propose in this paper to consider a sensor grid approach to tackle this issue.
 
 In this kind of approach, the crucial question is the nature of the data that is transmitted from the sensors to the processing and archival servers.
-To this end, we propose an efficient audio coding scheme based on third octave band spectral representation that allows 1) the estimation of most acousitc indicators and 2) the recognition of acoustic events at state of the art performance rate.
-The former is useful to provide quantitative information about the acoustic environment, while the latter is useful to gather more qualitative information and build perceptually motivated indicators using for example some emergence of a given sound source.
-
+To this end, we propose an efficient audio coding scheme based on third octave band spectral representation that allows 1) the estimation of standard acoustic indicators and 2) the recognition of acoustic events at state of the art performance rate.
+The former is useful to provide quantitative information about the acoustic environment, while the latter is useful to gather qualitative information and build perceptually motivated indicators using for example the emergence of a given sound source.
 The coding scheme is also demonstrated to transmit spectrally encoded data that, reverted to the time domain using state of the art techniques, is not intelligible, thus protecting the privacy of citizens.
@@
 
-The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc (wp.nyu.edu/sonyc) and cense (cense.ifsttar.fr) projects.
+The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc\footnote{\url{htttp://wp.nyu.edu/sonyc}} \cite{mydlarz2017implementation} and cense\footnote{\url{htttp://cense.ifsttar.fr}} \pa{ref papier de judicael ?} \cite{} projects.
 
@@
 First,  the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, \textit{i.e.} the approach shall be scalable.
-Second, the nodes shall be energy efficient in order ot ease the deployment of the sensors grid to the desired topology, ideally autonomous.
+Second, the nodes shall be energy efficient, ideally autonomous, in order to ease the deployment of the sensors grid to the desired topology.
 Third, the encoding scheme used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to ensure the privacy of the citizen.
-Lastly, the data stored shall be as rich as possible while remaining a low bitrate for efficient transmission and storage.
+Though, the data stored shall remain as rich as possible while maintaining a low bitrate for efficient transmission and storage.
 
@@
 The latter scheme has several benefits.
-First, the sensor is much simpler and can thus be autonomous in terms of energy, easing the deployment of the network.
+First, the sensor task is much simpler and can thus be implemented using low consumption processors, potentially being autonomous in terms of energy.
+This will ease the deployment of the network.
 Second, it allows researchers to gather large amount of data that can be post processed and studied further offline.
@@
 However, transmitting the raw audio through the network has several disavantages, in terms of required bandwidth, storage capabilities and privacy.
-Thus, for transmission from the sensors to the storage unit, the data can be encoded in a more efficient way than lossy audio encoding standards \cite{pan1995tutorial} as the audio signal is not mandatory for the computation of the acoustic indicators and the features needed for event recognition.
+Thus, for transmission from the sensors to the storage unit, the data shall be encoded in a more efficient way than lossy audio encoding standards \cite{pan1995tutorial}.Indeed, the audio signal is not mandatory for the computation of the acoustic indicators and the features needed for event recognition.
 Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.
@@
 We thus propose in this paper a audio coding scheme specifically tailored for use in a sensor grid which has the following features.
-It is of low bitrate but still allows the computation of most of the standard acoustics indicators with high precision.
-As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data.
+It is of low bitrate but still allows the computation of most of the standard acoustics indicators with controlable precision.
+As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data at production level rates.
 Finally, according to preliminary perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
 
-In order to promote reproducible research, the coder as well as the experiments needed to generate the figures will be made available to the community.
+In order to promote reproducible research, the coder as well as the experiments needed to generate the figures is available to the community\footnote{\url{https://github.com/felixgontier/cense-coder}}.
 The remaining of the paper is organized as follows: Section \ref{sec:background} reviews the types of data that needs to be estimated using the transmitted data and Section \ref{sec:coder} describes the proposed encoding scheme.
@@
 In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation.
-Thickness of arrows indicate bandwidth and thickness of boxes indicates the level of computation or storage required.}
+Thickness of arrows roughly indicate bandwidth and thickness of boxes roughly indicates the level of computation or storage required.}
 \label{fig:codingScheme}
@@
 The present work is constrained to allow both acoustic monitoring and sound event recognition in urban soundscapes.
-Here we briefly review state-of-the-art methods in both subjects in order to better motivate our choices.
+Here we briefly review state-of-the-art methods in both subjects in order to better motivate our design choices.
 
@@
 The considered sensor network primarily aims at monitoring urban soundscapes, that is, continously assessing their content and impact on the population.
-In the literature, this is typically enabled by measuring energetic acoustic indicators such as the equivalent sound pressure level $L_{eq}$ in dB SPL or its A-weighted equivalent $L_{Aeq}$ in dBA.
+In the literature, this is typically performed by measuring energetic acoustic indicators such as the equivalent sound pressure level $L_{eq}$ in dB SPL or its A-weighted equivalent $L_{Aeq}$ in dBA.
 However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe soundscapes \cite{rychtarikova2013}.
@@
 The recognition of sources of interest is thus of importance.
-As far as the encoding scheme is concerned, it is thus important that the encoded data allows the computation of the above cited indicators but also the recognition of sources of interest with state of the art methods.
+As far as the encoding scheme is concerned, it is thus important that the encoded data allows us to compute the above cited indicators but also to allow us to recognize the sources of interest with state of the art methods.
 
 The recognition of sources of interest from audio streams has been the subject of extensive research in the past on speech \cite{anusuya2009}, music \cite{tzanetakis2002}, and lately more complex scenes in which the current work falls.
-Studied classification methods are diverse, ranging from time-dependant modeling with HMMs \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}.
-Common architectures include learning-based classifiers such as support vector machines (SVM) \cite{kumar2016}, gaussian mixture models (GMM) \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}.
+Studied classification methods are diverse, ranging from time-dependant modeling with hidden markov models \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}.
+Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}.
 However, the selection of relevant features is still an open debate.
@@
 Among them, mel spectrograms and their cepstral-domain derivation, the mel-frequency cepstrum coefficients (MFCC), are the most recurrent.
-These representations effectively try to model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale, thus bearing important physical significance.
+These representations effectively model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale.
+
 They may also be exploited together with features computed in other domains to better model signal properties.
@@
 As mentionned, they provide advantages in both acoustic monitoring quality and reduced data volume per measurement period.
-The physical content is also close to that of mel spectrograms, being just another filterbank transform with logarithmic frequency scaling.\\
+The resulting representation is also close to that of mel spectrograms, being just another filterbank transform with logarithmic frequency scaling.\\
 
@@
 The continuously sampled audio is segmented into 125~ms frames to provide "fast" acoustic measurements.
-The data is zero-padded to the next power of two to allow best fft performances.
+The data is zero-padded to the next power of two to improve computational efficiency.
 No overlap is used as it doubles both computational and memory costs and is not required for our application.
 A windowing function can be applied, for instance a rectangular window to ensure energy conservation in a given analysis frame.
-The phase is unimportant to third-octave analysis, thus it is discarded.
-Similarly, negative frequency components contain the same information as positive ones because the base signal is real.
+The phase is discarded as it is not meaningful for third-octave analysis.
+Similarly, negative frequency components contain the same information as positive ones because the input signal is real.
 We then compute third-octave bands from the squared spectral magnitude by matrix multiplication with the frequency weights proposed in \cite{antoni2010} for $l = 2$\footnote{When implementing said method, we found that squaring the $\phi_l(p), l \geq 1$ intermediate function (p.
@@
 center frequencies $f_i$ ranging from $20~Hz$ to $20~kHz$ with $f_0 = 1~kHz$.
-This means the main representation is composed of 31 values sampled every 125~ms.
+The representation is thus composed of 31 values sampled every 125~ms.
 
@@
 
-A Huffman coding scheme \cite{huffman1952} is then used to further reduce data dimensionality.
+A Huffman coding scheme \cite{huffman1952} is then used to further reduce data rate.
 As in most entropy coding algorithms, the efficiency of this technique depends on two important factors.
 A reduced amount of symbols in the dictionnary yields smaller code size on lower probability symbols.
-Lower data entropy, ie.
-lower average information content of the signal distribution, also increases performance.
+Lower data entropy, \textit{i.e.} lower average information content of the signal distribution, also increases efficiency.
 The first is generally obtained by applying a quantization process to the signal, whereas the second is directly linked with the probability density function (PDF) of these symbols.
@@
 If it is specific to a given data packet, then it does not need to contain every possible value.
-This gain seem to outweight the additional complexity induced by the tree generation algorithm.
+This gain seem to outweight the additional complexity induced by the need to transmit the result of the tree generation algorithm.
 Alternatively, short texture frames or single analysis windows can be encoded using one general dictionnary to improve bitrate.
-This choice depends on which of the size and complexity parameters must be reduced most.\\
+Choosing between those two approaches is the result of a balance between requirements in terms of size and complexity.\\
 
@@
 	\caption{Example of estimated probability density functions of the data throughout the encoding step.
-(left) Unchanged output of the representation step, concentrated towards very low values.
-(middle) PDF "flattening" effect induced by logarithm application.
+Unchanged output of the representation step (left), concentrated towards very low values.
+PDF "flattening" effect induced by logarithm application (middle).
 Here values are mapped to the range $[0, 2^7-1]$ and rounded to perform quantization.
-(right) Output of the $\Delta$ compression, with desirable probabilities as the input to a Huffman algorithm.}
+Output of the $\Delta$ compression (right) -, with desirable probabilities as the input to a Huffman algorithm.}
 	\label{fig:pdf}
@@
 
-The decoding process is quite straightforward, as both Huffman and $\Delta$ compression are lossless and directly reversible. The entire coder scheme is summarized in Figure~\ref{fig:scheme}.
+The decoding process is quite straightforward, as both Huffman and $\Delta$ compression are lossless and invertible directly. The entire coder scheme is summarized in Figure~\ref{fig:scheme}.
 
@@
 
-A set of metrics is computed to assess the efficiency of the proposed coder scheme and determine the impact of the algorithm's parameters, which are as follow: the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, and only for Mel bands the number of coefficients between 10 and 40.
+A set of metrics is computed to assess the efficiency of the proposed coder scheme and to determine the impact of the degrees of freedom of the propoded algorithm.
+Those parameters are as follow: 1) the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, and 2) the number of coefficients between 10 and 40 (only for Mel bands).
 We also study the effect of time averaging analysis frames: to force a fixed amount of frames per second lesser than the average speech rate in phonemes per second is a possible way to alter intelligibility at the cost of temporal information resolution.
+
+///
 
@@
 
+An audio encoding scheme have been described and motivated for use in a sensor grid approach to the problem of acoustic monitoring.
+
+The proposed approach have the following benefits:
+\begin{itemize}
+	\item precision: the impact of the quantization step for 8 bits codewords is found to be negligible compared to sensor precision of class 2 sensors
+	\item efficiency: for fast and slow modes, the bitrate is respectively about \fg{numbers} kbps for high precision
+	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible.
+\end{itemize}
+
+As those constraints are to some extent orthogonal, the proposed approach is flexible enough to balance rapidly between several modes of operations by changing a few parameters in an intuitive manner.
+
+Future work will study the usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency and a more torough investigation on the inversion methods in order to ensure that the inintelligibility constraint is not violated.
+
 \section{Acknowlegments}

### 2017-07-20 paper/article.tex
ml proof read 3

@@
 
-///
-
 \subsection{Efficiency}
@@
 This metric is composed of band analysis error and the additional loss yielded by quantization before the encoding process.
-To this aim, third-octave bands are computed with the proposed method, then averaged and compared with the Matlab \textit{ita\_ toolbox}\cite{itatoolbox2017} implementation for the whole signal.
+To this aim, third-octave bands are computed with the proposed method, then averaged and compared to a trusted reference.
+The chosen reference consiiders the Matlab \textit{ita\_ toolbox} implementation \cite{itatoolbox2017} processed over the whole signal.
 We study both "fast" computation with 125~ms windows and no overlap and "slow" 1~s, 50\% overlap analysis to assess the impact of time integration.
-In both cases the reference is composed of 2~s extracts.
+In both cases the sound dataset is the same and is composed of 2~s extracts.
 The experiment is run for white noise as well as urban environmental recordings.
-As the analysis frames are of short duration, poor frequency resolution and spectral leakage are important, particularly in lower studied frequencies.
-For this reason we evaluate the effect of different windowing functions on each band measurement error.
-The toolbox's implementation shows less than 0.1~dB error when compared with a class 1 sound level meter and as such is considered a sufficient reference.
-To provide relevant statistics, these quantities are estimated for about 4500 extracts obtained from the UrbanSound8k dataset which we discuss in the next section.
+As the analysis frames are of short duration, poor frequency resolution and spectral leakage are expected, particularly in the lower frequencies bands.
+For this reason we evaluate the effect of the use of different windowing functions on each band measurement error in order to mitigate this loss of precision.
+The reference implementation shows less than 0.1~dB error when compared with a class 1 sound level meter and as such is considered a sufficient reference.
+To provide relevant statistics, these quantities are estimated for about 4500 extracts obtained from the UrbanSound8k dataset \cite{salamon2014}.
 
@@
 
-In order to ensure that the proposed scheme allows the recognition of events using state of the art methods, we consider the UrbanSound8k dataset\cite{salamon2014}.
+In order to ensure that the proposed scheme allows the recognition of events using state of the art methods, we consider the results achieved by several regognition systems on the UrbanSound8k dataset\cite{salamon2014}.
 It features about 9 hours of urban environmental sounds recordings separated in 8732 wave files ranging from 1 to 4 seconds each.
-The recordings are labeled in 10 classes (air conditioner, car horn, children playing, dog bark, drilling, enginge idling, gun shot, jackhammer, siren, street music), and distributed in 10 independant folds.
+The recordings are labeled in 10 classes (air conditioner, car horn, children playing, dog bark, drilling, enginge idling, gun shot, jackhammer, siren, street music), and distributed in 10 independent folds.
 A method and baseline results are also provided for the classification task.
 It is used in all the following experiments with the exception of intelligibility computation for which a small dataset of high-quality voice recordings is preferred.
-Audio files are resampled 44.1~kHz, normalized and reduced to a single channel.
+Audio files are resampled at 44.1~kHz, normalized and reduced to a single channel.
 
-We evaluate the global loss of information by implementing the four classification models proposed in \cite{salamon2014}: a support vector machine with a radial basis function kernel, a random forest classifier with 500 trees, a decision tree and a k-nearest neighbors classifier with $k = 5$.
+We evaluate the global loss of information induced by the coder by implementing the four classification models proposed in \cite{salamon2014}: a support vector machine with a radial basis function kernel, a random forest classifier with 500 trees, a decision tree and a k-nearest neighbors classifier with $k = 5$.
 Values for the SVM parameter $C$ and RBF kernel variance $\sigma^2$ are found with a grid search.
-We apply a discrete cosine transform to the critical band signal representation to obtain cepstra (known as Mel Frequency Cepstrum Coefficients or MFCC in the first case) of which we conserve the 25 first coefficients, and summarize along time with the mean, variance, skewness, kurtosis, minimum, maximum, median, derivative mean and variance, second order derivative mean and variance.
-The feature vector is thus comprised of 275 values to reproduce available results and compare with our own.
-Models are trained for each setup using a 10-fold cross validation method provided by the authors of \cite{salamon2014}, that is, every combination of testing one fold on models trained with the other nine.
+We opionaly apply a discrete cosine transform to the critical band signal representation to obtain cepstra (known as Mel Frequency Cepstrum Coefficients or MFCC in the first case) of which we conserve the 25 first coefficients, and summarize along time with the mean, variance, skewness, kurtosis, minimum, maximum, median, derivative mean and variance, second order derivative mean and variance.
+The feature vector is thus comprised of 275 values to reproduce available results and compare with the data produced by the proposed coding scheme.
+Models are trained for each setup using the 10-fold cross validation method provided by the authors of \cite{salamon2014}, that is, every combination of testing one fold on models trained with the other nine.
 
@@
 The use of an audio recording as an evidence is considered by the forensic phonetics \cite{baldwin1990forensic} domain.
-It shall be remebered that even recorded with a good quality, such recording remains a weak biometrical indicator \cite{boe2000forensic}.
+That being said, the readers shall be aware that even recorded with a good quality, such recording remains a weak biometrical indicator \cite{boe2000forensic}.
 Still, even if the identity of the speaker cannot be asserted, one can attempt to transcribe the spoken utterances.
@@
 Second, as the speech is mostly concentrated at a given frequency region, a band pass filter from 1 kHz to $~$4-5 kHz could be considered in order to remove the formant information \cite{kent1992acoustic}.
-However, as some frequency bands are no longer available, the computation of the acoustic indicators is no longer possible.
+However, as some frequency bands are no longer available, the computation of statndard acoustic indicators is no longer possible.
 
@@
 
-To evaluate the impact of the frame rate on intelligibility a perceptual test and the evolution of two objective measures are considered.
-For the evaluation, a dataset of clean speech recordings made of 9 french sentences enunciated by 3 male and 3 female speakers.
-The recorded sentences are encoded using the proposed approach with analysis frame rates of 50~Hz, 16~Hz, 8~Hz and 4~Hz for a total of 216 audio excerpts.
+Thus, the impact of the frame rate parameter of the proposed encoding scheme on intelligibility is evaluated.
+To do so, a perceptual test and the evolution of two objective measures are considered.
+For the evaluation, a dataset of clean speech recordings made of 9 french sentences enunciated by 3 male and 3 female speakers, for a total of 216 audio excerpts.
+The recorded sentences are encoded using the proposed approach with analysis frame rates of respectively 50~Hz, 16~Hz, 8~Hz and 4~Hz.
 For the perceptual test, each subject is presented with sentences and asked both to transcribe the utterances and rate the global intelligibility between 1 and 5.
@@
 12 subjects of age ranging from 17 to 60 which reported normal hearing participated to the listening test.
-The test was conducted using a Matlab interface displayed with a desktop computer and audio was played through Beyerdynamics DT 770 headphones.
+The test was conducted using a Matlab interface displayed with a desktop computer and audio was played through \textit{Beyerdynamics DT 770} headphones.
 The output level was set by the experimenter at the same level for all subjects.
 
-Concerning the objective measures, we computed the Coherence Speech Intelligibility Index \cite{kates2005} (CSII) and the frequency-weighted segmental SNR \cite{hu2008} (fwSNRseg) by comparing original unaltered samples and recovered audio as those two indicators have been shown to correlate well with perceptual tests \cite{ma2009}, although results are only available for lesser degradations and distortions than the ones we consider in this study.
+Concerning the objective measures, the Coherence Speech Intelligibility Index \cite{kates2005} (CSII) and the frequency-weighted segmental SNR \cite{hu2008} (fwSNRseg) are considered.
+They both compare original unaltered samples and recovered audio as those two indicators have been shown to correlate well with perceptual tests \cite{ma2009}, although results are only available for lesser degradations and distortions than the ones we consider in this study.
 
@@
 A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
-Signal phase is approximated by either white noise spectrogram scaling or the Griffin \& Lim algorithm \cite{griffin1984}.
-The signal is then retrieved using concatenation or overlap-add.
+Signal phase is then approximated by either white noise spectrogram scaling or the Griffin \& Lim algorithm \cite{griffin1984}.
+The signal is then retrieved using concatenation or overlap-add depending on the overlap setting.
 When using overlap to compute third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.
@@
 Third-octave representation on 31 bands yielded an overall higher size than their mel equivalent, here estimated for 30 bands.
-It however compares with the 40-mel bands representation which is the most used in litterature.
-This occurence is likely due to the distribution observed by the data prior to Huffman encoding.
+It however compares with the 40-mel bands representation which is the most used features in litterature.
+This hugher bitrate is likely due to the distribution observed by the data prior to Huffman encoding.
 
@@
 We evaluate the bitrate for 10 to 40 mel bands and a frame rate from 2 to 10 per second, with fixed $q = 8$.
-Results are exposed in Figure~\ref{fig:bitrate_mel_avg}.
+Results are shown in Figure~\ref{fig:bitrate_mel_avg}.
 As expected, the bitrate for a given word size $q$ can be modeled as a linear function of the representation dimensions for one second of analysis.
-Small variations are induced by data distributions on a per-frame level and their effect on the Huffman algorithm.
+Small variations are induced by data distributions on a per-frame level and their impact on the Huffman algorithm.
 
@@
 
-This experiment aims at assessing potential tradeoffs between bitrate and information. As such, it will be further discussed in the \textit{Event recognition} subsection.\\
+This experiment aims at an initial assessement of potential tradeoffs between bitrate and preservation of valuable information.
+As such, it will be further discussed in the \textit{Event recognition} subsection.\\
 
@@
 Results are displayed in Table~\ref{T1}.
-The error was found to be decreasing with frequency increasing.
+The error was found to be decreasing with respect to an increase of frequency.
 The study is thus focused on the 20~Hz and 1~kHz bands, respectively the lowest and reference frequencies.
@@
 This is expected as it provides a globally better resolution and therefore reduces the impact of spectral leakage effects in this region.
-When considering white noise the error is low on the whole spectrum, although this effectiveness does not translate to environmental sounds analysis.
-A factor of this phenomenon is found to be the sound level disparities absent in the first case but omnipresent in the second.
-For each frame, we computed the difference between the maximum and studied band levels in the reference, and compared it with the observed estimation error.
-The results show a correlation between the two quantities: when the sound level is low with respect to the peak, the error tends to increase.
-Furthermore, the closer a significantly higher level is to the studied frequency band, the larger the error is.
-This is due to framing and as such is particularly important in lower frequencies that suffer the most from it.
-The window function choice impact is closely related to these concerns.
+
+Closer inspection show that when considering white noise the error is low on the whole spectrum.
+This effectiveness does not translate though to environmental sounds analysis.
+One inducing factor for this phenomenon is the sound level disparities absent in the first case but omnipresent in the second.
+Let us consider, for each frame, the difference between the maximum and the remaining band levels in the reference, and compared it with the observed estimation error.
+The results show a correlation between the two quantities: when the average band level is low with respect to the peak, the error tends to increase.
+Furthermore, the closer a significantly higher level is to the considered frequency band, the larger the error is.
+This is due to framing that causes spectral leakage.
+This is found to be particularly important in lower frequencies.
+
+To mitigate this issue, the choice of the window function shall be studied further.
 As the bitrate constraint prioritizes no overlap use for a fast analysis, the rectangular window seems a reasonable choice at first with its energy conservation qualities.
-While it yields the lowest error in high frequency bands, its high spectral leakage effect makes it unprecise in lower frequencies.
+While it yields the lowest error in high frequency bands, its high spectral leakage effect makes it unprecise for lower frequency regions.
 Non-flat windows better account for this issue but require assuming that the signal is stationnary in a given frame and are thus biased.
@@
 \caption{Third-octave bands measurement absolute error in dB for fast and slow computations and four window functions.
-The proposed method is here compared with evaluations by the \textit{ITA-toolbox} for 2-seconds extracts.
+The proposed method is here compared with evaluations by the \textit{ITA-toolbox} for 2-seconds exerpts.
 }

### 2017-07-20 paper/article.tex
ml spell check

@@
 The spreading of urban areas and the growth of human population worldwide raised societal and environmental concerns.
-To better address those, the monitoring the acoustic environnment in urban but also rural or wilderness areas is among other monitoring efforts an important matter.
+To better address those, the monitoring the acoustic environment in urban but also rural or wilderness areas is among other monitoring efforts an important matter.
 Fostering on the recent development of low cost hardware acoustic sensors, we propose in this paper to consider a sensor grid approach to tackle this issue.
@@
 As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data at production level rates.
-Finally, according to preliminary perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
+Finally, according to a perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
 
@@
 \vspace{-0.15in}
-\caption{Alternative implementations of the sensor grid approach for the monitoring of the acoustic environnment.
+\caption{Alternative implementations of the sensor grid approach for the monitoring of the acoustic environment.
 In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation.
@@
 
-Eventhough the above discussed indicators provide more richness than $L_{eq}$, recent studies show that abstract statistics are still not sufficient to fully model the human perception of soundscapes.
+Even though the above discussed indicators provide more richness than $L_{eq}$, recent studies show that abstract statistics are still not sufficient to fully model the human perception of soundscapes.
 The recognition of sources of interest is thus of importance.
@@
 Following the considerations briefly exposed in the previous section, we conclude that third-octave bands are a reasonable choice.
-As mentionned, they provide advantages in both acoustic monitoring quality and reduced data volume per measurement period.
+As mentioned, they provide advantages in both acoustic monitoring quality and reduced data volume per measurement period.
 The resulting representation is also close to that of mel spectrograms, being just another filterbank transform with logarithmic frequency scaling.\\
@@
 As in most entropy coding algorithms, the efficiency of this technique depends on two important factors.
-A reduced amount of symbols in the dictionnary yields smaller code size on lower probability symbols.
+A reduced amount of symbols in the dictionary yields smaller code size on lower probability symbols.
 Lower data entropy, \textit{i.e.} lower average information content of the signal distribution, also increases efficiency.
@@
 In the example shown here, the former is $H_{log} = 6.24~sh$ and the latter $H_{\Delta} = 3.54~sh$.
-Huffman encoding is then computed with either a frame-specific symbol-code dictionnary or a constant one generated from an entire dataset.
+Huffman encoding is then computed with either a frame-specific symbol-code dictionary or a constant one generated from an entire dataset.
 A comparison of both methods is shown in Figure~\ref{fig:dict_comp}.
-For most short texture frame durations, we found the local Huffman algorithm to be much faster.
-In fact, encoding complexity is function of the amount of dictionnary elements.
+For most short texture frame duration, we found the local Huffman algorithm to be much faster.
+In fact, encoding complexity is function of the amount of dictionary elements.
 If it is specific to a given data packet, then it does not need to contain every possible value.
 This gain seem to outweight the additional complexity induced by the need to transmit the result of the tree generation algorithm.
-Alternatively, short texture frames or single analysis windows can be encoded using one general dictionnary to improve bitrate.
+Alternatively, short texture frames or single analysis windows can be encoded using one general dictionary to improve bitrate.
 Choosing between those two approaches is the result of a balance between requirements in terms of size and complexity.\\
@@
 		\includegraphics[width=\columnwidth]{figures/dict_comp.eps}
-	\caption{Performance comparison of locally and globally generated Huffman dictionnaries.
-(top) The mean execution time ratio favors the use of frame-specific dictionnaries for tested texture frame lengths.
+	\caption{Performance comparison of locally and globally generated Huffman dictionaries.
+(top) The mean execution time ratio favors the use of frame-specific dictionaries for tested texture frame lengths.
 (bottom) The mean output bitrate is close for both algorithms, showing that the necessity of sending symbol-code pairs mostly compensates for their optimality.}
@@
 
-A set of metrics is computed to assess the efficiency of the proposed coder scheme and to determine the impact of the degrees of freedom of the propoded algorithm.
+A set of metrics is computed to assess the efficiency of the proposed coder scheme and to determine the impact of the degrees of freedom of the proposed algorithm.
 Those parameters are as follow: 1) the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, and 2) the number of coefficients between 10 and 40 (only for Mel bands).
@@
 It features about 9 hours of urban environmental sounds recordings separated in 8732 wave files ranging from 1 to 4 seconds each.
-The recordings are labeled in 10 classes (air conditioner, car horn, children playing, dog bark, drilling, enginge idling, gun shot, jackhammer, siren, street music), and distributed in 10 independent folds.
+The recordings are labeled in 10 classes (air conditioner, car horn, children playing, dog bark, drilling, engine idling, gun shot, jackhammer, siren, street music), and distributed in 10 independent folds.
 A method and baseline results are also provided for the classification task.
@@
 Second, as the speech is mostly concentrated at a given frequency region, a band pass filter from 1 kHz to $~$4-5 kHz could be considered in order to remove the formant information \cite{kent1992acoustic}.
-However, as some frequency bands are no longer available, the computation of statndard acoustic indicators is no longer possible.
+However, as some frequency bands are no longer available, the computation of standard acoustic indicators is no longer possible.
 
@@
 The recorded sentences are encoded using the proposed approach with analysis frame rates of respectively 50~Hz, 16~Hz, 8~Hz and 4~Hz.
-For the perceptual test, each subject is presented with sentences and asked both to transcribe the utterances and rate the global intelligibility between 1 and 5.
+
+For the perceptual test, each subject is presented with sentences and asked both to transcribe the utterances and rate the global intelligibility from 1 (not intelligible) to 5 (intelligible).
 Due to the low number of sentences, each sentence is tested twice for the same subject but under different encoding setting and speaker identity.
@@
 Third-octave representation on 31 bands yielded an overall higher size than their mel equivalent, here estimated for 30 bands.
-It however compares with the 40-mel bands representation which is the most used features in litterature.
-This hugher bitrate is likely due to the distribution observed by the data prior to Huffman encoding.
+It however compares with the 40-mel bands representation which is the most used features in literature.
+This higher bitrate is likely due to the distribution observed by the data prior to Huffman encoding.
 
@@
 
-This experiment aims at an initial assessement of potential tradeoffs between bitrate and preservation of valuable information.
+This experiment aims at an initial assessment of potential tradeoffs between bitrate and preservation of valuable information.
 As such, it will be further discussed in the \textit{Event recognition} subsection.\\
@@
 While it yields the lowest error in high frequency bands, its high spectral leakage effect makes it unprecise for lower frequency regions.
-Non-flat windows better account for this issue but require assuming that the signal is stationnary in a given frame and are thus biased.
+Non-flat windows better account for this issue but require assuming that the signal is stationary in a given frame and are thus biased.
 For slow measurements, the rectangular window impact is less harmful to band analysis due to an increased frequency resolution.\\
@@
 
-We also examine the additionnal error caused by the encoding steps after obtaining the desired data representation.
+We also examine the additional error caused by the encoding steps after obtaining the desired data representation.
 The only lossy operation applied is quantization, which is defined by an output word size $q$ in bits.
@@
 
-The effect of changing representation time-frequency resolution is presented in Table~\ref{T2}.
+The effect of changing the time-frequency resolution of the representation is presented in Table~\ref{T2}.
 Similarly to baseline results, the random forest and SVM classifiers are the higher performing systems at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively.
-However, we find that given our setup, diminishing the number of analysis bands to some extent most often does not induce a strong drop of performance.
+However, we find that given our setup, reducing the number of analysis bands up to a given level most often does not induce a strong drop of performance.
 The performance of the decision tree classifier is a good example of this behavior, with best performances for 10 mel bands only and a 4\% lower accuracy for 40.
+The latter result may be due to the low ability of the decision tree classifier to handle hugh dimensional features.
 Even if the difference is small, all other models perform best with 30 or 40 mel bands as a representation.
-Time decimation is also possible, as the original representation can be averaged and consistently yield a good classification accuracy.
+Time decimation cn also be considered, as the original representation can be averaged and consistently yield a good classification accuracy.
 The loss of information can be considered negligible for FPS values as low as 20 or 10 depending on the method.
 Even below, classification accuracy only drops by one or a few percents.
-This means that we can effectively divide the data size by a factor of at most 10 without affecting sound event recognition performance.
+This means that we can effectively divide the data size by a factor of at most 10 without strongly affecting sound event recognition performance.
 It also provides us with a preliminary confirmation of the possibility for "fast"-sampled third-octave bands cepstra to match  MFCC performances.\\
@@
 Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps mel spectrograms seen in Table~\ref{T2} for all classification schemes.
-In this table, equivalence of performance with respect to the best performing setting (in red) is evaluated using the following procedure.
-We evaluate the null hypothesis that the substraction of the two compared distribution (the distribution of the setting we consider minus the distribution of the best performing one) comes from a normal distribution with mean equal to zero and unknown variance, using the paired-sample t-test at the 0.05 significance level.
+In this table, equivalence of performance with respect to the best performing setting (in red) is depicted with a bold font evaluated using the following procedure.
+The null hypothesis that the subtraction of the two compared distribution (the distribution of the setting we consider minus the distribution of the best performing one) comes from a normal distribution with mean equal to zero and unknown variance is evaluated using the paired-sample t-test at the 0.05 significance level.
 If the null hypothesis is not rejected, the setting is considered as equivalent in terms of performance to the best performing one.
@@
 It aims at providing information regarding class-by-class accuracy and misclassification rates.
-We thus compute these metrics for the SVM classifier, with predictions cumulated over the ten folds in test configuration.
+We thus compute these metrics for the SVM classifier, with predictions accumulated over the ten folds in test configuration.
 The analogous natures of the two descriptors is highlighted by close one-versus-one differentiation performances, with a slightly lower accuracy for third-octave bands on average.
@@
 
-Both descriptor are thus found to have similar representational capabilities despite minor construction differences.
+Both descriptor are thus found to have similar representational capabilities despite minor differences due to their respective designs.
 
@@
 Objective intelligibility metrics are then computed for the encoder's settings under evaluation and compared to the results of the perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{http://}}.
+The results of the perceptual test is evaluated using the average intelligibility score (AIS) given by the subjects and the ineligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
 Figures~\ref{fig:csii_tob_fps} and \ref{fig:fwsnrseg_tob_fps} shows both the CSII and fwSNRseg indicators for varying encoding frames per second.
@@
 		\includegraphics[width=\columnwidth]{figures/subj_int.eps}
-	\caption{Results of the perceptual intelligibility test with subjective normalized for visibility.
-A limit for intelligibility appears at around 10~Hz, corresponding to the average duration of a phoneme.}
+	\caption{Average intellibility score (AIS) given by the subjects and the inteligibility ratio (IR) as a function of the frame rate.
+Inintelligibility appears at around 10~Hz, corresponding to the average duration of a phoneme.
+\fg{update legend with acronyms}}
 	\label{fig:subj_int}
@@
 
-An audio encoding scheme have been described and motivated for use in a sensor grid approach to the problem of acoustic monitoring.
+An audio encoding scheme have been described and motivated for use in a sensor grid approach to tackle the problem of large scale acoustic monitoring.
 
@@
 	\item precision: the impact of the quantization step for 8 bits codewords is found to be negligible compared to sensor precision of class 2 sensors
-	\item efficiency: for fast and slow modes, the bitrate is respectively about \fg{numbers} kbps for high precision
+	\item efficiency: for fast and slow modes, the bitrate is respectively about \fg{numbers} kbps for the high precision mode
 	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible.
@@
 
-As those constraints are to some extent orthogonal, the proposed approach is flexible enough to balance rapidly between several modes of operations by changing a few parameters in an intuitive manner.
+%As those constraints are to some extent orthogonal, the proposed approach is flexible enough to balance rapidly between several modes of operations by changing a few parameters in an intuitive manner.
 
-Future work will study the usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency and a more torough investigation on the inversion methods in order to ensure that the inintelligibility constraint is not violated.
+Future work will study the usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency and a more thorough investigation on the inversion methods in order to ensure that the inintelligibility constraint is indeed not violated for fast settings.
 

### 2017-07-21 censeCoder/ceco1representation.m
Add gh-pages

@@ -1,0 +1,184 @@
+function [config, store, obs] = ceco1representation(config, setting, data)       
+% ceco1representation REPRESENTATION step of the expLanes experiment censeCoder  
+%    [config, store, obs] = ceco1representation(config, setting, data)           
+%      - config : expLanes configuration state                                   
+%      - setting   : set of factors to be evaluated                              
+%      - data   : processing data stored during the previous step                
+%      -- store  : processing data to be saved for the other steps               
+%      -- obs    : observations to be saved for analysis                         
+                                                                                 
+% Copyright: felix                                                               
+% Date: 20-Apr-2017                                                              
+                                                                                 
+% Set behavior for debug mode                                                    
+if nargin==0, censeCoder('do', 1, 'mask', {}); return; else store=[]; obs=[]; end
+                                                                                 
+addpath(genpath('C:\Program Files\MATLAB\R2015b\toolbox\rastamat'));
+addpath(genpath('util'));
+
+sr = 44100;
+%% Analysis window definition
+if strcmp(setting.desc, 'mel')
+    l_frame = 1024;
+    l_hop = 0.5*l_frame;
+    if setting.fps % 0 means none
+        n_fps = (sr+l_hop-l_frame)/l_hop; % Number of frames per second with base settings
+        n_avg = round(n_fps/setting.fps); % Number of consecutive frames to average into one
+        disp(['Chosen FPS is ' num2str(setting.fps) ', actual one is ' num2str(n_fps/n_avg) '.']);
+    end
+elseif strcmp(setting.desc, 'tob')
+    l_frame = (round(setting.toblen*sr)-mod(round(setting.toblen*sr), 2)); % Approximately 125ms, "fast" Leq
+    l_hop = round(setting.tobhop*l_frame);
+    %% Filterbank calculation, can be replaced with constant matrix
[…]

### 2017-07-21 censeCoder/ceco2coder.m

@@ -1,0 +1,109 @@
+function [config, store, obs] = ceco2coder(config, setting, data)                
+% ceco2coder CODER step of the expLanes experiment censeCoder                    
+%    [config, store, obs] = ceco2coder(config, setting, data)                    
+%      - config : expLanes configuration state                                   
+%      - setting   : set of factors to be evaluated                              
+%      - data   : processing data stored during the previous step                
+%      -- store  : processing data to be saved for the other steps               
+%      -- obs    : observations to be saved for analysis                         
+                                                                                 
+% Copyright: felix                                                               
+% Date: 20-Apr-2017                                                              
+                                                                                 
+% Set behavior for debug mode                                                    
+if nargin==0, censeCoder('do', 2, 'mask', {}); return; else store=[]; obs=[]; end
+           
+addpath(genpath('util'));
+
+if ~setting.quant
+    warning('Skipping ''coding'' step: no qauntization is applied, Huffman encoding cannot be applied.');
+    % Store
+    store.X_desc = data.X_desc;
+    % Observations
+    obs.code_len = [];
+    obs.bitrate = [];
+    return;
+end
+
+sr = 44100;
+%% Analysis window definition
+if strcmp(setting.desc, 'mel')
+    l_frame = 1024;
+    l_hop = 0.5*l_frame;
+    n_fps = 1+(sr-l_frame)/l_hop; % Number of frames per second with base settings
+    if setting.fps % 0 means none
+        n_avg = round(n_fps/setting.fps); % Number of consecutive frames to average into one
+        n_fps = n_fps/n_avg; % Number of frames per second with custom settings
+    else
+        n_fps = 1+(sr-l_frame)/l_hop; % Number of frames per second with base settings
+    end
+elseif strcmp(setting.desc, 'tob')
+    l_frame = (round(setting.toblen*sr)-mod(round(setting.toblen*sr), 2)); % Approximately 125ms, "fast" Leq
+    l_hop = setting.tobhop*l_frame;
+    n_fps = 1+(sr-l_frame)/l_hop;
+end
+
[…]

### 2017-07-21 censeCoder/ceco3decoder.m

@@ -1,0 +1,179 @@
+function [config, store, obs] = ceco3decoder(config, setting, data)              
+% ceco4decoder DECODER step of the expLanes experiment censeCoder                
+%    [config, store, obs] = ceco4decoder(config, setting, data)                  
+%      - config : expLanes configuration state                                   
+%      - setting   : set of factors to be evaluated                              
+%      - data   : processing data stored during the previous step                
+%      -- store  : processing data to be saved for the other steps               
+%      -- obs    : observations to be saved for analysis                         
+                                                                                 
+% Copyright: felix                                                               
+% Date: 27-Apr-2017                                                              
+                                                                                 
+% Set behavior for debug mode                                                    
+if nargin==0, censeCoder('do', 3, 'mask', {}); return; else store=[]; obs=[]; end
+                                                                                 
+addpath(genpath('C:\Program Files\MATLAB\R2015b\toolbox\rastamat'));
+addpath(genpath('util'));
+
+sr = 44100;
+%% Analysis window definition
+if strcmp(setting.desc, 'mel')
+    l_frame = 1024;
+    l_hop = 0.5*l_frame;
+    if setting.fps % 0 means none
+        n_fps = (sr+l_hop-l_frame)/l_hop; % Number of frames per second with base settings
+        n_avg = round(n_fps/setting.fps); % Number of consecutive frames to average into one
+    end
+elseif strcmp(setting.desc, 'tob')
+    l_frame = (round(setting.toblen*sr)-mod(round(setting.toblen*sr), 2)); % Approximately 125ms, "fast" Leq
+    l_hop = setting.tobhop*l_frame;
+    %% Filterbank calculation, can be replaced with constant matrix
+    N = 2^(ceil(log2(l_frame)));
+    N_filt = 2^17; % Design with a much greater precision
+    G = third_octave_filterbank(sr, N_filt, -17:13, 3);
[…]

### 2017-07-21 censeCoder/ceco4metrics.m

@@ -1,0 +1,175 @@
+function [config, store, obs] = ceco4metrics(config, setting, data)              
+% ceco3metrics METRICS step of the expLanes experiment censeCoder                
+%    [config, store, obs] = ceco3metrics(config, setting, data)                  
+%      - config : expLanes configuration state                                   
+%      - setting   : set of factors to be evaluated                              
+%      - data   : processing data stored during the previous step                
+%      -- store  : processing data to be saved for the other steps               
+%      -- obs    : observations to be saved for analysis                         
+                                                                                 
+% Copyright: felix                                                               
+% Date: 20-Apr-2017                                                              
+                                                                                 
+% Set behavior for debug mode                                                    
+if nargin==0, censeCoder('do', 4, 'mask', {}); return; else store=[]; obs=[]; end
+                                                                                 
+addpath(genpath('C:\Program Files\MATLAB\R2015b\toolbox\libsvm-3.22'));
+addpath(genpath('C:\Program Files\MATLAB\R2015b\toolbox\rastamat'));
+addpath(genpath('util'));
+
+switch setting.dataset
+    case 'speech' % Intelligibility I3 metric
+        sr = 44100;
+        l_frame = 1024;
+        l_hop = 0.5*l_frame;
+
+        if ispc; datapath = [config.inputPath 'rush\rush_clean_spec_' num2str(l_frame) '.mat']; else datapath = [config.inputPath 'rush/rush_clean_spec_' num2str(l_frame) '.mat']; end
+        if exist(datapath)
+            load(datapath);
+        else
+            if ispc; datapath = [config.inputPath 'rush\']; else datapath = [config.inputPath 'rush/']; end
+            rush_dir = dir(datapath);
+            rush_names = {rush_dir.name};
+            ind_wav = 0; % Real number of .wav files
+            for ind_file = 1:numel(rush_names)
[…]

### 2017-07-21 censeCoder/cecoReport.m

@@ -1,0 +1,100 @@
+function config = cecoReport(config)                        
+% cecoReport REPORTING of the expLanes experiment censeCoder
+%    config = cecoInitReport(config)                        
+%       config : expLanes configuration state               
+                                                            
+% Copyright: felix                                          
+% Date: 20-Apr-2017                                         
+                                                            
+if nargin==0, censeCoder('report', 'r'); return; end%censeCoder('report', 'rhv'); return; end      
+
+% {fps, mel, quant, dictgen, htreealg, textframe, dataset, classmethod, phaserec, desc, intelind, tobhop}
+
+%%% censeCoder('do', [step], 'mask', {fps, mel, quant, dictgen, htreealg, textframe, dataset, classmethod, phaserec, desc, intelind, tobhop});
+%%% Error - All quant
+% censeCoder('do', [1], 'mask', {-1, -1, 0, -1, -1, -1, 0, -1, -1, 2, -1, 2}); % Third-octave bands
+%%% Bitrate - All quant
+% censeCoder('do', [2], 'mask', {-1, -1, 0, 1, 2, 10, 2, -1, -1, 2, -1, 2});
+%%% Class - All quant
+% censeCoder('do', [4], 'mask', {-1, -1, 0, -1, -1, -1, 2, 1, -1, 2, -1, 2});
+% censeCoder('do', [4], 'mask', {-1, -1, 0, -1, -1, -1, 2, 2:4, -1, 2, -1, 2});
+%%% Intel indicators - All quant
+% censeCoder('do', [2 3 4], 'mask', {-1, -1, 2:6, 1, 2, 10, 1, -1, 1, 2, 0, 2});
+
+%%% Error/Class - No averaging, 30 bands, no quant
+% censeCoder('do', [1 4], 'mask', {7, 3, 1, -1, -1, -1, 2, 0, -1, 1, -1, -1});
+%%% Error/Bitrate/Class - No averaging, 30 bands, all quant
[…]

### 2017-07-21 censeCoder/perc_int.m

@@ -1,0 +1,116 @@
+function perc_int(act)
+
+if ~nargin; act = 'disp'; end;
+
+switch act
+    case 'test'
+        if exist('subj_notes.mat', 'file')
+            load('subj_notes.mat');
+            ind_test = length(subj_notes)+1;
+        else
+            q = 8;
+            toblen = 1000*[0.02 0.06 0.125 0.25];
+            ind_test = 1;
+        end
+        n_sen = 9;
+        sen_sfx = {'_C_1', '_C_2', '_F_1', '_F_2', '_Q_1', '_Q_2', '_S_1', '_S_2', '_S_3'};
+        subj_notes{ind_test} = zeros(2*n_sen, 1)-1;
+        sentences_tr{ind_test} = cell(2*n_sen, 1);
+        sp_cnt = zeros(6, 1); % Speaker test count
+        
+        
+        
+        % High fps
+        sen = randperm(n_sen);
+        set_cnt = round(rand(1, 1))+4;
+        setting{ind_test}(:, 1:n_sen) = [sen; [ones(1, set_cnt) 2*ones(1, n_sen-set_cnt)]];
+        
+        % Low fps
+        sen = randperm(n_sen);
+        set_cnt = round(rand(1, 1))+4;
+        setting{ind_test}(:, n_sen+1:2*n_sen) = [sen; [3*ones(1, set_cnt) 4*ones(1, n_sen-set_cnt)]];
+        
+        rp = randperm(size(setting{ind_test}, 2));
+        setting{ind_test} = setting{ind_test}(:, rp);
+
+        for ind_setting = 1:size(setting{ind_test}, 2)
+            clc;
+            disp('----- Perceptive test on intelligibility -----');
+            disp(['Test number ' num2str(ind_test) '.']);
+            disp(['Sample ' num2str(ind_setting) ' of ' num2str(size(setting{ind_test}, 2)) '.']);
+            sp = round(6*rand(1, 1)+0.5);
+            while sp_cnt(sp) > 3; sp = round(6*rand(1, 1)+0.5); end
+            sp_cnt(sp) = sp_cnt(sp)+1;
+            
+            [y, Fs] = audioread(['../../decoded_samples/perc_int/' num2str(sp) sen_sfx{setting{ind_test}(1, ind_setting)} '_q8_l' num2str(toblen(setting{ind_test}(2, ind_setting))) '.wav']);
+            
[…]

### 2017-07-21 censeCoder/report_figs.m

@@ -1,0 +1,172 @@
+clear all, close all, clc;
+
+real_fps = {'2', '4.1', '6.1', '7.7', '9.5', '21', '85'};
+fps_lgd = cell(1, length(real_fps));
+for ind_lgd = 1:length(real_fps)
+    fps_lgd{ind_lgd} = ['fps: ' real_fps{ind_lgd}];
+end
+
+%% Bitrate
+% fig = openfig('report/figures/bitrate_fps_mel_8.fig');
+% figure(fig);
+% ax = gca;
+% ax.XTickLabels = real_fps;
+% xlabel('Frames per second'), ylabel('Output bitrate (kbit/s)'), grid on;
+% for ind_ylbl = 1:length(ax.YTickLabels)
+%     ax.YTickLabels{ind_ylbl} = num2str(str2double(ax.YTickLabels{ind_ylbl})/1000);
+% end
+% legend('Location', 'northwest');
+% print(fig, '-dpdf', 'report/figures/processed/bitrate_fps_mel.pdf');
+% close all;
+
+%% KNN accuracy
+% fig = openfig('report/figures/knn_fps_mel_8.fig');
+% figure(fig);
+% ax = gca;
+% ax.XTickLabels = real_fps;
+% xlabel('Frames per second'), ylabel('KNN-5 accuracy'), grid on;
+% load('report/tables/knn_base.mat');
+% hold on, errorbar(7.15, data.meanData, data.stdData, 'LineWidth', 2, 'color', 'black', 'marker', 'x')
+% legend({'mel: 10', 'mel: 20', 'mel: 30', 'mel: 40', 'baseline'}, 'Location', 'southeast');
+% print(fig, '-dpdf', 'report/figures/processed/knn_fps_mel.pdf');
+% close all;
+
+%% CSII
+% fig = openfig('report/figures/csii_fps_mel_8.fig');
+% figure(fig);
+% xlabel('Mel bands'), ylabel('CSII indicator'), grid on;
+%load('report/tables/csii_base.mat');
+%hold on, plot(4, data.meanData, 'LineWidth', 2, 'color', 'black', 'marker', 'x')
+%legend([fps_lgd {'baseline'}], 'Location', 'northwest');
+%axis([0.5 4.5 0.3 0.65]);
+% print(fig, '-dpdf', 'report/figures/processed/csii_fps_mel.pdf');
+% close all;
+
+%% Error
[…]

### 2017-07-21 censeCoder/run_script.m

@@ -1,0 +1,37 @@
+clear all, close all, clc;
+
+%% Global run
+%%% censeCoder('do', [step], 'mask', {fps, mel, quant, dictgen, htreealg, textframe, dataset, classmethod, phaserec, desc, intelind, tobhop, toblen});
+%%% Error - All quant
+% censeCoder('do', [1], 'mask', {-1, -1, 0, -1, -1, -1, 0, -1, -1, 2, -1, 2}); % Third-octave bands
+%%% Bitrate - All quant
+% censeCoder('do', [2], 'mask', {-1, -1, 0, 1, 2, 10, 2, -1, -1, 2, -1, 2});
+%%% Class - All quant
+% censeCoder('do', [4], 'mask', {-1, -1, 0, -1, -1, -1, 2, 1, -1, 2, -1, 2});
+% censeCoder('do', [4], 'mask', {-1, -1, 0, -1, -1, -1, 2, 2:4, -1, 2, -1, 2});
+%%% Intel indicators - All quant
+% censeCoder('do', [2 3 4], 'mask', {-1, -1, 2:6, 1, 2, 10, 1, -1, 1, 2, 0, 2});
+
+%%% Error/Class - No averaging, 30 bands, no quant
+% censeCoder('do', [1 4], 'mask', {7, 3, 1, -1, -1, -1, 2, 0, -1, 1, -1, -1});
+%%% Error/Bitrate/Class - 8 fps, 40 bands, all quant
+% censeCoder('do', [1 2], 'mask', {4, 4, 2:6, 1, 2, 10, 2, -1, -1, 1, -1, -1});
+% censeCoder('do', [4], 'mask', {7, 4, 2:6, 1, 2, 10, 2, 0, -1, 1, -1, -1});
+% censeCoder('do', [1 4], 'mask', {7, 4, 1, 1, 2, 10, 2, 0, -1, 1, -1, -1});
+
+% censeCoder('do', [1 2 4], 'mask', {7, 4, 2:6, 1, 2, 10, 2, 0, -1, 1, -1, -1});
+%%% Error/Bitrate/Class - All mel settings, 8 bit
+% censeCoder('do', [2], 'mask', {1:5, 0, 6, 1, 2, 10, 2, 0, -1, 1, -1, -1});
[…]

### 2017-07-21 censeCoder/util/delta_enc.m

@@ -1,0 +1,20 @@
+function x_c = delta_enc(x)
+
+if isvector(x)
+    x_c = zeros(size(x));
+    prev = 0;
+    for indel = 1:length(x)
+        x_c(indel) = x(indel) - prev;
+        prev = x(indel);
+    end
+else
+    assert(ndims(x)<=2);
+    x_c = zeros(size(x));
+    prev = 0;
+    for indel = 1:size(x, 2)
+        x_c(:, indel) = x(:, indel) - prev;
+        prev = x(:, indel);
+    end
+end
+
+end

### 2017-07-21 censeCoder/util/sroexfilter.m

@@ -1,0 +1,23 @@
+function w = sroexfilter(f)
+% Simplified rounded exponential (ro-ex) filterbank (with equal
+% band-importance critical bands)
+
+% Zwicker & Terhardt, Analytical expressions for critical-band rate and critical bandwidth as a function of frequency, 1980
+% ANSI S3.5-1997
+q = [.35 .45 .57 .7 .84 1 1.17 1.37 1.6 1.85 2.15 2.5 2.9 3.4 4 4.8 5.8];
+
+%f_l = [.3 .4 .51 .63 .77 .92 1.08 1.27 1.48 1.72 2 2.32 2.7 3.15 3.7 4.4 5.3];
+%f_u = [.4 .51 .63 .77 .92 1.08 1.27 1.48 1.72 2 2.32 2.7 3.15 3.7 4.4 5.3 6.4];
+%erb = (f_u-f_l);
+% Moore & Glasberg, Suggested formulae for calculating auditory-filter bandwidths and excitation patterns, 1983
+erb = 24.7*(4.37*q+1);
+% Glasberg & Moore, Derivation of auditory filter shapes from notched-noise data, 1990
+%erb = 6.23*q.^2+93.39*q+28.52;
+
+p = 4*1000*q./erb;
+g = abs(1-repmat(f, 1, length(q))./repmat(q, length(f), 1));
+
+% Simplified ro-ex filter bank
+w = (1+repmat(p, length(f), 1).*g).*exp(-repmat(p, length(f), 1).*g);
+
+end

### 2017-07-21 tobError/report_figs.m

@@ -1,0 +1,281 @@
+clear all, close all, clc;
+
+%% Reference length
+% load('report/figures/tobErr_n_rlen_f.mat');
+% % load('report/figures/tobErr_s_rlen.mat');
+% % load('report/figures/tobErr_u_rlen.mat');
+% 
+% for ind_rlen = 1:length(data.rawData)
+%     errMean(:, ind_rlen) = data.rawData{ind_rlen}.errMean;
+%     errStd(:, ind_rlen) = data.rawData{ind_rlen}.errStd;
+% end
+% 
+% tob_f  = 10^3 * (2 .^ ([-17:11]/3));
+% 
+% figure(1), clf, errorbar(tob_f(2:end), errMean(2:end, 1), errStd(2:end, 1), '-x'), hold on,
+% for ind_rlen = 2:size(errMean, 2)
+%     errorbar(tob_f(2:end), errMean(2:end, ind_rlen), errStd(2:end, ind_rlen), '-x')
+% end
+% set(gca, 'xscale', 'log');
+% grid on, legend('0.125~s', '0.25~s', '0.5~s', '1~s', '1.5~s', '2~s', '2.5~s', '3~s', '3.5~s', '4~s')%, axis([3.5 8.5 0 5.5])
+% xlabel('Frequency'), ylabel('Measurement error (dB)')
+
+%% Window type
+% load('report/figures/tobErr_n_win.mat');
+% % load('report/figures/tobErr_s_win.mat');
+% % load('report/figures/tobErr_u_win.mat');
+% 
+% for ind_rlen = 1:length(data.rawData)
+%     errMean(:, ind_rlen) = data.rawData{ind_rlen}.errMean;
+%     errStd(:, ind_rlen) = data.rawData{ind_rlen}.errStd;
+% end
+% 
+% tob_f  = 10^3 * (2 .^ ([-17:11]/3));
+% 
+% figure(1), clf, errorbar(tob_f(2:end), errMean(2:end, 1), errStd(2:end, 1), '-x'), hold on,
+% for ind_rlen = 2:size(errMean, 2)
+%     errorbar(tob_f(2:end), errMean(2:end, ind_rlen), errStd(2:end, ind_rlen), '-x')
+% end
+% set(gca, 'xscale', 'log');
[…]

### 2017-07-21 tobError/stft.m

@@ -1,0 +1,64 @@
+function x_stft = stft(x, l_win, l_hop, wintype, zero_pad, winparam)
+
+if nargin < 4
+    wintype = 'hamming'; % Default window: hamming
+end
+if nargin < 3
+    l_hop = round(0.5*l_win); % Default overlap: 50%
+end
+
+n_win = 1+(length(x)-l_win)/l_hop; % Number of windows
+
+%% Window generation
+switch wintype % Other windows to implement
+    case 'hamming'
+        w = hamming(l_win, 'periodic');
+    case 'hanning'
+        w = hanning(l_win, 'periodic');
+    case 'blackmanharris'
+        w = blackmanharris(l_win, 'periodic');
+    case 'bartlett'
+        w = bartlett(l_win);
+    case 'bartletthann'
+        w = barthannwin(l_win);
+    case 'gaussian'
+        w = gausswin(l_win);
+    case 'kaiser'
+        w = kaiser(l_win, 0.25);
+    case 'tukey01'
+        w = tukeywin(l_win, 0.1);
+    case 'tukey02'
+        w = tukeywin(l_win, 0.2);
+    case 'tukey03'
+        w = tukeywin(l_win, 0.3);
+    case 'tukey04'
+        w = tukeywin(l_win, 0.4);
+    case 'tukey05'
+        w = tukeywin(l_win, 0.5);
+    case 'tukey06'
+        w = tukeywin(l_win, 0.6);
+    case 'tukey07'
+        w = tukeywin(l_win, 0.7);
+    case 'tukey08'
+        w = tukeywin(l_win, 0.8);
+    case 'tukey09'
+        w = tukeywin(l_win, 0.9);
+    case 'rect'
+        w = ones(l_win, 1);
+end
+
+if zero_pad; n_pad = 2^(ceil(log2(l_win)))-l_win; else n_pad = 0; end; % Zero pad to next power of 2
+%% STFT
+x_stft = zeros(l_win+n_pad, n_win);
+for indwin = 1:n_win
+    
+    %% Windowing
+    x_win = [x((indwin-1)*l_hop+1:(indwin-1)*l_hop+l_win).*w; zeros(n_pad, 1)];
+    %% FFT
+    x_stft(:, indwin) = fft(x_win); % FFT magnitude
+end
+
+x_stft = x_stft(1:end/2+1,:);
+
+end
+

### 2017-07-21 tobError/tobError.m

@@ -1,0 +1,190 @@
+function tobError(varargin)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     
+% Welcome to the main entry point of tobError                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   
+% Please DO NOT modify this file unless you have a precise intent.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              
+                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                
+shortExperimentName = 'toer';                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   
+[p, experimentName] = fileparts(mfilename('fullpath'));                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         
[…]

### 2017-07-21 tobError/toer1cense.m

@@ -1,0 +1,169 @@
+function [config, store, obs] = toer1cense(config, setting, data)              
+% toer1cense CENSE step of the expLanes experiment tobError                    
+%    [config, store, obs] = toer1cense(config, setting, data)                  
+%      - config : expLanes configuration state                                 
+%      - setting   : set of factors to be evaluated                            
+%      - data   : processing data stored during the previous step              
+%      -- store  : processing data to be saved for the other steps             
+%      -- obs    : observations to be saved for analysis                       
+                                                                               
+% Copyright: felix                                                             
+% Date: 12-Jul-2017                                                            
+                                                                               
+% Set behavior for debug mode                                                  
+if nargin==0, tobError('do', 1, 'mask', {}); return; else store=[]; obs=[]; end
+                                                                               
+sr = 32000;
+
+l_frame = round(setting.framelen*sr);
+if setting.framelen == 0.125; l_hop = 1*l_frame; else l_hop = 0.5*l_frame; end
+
+N = 2^(ceil(log2(l_frame)));
+N_filt = 2^20; % Design with a much higher precision
+G = third_octave_filterbank(sr, N_filt, -17:11, 3);
+switch setting.gcalc
+    case 'sub'
+        G = G(:, 1:round(N_filt/N):end); % Only take the resolution needed
+        H_st = G.^2;
+    case 'mean'
+        G = G.^2;
+        G_mean(:, 1) = mean(G(:, 1:1+round(N_filt/(2*N))), 2);
+        G_mean(:, N/2+1) = mean(G(:, 1+(N/2)*round(N_filt/N)-round(N_filt/(2*N)):end), 2);
+        for ind_f = 2:N/2
+            G_mean(:, ind_f) = mean(G(:, 1+(ind_f-1)*round(N_filt/N)-round(N_filt/(2*N)):1+(ind_f-1)*round(N_filt/N)+round(N_filt/(2*N))), 2);
+        end
+        H_st = G_mean;
+        clear ind_f G_mean;
+    case 'dec'
+        for ind_b = 1:size(G, 1)
[…]

### 2017-07-21 tobError/toer2ref_ita.m

@@ -1,0 +1,108 @@
+function [config, store, obs] = toer2ref_ita(config, setting, data)            
+% toer2ref_ita REF_ITA step of the expLanes experiment tobError                
+%    [config, store, obs] = toer2ref_ita(config, setting, data)                
+%      - config : expLanes configuration state                                 
+%      - setting   : set of factors to be evaluated                            
+%      - data   : processing data stored during the previous step              
+%      -- store  : processing data to be saved for the other steps             
+%      -- obs    : observations to be saved for analysis                       
+                                                                               
+% Copyright: felix                                                             
+% Date: 12-Jul-2017                                                            
+                                                                               
+% Set behavior for debug mode                                                  
+if nargin==0, tobError('do', 2, 'mask', {}); return; else store=[]; obs=[]; end
+                                                                               
+sr = 32000;
+
+l_frame = round(setting.reflen*sr);
+l_hop = 1*l_frame;
+
+switch setting.dataset
+    case 'noise'
+    case 'speech'
+        datapath = [config.inputPath 'rush/'];
+        rush_dir = dir(datapath);
+        rush_names = {rush_dir.name};
+        ind_wav = 0; % Real number of .wav files
+        for ind_file = 1:numel(rush_names)
+            if length(rush_names{ind_file}) > 4 && strcmp(rush_names{ind_file}(end-3:end), '.wav')
+                ind_wav = ind_wav+1;
+                file_path{ind_wav} = [datapath rush_names{ind_file}];
+            end
+        end
+    case 'urbansound8k'
+        ind_wav = 0; % Real number of .wav files
+        for ind_fold = 1:5
+            datapath = [config.inputPath 'UrbanSound8K/audio/fold' num2str(ind_fold) '/'];
+            us8k_dir = dir(datapath);
+            us8k_names = {us8k_dir.name};
+            for ind_file = 1:numel(us8k_names)
+                if length(us8k_names{ind_file}) > 4 && strcmp(us8k_names{ind_file}(end-3:end), '.wav')
+                    ind_wav = ind_wav+1;
[…]

### 2017-07-21 tobError/toerReport.m

@@ -1,0 +1,37 @@
+function config = toerReport(config)                      
+% toerReport REPORTING of the expLanes experiment tobError
+%    config = toerInitReport(config)                      
+%       config : expLanes configuration state             
+                                                          
+% Copyright: felix                                        
+% Date: 12-Jul-2017                                       
+                                                          
+if nargin==0, tobError('report', 'r'); return; end      
+                                                          
+% %% Noise
+% config = expExpose(config, 't', 'mask', {12, 1, 1, 0}, 'obs', 0, 'save', 'tobErr_n_rlen_f', 'step', 3);
+% config = expExpose(config, 't', 'mask', {0, 1, 1, 4}, 'obs', 0, 'save', 'tobErr_n_win_f', 'step', 3);
+% 
+% %% Speech
+% config = expExpose(config, 't', 'mask', {12, 2, 1, 0}, 'obs', 0, 'save', 'tobErr_s_rlen_f', 'step', 3);
+% config = expExpose(config, 't', 'mask', {0, 2, 1, 4}, 'obs', 0, 'save', 'tobErr_s_win_f', 'step', 3);
+% 
+% %% US8k
+% config = expExpose(config, 't', 'mask', {12, 3, 1, 0}, 'obs', 0, 'save', 'tobErr_u_rlen_f', 'step', 3);
+% config = expExpose(config, 't', 'mask', {0, 3, 1, 4}, 'obs', 0, 'save', 'tobErr_u_win_f', 'step', 3);
+
+% %% Noise
+% config = expExpose(config, 't', 'mask', {12, 1, 2, 4:10}, 'obs', 0, 'save', 'tobErr_n_rlen_s', 'step', 3);
+% config = expExpose(config, 't', 'mask', {0, 1, 2, 4}, 'obs', 0, 'save', 'tobErr_n_win_s', 'step', 3);
+% 
+% %% Speech
+% config = expExpose(config, 't', 'mask', {12, 2, 2, 4:10}, 'obs', 0, 'save', 'tobErr_s_rlen_s', 'step', 3);
+% config = expExpose(config, 't', 'mask', {0, 2, 2, 4}, 'obs', 0, 'save', 'tobErr_s_win_s', 'step', 3);
+% 
+% %% US8k
[…]

### 2017-07-21 censeCoder/ceco1representation.m
Revert "Add gh-pages"
This reverts commit db4c539bdd8d408756ce5762b8cde8dbc984a816.

@@ -1,184 +1,0 @@
-function [config, store, obs] = ceco1representation(config, setting, data)       
-% ceco1representation REPRESENTATION step of the expLanes experiment censeCoder  
-%    [config, store, obs] = ceco1representation(config, setting, data)           
-%      - config : expLanes configuration state                                   
-%      - setting   : set of factors to be evaluated                              
-%      - data   : processing data stored during the previous step                
-%      -- store  : processing data to be saved for the other steps               
-%      -- obs    : observations to be saved for analysis                         
-                                                                                 
-% Copyright: felix                                                               
-% Date: 20-Apr-2017                                                              
-                                                                                 
-% Set behavior for debug mode                                                    
-if nargin==0, censeCoder('do', 1, 'mask', {}); return; else store=[]; obs=[]; end
-                                                                                 
-addpath(genpath('C:\Program Files\MATLAB\R2015b\toolbox\rastamat'));
-addpath(genpath('util'));
-
-sr = 44100;
-%% Analysis window definition
-if strcmp(setting.desc, 'mel')
-    l_frame = 1024;
-    l_hop = 0.5*l_frame;
-    if setting.fps % 0 means none
-        n_fps = (sr+l_hop-l_frame)/l_hop; % Number of frames per second with base settings
-        n_avg = round(n_fps/setting.fps); % Number of consecutive frames to average into one
-        disp(['Chosen FPS is ' num2str(setting.fps) ', actual one is ' num2str(n_fps/n_avg) '.']);
-    end
-elseif strcmp(setting.desc, 'tob')
-    l_frame = (round(setting.toblen*sr)-mod(round(setting.toblen*sr), 2)); % Approximately 125ms, "fast" Leq
-    l_hop = round(setting.tobhop*l_frame);
-    %% Filterbank calculation, can be replaced with constant matrix
[…]

### 2017-07-21 censeCoder/ceco2coder.m

@@ -1,109 +1,0 @@
-function [config, store, obs] = ceco2coder(config, setting, data)                
-% ceco2coder CODER step of the expLanes experiment censeCoder                    
-%    [config, store, obs] = ceco2coder(config, setting, data)                    
-%      - config : expLanes configuration state                                   
-%      - setting   : set of factors to be evaluated                              
-%      - data   : processing data stored during the previous step                
-%      -- store  : processing data to be saved for the other steps               
-%      -- obs    : observations to be saved for analysis                         
-                                                                                 
-% Copyright: felix                                                               
-% Date: 20-Apr-2017                                                              
-                                                                                 
-% Set behavior for debug mode                                                    
-if nargin==0, censeCoder('do', 2, 'mask', {}); return; else store=[]; obs=[]; end
-           
-addpath(genpath('util'));
-
-if ~setting.quant
-    warning('Skipping ''coding'' step: no qauntization is applied, Huffman encoding cannot be applied.');
-    % Store
-    store.X_desc = data.X_desc;
-    % Observations
-    obs.code_len = [];
-    obs.bitrate = [];
-    return;
-end
-
-sr = 44100;
-%% Analysis window definition
-if strcmp(setting.desc, 'mel')
-    l_frame = 1024;
-    l_hop = 0.5*l_frame;
-    n_fps = 1+(sr-l_frame)/l_hop; % Number of frames per second with base settings
-    if setting.fps % 0 means none
-        n_avg = round(n_fps/setting.fps); % Number of consecutive frames to average into one
-        n_fps = n_fps/n_avg; % Number of frames per second with custom settings
-    else
-        n_fps = 1+(sr-l_frame)/l_hop; % Number of frames per second with base settings
-    end
-elseif strcmp(setting.desc, 'tob')
-    l_frame = (round(setting.toblen*sr)-mod(round(setting.toblen*sr), 2)); % Approximately 125ms, "fast" Leq
-    l_hop = setting.tobhop*l_frame;
-    n_fps = 1+(sr-l_frame)/l_hop;
-end
-
[…]

### 2017-07-21 censeCoder/ceco3decoder.m

@@ -1,179 +1,0 @@
-function [config, store, obs] = ceco3decoder(config, setting, data)              
-% ceco4decoder DECODER step of the expLanes experiment censeCoder                
-%    [config, store, obs] = ceco4decoder(config, setting, data)                  
-%      - config : expLanes configuration state                                   
-%      - setting   : set of factors to be evaluated                              
-%      - data   : processing data stored during the previous step                
-%      -- store  : processing data to be saved for the other steps               
-%      -- obs    : observations to be saved for analysis                         
-                                                                                 
-% Copyright: felix                                                               
-% Date: 27-Apr-2017                                                              
-                                                                                 
-% Set behavior for debug mode                                                    
-if nargin==0, censeCoder('do', 3, 'mask', {}); return; else store=[]; obs=[]; end
-                                                                                 
-addpath(genpath('C:\Program Files\MATLAB\R2015b\toolbox\rastamat'));
-addpath(genpath('util'));
-
-sr = 44100;
-%% Analysis window definition
-if strcmp(setting.desc, 'mel')
-    l_frame = 1024;
-    l_hop = 0.5*l_frame;
-    if setting.fps % 0 means none
-        n_fps = (sr+l_hop-l_frame)/l_hop; % Number of frames per second with base settings
-        n_avg = round(n_fps/setting.fps); % Number of consecutive frames to average into one
-    end
-elseif strcmp(setting.desc, 'tob')
-    l_frame = (round(setting.toblen*sr)-mod(round(setting.toblen*sr), 2)); % Approximately 125ms, "fast" Leq
-    l_hop = setting.tobhop*l_frame;
-    %% Filterbank calculation, can be replaced with constant matrix
-    N = 2^(ceil(log2(l_frame)));
-    N_filt = 2^17; % Design with a much greater precision
-    G = third_octave_filterbank(sr, N_filt, -17:13, 3);
[…]

### 2017-07-21 censeCoder/ceco4metrics.m

@@ -1,175 +1,0 @@
-function [config, store, obs] = ceco4metrics(config, setting, data)              
-% ceco3metrics METRICS step of the expLanes experiment censeCoder                
-%    [config, store, obs] = ceco3metrics(config, setting, data)                  
-%      - config : expLanes configuration state                                   
-%      - setting   : set of factors to be evaluated                              
-%      - data   : processing data stored during the previous step                
-%      -- store  : processing data to be saved for the other steps               
-%      -- obs    : observations to be saved for analysis                         
-                                                                                 
-% Copyright: felix                                                               
-% Date: 20-Apr-2017                                                              
-                                                                                 
-% Set behavior for debug mode                                                    
-if nargin==0, censeCoder('do', 4, 'mask', {}); return; else store=[]; obs=[]; end
-                                                                                 
-addpath(genpath('C:\Program Files\MATLAB\R2015b\toolbox\libsvm-3.22'));
-addpath(genpath('C:\Program Files\MATLAB\R2015b\toolbox\rastamat'));
-addpath(genpath('util'));
-
-switch setting.dataset
-    case 'speech' % Intelligibility I3 metric
-        sr = 44100;
-        l_frame = 1024;
-        l_hop = 0.5*l_frame;
-
-        if ispc; datapath = [config.inputPath 'rush\rush_clean_spec_' num2str(l_frame) '.mat']; else datapath = [config.inputPath 'rush/rush_clean_spec_' num2str(l_frame) '.mat']; end
-        if exist(datapath)
-            load(datapath);
-        else
-            if ispc; datapath = [config.inputPath 'rush\']; else datapath = [config.inputPath 'rush/']; end
-            rush_dir = dir(datapath);
-            rush_names = {rush_dir.name};
-            ind_wav = 0; % Real number of .wav files
-            for ind_file = 1:numel(rush_names)
[…]

### 2017-07-21 censeCoder/cecoInit.m

@@ -1,10 +1,0 @@
-function [config, store] = cecoInit(config)                        
-% cecoInit INITIALIZATION of the expLanes experiment censeCoder    
-%    [config, store] = cecoInit(config)                            
-%      - config : expLanes configuration state                     
-%      -- store  : processing data to be saved for the other steps 
-                                                                   
-% Copyright: felix                                                 
-% Date: 20-Apr-2017                                                
-                                                                   
-if nargin==0, censeCoder(); return; else store=[];  end            

### 2017-07-21 censeCoder/cecoReport.m

@@ -1,100 +1,0 @@
-function config = cecoReport(config)                        
-% cecoReport REPORTING of the expLanes experiment censeCoder
-%    config = cecoInitReport(config)                        
-%       config : expLanes configuration state               
-                                                            
-% Copyright: felix                                          
-% Date: 20-Apr-2017                                         
-                                                            
-if nargin==0, censeCoder('report', 'r'); return; end%censeCoder('report', 'rhv'); return; end      
-
-% {fps, mel, quant, dictgen, htreealg, textframe, dataset, classmethod, phaserec, desc, intelind, tobhop}
-
-%%% censeCoder('do', [step], 'mask', {fps, mel, quant, dictgen, htreealg, textframe, dataset, classmethod, phaserec, desc, intelind, tobhop});
-%%% Error - All quant
-% censeCoder('do', [1], 'mask', {-1, -1, 0, -1, -1, -1, 0, -1, -1, 2, -1, 2}); % Third-octave bands
-%%% Bitrate - All quant
-% censeCoder('do', [2], 'mask', {-1, -1, 0, 1, 2, 10, 2, -1, -1, 2, -1, 2});
-%%% Class - All quant
-% censeCoder('do', [4], 'mask', {-1, -1, 0, -1, -1, -1, 2, 1, -1, 2, -1, 2});
-% censeCoder('do', [4], 'mask', {-1, -1, 0, -1, -1, -1, 2, 2:4, -1, 2, -1, 2});
-%%% Intel indicators - All quant
-% censeCoder('do', [2 3 4], 'mask', {-1, -1, 2:6, 1, 2, 10, 1, -1, 1, 2, 0, 2});
-
-%%% Error/Class - No averaging, 30 bands, no quant
-% censeCoder('do', [1 4], 'mask', {7, 3, 1, -1, -1, -1, 2, 0, -1, 1, -1, -1});
-%%% Error/Bitrate/Class - No averaging, 30 bands, all quant
[…]

### 2017-07-21 censeCoder/censeCoder.m

@@ -1,190 +1,0 @@
-function censeCoder(varargin)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   
-% Welcome to the main entry point of censeCoder                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 
-% Please DO NOT modify this file unless you have a precise intent.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              
-                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                
-shortExperimentName = 'ceco';                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   
-[p, experimentName] = fileparts(mfilename('fullpath'));                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         
[…]

### 2017-07-21 censeCoder/perc_int.m

@@ -1,116 +1,0 @@
-function perc_int(act)
-
-if ~nargin; act = 'disp'; end;
-
-switch act
-    case 'test'
-        if exist('subj_notes.mat', 'file')
-            load('subj_notes.mat');
-            ind_test = length(subj_notes)+1;
-        else
-            q = 8;
-            toblen = 1000*[0.02 0.06 0.125 0.25];
-            ind_test = 1;
-        end
-        n_sen = 9;
-        sen_sfx = {'_C_1', '_C_2', '_F_1', '_F_2', '_Q_1', '_Q_2', '_S_1', '_S_2', '_S_3'};
-        subj_notes{ind_test} = zeros(2*n_sen, 1)-1;
-        sentences_tr{ind_test} = cell(2*n_sen, 1);
-        sp_cnt = zeros(6, 1); % Speaker test count
-        
-        
-        
-        % High fps
-        sen = randperm(n_sen);
-        set_cnt = round(rand(1, 1))+4;
-        setting{ind_test}(:, 1:n_sen) = [sen; [ones(1, set_cnt) 2*ones(1, n_sen-set_cnt)]];
-        
-        % Low fps
-        sen = randperm(n_sen);
-        set_cnt = round(rand(1, 1))+4;
-        setting{ind_test}(:, n_sen+1:2*n_sen) = [sen; [3*ones(1, set_cnt) 4*ones(1, n_sen-set_cnt)]];
-        
-        rp = randperm(size(setting{ind_test}, 2));
-        setting{ind_test} = setting{ind_test}(:, rp);
-
-        for ind_setting = 1:size(setting{ind_test}, 2)
-            clc;
-            disp('----- Perceptive test on intelligibility -----');
-            disp(['Test number ' num2str(ind_test) '.']);
-            disp(['Sample ' num2str(ind_setting) ' of ' num2str(size(setting{ind_test}, 2)) '.']);
-            sp = round(6*rand(1, 1)+0.5);
-            while sp_cnt(sp) > 3; sp = round(6*rand(1, 1)+0.5); end
-            sp_cnt(sp) = sp_cnt(sp)+1;
-            
-            [y, Fs] = audioread(['../../decoded_samples/perc_int/' num2str(sp) sen_sfx{setting{ind_test}(1, ind_setting)} '_q8_l' num2str(toblen(setting{ind_test}(2, ind_setting))) '.wav']);
-            
[…]

### 2017-07-21 censeCoder/report_figs.m

@@ -1,172 +1,0 @@
-clear all, close all, clc;
-
-real_fps = {'2', '4.1', '6.1', '7.7', '9.5', '21', '85'};
-fps_lgd = cell(1, length(real_fps));
-for ind_lgd = 1:length(real_fps)
-    fps_lgd{ind_lgd} = ['fps: ' real_fps{ind_lgd}];
-end
-
-%% Bitrate
-% fig = openfig('report/figures/bitrate_fps_mel_8.fig');
-% figure(fig);
-% ax = gca;
-% ax.XTickLabels = real_fps;
-% xlabel('Frames per second'), ylabel('Output bitrate (kbit/s)'), grid on;
-% for ind_ylbl = 1:length(ax.YTickLabels)
-%     ax.YTickLabels{ind_ylbl} = num2str(str2double(ax.YTickLabels{ind_ylbl})/1000);
-% end
-% legend('Location', 'northwest');
-% print(fig, '-dpdf', 'report/figures/processed/bitrate_fps_mel.pdf');
-% close all;
-
-%% KNN accuracy
-% fig = openfig('report/figures/knn_fps_mel_8.fig');
-% figure(fig);
-% ax = gca;
-% ax.XTickLabels = real_fps;
-% xlabel('Frames per second'), ylabel('KNN-5 accuracy'), grid on;
-% load('report/tables/knn_base.mat');
-% hold on, errorbar(7.15, data.meanData, data.stdData, 'LineWidth', 2, 'color', 'black', 'marker', 'x')
-% legend({'mel: 10', 'mel: 20', 'mel: 30', 'mel: 40', 'baseline'}, 'Location', 'southeast');
-% print(fig, '-dpdf', 'report/figures/processed/knn_fps_mel.pdf');
-% close all;
-
-%% CSII
-% fig = openfig('report/figures/csii_fps_mel_8.fig');
-% figure(fig);
-% xlabel('Mel bands'), ylabel('CSII indicator'), grid on;
-%load('report/tables/csii_base.mat');
-%hold on, plot(4, data.meanData, 'LineWidth', 2, 'color', 'black', 'marker', 'x')
-%legend([fps_lgd {'baseline'}], 'Location', 'northwest');
-%axis([0.5 4.5 0.3 0.65]);
-% print(fig, '-dpdf', 'report/figures/processed/csii_fps_mel.pdf');
-% close all;
-
-%% Error
[…]

### 2017-07-21 censeCoder/run_script.m

@@ -1,37 +1,0 @@
-clear all, close all, clc;
-
-%% Global run
-%%% censeCoder('do', [step], 'mask', {fps, mel, quant, dictgen, htreealg, textframe, dataset, classmethod, phaserec, desc, intelind, tobhop, toblen});
-%%% Error - All quant
-% censeCoder('do', [1], 'mask', {-1, -1, 0, -1, -1, -1, 0, -1, -1, 2, -1, 2}); % Third-octave bands
-%%% Bitrate - All quant
-% censeCoder('do', [2], 'mask', {-1, -1, 0, 1, 2, 10, 2, -1, -1, 2, -1, 2});
-%%% Class - All quant
-% censeCoder('do', [4], 'mask', {-1, -1, 0, -1, -1, -1, 2, 1, -1, 2, -1, 2});
-% censeCoder('do', [4], 'mask', {-1, -1, 0, -1, -1, -1, 2, 2:4, -1, 2, -1, 2});
-%%% Intel indicators - All quant
-% censeCoder('do', [2 3 4], 'mask', {-1, -1, 2:6, 1, 2, 10, 1, -1, 1, 2, 0, 2});
-
-%%% Error/Class - No averaging, 30 bands, no quant
-% censeCoder('do', [1 4], 'mask', {7, 3, 1, -1, -1, -1, 2, 0, -1, 1, -1, -1});
-%%% Error/Bitrate/Class - 8 fps, 40 bands, all quant
-% censeCoder('do', [1 2], 'mask', {4, 4, 2:6, 1, 2, 10, 2, -1, -1, 1, -1, -1});
-% censeCoder('do', [4], 'mask', {7, 4, 2:6, 1, 2, 10, 2, 0, -1, 1, -1, -1});
-% censeCoder('do', [1 4], 'mask', {7, 4, 1, 1, 2, 10, 2, 0, -1, 1, -1, -1});
-
-% censeCoder('do', [1 2 4], 'mask', {7, 4, 2:6, 1, 2, 10, 2, 0, -1, 1, -1, -1});
-%%% Error/Bitrate/Class - All mel settings, 8 bit
-% censeCoder('do', [2], 'mask', {1:5, 0, 6, 1, 2, 10, 2, 0, -1, 1, -1, -1});
[…]

### 2017-07-21 censeCoder/util/delta_dec.m

@@ -1,12 +1,0 @@
-function x_d = delta_dec(x_c)
-
-assert(isvector(x_c));
-
-x_d = zeros(size(x_c));
-prev = 0;
-for indel = 1:length(x_c)
-    x_d(indel) = x_c(indel) + prev;
-    prev = x_d(indel);
-end
-
-end

### 2017-07-21 censeCoder/util/delta_enc.m

@@ -1,20 +1,0 @@
-function x_c = delta_enc(x)
-
-if isvector(x)
-    x_c = zeros(size(x));
-    prev = 0;
-    for indel = 1:length(x)
-        x_c(indel) = x(indel) - prev;
-        prev = x(indel);
-    end
-else
-    assert(ndims(x)<=2);
-    x_c = zeros(size(x));
-    prev = 0;
-    for indel = 1:size(x, 2)
-        x_c(:, indel) = x(:, indel) - prev;
-        prev = x(:, indel);
-    end
-end
-
-end

### 2017-07-21 censeCoder/util/huff_dict.m

@@ -1,80 +1,0 @@
-function [symbol, prob, prob_time] = huff_dict(x, mode, nbits)
-
-assert(isvector(x), 'x must be a vector.');
-if nargin < 2;
-    mode = 'seq';
-end
-
-if strcmp(mode, 'seq')
-    %% Sequential search
-    tic;
-    symbol = [];
-    count = [];
-    for inds = 1:length(x)
-        found = 0;
-        for indd = 1:length(symbol)
-            if symbol(indd) == x(inds)
-                count(indd) = count(indd) + 1;
-                found = 1;
-                break;
-            end
-        end
-        if found == 0
-            symbol(end+1) = x(inds);
-            count(end+1) = 1;
-        end
-    end
-    prob = count/length(x);
-    prob_time = toc;
-    disp(['Sequential algorithm complete. Time elapsed is ' num2str(prob_time) ' seconds.']);
-elseif strcmp(mode, 'sort')
-    %% Sorting
-%     tic;
-    x_sort = sort(x);
-    symbol = x_sort(1);
-    count = 0;
-    cur_ind = 1;
-
-    while true
-        next_ind = cur_ind-1+find(x_sort(cur_ind:end)~=symbol(end), 1);
-        if ~isempty(next_ind)
-            count(end) = count(end)+next_ind-cur_ind;
-        else
-            count(end) = count(end)+length(x_sort)-cur_ind+1;
-            break;
-        end
-        symbol(end+1) = x_sort(next_ind);
-        count(end+1) = 0;
-        cur_ind = next_ind;
-    end
-    prob = count/length(x);
-%     prob_time = toc;
-%     disp(['Sorting algorithm complete. Time elapsed is ' num2str(prob_time) ' seconds.']);
-elseif strcmp(mode, 'unique')
-    tic;
-%     symbol = unique(x);
-    %% ADDED TO GENERATE A GLOBAL DICTIONNARY - EVERY CASE IS NEEDED
-    symbol = (-2^(nbits-1):2^(nbits-1)-1);
-    count = zeros(size(symbol));
-    parfor ind_sym = 1:length(symbol)
-        %disp(num2str(symbol(ind_sym)));
-        count(ind_sym) = count(ind_sym)+sum(x==symbol(ind_sym));
-    end
-    sym_zero = count == 0;
-    count(sym_zero) = 1;
-    prob = count/(length(x)+sum(sym_zero));
-    %% END
[…]

### 2017-07-21 censeCoder/util/istft.m

@@ -1,33 +1,0 @@
-function x = istft(x_stft, l_frame, l_hop, wintype)
-
-if nargin < 4
-    wintype = 'hamming'; % Default window: hamming
-end
-
-n_win = size(x_stft, 2);
-l_win = l_frame;%(size(x_stft, 1)-1)*2;
-x_stft = [x_stft; conj(flipud(x_stft(2:end-1, :)))];
-%% Window generation
-switch wintype % Other windows to implement
-    case 'hamming'
-        w = hamming(l_win, 'periodic');
-    case 'hanning'
-        w = hanning(l_win, 'periodic');
-    case 'rect'
-        w = ones(l_win, 1);
-end
-
-%% Inverse STFT
-x = zeros(l_win+(n_win-1)*l_hop, 1);
-w_norm = zeros(size(x));
-for indwin = 1:n_win
-    indt = (indwin-1)*l_hop; % Start time of the current window
-    x_temp = x_stft(:, indwin);
-    x_temp = real(ifft(x_temp));
-    x(indt+1:indt+l_win) = x(indt+1:indt+l_win) + x_temp(1:l_win).*w;
-    w_norm(indt+1:indt+l_win) = w_norm(indt+1:indt+l_win)+w.^2;
-end
-x = x./w_norm;
-
-end
-

### 2017-07-21 censeCoder/util/sroexfilter.m

@@ -1,23 +1,0 @@
-function w = sroexfilter(f)
-% Simplified rounded exponential (ro-ex) filterbank (with equal
-% band-importance critical bands)
-
-% Zwicker & Terhardt, Analytical expressions for critical-band rate and critical bandwidth as a function of frequency, 1980
-% ANSI S3.5-1997
-q = [.35 .45 .57 .7 .84 1 1.17 1.37 1.6 1.85 2.15 2.5 2.9 3.4 4 4.8 5.8];
-
-%f_l = [.3 .4 .51 .63 .77 .92 1.08 1.27 1.48 1.72 2 2.32 2.7 3.15 3.7 4.4 5.3];
-%f_u = [.4 .51 .63 .77 .92 1.08 1.27 1.48 1.72 2 2.32 2.7 3.15 3.7 4.4 5.3 6.4];
-%erb = (f_u-f_l);
-% Moore & Glasberg, Suggested formulae for calculating auditory-filter bandwidths and excitation patterns, 1983
-erb = 24.7*(4.37*q+1);
-% Glasberg & Moore, Derivation of auditory filter shapes from notched-noise data, 1990
-%erb = 6.23*q.^2+93.39*q+28.52;
-
-p = 4*1000*q./erb;
-g = abs(1-repmat(f, 1, length(q))./repmat(q, length(f), 1));
-
-% Simplified ro-ex filter bank
-w = (1+repmat(p, length(f), 1).*g).*exp(-repmat(p, length(f), 1).*g);
-
-end

### 2017-07-21 censeCoder/util/stft.m

@@ -1,36 +1,0 @@
-function x_stft = stft(x, l_win, l_hop, wintype, zero_pad)
-
-if nargin < 4
-    wintype = 'hamming'; % Default window: hamming
-end
-if nargin < 3
-    l_hop = round(0.5*l_win); % Default overlap: 50%
-end
-
-n_win = 1+(length(x)-l_win)/l_hop; % Number of windows
-
-%% Window generation
-switch wintype % Other windows to implement
-    case 'hamming'
-        w = hamming(l_win, 'periodic');
-    case 'hanning'
-        w = hanning(l_win, 'periodic');
-    case 'rect'
-        w = ones(l_win, 1);
-end
-
-if zero_pad; n_pad = 2^(ceil(log2(l_win)))-l_win; else n_pad = 0; end; % Zero pad to next power of 2
-%% STFT
-x_stft = zeros(l_win+n_pad, n_win);
-for indwin = 1:n_win
-    
-    %% Windowing
-    x_win = [x((indwin-1)*l_hop+1:(indwin-1)*l_hop+l_win).*w; zeros(n_pad, 1)];
-    %% FFT
-    x_stft(:, indwin) = fft(x_win); % FFT magnitude
-end
-
-x_stft = x_stft(1:end/2+1,:);
-
-end
-

### 2017-07-21 censeCoder/util/third_octave_filterbank.m

@@ -1,71 +1,0 @@
-function G = third_octave_filterbank(sr, N, bands, l)
-
-f = (0:sr/N:sr/2);
-
-wm  = 2*pi*10^3 * (2 .^ (bands/3)); % 20Hz-20kHz bands center freqs
-wd = 2^(1/6);
-w2 = wm * wd; % Upper bandedge freqs
-w1 = wm / wd; % Lower bandedge freqs
-ws = 2*pi*sr;
-
-k_i = round(N*w1/ws)+1;
-k2 = round(N*w2/ws)+1;
-N_i = k2-k_i;
-d_i = N./(2*N_i);
-
-% l = 2;
-G = zeros(length(wm), N/2+1);
-for ind_wm = 1:length(wm)
-    % Construct freq weights G
-    if ind_wm == 1 % No ind_wm-1 this time
-        P = round(N*(wm(ind_wm)-w1(ind_wm))/ws)-1; % Antoni, right
-    else
-        % P = round(N*(wm(ind_wm)-w1(ind_wm))/ws)-1; % Antoni, wrong
-        P = round(N*(w1(ind_wm)-wm(ind_wm-1))/ws)-1; % Right
-    end
-    if P < 1
-        warning(['Not enough fft points for analysis at center frequency fm = ' num2str(wm(ind_wm)/2/pi) '. G = 1 at closest frequency fm = ' num2str(f(round(N*wm(ind_wm)/ws)+1)) ' and G = 0 otherwise.']);
-        nep(ind_wm) = 1;
-        G(ind_wm, round(N*wm(ind_wm)/ws)+1) = 1;
-    else
-        nep(ind_wm) = 0;
-        p = -P:P;
-        phi = .5*(p./P+1);
-        % We found that inverting cos and sin seemed better
-        for ind_l = 1:l
-            phi = sin(pi/2*phi).^2;
-%             plot(phi)
-        end
-        G(ind_wm, k_i(ind_wm)+p(1):k_i(ind_wm)+p(end)) = sin(pi/2*phi);
-        if ind_wm>1
-            G(ind_wm-1, k_i(ind_wm)+p(1):k_i(ind_wm)+p(end)) = cos(pi/2*phi);
-        end
-%          plot(G')
-    end
-end
-P = round(N*(w1(end)*wd*wd-wm(end))/ws)-1;
-p = -P:P;
-phi = .5*(p./P+1);
-for ind_l = 1:l
[…]

### 2017-07-21 tobError/report_figs.m

@@ -1,281 +1,0 @@
-clear all, close all, clc;
-
-%% Reference length
-% load('report/figures/tobErr_n_rlen_f.mat');
-% % load('report/figures/tobErr_s_rlen.mat');
-% % load('report/figures/tobErr_u_rlen.mat');
-% 
-% for ind_rlen = 1:length(data.rawData)
-%     errMean(:, ind_rlen) = data.rawData{ind_rlen}.errMean;
-%     errStd(:, ind_rlen) = data.rawData{ind_rlen}.errStd;
-% end
-% 
-% tob_f  = 10^3 * (2 .^ ([-17:11]/3));
-% 
-% figure(1), clf, errorbar(tob_f(2:end), errMean(2:end, 1), errStd(2:end, 1), '-x'), hold on,
-% for ind_rlen = 2:size(errMean, 2)
-%     errorbar(tob_f(2:end), errMean(2:end, ind_rlen), errStd(2:end, ind_rlen), '-x')
-% end
-% set(gca, 'xscale', 'log');
-% grid on, legend('0.125~s', '0.25~s', '0.5~s', '1~s', '1.5~s', '2~s', '2.5~s', '3~s', '3.5~s', '4~s')%, axis([3.5 8.5 0 5.5])
-% xlabel('Frequency'), ylabel('Measurement error (dB)')
-
-%% Window type
-% load('report/figures/tobErr_n_win.mat');
-% % load('report/figures/tobErr_s_win.mat');
-% % load('report/figures/tobErr_u_win.mat');
-% 
-% for ind_rlen = 1:length(data.rawData)
-%     errMean(:, ind_rlen) = data.rawData{ind_rlen}.errMean;
-%     errStd(:, ind_rlen) = data.rawData{ind_rlen}.errStd;
-% end
-% 
-% tob_f  = 10^3 * (2 .^ ([-17:11]/3));
-% 
-% figure(1), clf, errorbar(tob_f(2:end), errMean(2:end, 1), errStd(2:end, 1), '-x'), hold on,
-% for ind_rlen = 2:size(errMean, 2)
-%     errorbar(tob_f(2:end), errMean(2:end, ind_rlen), errStd(2:end, ind_rlen), '-x')
-% end
-% set(gca, 'xscale', 'log');
[…]

### 2017-07-21 tobError/run_script.m

@@ -1,33 +1,0 @@
-%clear all, close all, clc;
-
-%% Noise
-% tobError('do', 1:3, 'mask', {0, 1, 1, 4});
-% tobError('do', 1:3, 'mask', {12, 1, 1, 0});
-
-%% Speech
-% tobError('do', 1:3, 'mask', {0, 2, 1, 4, 2});
-% tobError('do', 1:3, 'mask', {12, 2, 1, 0, 2});
-
-%% US8k
-% tobError('do', 1:3, 'mask', {0, 3, 1, 4});
-% tobError('do', 1:3, 'mask', {12, 3, 1, 0});
-
-%% Noise
-% tobError('do', 1:3, 'mask', {0, 1, 2, 4});
-% tobError('do', 1:3, 'mask', {12, 1, 2, 4:10});
-
-%% Speech
-% tobError('do', 1:3, 'mask', {0, 2, 2, 4});
-% tobError('do', 1:3, 'mask', {12, 2, 2, 4:10});
-
-%% US8k
-% tobError('do', 1:3, 'mask', {0, 3, 2, 4});
-% tobError('do', 1:3, 'mask', {12, 3, 2, 4:10});
-
-%% Noise
-% tobError('do', [1 2 3], 'mask', {12, 1, 1, 4, 2});
-% tobError('do', [3], 'mask', {12, 1, 1, 4, 2});
-% [1 6 12 17]
-% tobError('do', [1 3], 'mask', {12, 1, 2, 6, 2});
-tobError('do', [3], 'mask', {17, 3, 0, 6, 2});
-

### 2017-07-21 tobError/stft.m

@@ -1,64 +1,0 @@
-function x_stft = stft(x, l_win, l_hop, wintype, zero_pad, winparam)
-
-if nargin < 4
-    wintype = 'hamming'; % Default window: hamming
-end
-if nargin < 3
-    l_hop = round(0.5*l_win); % Default overlap: 50%
-end
-
-n_win = 1+(length(x)-l_win)/l_hop; % Number of windows
-
-%% Window generation
-switch wintype % Other windows to implement
-    case 'hamming'
-        w = hamming(l_win, 'periodic');
-    case 'hanning'
-        w = hanning(l_win, 'periodic');
-    case 'blackmanharris'
-        w = blackmanharris(l_win, 'periodic');
-    case 'bartlett'
-        w = bartlett(l_win);
-    case 'bartletthann'
-        w = barthannwin(l_win);
-    case 'gaussian'
-        w = gausswin(l_win);
-    case 'kaiser'
-        w = kaiser(l_win, 0.25);
-    case 'tukey01'
-        w = tukeywin(l_win, 0.1);
-    case 'tukey02'
-        w = tukeywin(l_win, 0.2);
-    case 'tukey03'
-        w = tukeywin(l_win, 0.3);
-    case 'tukey04'
-        w = tukeywin(l_win, 0.4);
-    case 'tukey05'
-        w = tukeywin(l_win, 0.5);
-    case 'tukey06'
-        w = tukeywin(l_win, 0.6);
-    case 'tukey07'
-        w = tukeywin(l_win, 0.7);
-    case 'tukey08'
-        w = tukeywin(l_win, 0.8);
-    case 'tukey09'
-        w = tukeywin(l_win, 0.9);
-    case 'rect'
-        w = ones(l_win, 1);
-end
-
-if zero_pad; n_pad = 2^(ceil(log2(l_win)))-l_win; else n_pad = 0; end; % Zero pad to next power of 2
-%% STFT
-x_stft = zeros(l_win+n_pad, n_win);
-for indwin = 1:n_win
-    
-    %% Windowing
-    x_win = [x((indwin-1)*l_hop+1:(indwin-1)*l_hop+l_win).*w; zeros(n_pad, 1)];
-    %% FFT
-    x_stft(:, indwin) = fft(x_win); % FFT magnitude
-end
-
-x_stft = x_stft(1:end/2+1,:);
-
-end
-

### 2017-07-21 tobError/tobError.m

@@ -1,190 +1,0 @@
-function tobError(varargin)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     
-% Welcome to the main entry point of tobError                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   
-% Please DO NOT modify this file unless you have a precise intent.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              
-                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                
-shortExperimentName = 'toer';                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   
-[p, experimentName] = fileparts(mfilename('fullpath'));                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         
[…]

### 2017-07-21 tobError/toer1cense.m

@@ -1,169 +1,0 @@
-function [config, store, obs] = toer1cense(config, setting, data)              
-% toer1cense CENSE step of the expLanes experiment tobError                    
-%    [config, store, obs] = toer1cense(config, setting, data)                  
-%      - config : expLanes configuration state                                 
-%      - setting   : set of factors to be evaluated                            
-%      - data   : processing data stored during the previous step              
-%      -- store  : processing data to be saved for the other steps             
-%      -- obs    : observations to be saved for analysis                       
-                                                                               
-% Copyright: felix                                                             
-% Date: 12-Jul-2017                                                            
-                                                                               
-% Set behavior for debug mode                                                  
-if nargin==0, tobError('do', 1, 'mask', {}); return; else store=[]; obs=[]; end
-                                                                               
-sr = 32000;
-
-l_frame = round(setting.framelen*sr);
-if setting.framelen == 0.125; l_hop = 1*l_frame; else l_hop = 0.5*l_frame; end
-
-N = 2^(ceil(log2(l_frame)));
-N_filt = 2^20; % Design with a much higher precision
-G = third_octave_filterbank(sr, N_filt, -17:11, 3);
-switch setting.gcalc
-    case 'sub'
-        G = G(:, 1:round(N_filt/N):end); % Only take the resolution needed
-        H_st = G.^2;
-    case 'mean'
-        G = G.^2;
-        G_mean(:, 1) = mean(G(:, 1:1+round(N_filt/(2*N))), 2);
-        G_mean(:, N/2+1) = mean(G(:, 1+(N/2)*round(N_filt/N)-round(N_filt/(2*N)):end), 2);
-        for ind_f = 2:N/2
-            G_mean(:, ind_f) = mean(G(:, 1+(ind_f-1)*round(N_filt/N)-round(N_filt/(2*N)):1+(ind_f-1)*round(N_filt/N)+round(N_filt/(2*N))), 2);
-        end
-        H_st = G_mean;
-        clear ind_f G_mean;
-    case 'dec'
-        for ind_b = 1:size(G, 1)
[…]

### 2017-07-21 tobError/toer2ref_ita.m

@@ -1,108 +1,0 @@
-function [config, store, obs] = toer2ref_ita(config, setting, data)            
-% toer2ref_ita REF_ITA step of the expLanes experiment tobError                
-%    [config, store, obs] = toer2ref_ita(config, setting, data)                
-%      - config : expLanes configuration state                                 
-%      - setting   : set of factors to be evaluated                            
-%      - data   : processing data stored during the previous step              
-%      -- store  : processing data to be saved for the other steps             
-%      -- obs    : observations to be saved for analysis                       
-                                                                               
-% Copyright: felix                                                             
-% Date: 12-Jul-2017                                                            
-                                                                               
-% Set behavior for debug mode                                                  
-if nargin==0, tobError('do', 2, 'mask', {}); return; else store=[]; obs=[]; end
-                                                                               
-sr = 32000;
-
-l_frame = round(setting.reflen*sr);
-l_hop = 1*l_frame;
-
-switch setting.dataset
-    case 'noise'
-    case 'speech'
-        datapath = [config.inputPath 'rush/'];
-        rush_dir = dir(datapath);
-        rush_names = {rush_dir.name};
-        ind_wav = 0; % Real number of .wav files
-        for ind_file = 1:numel(rush_names)
-            if length(rush_names{ind_file}) > 4 && strcmp(rush_names{ind_file}(end-3:end), '.wav')
-                ind_wav = ind_wav+1;
-                file_path{ind_wav} = [datapath rush_names{ind_file}];
-            end
-        end
-    case 'urbansound8k'
-        ind_wav = 0; % Real number of .wav files
-        for ind_fold = 1:5
-            datapath = [config.inputPath 'UrbanSound8K/audio/fold' num2str(ind_fold) '/'];
-            us8k_dir = dir(datapath);
-            us8k_names = {us8k_dir.name};
-            for ind_file = 1:numel(us8k_names)
-                if length(us8k_names{ind_file}) > 4 && strcmp(us8k_names{ind_file}(end-3:end), '.wav')
-                    ind_wav = ind_wav+1;
[…]

### 2017-07-21 tobError/toer3error.m

@@ -1,59 +1,0 @@
-function [config, store, obs] = toer3error(config, setting, data)              
-% toer3error ERROR step of the expLanes experiment tobError                    
-%    [config, store, obs] = toer3error(config, setting, data)                  
-%      - config : expLanes configuration state                                 
-%      - setting   : set of factors to be evaluated                            
-%      - data   : processing data stored during the previous step              
-%      -- store  : processing data to be saved for the other steps             
-%      -- obs    : observations to be saved for analysis                       
-                                                                               
-% Copyright: felix                                                             
-% Date: 12-Jul-2017                                                            
-                                                                               
-% Set behavior for debug mode                                                  
-if nargin==0, tobError('do', 3, 'mask', {}); return; else store=[]; obs=[]; end
-                                                                               
-data_cen = expLoad(config, [], 1);
-
-assert(setting.reflen>=setting.framelen);
-err_cen_ref = [];
-r_level = [];
-for ind_wav = 1:length(data.X_tob_ref)
-    if setting.framelen == 0.125
-        X_tob_cen = [];
-        if strcmp(setting.dataset, 'noise'); n_ref = 1; else n_ref = size(data.X_tob_ref{ind_wav}, 2)-1; end
-        if n_ref > 0
-            for ind_ref = 1:n_ref
-                n_avg = round(setting.reflen/setting.framelen);
-                X_tob_cen(:, ind_ref) = mean(data_cen.X_tob_cen{ind_wav}(:, (ind_ref-1)*n_avg+1:min(ind_ref*n_avg, end))/4096, 2);
-                X_tob_cen(X_tob_cen == 0) = eps;
-            end
-            err_cen_ref = [err_cen_ref 10*log10(X_tob_cen)-10*log10(data.X_tob_ref{ind_wav}(:, 1:n_ref))];
-%             r_level = [r_level max(10*log10(data.X_tob_ref{ind_wav}(:, 1:n_ref)))-10*log10(data.X_tob_ref{ind_wav}(18, 1:n_ref))];
-        end
-    else
-        X_tob_cen = [];
[…]

### 2017-07-21 tobError/toerInit.m

@@ -1,10 +1,0 @@
-function [config, store] = toerInit(config)                        
-% toerInit INITIALIZATION of the expLanes experiment tobError      
-%    [config, store] = toerInit(config)                            
-%      - config : expLanes configuration state                     
-%      -- store  : processing data to be saved for the other steps 
-                                                                   
-% Copyright: felix                                                 
-% Date: 12-Jul-2017                                                
-                                                                   
-if nargin==0, tobError(); return; else store=[];  end              

### 2017-07-21 tobError/toerReport.m

@@ -1,37 +1,0 @@
-function config = toerReport(config)                      
-% toerReport REPORTING of the expLanes experiment tobError
-%    config = toerInitReport(config)                      
-%       config : expLanes configuration state             
-                                                          
-% Copyright: felix                                        
-% Date: 12-Jul-2017                                       
-                                                          
-if nargin==0, tobError('report', 'r'); return; end      
-                                                          
-% %% Noise
-% config = expExpose(config, 't', 'mask', {12, 1, 1, 0}, 'obs', 0, 'save', 'tobErr_n_rlen_f', 'step', 3);
-% config = expExpose(config, 't', 'mask', {0, 1, 1, 4}, 'obs', 0, 'save', 'tobErr_n_win_f', 'step', 3);
-% 
-% %% Speech
-% config = expExpose(config, 't', 'mask', {12, 2, 1, 0}, 'obs', 0, 'save', 'tobErr_s_rlen_f', 'step', 3);
-% config = expExpose(config, 't', 'mask', {0, 2, 1, 4}, 'obs', 0, 'save', 'tobErr_s_win_f', 'step', 3);
-% 
-% %% US8k
-% config = expExpose(config, 't', 'mask', {12, 3, 1, 0}, 'obs', 0, 'save', 'tobErr_u_rlen_f', 'step', 3);
-% config = expExpose(config, 't', 'mask', {0, 3, 1, 4}, 'obs', 0, 'save', 'tobErr_u_win_f', 'step', 3);
-
-% %% Noise
-% config = expExpose(config, 't', 'mask', {12, 1, 2, 4:10}, 'obs', 0, 'save', 'tobErr_n_rlen_s', 'step', 3);
-% config = expExpose(config, 't', 'mask', {0, 1, 2, 4}, 'obs', 0, 'save', 'tobErr_n_win_s', 'step', 3);
-% 
-% %% Speech
-% config = expExpose(config, 't', 'mask', {12, 2, 2, 4:10}, 'obs', 0, 'save', 'tobErr_s_rlen_s', 'step', 3);
-% config = expExpose(config, 't', 'mask', {0, 2, 2, 4}, 'obs', 0, 'save', 'tobErr_s_win_s', 'step', 3);
-% 
-% %% US8k
[…]

### 2017-07-21 paper/article.tex
Paper corrections

@@
 
-Objective intelligibility metrics are then computed for the encoder's settings under evaluation and compared to the results of the perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{http://}}.
+Objective intelligibility metrics are then computed for the encoder's settings under evaluation and compared to the results of the perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/}}.
 The results of the perceptual test is evaluated using the average intelligibility score (AIS) given by the subjects and the ineligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
@@
 	\caption{Average intellibility score (AIS) given by the subjects and the inteligibility ratio (IR) as a function of the frame rate.
-Inintelligibility appears at around 10~Hz, corresponding to the average duration of a phoneme.
-\fg{update legend with acronyms}}
+Inintelligibility appears at around 10~Hz, corresponding to the average duration of a phoneme.}
 	\label{fig:subj_int}
@@
 	\item precision: the impact of the quantization step for 8 bits codewords is found to be negligible compared to sensor precision of class 2 sensors
-	\item efficiency: for fast and slow modes, the bitrate is respectively about \fg{numbers} kbps for the high precision mode
+	\item efficiency: for fast and slow modes, the bitrate is respectively about 1.4~kbps and 0.4~kbps for the high precision mode
 	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible.
@@
 
-%\ml{USE BIBTEX !!}
-%\bibliography{mybib}{}
-%
-%
-%\begin{thebibliography}{09}
-%
-%\bibitem{gozalo2015}
-%Rey Gozalo, G.
-and Trujillo Carmona, J.
-and Barrigon Morillas, J.M.
-and Gomez Escobar, V.
-(2015).
-Relationship between objective acoustic indices and subjective assessments for the quality of soundscapes.
-\textit{Applied Acoustics}, 97, pp.
-1-10
-%
-%\bibitem{rychtarikova2013}
-%Rychtarikova, M. and Vermeir, G. (2013). Soundscape categorization on the basis of objective acoustical parameters. \textit{Applied Acoustics}, 74(2), pp. 240-247
-%
-%\bibitem{can2016}
-%Can, A.
-and Aumond, P.
-and Michel, S.
-and De Coensel, B.
-and Ribeiro, C.
-and Botteldooren, D.
-and Lavandier, C.
-(2016).
-Comparison of noise indicators in an urban context.
-In: \textit{Proceedings of the 45th International Congress and Exposition on Noise Control Engineering}, pp.
-5678-5686
-%
-%\bibitem{can2015}
-%Can, A. and Gauvreau, B. (2015). Describing and classifying urban sound environments with a relevant set of physical indicators. \textit{J. Ac. Soc. Am.}, 137(1), pp. 208-218
-%
-%\bibitem{brocolini2013}
-%Brocolini, L.
-and Lavandier, C.
-and Quoy, M.
-and Ribeiro, C.
-(2013).
-Measurements of acoustic environments for urban soundscapes: Choice of homogeneous periods, optimization of durations, and selection of indicators.
-\textit{J.
-Ac.
-Soc.
-Am.}, 134(1), pp.
-813-821
-%
-%\bibitem{nilsson2007}
-%Nilsson, M.
-and Botteldooren, D.
-and De Coensel, B.
-(2007).
-Acoustic indicators of soundscape quality and noise annoyance in outdoor urban areas.
-In: \textit{Proceedings of the 19th International Congress on Acoustics}
-%
-%\bibitem{ishiyama2000}
-%Ishiyama, T. and Hashimoto, T. (2000). The impact of sound quality on annoyance caused by road traffc noise: an influence of frequency spectra on annoyance. \textit{JSAE Review}, 21(2), pp. 225-230
-%
-%\bibitem{torija2013}
-%Torija, A.
-and Ruiz, D.
-and Ramos-Ridao, A.
-(2013).
-Application of a methodology for categorizing and differentiating urban soundscapes using acoustical descriptors and semantic-differential attributes.
-\textit{J.
-Ac.
-Soc.
-Am.}, 134(1), pp.
-791-802
-%
-%\bibitem{anusuya2009}
-%Anusuya, M. and Katty, S. (2009). Speech recognition by machine, a review. \textit{International Journal of Computer Science and Information Security}, 6(3), pp. 181-205
-%
-%\bibitem{tzanetakis2002}
-%Tzanztakis, G. and Essl, G. and Cook, P. (2002). Automatic musical genre classification of audio signals. \textit{IEEE Transactions on Speech and Audio Processing}, 10(5), pp. 293-302
-%
-%\bibitem{ntalampiras2014}
-%Ntalampiras, S. (2014). Universal background modeling for acoustic surveillance of urban traffic. \textit{Digital Signal Processing}, 31, pp. 69-78
-%
-%\bibitem{aucouturier2007}
-%Aucouturier, J.
-and Defreville, B.
-and Pachet, F.
-(2007).
-The bag-of-frames approach to audio pattern recognition: A sufficient model for urban soundscapes but not for polyphonic music.
-\textit{J.
-Ac.
-Soc.
-Am.}, 122(2), pp.
-881-891
-%
-%\bibitem{foggia2015}
-%Foggia, P.
-and Petkov, N.
-and Saggese, A.
-and Strisciuglio, N.
-and Vento, M.
-(2015).
-Reliable detection of audio events in highly noisy environments.
-\textit{Pattern Recognition Letters}, 65, pp.
-22-28
-%
-%\bibitem{kumar2016}
-%Kumar, A. and Raj, B. (2016). Features and Kernels for Audio Event Recognition. \textit{arXiv Preprint}, Available at: \url{https://arxiv.org/abs/1607.05765}
-%
-%\bibitem{radhakrishnan2005}
-%Radhakrishnan, R. and Divakaran, A. and Smaragdis, P. (2005). Audio analysis for surveillance applications. In: \textit{IEEE Workshop on Applications of Signal Processing to Audio and Acoustics}
-%
-%\bibitem{salamon2017}
-%Salamon, J. and Bello, J. (2017). Deep convolutional neural networks and data augmentation for environmental sound classification. \textit{IEEE Signal Processing Letters}, 24(3), pp. 279-283
-%
-%\bibitem{piczak2015}
-%Piczak, K. (2015). Environmental sound classification with convolutional neural networks. In: \textit{IEEE 25th International Workshop on Machine Learning for Signal Processing}
-%
-%\bibitem{khunarsal2013}
-%Khunarsal, P. and Lursinsap, C. and Raicharoen, T. (2013). Very short time environmental sound classification based on spectrogram pattern matching. \textit{Information Sciences}, 243, pp. 57-74
-%
-%\bibitem{couvreur2004}
-%Couvreur, L.
-and Laniray, M.
-(2004).
-Automatic noise recognition in urban environments based on artificial neural networks and hidden markov models.
-In: \textit{The 33rd International Congress and Exposition on Noise Control Engineering}
-%
-%\bibitem{cai2006}
-%Cai, R.
-and Lu, L.
-and Hanjalic, A.
-and Zhang, H.
-and Cai, L.
-(2006).
-A flexible framewok for key audio effects detection and auditory context inference.
-\textit{IEEE Transactions on Audio, Speech, and Language Processing}, 14(3), pp.
-1026-1039
-%
-%\bibitem{chu2009}
-%Chu, S.
-and Narayanan, S.
-and Kuo, C.
-(2009).
-Environmental sound recognition with time-frequency audio features.
-\textit{IEEE Transactions on Audio, Speech, and Language Processing}, 17(6), pp.
-1142-1158
-%
-%\bibitem{salamon2015-2}
-%Salamon, J. and Bello, J. (2015). Unsupervised feature learning for urman sound classification. In: \textit{2015 IEEE International Conference on Acoustics, Speech and Signal Processing}
-%
-%\bibitem{bauge2013}
-%Baugé, C.
-and Lagrange, M.
-and Andén, J.
-and Mallat, S.
-(2013).
-Representing environmental sounds using the separable scattering transform.
-In: \textit{2013 IEEE International Conference on Acoustics, Speech and Signal Processing}
-%
-%\bibitem{salamon2015}
-%Salamon, J. and Bello, J. (2015). Feature learning with deep scattering for urban sound analysis. In: \textit{23rd European Signal Processing Conference}
-%
-%\bibitem{chachada2013}
-%Chachada, S. and Kuo, C. (2013). Environmental sound recognition: A survey. In: \textit{2013 Asia-Pacific Signal and Information Processing Association Annual Summit and Conference}
-%
-%\bibitem{davis1986}
-%Davis, S. (1986). Octave and fractional-octave band digital filtering based on the proposed ANSI standard. In: \textit{1986 IEEE International Conference on Acoustics, Speech and Signal Processing}
-%
-%\bibitem{ellis2005}
-%Ellis, D. (2005). \textit{{PLP} and {RASTA} (and {MFCC}, and inversion) in {M}atlab}. Available at: \url{http://www.ee.columbia.edu/~dpwe/resources/matlab/rastamat/}
-%
-%\bibitem{huffman1952}
-%Huffman, D. (1952). A method for the construction of minimum-redundancy codes. \textit{Proceedings of the IRE}, 40(9), pp. 1098-1101
-%
-%\bibitem{antoni2010}
-%Antoni, J. (2010). Orthogonal-like fractional-octave-band filters. \textit{J. Ac. Soc. Am.}, 127(2), pp. 884–895
-%
-%\bibitem{couvreur}
-%Couvreur, C. \textit{Implementation of a one-third-octave filter bank in Matlab}. Available at: \url{http://citeseer.ist.psu.edu/24150.html}
-%
-%\bibitem{griffin1984}
-%Griffin, D. and Lim, J. (1984). Signal Estimation from Modified Short-Time Fourier Transform. \textit{IEEE Transactions on Acoustics, Speech, and Signal Processing}, 32(2), pp. 236-243
-%
-%\bibitem{salamon2014}
-%Salamon, J. and Jacoby, C. and Bello, J. (2014). A Dataset and Taxonomy for Urban Sound Research. \textit{Proceedings of the 22nd ACM international conference on Multimedia}
-%
-%\bibitem{kates2005}
-%Kates, J. and Arehart, K. (2005). Coherence and the Speech Intelligibility Index. \textit{J. Ac. Soc. Am.}, 115(5), pp. 2224–2237
-%
-%\bibitem{hu2008}
-%Hu, Y. and Loizou, P. (2008). Evaluation of objective quality measures for speech enhancement. \textit{IEEE Transactions on Audio, Speech, and Language Processing}, 16(1), pp. 229–238
-%
-%\bibitem{ma2009}
-%Ma, J.
-and Hu, Y.
-and Loizou, P.
-(2009).
-Objective measures for predicting speech intelligibility in noisy conditions based on new band-importance functions.
-\textit{J.
-Ac.
-Soc.
-Am.}, 125(5), pp.
-3387–3405
-%
-%
-%\end{thebibliography}
 \end{document}

### 2017-07-21 censeCoder/perc_int.m

@@ -104,7 +104,7 @@ switch act
         hold on,
         errorbar([4.2 8.2 16.2 50.2], flip(m_tr), flip(s_tr)),
         axis([0 55 -0.1 1.1]), grid on, xlabel('Analysis frames per second'), ylabel('Intelligibility metric')
-        legend('Subjective judgement', 'Transcription ratio', 'location', 'southeast')
+        legend('Average Intelligibility Score (AIS)', 'Intelligibility ratio (IR)', 'location', 'southeast')
         set(gca, 'xtick', [4 8 16 50]);
 
         % 23M-55F-17M-60M-22F-22M-24M-23M

### 2017-08-07 paper/article.tex
Paper corrections

@@
 \usepackage{multirow}
+\usepackage{subcaption}
 
@@
 In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation.
-Thickness of arrows roughly indicate bandwidth and thickness of boxes roughly indicates the level of computation or storage required.}
+Thickness of arrows roughly indicate bandwidth and thickness of boxes roughly indicates the level of computation or storage required.\pa{Figure non appelee}}
 \label{fig:codingScheme}
@@
 
-A Huffman coding scheme \cite{huffman1952} is then used to further reduce data rate.
-As in most entropy coding algorithms, the efficiency of this technique depends on two important factors.
-A reduced amount of symbols in the dictionary yields smaller code size on lower probability symbols.
-Lower data entropy, \textit{i.e.} lower average information content of the signal distribution, also increases efficiency.
-The first is generally obtained by applying a quantization process to the signal, whereas the second is directly linked with the probability density function (PDF) of these symbols.
-It is defined as $H = -\sum\limits_i p_ilog_n(p_i)$, where $p_i$ is the probability of appearance of a given symbol and $n$ the numerical base in which information is represented.
+A Huffman coding scheme \cite{huffman1952} is an efficient method to further reduce data rate.
+At this point of the processing chain, the data takes the form of a spectrogram with amplitude values represented on an arbitrary data type.
+It is therefore assimilable to a discrete distribution.
+By defining symbols as the possible values taken by the data, a discrete probability density function (PDF) can be expressed and estimated.
+The Shannon entropy then specifies the minimum average obtainable output data rate for this given distribution, or average information content.
+The Huffman algorithm is an entropy coding scheme, as it uses the PDF to assign an code to each symbol so that the average output rate is the closest to the entropy.
+The resulting mapping function is called a Huffman dictionnary.
 
-As such, entropy decreases when very few symbols have a very high probability of appearance and is maximum for a uniform distribution.
+The efficiency of the coding step thus directly depends on the entropy of the transmitted data.
+It is defined as $H = -\sum\limits_i p_ilog_n(p_i)$, where $p_i$ is the probability of appearance of a given symbol and $n$ the numerical base in which the output code is represented.
+A lower entropy can be obtained with two factors.
+First, the dictionnary size \textit{i.e.} the number of symbols must be kept low.
+This implies performing a quantization on the data resulting in a loss of precision.
+Second, the data distribution itself is important.
+Entropy decreases when very few symbols have a very high probability of appearance and is maximum for a uniform distribution.
+
+%The algorithm concepts are summarized in Figure~\ref{fig:huffalg}.
+%\fg{Schéma}
 Considering an estimated PDF for our data as shown in Figure~\ref{fig:pdf}a, immediately applying a linear quantization clearly results in most of the information being lost.
@@
 The chosen reference consiiders the Matlab \textit{ita\_ toolbox} implementation \cite{itatoolbox2017} processed over the whole signal.
-We study both "fast" computation with 125~ms windows and no overlap and "slow" 1~s, 50\% overlap analysis to assess the impact of time integration.
+We study both "fast" computation with 125~ms windows and "slow" 1~s analysis to assess the impact of time integration.
 In both cases the sound dataset is the same and is composed of 2~s extracts.
@@
 As the analysis frames are of short duration, poor frequency resolution and spectral leakage are expected, particularly in the lower frequencies bands.
-For this reason we evaluate the effect of the use of different windowing functions on each band measurement error in order to mitigate this loss of precision.
-The reference implementation shows less than 0.1~dB error when compared with a class 1 sound level meter and as such is considered a sufficient reference.
-To provide relevant statistics, these quantities are estimated for about 4500 extracts obtained from the UrbanSound8k dataset \cite{salamon2014}.
+For this reason we evaluate the effect of the use of windowing functions on each band measurement error in order to mitigate this loss of precision.
+To provide relevant statistics, these quantities are estimated for about 4500 extracts obtained from the UrbanSound8k dataset \cite{salamon2014} and 4500 \textit{iid.} noise sequences.
 
@@
 Thus, the impact of the frame rate parameter of the proposed encoding scheme on intelligibility is evaluated.
-To do so, a perceptual test and the evolution of two objective measures are considered.
+To do so, a perceptual test is conducted.
 For the evaluation, a dataset of clean speech recordings made of 9 french sentences enunciated by 3 male and 3 female speakers, for a total of 216 audio excerpts.
@@
 
-Concerning the objective measures, the Coherence Speech Intelligibility Index \cite{kates2005} (CSII) and the frequency-weighted segmental SNR \cite{hu2008} (fwSNRseg) are considered.
-They both compare original unaltered samples and recovered audio as those two indicators have been shown to correlate well with perceptual tests \cite{ma2009}, although results are only available for lesser degradations and distortions than the ones we consider in this study.
-
-These metrics require an estimate of the time-domain signal.
+This test requires an estimate of the time-domain signal.
 To do so, a linearly-scaled spectrogram from the band-focused representations is estimated.
@@
 
-The measurement error is computed for third-octave bands and different windowing functions.
-Results are displayed in Table~\ref{T1}.
-The error was found to be decreasing with respect to an increase of frequency.
-The study is thus focused on the 20~Hz and 1~kHz bands, respectively the lowest and reference frequencies.
-The first observation is that using 1~s analysis over 125~ms yields better estimations at 20~Hz.
-This is expected as it provides a globally better resolution and therefore reduces the impact of spectral leakage effects in this region.
+The measurement error is computed for third-octave bands.
+Results are displayed in Figure~\ref{fig:error_m}.
+Only full-octave bands are shown for visibility.
+When computing the slow analysis, we found that applying overlap attenuated the error.
+This was not observed for fast analysis where the error was similar or higher with the use of overlapping frames.
+We propose to study the absolute error metric, as all experiments show a mean error close to zero.
 
-Closer inspection show that when considering white noise the error is low on the whole spectrum.
-This effectiveness does not translate though to environmental sounds analysis.
-One inducing factor for this phenomenon is the sound level disparities absent in the first case but omnipresent in the second.
-Let us consider, for each frame, the difference between the maximum and the remaining band levels in the reference, and compared it with the observed estimation error.
-The results show a correlation between the two quantities: when the average band level is low with respect to the peak, the error tends to increase.
-Furthermore, the closer a significantly higher level is to the considered frequency band, the larger the error is.
-This is due to framing that causes spectral leakage.
-This is found to be particularly important in lower frequencies.
+As can be expected when performing a short time analysis, high errors appear in low frequency bands where precision is poor.
+The slow analysis yields better estimations as it provides a globally better resolution and thus also reduces the impact of spectral leakage effects in this region.
+When considering white noise the error is low on the whole spectrum.
+This effectiveness does not translate to environmental sounds analysis.
+A factor of this phenomenon is the sound level disparities absent in the first case but omnipresent in the second.
+In fact, spectral leakage induces a correlation between close frequency components.
+In lower frequencies, large differences between adjacent frequency bins can cause important errors on third-octave bands computations.
+This issue is however not specific to Fourier transform based schemes as it is also encountered with a time domain filtering approach.
 
-To mitigate this issue, the choice of the window function shall be studied further.
-As the bitrate constraint prioritizes no overlap use for a fast analysis, the rectangular window seems a reasonable choice at first with its energy conservation qualities.
+To mitigate this phenomenon, the choice of the window function shall be studied further.
+For a fast analysis with no overlap, the rectangular window seems a reasonable choice at first with its energy conservation qualities.
 While it yields the lowest error in high frequency bands, its high spectral leakage effect makes it unprecise for lower frequency regions.
@@
 
-\begin{table*}[h]
+\begin{figure*}[h!]
     \centering
-\caption{Third-octave bands measurement absolute error in dB for fast and slow computations and four window functions.
+    \begin{subfigure}[h]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{figures/err_m_n.eps} 
+        \caption{Noise extracts}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[h]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{figures/err_m_u.eps} 
+        \caption{Urban sounds recordings}
+    \end{subfigure}
+    \label{fig:error_m}
+    \caption{Measurement error of third-octave bands over two-seconds recordings.
+The analysis of short frames has an effect on energy estimation at low frequencies.
+Framing is more impactful on signals where the energy is localized in frequency.}
+\end{figure*}
+
+%\begin{table*}[h]
+%\centering
+%\caption{Third-octave bands measurement absolute error in dB for fast and slow computations and four window functions.
 The proposed method is here compared with evaluations by the \textit{ITA-toolbox} for 2-seconds exerpts.
 }
-\label{T1}
-\begin{tabular}{|c|c|c|c|c|c|}
-\cline{1-6}
-\multirow{2}{*}{Analysis} & \multirow{2}{*}{Window} & \multicolumn{2}{|c|}{White noise} & \multicolumn{2}{|c|}{Environmental recordings}\\ \cline{3-6}
- & & 20~Hz & 1~kHz & 20~Hz & 1~kHz\\ \cline{1-6}
-\multicolumn{1}{|c}{\multirow{4}{*}{Fast - 125~ms, 0$\%$ overlap}}
- & \multicolumn{1}{|c|}{Rectangular} & 0.94$\pm$0.75 & 0.07$\pm$0.02 & 5.59$\pm$5.64 & 0.21$\pm$0.76\\ \cline{2-6}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{Hamming} & 1.02$\pm$0.71\newline & 0.16$\pm$0.14 & 3.34$\pm$3.41 & 0.44$\pm$0.76\\ \cline{2-6}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{Gaussian} & 1.04$\pm$0.71 & 0.17$\pm$0.15 & 3.56$\pm$3.63 & 0.48$\pm$0.83\\ \cline{2-6}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{Tukey ($\alpha = 0.5$)} & 0.97$\pm$0.75 & 0.11$\pm$0.09 & 4.16$\pm$5.58 & 0.32$\pm$0.80\\ \cline{1-6}
- \multicolumn{1}{|c}{\multirow{4}{*}{Slow - 1~s, 50$\%$ overlap}}
- & \multicolumn{1}{|c|}{Rectangular} & 0.48$\pm$0.36 & 0.08$\pm$0.05 & 1.86$\pm$3.13 & 0.40$\pm$0.55\\ \cline{2-6}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{Hamming} & 0.57$\pm$0.56 & 0.09$\pm$0.07 & 2.23$\pm$3.58 & 0.74$\pm$1.61\\ \cline{2-6}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{Gaussian} & 0.62$\pm$0.61 & 0.10$\pm$0.08 & 2.48$\pm$4.16 & 0.80$\pm$1.75\\ \cline{2-6}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{Tukey ($\alpha = 0.5$)} & 0.53$\pm$0.48 & 0.09$\pm$0.07 & 2.82$\pm$6.64 & 0.61$\pm$1.40\\ \cline{1-6}
-\end{tabular}
-\end{table*}
+%\label{T1}
+%\begin{tabular}{|c|c|c|c|c|c|}
+%\cline{1-6}
+%\multirow{2}{*}{Analysis} & \multirow{2}{*}{Window} & \multicolumn{2}{|c|}{White noise} & \multicolumn{2}{|c|}{Environmental recordings}\\ \cline{3-6}
+% & & 20~Hz & 1~kHz & 20~Hz & 1~kHz\\ \cline{1-6}
+%\multicolumn{1}{|c}{\multirow{4}{*}{Fast - 125~ms, 0$\%$ overlap}}
+% & \multicolumn{1}{|c|}{Rectangular} & 0.94$\pm$0.75 & 0.07$\pm$0.02 & 5.59$\pm$5.64 & 0.21$\pm$0.76\\ \cline{2-6}
+%\multicolumn{1}{|c}{}
+% & \multicolumn{1}{|c|}{Hamming} & 1.02$\pm$0.71\newline & 0.16$\pm$0.14 & 3.34$\pm$3.41 & 0.44$\pm$0.76\\ \cline{2-6}
+%\multicolumn{1}{|c}{}
+% & \multicolumn{1}{|c|}{Gaussian} & 1.04$\pm$0.71 & 0.17$\pm$0.15 & 3.56$\pm$3.63 & 0.48$\pm$0.83\\ \cline{2-6}
+%\multicolumn{1}{|c}{}
+% & \multicolumn{1}{|c|}{Tukey ($\alpha = 0.5$)} & 0.97$\pm$0.75 & 0.11$\pm$0.09 & 4.16$\pm$5.58 & 0.32$\pm$0.80\\ \cline{1-6}
+% \multicolumn{1}{|c}{\multirow{4}{*}{Slow - 1~s, 50$\%$ overlap}}
+% & \multicolumn{1}{|c|}{Rectangular} & 0.48$\pm$0.36 & 0.08$\pm$0.05 & 1.86$\pm$3.13 & 0.40$\pm$0.55\\ \cline{2-6}
+%\multicolumn{1}{|c}{}
+% & \multicolumn{1}{|c|}{Hamming} & 0.57$\pm$0.56 & 0.09$\pm$0.07 & 2.23$\pm$3.58 & 0.74$\pm$1.61\\ \cline{2-6}
+%\multicolumn{1}{|c}{}
+% & \multicolumn{1}{|c|}{Gaussian} & 0.62$\pm$0.61 & 0.10$\pm$0.08 & 2.48$\pm$4.16 & 0.80$\pm$1.75\\ \cline{2-6}
+%\multicolumn{1}{|c}{}
+% & \multicolumn{1}{|c|}{Tukey ($\alpha = 0.5$)} & 0.53$\pm$0.48 & 0.09$\pm$0.07 & 2.82$\pm$6.64 & 0.61$\pm$1.40\\ \cline{1-6}
+%\end{tabular}
+%\end{table*}
 
@@
 The results of the perceptual test is evaluated using the average intelligibility score (AIS) given by the subjects and the ineligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
-Figures~\ref{fig:csii_tob_fps} and \ref{fig:fwsnrseg_tob_fps} shows both the CSII and fwSNRseg indicators for varying encoding frames per second.
 Figure~\ref{fig:subj_int} presents the results of the perceptual test for the same encoder's settings.
@@
 Similarly, framing effects induced by the proposed processing scheme yielded errors for higher frame rates transcriptions and a globally lower perceptual intelligibility.\\
-
-The CSII accounts for the spectrogram distance between clean and distorted audio at each point in time and frequency.
-This includes the phase, which we discard early in the representation step.
-The error induced by forward and inverse third-octave bands transformation as well as operations reducing data dimensionality further contribute to very high point-wise disparities.
-In fact, the signal is too distorted for the proposed SNR normalization to ensure CSII values in the 0-1 range.
-When compared to perceptual test results, the CSII shows no clear separation around 10 frames per second.
-It is therefore not a good indicator in our conditions.\\
-
-More interestingly, the frequency-weighted segmental SNR considers only spectrogram magnitudes.
-As a result, distance is generally lower and more representative of the induced perceptual distortion.
-Nevertheless, the fwSNRseg still uses a point-wise comparison which is certainly too precise for the level of degradations considered in this study.
-Indeed, it seems more accurate at higher frame rates compared to the results achieved using the perceptual test.
-Though, the threshold observed in the results of the perceptual test is not measured using the fwSNRseg metric and the difference between 8~Hz and 16~Hz is not large enough to match subjective measurements.\\
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=\columnwidth]{figures/csii_tob_fps.eps}
-	\caption{The Coherence SII objective indicator computed for intelligibility assessment.
-Negative CSII values indicate a signal-to-noise ratio too low for the recommended normalization, thus severe disparities between the original and reconstructed signal.}
-	\label{fig:csii_tob_fps}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=\columnwidth]{figures/fwsnrseg_tob_fps.eps}
-	\caption{Frequency-weighted segmental SNR with varying analysis frame rates around the considered 8~Hz value.
-This indicator shows a better correlation with subjective tests but lacks an inintelligibility threshold.}
-	\label{fig:fwsnrseg_tob_fps}
-\end{figure}
 

### 2017-08-16 paper/article.tex
Add files via upload

@@
 
-acoustic monitoring \sep soundscape assessment \sep
+acoustic monitoring \sep audio encoding \sep
 %% keywords here, in the form: keyword \sep keyword
@@
 %\label{}
-
+\pa{
+// Beaucoup de fomer/latter
+// Le terme soundscape inclut la perception de lenvironnment sonore. Si tu veux parler juste de lenvironnement sonore "urban sound environment" est plus approprie.
+// Ref Judi: Picaut, Judicaël, Arnaud Can, Jérémy Ardouin, Pierre Crépeaux, Thierry Dhorne, David Écotière, Mathieu Lagrange, et al.
+« Characterization of urban sound environments using a comprehensive approach combining open data, measurements, and modeling ».
+In The Journal of the Acoustical Society of America, 141:3808-3808.
+Boston, USA: Acoustical Society of America, 2017.
+doi:10.1121/1.4988416.
+}
 The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc\footnote{\url{htttp://wp.nyu.edu/sonyc}} \cite{mydlarz2017implementation} and cense\footnote{\url{htttp://cense.ifsttar.fr}} \pa{ref papier de judicael ?} \cite{} projects.
@@
 
-The data of interest is first acoustic indicators (LAeq, ...) and second the presence of sound sources of interest (bird calls, sirens, explosion, ...).
-The latter allow us to better assess soundscapes in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}.
+The data of interest is first acoustic indicators (LAeq, ...) and second the presence of sound sources of interest (bird calls, sirens, ...).
+The latter allows us to better assess soundscapes in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}.
 This detection step can respectively be operated online (on the sensors) or offline (on the data servers).
@@
 Second, it allows researchers to gather large amount of data that can be post processed and studied further offline.
-Data can be re analysed following newer classification schemes or using new indicators.
+Data can be re analyzed following newer classification schemes or using new indicators.
 
-However, transmitting the raw audio through the network has several disavantages, in terms of required bandwidth, storage capabilities and privacy.
-Thus, for transmission from the sensors to the storage unit, the data shall be encoded in a more efficient way than lossy audio encoding standards \cite{pan1995tutorial}.Indeed, the audio signal is not mandatory for the computation of the acoustic indicators and the features needed for event recognition.
+Transmitting the raw audio through the network has several disadvantages, in terms of required bandwidth, storage capabilities and privacy.
+Thus, for transmission from the sensors to the storage unit, the data shall be encoded in a more efficient way than lossy audio encoding standards \cite{pan1995tutorial}.
+Indeed, the audio signal is not mandatory for the computation of the acoustic indicators and the features needed for event recognition.
 Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.
 
-We thus propose in this paper a audio coding scheme specifically tailored for use in a sensor grid which has the following features.
-It is of low bitrate but still allows the computation of most of the standard acoustics indicators with controlable precision.
+We thus propose in this paper an audio coding scheme specifically tailored for use in a sensor grid which has the following features.
+It is of low bitrate but still allows the computation of most of the standard acoustics indicators with controllable precision.
 As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data at production level rates.
@@
 
-The present work is constrained to allow both acoustic monitoring and sound event recognition in urban soundscapes.
+The present work is constrained to allow both acoustic monitoring and sound event recognition in urban sound environment.
 Here we briefly review state-of-the-art methods in both subjects in order to better motivate our design choices.
@@
 
-The considered sensor network primarily aims at monitoring urban soundscapes, that is, continously assessing their content and impact on the population.
+The considered sensor network primarily aims at monitoring urban sound environment, that is, continuously assessing their content and impact on the population.
 In the literature, this is typically performed by measuring energetic acoustic indicators such as the equivalent sound pressure level $L_{eq}$ in dB SPL or its A-weighted equivalent $L_{Aeq}$ in dBA.
-However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe soundscapes \cite{rychtarikova2013}.
-Many other variables can be derived to better account for previously implicit properties \cite{can2016} including percentile values or time evolution.
+However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe urban sound environments \cite{rychtarikova2013}.
+Many other variables can be derived to better account for previously implicit properties \cite{can2016} including percentile values or time dynamics.
 Studies have been conducted to select relevant subsets of descriptors in sound environment characterization \cite{can2015, brocolini2013, nilsson2007}.\\
 
-All the mentionned indicators are measured at periods ranging from 0.125~ms or 1~s (resp.
-fast and slow) to longer periods of several minutes.
-Therefore, sound frequency information remains unused despite being closely related with subjective evaluations \cite{ishiyama2000}.
-A simple solution is the calculation of energetic indicators for the 31 third-octave bands within the human audition range 20~Hz - 20~kHz.\\
+\pa{En fait tu as aussi des indicateurs sur le spectre, le très utilisé CGS par exemple.
+En fait tu devrais peut-être t'arrêter à dire que il y a pleins d'indicateurs, mais ces indics donnent de l'info sur l'env.
+sonore dans sa globalité, mais pas sur les sources sonores en particulier.
+Pourtant les sources ont de la place sur l'appréciation du soundscape (et peut-être plus que des indics globaux, par exemple 50dB de voix humaine, c'est pas la même chose que 50dB d'oiseaux).
+Tu peux citer la tentative dans la publi avec Catherine où on calculait le TFSD4khz qui est bien corrêlé avec les oiseaux, mais ça ne remplacera pas une vrai detection de sources.
+}
 
-This measurement appears well-suited for this work's purpose: in addition to being an efficient descriptor \cite{torija2013}, it allows for the computation of most cited indicators while representing reasonably small, fixed amounts of data to be transmitted.
+A simple solution is the calculation of energetic indicators for the 31 third-octave bands within the human audition range 20~Hz - 20~kHz.\\ \pa{pour des périodes très courtes (fast or slow)} This measurement appears well-suited for this work's purpose: in addition to being an efficient descriptor \cite{torija2013}, it allows for the computation of most cited indicators while representing reasonably small, fixed amounts of data to be transmitted.
+ \pa{le spectrogramme en soit c'est pas un descripteur efficient, bcp trop d'info, par contre, tu as raison, avec lui on peut calculer la plupart des indicateurs cités et en plus sert pour faire de la reconnaissance.
+Tu peux aussi dire que du coup on fait l'impasse sur les Mel ou sur les indicateurs psychoacoustiques comme la Sonie ou le roughness.
+On en reparlera de vive voix si tu veux.}
 
@@
 
-Even though the above discussed indicators provide more richness than $L_{eq}$, recent studies show that abstract statistics are still not sufficient to fully model the human perception of soundscapes.
+Even though the above discussed indicators provide more richness than $L_{eq}$, studies show that abstract statistics are still not sufficient to fully model the soundscapes \pa{refs}.
 The recognition of sources of interest is thus of importance.
@@
 Studied classification methods are diverse, ranging from time-dependant modeling with hidden markov models \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}.
-Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}.
+Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, Gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}.
 However, the selection of relevant features is still an open debate.
@@
 They may also be exploited together with features computed in other domains to better model signal properties.
-For instance, \cite{cai2006} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domaid features.
+For instance, \cite{cai2006} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domain features.
 Another promising solution is feature engineering via unsupervised learning, which \cite{salamon2015-2} implements with a k-means clustering technique.
@@
 
-The technical constraints of size inherent to the studied setup make it impossible to transmit raw audio recordings.
+The technical constraints of size inherent to the studied setup make it impossible to transmit raw audio recordings \pa{and not wanted for privacy reason}.
 Following the considerations briefly exposed in the previous section, we conclude that third-octave bands are a reasonable choice.
@@
 A common way to implement third-octave analysis is to first design the highest octave three filters, and use them on progressively time-decimated versions of the input signal \cite{davis1986}.
+Antoni et al.
 \cite{antoni2010} presents an alternative analysis method based on direct frequency weighting, which yields a lower computational complexity as opposed to time filtering.
@@
 
+\pa{desfois tu mets une majuscule à mel et desfois non...}
+
 The first step is to represent the signal in the frequency domain using a short-term Fourier transform (STFT).
@@
 The data is zero-padded to the next power of two to improve computational efficiency.
-No overlap is used as it doubles both computational and memory costs and is not required for our application.
-A windowing function can be applied, for instance a rectangular window to ensure energy conservation in a given analysis frame.
+No overlap is used.
+A rectangular windowing function is applied to ensure energy conservation in a given analysis frame.
 The phase is discarded as it is not meaningful for third-octave analysis.
@@
 The Huffman algorithm is an entropy coding scheme, as it uses the PDF to assign an code to each symbol so that the average output rate is the closest to the entropy.
-The resulting mapping function is called a Huffman dictionnary.
+The resulting mapping function is called a Huffman dictionary.
 
@@
 A lower entropy can be obtained with two factors.
-First, the dictionnary size \textit{i.e.} the number of symbols must be kept low.
+First, the dictionary size \textit{i.e.} the number of symbols must be kept low.
 This implies performing a quantization on the data resulting in a loss of precision.
@@
 To this aim, third-octave bands are computed with the proposed method, then averaged and compared to a trusted reference.
-The chosen reference consiiders the Matlab \textit{ita\_ toolbox} implementation \cite{itatoolbox2017} processed over the whole signal.
+The chosen reference considers the Matlab \textit{ita\_ toolbox} implementation \cite{itatoolbox2017} processed over the whole signal.
 We study both "fast" computation with 125~ms windows and "slow" 1~s analysis to assess the impact of time integration.
@@
 
-In order to ensure that the proposed scheme allows the recognition of events using state of the art methods, we consider the results achieved by several regognition systems on the UrbanSound8k dataset\cite{salamon2014}.
+In order to ensure that the proposed scheme allows the recognition of events using state of the art methods, we consider the results achieved by several recognition systems on the UrbanSound8k dataset\cite{salamon2014}.
 It features about 9 hours of urban environmental sounds recordings separated in 8732 wave files ranging from 1 to 4 seconds each.
@@
 Values for the SVM parameter $C$ and RBF kernel variance $\sigma^2$ are found with a grid search.
-We opionaly apply a discrete cosine transform to the critical band signal representation to obtain cepstra (known as Mel Frequency Cepstrum Coefficients or MFCC in the first case) of which we conserve the 25 first coefficients, and summarize along time with the mean, variance, skewness, kurtosis, minimum, maximum, median, derivative mean and variance, second order derivative mean and variance.
+We optionally apply a discrete cosine transform to the critical band signal representation to obtain cepstra (known as Mel Frequency Cepstrum Coefficients or MFCC in the first case) of which we conserve the 25 first coefficients, and summarize along time with the mean, variance, skewness, kurtosis, minimum, maximum, median, derivative mean and variance, second order derivative mean and variance.
 The feature vector is thus comprised of 275 values to reproduce available results and compare with the data produced by the proposed coding scheme.
@@
 If some speech is detected, the data is not transmitted.
-This approach is however prone to failure of the detector and will lead to unavailibility of data during speech time periods which might compromise the computation of some indicators.
+This approach is however prone to failure of the detector and will lead to unavailability of data during speech time periods which might compromise the computation of some indicators.
 
@@
 \section{Conclusion}
+\pa{Je repasserais un coup sur la conclusion en fonction des changements apportés}
 
@@
 \begin{itemize}
-	\item precision: the impact of the quantization step for 8 bits codewords is found to be negligible compared to sensor precision of class 2 sensors
+	\item precision: the impact of the quantization step for 8 bits codewords is found to be very small (< 0.5dB) and thus:
+	- respect the acoustics indicators which could be calculated from the spectrogram.
+	- permits to perform the sound recognition with the same quality than directly from the spectrogram.
 	\item efficiency: for fast and slow modes, the bitrate is respectively about 1.4~kbps and 0.4~kbps for the high precision mode

### 2017-08-22 paper/article.tex
fix ref

@@
 The spreading of urban areas and the growth of human population worldwide raised societal and environmental concerns.
-To better address those, the monitoring the acoustic environment in urban but also rural or wilderness areas is among other monitoring efforts an important matter.
+To better address those, the monitoring of the acoustic environment in urban but also rural or wilderness areas is among other monitoring efforts an important matter.
 Fostering on the recent development of low cost hardware acoustic sensors, we propose in this paper to consider a sensor grid approach to tackle this issue.
@@
 Many other variables can be derived to better account for previously implicit properties \cite{can2016} including percentile values or time dynamics.
-Studies have been conducted to select relevant subsets of descriptors in sound environment characterization \cite{can2015, brocolini2013, nilsson2007}.\\
+Studies have been conducted to select relevant subsets of descriptors in sound environment characterization \cite{can2015, brocolini2013, nilsson2007}.
+The mentionned $L_{eq}$ features are measured at periods of 0.125~ms or 1~s, respectively fast and slow as a convention.
 
-\pa{En fait tu as aussi des indicateurs sur le spectre, le très utilisé CGS par exemple.
-En fait tu devrais peut-être t'arrêter à dire que il y a pleins d'indicateurs, mais ces indics donnent de l'info sur l'env.
-sonore dans sa globalité, mais pas sur les sources sonores en particulier.
-Pourtant les sources ont de la place sur l'appréciation du soundscape (et peut-être plus que des indics globaux, par exemple 50dB de voix humaine, c'est pas la même chose que 50dB d'oiseaux).
-Tu peux citer la tentative dans la publi avec Catherine où on calculait le TFSD4khz qui est bien corrêlé avec les oiseaux, mais ça ne remplacera pas une vrai detection de sources.
-}
+Most measured or derived indicators describe the global urban soundscape and lack information on its composition.
+Sound sources recognition enables a more efficient understanding of soundscape properties.
+For instance, a bird song and traffic noise with the same energy can be perceived very differently.
+The analysis of sources within a sound environment is generally linked with spectral content \cite{ishiyama2000} and high temporal measurement resolutions.
+Other indicators can correlate with specific sound environment content \fg{cite Aumond/Lavandier TFSD} but do not achieve the same performances as a source detection scheme in characterizing soundscapes.
 
-A simple solution is the calculation of energetic indicators for the 31 third-octave bands within the human audition range 20~Hz - 20~kHz.\\ \pa{pour des périodes très courtes (fast or slow)} This measurement appears well-suited for this work's purpose: in addition to being an efficient descriptor \cite{torija2013}, it allows for the computation of most cited indicators while representing reasonably small, fixed amounts of data to be transmitted.
- \pa{le spectrogramme en soit c'est pas un descripteur efficient, bcp trop d'info, par contre, tu as raison, avec lui on peut calculer la plupart des indicateurs cités et en plus sert pour faire de la reconnaissance.
-Tu peux aussi dire que du coup on fait l'impasse sur les Mel ou sur les indicateurs psychoacoustiques comme la Sonie ou le roughness.
-On en reparlera de vive voix si tu veux.}
+A solution is the calculation of spectral energetic indicators such as the 31 third-octave bands within the human audition range 20~Hz - 20~kHz.\\ Slow or fast third-octave bands measurement appears suitable for this work's purpose: in addition to being a relevant descriptor \cite{torija2013} for urban sound environment assessment, it allows for the computation of most cited indicators while representing reasonably small, fixed amounts of data to be transmitted.
+It additionnaly contains spectral information that can be used for source recognition tasks.
+However, as a tradeoff other representations such as Mel or Bark spectrograms, as well as psychoacoustical indicators cannot be precisely estimated.
 
@@
 The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal.
-Among them, mel spectrograms and their cepstral-domain derivation, the mel-frequency cepstrum coefficients (MFCC), are the most recurrent.
+Among them, Mel spectrograms and their cepstral-domain derivation, the Mel-frequency cepstrum coefficients (MFCC), are the most recurrent.
 These representations effectively model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale.
+While parameters are empirical and vary in the litterature, a reference implementation includes 23.2~ms analysis and a 40 Mel bands resolution.
+The resulting representations are generally more precise in time and frequency than in acoustic monitoring applications because it is a primordial factor for classification whereas acoustic indicators must be computed more accurately.
 
@@
 
-The technical constraints of size inherent to the studied setup make it impossible to transmit raw audio recordings \pa{and not wanted for privacy reason}.
+The technical constraints of size inherent to the studied setup as well as privacy concerns make it impossible to transmit raw audio recordings.
 Following the considerations briefly exposed in the previous section, we conclude that third-octave bands are a reasonable choice.
 As mentioned, they provide advantages in both acoustic monitoring quality and reduced data volume per measurement period.
-The resulting representation is also close to that of mel spectrograms, being just another filterbank transform with logarithmic frequency scaling.\\
+The resulting representation is also close to that of Mel spectrograms, being just another filterbank transform with logarithmic frequency scaling.\\
 
@@
 
-\pa{desfois tu mets une majuscule à mel et desfois non...}
-
 The first step is to represent the signal in the frequency domain using a short-term Fourier transform (STFT).
@@
 
-Alternatively, we also implement the mel filterbank for comparison purposes, as the mel filterbank is the root representation of many state of the art classification algorithms.
+Alternatively, we also implement the Mel filterbank for comparison purposes, as the Mel filterbank is the root representation of many state of the art classification algorithms.
 Mel spectrograms can thus be used as a baseline method to evaluate the relative performance of third-octave bands in sound event recognition.
@@
 If it is specific to a given data packet, then it does not need to contain every possible value.
-This gain seem to outweight the additional complexity induced by the need to transmit the result of the tree generation algorithm.
+This gain seems to outweight the additional complexity induced by the need to transmit the result of the tree generation algorithm.
 Alternatively, short texture frames or single analysis windows can be encoded using one general dictionary to improve bitrate.
@@
 
-The decoding process is quite straightforward, as both Huffman and $\Delta$ compression are lossless and invertible directly. The entire coder scheme is summarized in Figure~\ref{fig:scheme}.
+The decoding process is quite straightforward, as both Huffman and $\Delta$ compressions are lossless and directly invertible. The entire coder scheme is summarized in Figure~\ref{fig:scheme}.
 
@@
 Figure~\ref{fig:bitrate_q} shows estimations of the output bitrate for different values of $q$.
-To match third-octave bands computation principle where a 125~ms analysis is mandatory, we averaged mel frames over time.
+To match third-octave bands computation principle where a 125~ms analysis is mandatory, we averaged Mel frames over time.
 Because we use the most common parameters, namely 23.2~ms window with 50\% overlap, the closest achievable rate considering simple averaging is 7.74 frames per second.
-Third-octave representation on 31 bands yielded an overall higher size than their mel equivalent, here estimated for 30 bands.
-It however compares with the 40-mel bands representation which is the most used features in literature.
+Third-octave representation on 31 bands yielded an overall higher size than their Mel equivalent, here estimated for 30 bands.
+It however compares with the 40-Mel bands representation which is the most used features in literature.
 This higher bitrate is likely due to the distribution observed by the data prior to Huffman encoding.
@@
 		\includegraphics[width=\columnwidth]{figures/bitrate_qall.eps}
-	\caption{Coder output bitrate as a function of quantization for third-octave and mel bands with 8 frames per second.}
+	\caption{Coder output bitrate as a function of quantization for third-octave and Mel bands with 8 frames per second.}
 	\label{fig:bitrate_q}
@@
 By choosing a frame rate and number of bands, one can effectively control the size of periodically transmitted data.
-We evaluate the bitrate for 10 to 40 mel bands and a frame rate from 2 to 10 per second, with fixed $q = 8$.
+We evaluate the bitrate for 10 to 40 Mel bands and a frame rate from 2 to 10 per second, with fixed $q = 8$.
 Results are shown in Figure~\ref{fig:bitrate_mel_avg}.
@@
 The measurement error is computed for third-octave bands.
-Results are displayed in Figure~\ref{fig:error_m}.
+Results are displayed in Figure~\ref{fig:errorm}.
 Only full-octave bands are shown for visibility.
@@
     \end{subfigure}
-    \label{fig:error_m}
+
     \caption{Measurement error of third-octave bands over two-seconds recordings.
 The analysis of short frames has an effect on energy estimation at low frequencies.
-Framing is more impactful on signals where the energy is localized in frequency.}
+Framing is more impactful on signals where the energy is localized in frequency.
+\label{fig:errorm}}
 \end{figure*}
@@
 \end{equation*}
-Figure~\ref{fig:error_q} shows an estimation of $\varepsilon$ as a function of $q$ for third-octave and mel bands.
+Figure~\ref{fig:error_q} shows an estimation of $\varepsilon$ as a function of $q$ for third-octave and Mel bands.
 In both cases, the mean and standard deviation seem to decrease by a factor of 2 as $q$ increases.
@@
 The models are trained on the most complete implemented representation, ie.
-40 mel bands and no time averaging (85 frames per second).
+40 Mel bands, 23.2~ms, 50\% overlap and no time averaging (85 frames per second).
 Figure~\ref{fig:class_mel_q} shows that this process yields equivalent accuracy for higher resolutions.\\
@@
 However, we find that given our setup, reducing the number of analysis bands up to a given level most often does not induce a strong drop of performance.
-The performance of the decision tree classifier is a good example of this behavior, with best performances for 10 mel bands only and a 4\% lower accuracy for 40.
+The performance of the decision tree classifier is a good example of this behavior, with best performances for 10 Mel bands only and a 4\% lower accuracy for 40.
 The latter result may be due to the low ability of the decision tree classifier to handle hugh dimensional features.
-Even if the difference is small, all other models perform best with 30 or 40 mel bands as a representation.
+Even if the difference is small, all other models perform best with 30 or 40 Mel bands as a representation.
 Time decimation cn also be considered, as the original representation can be averaged and consistently yield a good classification accuracy.
@@
 
-We now compare the efficiency of third-octave bands at characterizing urban soundscapes to that of mel spectrograms.
+We now compare the efficiency of third-octave bands at characterizing urban soundscapes to that of Mel spectrograms.
 Following the previous discussions, the classification task is run on corresponding cepstra with a fixed 8 frames per second and 31 bands.
-Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps mel spectrograms seen in Table~\ref{T2} for all classification schemes.
+Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps Mel spectrograms seen in Table~\ref{T2} for all classification schemes.
 In this table, equivalence of performance with respect to the best performing setting (in red) is depicted with a bold font evaluated using the following procedure.
@@
 The analogous natures of the two descriptors is highlighted by close one-versus-one differentiation performances, with a slightly lower accuracy for third-octave bands on average.
-Both representations yield best results for the \textit{Gun shot} class with 88.2\% for third-octave cepstra and 86.6\% for mel cepstra.
+Both representations yield best results for the \textit{Gun shot} class with 88.2\% for third-octave cepstra and 86.6\% for Mel cepstra.
 Their poorest accuracy is on the \textit{Air conditioning} class with 32.0\% and 38.1\% respectively.
-However, a noticeable difference between them is that on the log-frequency scale the bandwidth of mel filters narrows as frequency increases, while third-octave are evenly distributed.
+However, a noticeable difference between them is that on the log-frequency scale the bandwidth of Mel filters narrows as frequency increases, while third-octave are evenly distributed.
 The effect of this can be seen between classes \textit{Drilling} and \textit{Jackhammer}.
 These sounds involve important low-frequency information which can generally differentiate them, leading third-octave descriptors to perform better.
-Conversely, using mel-based cepstra improves globally \textit{Air conditioning} recognition as most of its defining components are situated in higher frequencies.\\
+Conversely, using Mel-based cepstra improves globally \textit{Air conditioning} recognition as most of its defining components are situated in higher frequencies.\\
 
@@
 
-Objective intelligibility metrics are then computed for the encoder's settings under evaluation and compared to the results of the perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/}}.
-The results of the perceptual test is evaluated using the average intelligibility score (AIS) given by the subjects and the ineligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
+Subjective intelligibility metrics are then computed for the encoder's settings under evaluation and compared to the results of the perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/}}.
+The results of the perceptual test is evaluated using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
 Figure~\ref{fig:subj_int} presents the results of the perceptual test for the same encoder's settings.
@@
 
-An audio encoding scheme have been described and motivated for use in a sensor grid approach to tackle the problem of large scale acoustic monitoring.
+An audio encoding scheme has been described and motivated for use in a sensor grid approach to tackle the problem of large scale acoustic monitoring.
 
-The proposed approach have the following benefits:
+The proposed approach has the following benefits:
 \begin{itemize}

### 2017-08-22 paper/article.tex
Paper corrections

@@
 %\label{}
+\ac{-> Est-ce que le spectre est intelligible?
+-> Reconnaissance?
+-> Est-ce que envoyer le spectrogramme avec peu de bitrate?}
 \pa{
@@
 The measurement error is computed for third-octave bands.
-Results are displayed in Figure~\ref{fig:errorm}.
+Results are displayed in Figure~\ref{fig:error_m}.
 Only full-octave bands are shown for visibility.
@@
     \end{subfigure}
-
+    \label{fig:error_m}
     \caption{Measurement error of third-octave bands over two-seconds recordings.
 The analysis of short frames has an effect on energy estimation at low frequencies.
-Framing is more impactful on signals where the energy is localized in frequency.
-\label{fig:errorm}}
+Framing is more impactful on signals where the energy is localized in frequency.}
 \end{figure*}

### 2017-08-22 paper/template.tex
move to sensors

%  LaTeX support: latex@mdpi.com 
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.

%=================================================================
\documentclass[journal,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi} 
%
%--------------------
% Class Options:
%--------------------
% journal
%----------
% Choose between the following MDPI journals:
% actuators, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, atmosphere, atoms, axioms, batteries, bdcc, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, challenges, chemengineering, chemosensors, children, chromatography, climate, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, data, dentistry, designs, diagnostics, diseases, diversity, econometrics, economies, education, electrochemistry, electronics, energies, entropy, environments, epigenomes, fermentation, fibers, fishes, fluids, foods, forests, fractalfract, futureinternet, galaxies, games, gastrointestdisord, gels, genealogy, genes, geosciences, geriatrics, healthcare, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, ijtpp, inventions, jcdd, jcm, jcs, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmmp, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, mti, medsci, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, molbank, molecules, mps, nanomaterials, ncrna, neonatalscreening, nitrogen, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, polymers, proceedings, processes, proteomes, publications, quaternary, qubs, recycling, religions, remotesensing, resources, risks, robotics, safety, scipharm, sensors, separations, sexes, sinusitis, socsci, societies, soilprocesses, soils, sports, standards, strdrugs, surgeries, sustainability, symmetry, systems, technologies, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vetsci, viruses, vision, water, wem
%---------
% article
%---------
% The default type of manuscript is article, but can be replaced by: 
% addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferenceproceedings, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, newbookreceived, opinion, obituary, projectreport, reply, reprint, retraction, review, perspective, preprints, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials
% protocol: If you are preparing a "Protocol" paper, please refer to http://www.mdpi.com/journal/mps/instructions for details on its expected structure and content.
%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g. the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figure are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother 
\articlenumber{x}
\doinum{10.3390/------}
\pubvolume{xx}
\pubyear{2017}
\copyrightyear{2017}
\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Title}

% If this is an expanded version of a conference paper, please cite it here: enter the full citation of your conference paper, and add $^\dagger$ in the end of the title of this article.
%\conference{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

% Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: e-mail@e-mail.com; Tel.: +x-xxx-xxx-xxxx}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

% Simple summary
%\simplesumm{}

% Abstract (Do not use inserted blank lines, i.e. \\) 
\abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: 1) Background: Place the question addressed in a broad context and highlight the purpose of the study; 2) Methods: Describe briefly the main methods or treatments applied; 3) Results: Summarize the article's main findings; and 4) Conclusion: Indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.)}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% For Conference Proceedings Papers:
%\conferencetitle{Add the conference title here}

%\setcounter{secnumdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Only for the journal Gels: Please place the Experimental Section after the Conclusions

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}
The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g. the positioning of the Materials and Methods section). Please check the instructions for authors page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX related questions please contact Janine Daum at latex-support@mdpi.com.

\section{Introduction}

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. And now citing a book reference \cite{ref-book}. Please use the command \citep{ref-journal} for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Subsection}

\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}[leftmargin=*,labelsep=5.8mm]
\item	First bullet
\item	Second bullet
\item	Third bullet
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}[leftmargin=*,labelsep=4.9mm]
\item	First item 
\item	Second item
\item	Third item
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure 1, Table 1, etc.

\begin{figure}[H]
\centering
\includegraphics[width=3 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
entry 1		& data			& data\\
entry 2		& data			& data\\
\bottomrule
\end{tabular}
\end{table}

\subsection{Formatting of Mathematical Components}

This is an example of an equation:

\begin{equation}
\mathbb{S}
\end{equation}

%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph. 
Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{All sources of funding of the study should be disclosed. Please clearly indicate grants that you have received in support of your research work. Clearly state if you received funds for covering the costs to publish in open access.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``X.X. and Y.Y. conceived and designed the experiments; X.X. performed the experiments; X.X. and Y.Y. analyzed the data; W.W. contributed reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be limited to those who have contributed substantially to the work reported.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funding sponsors in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, and in the decision to publish the results''.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\abbreviations{The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & linear dichroism
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\appendixtitles{no} %Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixsections{multiple} %Leave argument "multiple" if there are multiple sections. Then a counter is printed ("Appendix A"). If there is only one appendix section then change the argument to "one" and no counter is printed ("Appendix").
\appendix
\section{}
\subsection{}
The appendix is an optional section that can contain details and data supplemental to the main text. For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data. Mathematical proofs of results not central to the paper can be added as an appendix.

\section{}
All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: internal bibliography
%=====================================
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142-149, DOI.
% Reference 2
\bibitem[Author2(year)]{ref-book}
Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32-58, ISBN.
\end{thebibliography}

% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%=====================================
% References, variant B: external bibliography
%=====================================
%\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds ...... are available from the authors.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2017-08-22 paper/article.tex
Paper corrections
more inputs

--- 2017-08-22 paper/article.tex
@@
 %\label{}
-\pa{
-// Beaucoup de fomer/latter
-// Le terme soundscape inclut la perception de lenvironnment sonore. Si tu veux parler juste de lenvironnement sonore "urban sound environment" est plus approprie.
-// Ref Judi: Picaut, Judicaël, Arnaud Can, Jérémy Ardouin, Pierre Crépeaux, Thierry Dhorne, David Écotière, Mathieu Lagrange, et al.
-« Characterization of urban sound environments using a comprehensive approach combining open data, measurements, and modeling ».
-In The Journal of the Acoustical Society of America, 141:3808-3808.
-Boston, USA: Acoustical Society of America, 2017.
-doi:10.1121/1.4988416.
-}
-The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc\footnote{\url{htttp://wp.nyu.edu/sonyc}} \cite{mydlarz2017implementation} and cense\footnote{\url{htttp://cense.ifsttar.fr}} \pa{ref papier de judicael ?} \cite{} projects.
+
+The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc\footnote{\url{htttp://wp.nyu.edu/sonyc}} \cite{mydlarz2017implementation} and cense\footnote{\url{htttp://cense.ifsttar.fr}} \cite{picault2017} projects.
 
@@
 The data of interest is first acoustic indicators (LAeq, ...) and second the presence of sound sources of interest (bird calls, sirens, ...).
-The latter allows us to better assess soundscapes in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}.
-This detection step can respectively be operated online (on the sensors) or offline (on the data servers).
+The latter allows us to better assess the human perception of the urban sound environment in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}.
+This detection step can respectively be operated online (on the sensors) or offline (on the data servers) leading to different grid designs, see Figure \ref{fig:codingScheme}.
 
-The former is efficient in terms of data storage as only the detection events are transmitted and is thus currently considered in several approaches \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
+Online detection is efficient in terms of data storage as only the detection events are transmitted and is thus currently considered in several approaches \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
 Though, it requires the availability of computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware do not allow them to be autonomous using power sources like decent size solar panels.
@@
 
-The latter scheme has several benefits.
-First, the sensor task is much simpler and can thus be implemented using low consumption processors, potentially being autonomous in terms of energy.
+The alternative scheme has several benefits.
+First, the sensor task is much simpler and can thus be implemented on low energy consumption processors, potentially being autonomous in terms of energy.
 This will ease the deployment of the network.
@@
 In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation.
-Thickness of arrows roughly indicate bandwidth and thickness of boxes roughly indicates the level of computation or storage required.\pa{Figure non appelee}}
+Thickness of arrows roughly indicate bandwidth and thickness of boxes roughly indicates the level of computation or storage required.}
 \label{fig:codingScheme}
@@
 
-Even though the above discussed indicators provide more richness than $L_{eq}$, studies show that abstract statistics are still not sufficient to fully model the soundscapes \pa{refs}.
+Even though the above discussed indicators provide more richness than $L_{eq}$, studies show that abstract statistics are still not sufficient to fully model the soundscapes \pa{refs} \cl{can you add some ?}.
 The recognition of sources of interest is thus of importance.
@@
 An audio encoding scheme has been described and motivated for use in a sensor grid approach to tackle the problem of large scale acoustic monitoring.
+It has been designed to transfer data from acoustic sensors to processing and storage servers in an efficient and effective manner.
+It relies on a lossy audio coding scheme designed to the ensure privacy of citizens while retaining the needed amount of acoustic precision to compute standard acoustic descriptors and to allow the recognition of events of interest at a state of the art level of recognition accuracy.
+
+It is based on a third octave spectral representation computed at an adjustable frame rate, encoded using an Huffman encoding scheme after logarithmic compression and differential encoding.
 
@@
 	\item precision: the impact of the quantization step for 8 bits codewords is found to be very small (< 0.5dB) and thus:
-	- respect the acoustics indicators which could be calculated from the spectrogram.
+	- do not impact the quality of the acoustics indicators.
 	- permits to perform the sound recognition with the same quality than directly from the spectrogram.
 	\item efficiency: for fast and slow modes, the bitrate is respectively about 1.4~kbps and 0.4~kbps for the high precision mode
-	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible.
+	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible according to a perceputal test.
 \end{itemize}
+
+The encoding scheme is designed to be simple to use and to lead to an efficient data format for storage and sharing acroos the research community.
+To encourage its use for other research projects, an open source Matlab implementation of the coder is available.
 
@@
 
-Future work will study the usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency and a more thorough investigation on the inversion methods in order to ensure that the inintelligibility constraint is indeed not violated for fast settings.
+Future work will focus on the use of such a sensor grid approach as part of the cense project where its effectiveness will be assessed in filed conditions.
+The usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency should also be studied.
+Also, a more thorough investigation shall be performed on the inversion methods used to recover audio data from encoded data in order to ensure that the inintelligibility constraint is indeed not violated for fast settings.
 

### 2017-08-28 paper/article.tex
Paper update - error

@@
 This metric is composed of band analysis error and the additional loss yielded by quantization before the encoding process.
-To this aim, third-octave bands are computed with the proposed method, then averaged and compared to a trusted reference.
-The chosen reference considers the Matlab \textit{ita\_ toolbox} implementation \cite{itatoolbox2017} processed over the whole signal.
+
+To evaluate the analysis error, we consider the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017} as a reference.
 We study both "fast" computation with 125~ms windows and "slow" 1~s analysis to assess the impact of time integration.
-In both cases the sound dataset is the same and is composed of 2~s extracts.
+Third-octave bands are computed using the proposed method as well as the \textit{ita\_toolbox} in the same conditions, then averaged over time and compared to the toolbox's measurements on longer extracts.
+In all experiments the sound dataset is the same and is composed of 2~s extracts.
 The experiment is run for white noise as well as urban environmental recordings.
@@
 The measurement error is computed for third-octave bands.
-Results are displayed in Figure~\ref{fig:errorm}.
+Results are displayed in Figure~\ref{fig:errormn} for white noise extracts and in Figure~\ref{fig:errormu} for environmental sounds.
 Only full-octave bands are shown for visibility.
@@
 This was not observed for fast analysis where the error was similar or higher with the use of overlapping frames.
-We propose to study the absolute error metric, as all experiments show a mean error close to zero.
 
@@
 When considering white noise the error is low on the whole spectrum.
-This effectiveness does not translate to environmental sounds analysis.
+Its mean over the testing samples is close to zero and its standard deviation increases in low frequencies, confirming the above-mentioned considerations.
+This effectiveness does not translate well to environmental sounds analysis.
 A factor of this phenomenon is the sound level disparities absent in the first case but omnipresent in the second.
@@
 While it yields the lowest error in high frequency bands, its high spectral leakage effect makes it unprecise for lower frequency regions.
-Non-flat windows better account for this issue but require assuming that the signal is stationary in a given frame and are thus biased.
-For slow measurements, the rectangular window impact is less harmful to band analysis due to an increased frequency resolution.\\
+Non-flat windows better account for this issue but require assuming that the signal is stationary in a given frame.
+The use of overlap then results in better estimates at the cost of an increased data size.
+For slow measurements, the rectangular window impact is less harmful to band analysis due to an increased frequency resolution.
+
+Comparing the error to that of third-octave bands estimated by a time-filtering algorithm results in important similarities being found.
+For fast measurements and a rectangular window (Figure~\ref{fig:errormu}a), a student t-test ($p<0.05$) shows that the errors are not significantly different between 125~Hz and 12~kHz bands.
+For the first bands, the two methods yield different error distributions but of similar importance.
+\fg{fast, Hann}.
+A slow analysis results in statistically equivalent errors between the two methods apart from the very low frequencies: $p = 0.011$ with the rectangular window (Figure~\ref{fig:errormu}c), $p = 0.003$ at 20~Hz and $p = 0.021$ at 25~Hz for the Hann window and 66\% overlap (Figure~\ref{fig:errormu}d).\\
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/err_m_n.eps}
+    \caption{Measurement error of third-octave bands over two-seconds white noise extracts, with rectangular window and no overlap.
+The analysis of short frames has an effect on energy estimation at low frequencies that is corrected as the frequency resolution increases.\label{fig:errormn}}
+\end{figure}
 
@@
         \centering
-        \includegraphics[width=\linewidth]{figures/err_m_n.eps}
-        \caption{Noise extracts}
+        \includegraphics[width=\linewidth]{figures/err_m_u_f_r.eps}
+        \caption{Fast analysis, rectangular window, no overlap}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\linewidth]{figures/err_m_u.eps}
-        \caption{Urban sounds recordings}
+        \includegraphics[width=\linewidth]{figures/err_m_u_f_r.eps}
+        \caption{Fast analysis, Hann window, 66\% overlap\fg{missing}}
     \end{subfigure}
-
-    \caption{Measurement error of third-octave bands over two-seconds recordings.
-The analysis of short frames has an effect on energy estimation at low frequencies.
-Framing is more impactful on signals where the energy is localized in frequency.
-\label{fig:errorm}}
+	\begin{subfigure}[h]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{figures/err_m_u_s_r.eps}
+        \caption{Slow analysis, rectangular window, 50\% overlap}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[h]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\linewidth]{figures/err_m_u_s_h.eps}
+        \caption{Slow analysis, Hann window, 66\% overlap}
+    \end{subfigure}
+    \caption{Measurement error of third-octave bands over two-seconds environmental sounds recordings (US8k database).
+For most settings the FFT-based method yields similar errors to the time-domain filtering reference.
+\label{fig:errormu}}
 \end{figure*}
-
-%\begin{table*}[h]
-%\centering
-%\caption{Third-octave bands measurement absolute error in dB for fast and slow computations and four window functions.
-The proposed method is here compared with evaluations by the \textit{ITA-toolbox} for 2-seconds exerpts.
-}
-%\label{T1}
-%\begin{tabular}{|c|c|c|c|c|c|}
-%\cline{1-6}
-%\multirow{2}{*}{Analysis} & \multirow{2}{*}{Window} & \multicolumn{2}{|c|}{White noise} & \multicolumn{2}{|c|}{Environmental recordings}\\ \cline{3-6}
-% & & 20~Hz & 1~kHz & 20~Hz & 1~kHz\\ \cline{1-6}
-%\multicolumn{1}{|c}{\multirow{4}{*}{Fast - 125~ms, 0$\%$ overlap}}
-% & \multicolumn{1}{|c|}{Rectangular} & 0.94$\pm$0.75 & 0.07$\pm$0.02 & 5.59$\pm$5.64 & 0.21$\pm$0.76\\ \cline{2-6}
-%\multicolumn{1}{|c}{}
-% & \multicolumn{1}{|c|}{Hamming} & 1.02$\pm$0.71\newline & 0.16$\pm$0.14 & 3.34$\pm$3.41 & 0.44$\pm$0.76\\ \cline{2-6}
-%\multicolumn{1}{|c}{}
-% & \multicolumn{1}{|c|}{Gaussian} & 1.04$\pm$0.71 & 0.17$\pm$0.15 & 3.56$\pm$3.63 & 0.48$\pm$0.83\\ \cline{2-6}
-%\multicolumn{1}{|c}{}
-% & \multicolumn{1}{|c|}{Tukey ($\alpha = 0.5$)} & 0.97$\pm$0.75 & 0.11$\pm$0.09 & 4.16$\pm$5.58 & 0.32$\pm$0.80\\ \cline{1-6}
-% \multicolumn{1}{|c}{\multirow{4}{*}{Slow - 1~s, 50$\%$ overlap}}
-% & \multicolumn{1}{|c|}{Rectangular} & 0.48$\pm$0.36 & 0.08$\pm$0.05 & 1.86$\pm$3.13 & 0.40$\pm$0.55\\ \cline{2-6}
-%\multicolumn{1}{|c}{}
-% & \multicolumn{1}{|c|}{Hamming} & 0.57$\pm$0.56 & 0.09$\pm$0.07 & 2.23$\pm$3.58 & 0.74$\pm$1.61\\ \cline{2-6}
-%\multicolumn{1}{|c}{}
-% & \multicolumn{1}{|c|}{Gaussian} & 0.62$\pm$0.61 & 0.10$\pm$0.08 & 2.48$\pm$4.16 & 0.80$\pm$1.75\\ \cline{2-6}
-%\multicolumn{1}{|c}{}
-% & \multicolumn{1}{|c|}{Tukey ($\alpha = 0.5$)} & 0.53$\pm$0.48 & 0.09$\pm$0.07 & 2.82$\pm$6.64 & 0.61$\pm$1.40\\ \cline{1-6}
-%\end{tabular}
-%\end{table*}
 

### 2017-08-28 tobError/report_figs.m

@@ -150,26 +150,26 @@ clear all, close all, clc;
 % xlabel('Frequency'), ylabel('Measurement error (dB)')
 
 %% Window type - Noise - Fast
-load('report/figures/tobErr_n_win_f.mat');
-% load('report/figures/tobErr_s_win_f.mat');
-% load('report/figures/tobErr_u_win_f.mat');
-% win_mask = [1 2 3 4 5 6 7 8 9 10 11 12 13 14 15 16 17];
-win_mask = [12];
-wintype = {'hamming', 'hanning', 'blackmanharris', 'bartlett', 'bartletthann', 'gaussian', 'kaiser', 'tukey01', 'tukey02', 'tukey03', 'tukey04', 'tukey05', 'tukey06', 'tukey07', 'tukey08', 'tukey09', 'rect'};
-for ind_rlen = 1:length(data.rawData)
-    errMean(:, ind_rlen) = data.rawData{ind_rlen}.errMean;
-    errStd(:, ind_rlen) = data.rawData{ind_rlen}.errStd;
-end
-
-tob_f  = 10^3 * (2 .^ ([-17:11]/3));
-
-figure(1), clf, %errorbar(tob_f(2:end), errMean(2:end, 1), errStd(2:end, 1), '-x'), 
-for ind_rlen = win_mask%2:size(errMean, 2)
-    errorbar(tob_f(2:end), errMean(2:end, ind_rlen), errStd(2:end, ind_rlen), '-x'), hold on,
-end
-set(gca, 'xscale', 'log');
-grid on, legend(wintype([win_mask])), axis([1e1 5e4 -6 8])
-xlabel('Frequency'), ylabel('Measurement error (dB)')
+% load('report/figures/tobErr_n_win_f.mat');
+% % load('report/figures/tobErr_s_win_f.mat');
+% % load('report/figures/tobErr_u_win_f.mat');
+% % win_mask = [1 2 3 4 5 6 7 8 9 10 11 12 13 14 15 16 17];
+% win_mask = [12];
+% wintype = {'hamming', 'hanning', 'blackmanharris', 'bartlett', 'bartletthann', 'gaussian', 'kaiser', 'tukey01', 'tukey02', 'tukey03', 'tukey04', 'tukey05', 'tukey06', 'tukey07', 'tukey08', 'tukey09', 'rect'};
[…]

### 2017-08-28 tobError/run_script.m

@@ -29,5 +29,33 @@
 % tobError('do', [3], 'mask', {12, 1, 1, 4, 2});
 % [1 6 12 17]
 % tobError('do', [1 3], 'mask', {12, 1, 2, 6, 2});
-tobError('do', [3], 'mask', {17, 3, 0, 6, 2});
 
+% tobError('do', [3], 'mask', {1, [1 3], 0, 6, 2});
+% tobError('do', [1 3], 'mask', {17, [1 3], 0, 6, 2, 0});
+% tobError('do', [1 3], 'mask', {[1 17], [1], 0, 6, 2, 0});
+% tobError('do', [3], 'mask', {[1], [3], 2, 6, 2, 3, 2});
+% tobError('do', [3], 'mask', {[17], [3], 2, 6, 2, 3, 2});
+% tobError('do', [3], 'mask', {[17], [3], 2, 6, 2, 3, 2});
+%% DONE
+
+
+% 125ms - No overlap - Hann
+% tobError('do', [4], 'mask', {2, 3, 1, 6, 2, 3, 0});
+% 1s - 50% overlap - Hann
+% tobError('do', [4], 'mask', {2, 3, 2, 6, 2, 2, 0});
+% 1s - 66% overlap - Hann
+% tobError('do', [1 3 4], 'mask', {2, 3, 2, 6, 2, 4, 0});
+% 125ms - 66% overlap - Hann
+% tobError('do', [1 3 4], 'mask', {2, 3, 1, 6, 2, 4, 0});
+
+%% Not used
+% 125ms - 66% overlap - Rect
+% tobError('do', [4], 'mask', {17, 3, 1, 6, 2, 4, 0});
+% 1s - 66% overlap - Rect
+% tobError('do', [4], 'mask', {17, 3, 2, 6, 2, 4, 0});
+
+%% Used
+% 125ms - No overlap - Rect
+% tobError('do', [4], 'mask', {17, 3, 1, 6, 2, 3, 0});
+% 1s - 50% overlap - Rect
+% tobError('do', [4], 'mask', {17, 3, 2, 6, 2, 2, 0});

### 2017-08-28 tobError/stft.m

@@ -7,7 +7,7 @@ if nargin < 3
     l_hop = round(0.5*l_win); % Default overlap: 50%
 end
 
-n_win = 1+(length(x)-l_win)/l_hop; % Number of windows
+n_win = floor(1+(length(x)-l_win)/l_hop); % Number of windows
 
 %% Window generation
 switch wintype % Other windows to implement

### 2017-08-28 tobError/toer1cense.m

@@ -16,7 +16,8 @@ if nargin==0, tobError('do', 1, 'mask', {}); return; else store=[]; obs=[]; end
 sr = 32000;
 
 l_frame = round(setting.framelen*sr);
-if setting.framelen == 0.125; l_hop = 1*l_frame; else l_hop = 0.5*l_frame; end
+% if setting.framelen == 0.125; l_hop = 1*l_frame; else l_hop = 0.5*l_frame; end
+l_hop = setting.hopsize*l_frame;
 
 N = 2^(ceil(log2(l_frame)));
 N_filt = 2^20; % Design with a much higher precision
@@ -47,8 +48,10 @@ clear G N_filt;
 switch setting.wintype % Other windows to implement
     case 'hamming'
         w = hamming(l_frame, 'periodic');
+        w_ita = @hamming;
     case 'hanning'
         w = hanning(l_frame, 'periodic');
+        w_ita = @hann;
     case 'blackmanharris'
         w = blackmanharris(l_frame, 'periodic');
     case 'bartlett'
@@ -79,6 +82,7 @@ switch setting.wintype % Other windows to implement
         w = tukeywin(l_frame, 0.9);
     case 'rect'
         w = ones(l_frame, 1);
+        w_ita = @rectwin;
 end
 
 switch setting.dataset
@@ -117,8 +121,31 @@ switch setting.dataset
             for ind_wav = 1:100
                 assert(setting.reflen>=setting.framelen);
                 x = x_noise{ind_wav};
-                X_st = (abs(stft(x, l_frame, l_hop, setting.wintype, 1)).^2)/(sum(w.^2)*(l_frame/2+1)/l_frame);
-                X_tob_cen{ind_wav} = H_st*X_st;
+                switch setting.centype
+                    case 'cense'
+                        if mod(size(x, 1)-l_frame, l_hop)
+                            x = [x; zeros(l_hop-mod(size(x, 1)-l_frame, l_hop), 1)]; % Sup
+                        end
+                        X_st = (abs(stft(x, l_frame, l_hop, setting.wintype, 1)).^2)/(sum(w.^2)*(l_frame/2+1)/l_frame);
+                        X_tob_cen{ind_wav} = H_st*X_st;
+                    case 'ita'
+                        if mod(size(x, 1)-l_frame, l_hop)
+                            x = [x; zeros(l_hop-mod(size(x, 1)-l_frame, l_hop), 1)]; % Sup
+                        end
[…]

### 2017-08-28 tobError/toer2ref_ita.m

@@ -59,33 +59,47 @@ switch setting.dataset
                 n_x = floor(length(x)/l_frame);
                 for ind_x = 1:n_x
                     a = itaAudio(x((ind_x-1)*l_frame+1:ind_x*l_frame), sr, 'time');
-                    b = ita_mpb_filter(a, '3-oct');
-                    X_tob_ref{ind_wav}(:, ind_x) = sum(b.time.^2/length(x((ind_x-1)*l_frame+1:ind_x*l_frame)), 1)';
+%                     b = ita_mpb_filter(a, '3-oct');
+                    b = ita_spk2frequencybands(a, 'mode', 'filter');
+                    X_tob_ref{ind_wav}(:, ind_x) = 20*log10(b.freq);
+%                     X_tob_ref{ind_wav}(:, ind_x) = sum(b.time.^2/length(x((ind_x-1)*l_frame+1:ind_x*l_frame)), 1)';
                 end
             end
         else
             error('No file found');
         end
     case 'speech'
-        for ind_wav = 1:length(file_path)
+        for ind_wav = 1:1%length(file_path)
             disp(['Processing file ' num2str(ind_wav) ' of ' num2str(length(file_path)) '...']);
-            [x, sr2] = audioread(file_path{ind_wav});
-            x = resample(x(:, 1), sr, sr2);
-            % Analysis
-            if mod(size(x, 1)-l_frame, l_hop)
-                x = [x; zeros(l_hop-mod(size(x, 1)-l_frame, l_hop), 1)]; % Sup
-            end
-            n_x = floor(length(x)/l_frame);
+%             [x, sr2] = audioread(file_path{ind_wav});
+            x = ita_read(file_path{ind_wav});
+            x = ita_resample(x, sr);
+            n_x = floor(x.nSamples/l_frame);
+            
             for ind_x = 1:n_x
-                a = itaAudio(x((ind_x-1)*l_frame+1:ind_x*l_frame), sr, 'time');
-                b = ita_mpb_filter(a, '3-oct');
-                X_tob_ref{ind_wav}(:, ind_x) = sum(b.time.^2/length(x((ind_x-1)*l_frame+1:ind_x*l_frame)), 1)';
+                sample1 = ita_time_window(x,[((ind_x-1)*l_frame+1)/sr, ind_x*l_frame/sr],@rectwin,'time', 'crop');
+                oct_sample1=ita_spk2frequencybands(sample1,'mode','filter');
[…]

### 2017-08-28 tobError/toer3error.m

@@ -13,8 +13,15 @@ function [config, store, obs] = toer3error(config, setting, data)
 % Set behavior for debug mode                                                  
 if nargin==0, tobError('do', 3, 'mask', {}); return; else store=[]; obs=[]; end
                                                                                
+if strcmp(setting.centype, 'ita')&& strcmp(setting.wintype, 'hanning')&& ~strcmp(setting.dataset, 'noise') && setting.hopsize~=0.33
+        l_frame = setting.framelen*32000;
+        w = hann(l_frame, 'periodic');
+end
+
 data_cen = expLoad(config, [], 1);
 
+load names;
+wav_names = [];
 assert(setting.reflen>=setting.framelen);
 err_cen_ref = [];
 r_level = [];
@@ -25,11 +32,27 @@ for ind_wav = 1:length(data.X_tob_ref)
         if n_ref > 0
             for ind_ref = 1:n_ref
                 n_avg = round(setting.reflen/setting.framelen);
-                X_tob_cen(:, ind_ref) = mean(data_cen.X_tob_cen{ind_wav}(:, (ind_ref-1)*n_avg+1:min(ind_ref*n_avg, end))/4096, 2);
+                if strcmp(setting.centype, 'cense'); X_tob_cen(:, ind_ref) = mean(data_cen.X_tob_cen{ind_wav}(:, (ind_ref-1)*n_avg+1:min(ind_ref*n_avg, end))/4000, 2); 
+%                 else X_tob_cen(:, ind_ref) = mean(data_cen.X_tob_cen{ind_wav}(:, (ind_ref-1)*n_avg+1:min(ind_ref*n_avg, end)), 2); end;
+                else X_tob_cen(:, ind_ref) = 10*log10(mean(10.^(data_cen.X_tob_cen{ind_wav}(:, (ind_ref-1)*(n_avg+1)+1:min((ind_ref-1)*(n_avg+1)+n_avg, end))/10)/4000, 2)); end;
+                if strcmp(setting.centype, 'ita')&& strcmp(setting.wintype, 'hanning')&& ~strcmp(setting.dataset, 'noise') && setting.hopsize~=0.33
[…]

### 2017-08-28 tobError/toer4ttest.m

@@ -1,0 +1,55 @@
+function [config, store, obs] = toer4ttest(config, setting, data)              
+% toer4ttest TTEST step of the expLanes experiment tobError                    
+%    [config, store, obs] = toer4ttest(config, setting, data)                  
+%      - config : expLanes configuration state                                 
+%      - setting   : set of factors to be evaluated                            
+%      - data   : processing data stored during the previous step              
+%      -- store  : processing data to be saved for the other steps             
+%      -- obs    : observations to be saved for analysis                       
+                                                                               
+% Copyright: felix                                                             
+% Date: 09-Aug-2017                                                            
+                                                                               
+% Set behavior for debug mode                                                  
+if nargin==0, tobError('do', 4, 'mask', {}); return; else store=[]; obs=[]; end
+                                                                               
+if strcmp(setting.wintype, 'hanning') && setting.hopsize~=0.33
+    l_frame = setting.framelen*32000;
+    w = hann(l_frame, 'periodic');
+end
+
+data_cen = [];
+data_ita = [];
+data_cen_ita = expLoad(config, [], 1);
+for ind_wav = 1:length(data_cen_ita(1).X_tob_cen)
+    data_cen_ita(1).X_tob_cen{ind_wav} = 10*log10(data_cen_ita(1).X_tob_cen{ind_wav});
+    if strcmp(setting.wintype, 'hanning') && setting.hopsize~=0.33
+        data_cen_ita(2).X_tob_cen{ind_wav} = 10*log10(10.^(data_cen_ita(2).X_tob_cen{ind_wav}/10)/(l_frame/sum(w)).^2*l_frame/sum(w.^2));
+    end
+    ttest_wav(:, ind_wav) = ttest2(data_cen_ita(1).X_tob_cen{ind_wav}(:), data_cen_ita(2).X_tob_cen{ind_wav}(:));
[…]

### 2017-08-28 tobError/toerReport.m

@@ -33,5 +33,24 @@ if nargin==0, tobError('report', 'r'); return; end
 % config = expExpose(config, 't', 'mask', {0, 3, 2, 4}, 'obs', 0, 'save', 'tobErr_u_win_s', 'step', 3);
 
 % config = expExpose(config, 't', 'mask', {12, 1, 1, 4, 2}, 'obs', 0, 'save', 'tobErr_test', 'step', 3);
-config = expExpose(config, 't', 'mask', {[1 6 12 17], 1, 0, 6, 2}, 'obs', 0, 'save', 'tobErr_noise', 'step', 3);
-config = expExpose(config, 't', 'mask', {[1 6 12 17], 3, 0, 6, 2}, 'obs', 0, 'save', 'tobErr_us8k', 'step', 3);
+% config = expExpose(config, 't', 'mask', {[1 6 12 17], 1, 0, 6, 2}, 'obs', 0, 'save', 'tobErr_noise', 'step', 3);
+% config = expExpose(config, 't', 'mask', {[1 6 12 17], 3, 0, 6, 2}, 'obs', 0, 'save', 'tobErr_us8k', 'step', 3);
+
+
+% config = expExpose(config, 't', 'mask', {[1], 1, 0, 6, 2, 0}, 'obs', 0, 'save', 'tobErr_noise', 'step', 3);
+% config = expExpose(config, 't', 'mask', {[1], 3, 0, 6, 2, 0}, 'obs', 0, 'save', 'tobErr_us8k', 'step', 3);
+% config = expExpose(config, 't', 'mask', {[17], 1, 0, 6, 2, 0}, 'obs', 0, 'save', 'tobErr_noise_rect', 'step', 3);
+% config = expExpose(config, 't', 'mask', {[17], 3, 0, 6, 2, 0}, 'obs', 0, 'save', 'tobErr_us8k_rect', 'step', 3);
+
+
+% config = expExpose(config, 't', 'mask', {[17], 3, 1, 6, 2, 3, 2}, 'obs', 0, 'save', 'tobErr_us8k_rect_ita_f', 'step', 3);
+% config = expExpose(config, 't', 'mask', {[2], 3, 1, 6, 2, 3, 2}, 'obs', 0, 'save', 'tobErr_us8k_hann_ita_f', 'step', 3);
[…]

### 2017-08-28 paper/article.tex
Paper update - Error

@@
 The analysis of sources within a sound environment is generally linked with spectral content \cite{ishiyama2000} and high temporal measurement resolutions.
-Other indicators can correlate with specific sound environment content \fg{cite Aumond/Lavandier TFSD} but do not achieve the same performances as a source detection scheme in characterizing soundscapes.
+Other indicators can correlate with specific sound environment content \cite{aumond2017} but do not achieve the same performances as a source detection scheme in characterizing soundscapes.
 
@@
 
-Even though the above discussed indicators provide more richness than $L_{eq}$, studies show that abstract statistics are still not sufficient to fully model the soundscapes \pa{refs} \cl{can you add some ?}.
-The recognition of sources of interest is thus of importance.
-As far as the encoding scheme is concerned, it is thus important that the encoded data allows us to compute the above cited indicators but also to allow us to recognize the sources of interest with state of the art methods.
+As discussed in the previous section, the recognition of sources of interest is of importance to fully model the studied soundscapes.
+As far as the encoding scheme is concerned, it is thus primordial that the encoded data allows us to compute the above cited indicators but also to detect the different sound sources with state of the art methods.
 
@@
 These representations effectively model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale.
-While parameters are empirical and vary in the litterature, a reference implementation includes 23.2~ms analysis and a 40 Mel bands resolution.
+While parameters are empirical and vary in the literature, a reference implementation includes 23.2~ms analysis and a 40 Mel bands resolution.
 The resulting representations are generally more precise in time and frequency than in acoustic monitoring applications because it is a primordial factor for classification whereas acoustic indicators must be computed more accurately.

### 2017-08-29 paper/article.tex
Paper - MDPI

@@
 For the first bands, the two methods yield different error distributions but of similar importance.
-\fg{fast, Hann}.
+Using a Hann window function results in lower error in low frequencies but adds a bias to the previously accurate band measurements.
+Again comparing the two computation methods shows a significant difference in the bands below 100~Hz only.
 A slow analysis results in statistically equivalent errors between the two methods apart from the very low frequencies: $p = 0.011$ with the rectangular window (Figure~\ref{fig:errormu}c), $p = 0.003$ at 20~Hz and $p = 0.021$ at 25~Hz for the Hann window and 66\% overlap (Figure~\ref{fig:errormu}d).\\
@@
         \centering
-        \includegraphics[width=\linewidth]{figures/err_m_u_f_r.eps}
-        \caption{Fast analysis, Hann window, 66\% overlap\fg{missing}}
+        \includegraphics[width=\linewidth]{figures/err_m_u_f_h.eps}
+        \caption{Fast analysis, Hann window, 66\% overlap}
     \end{subfigure}

### 2017-08-29 paper/article_mdpi.tex
Paper - MDPI

--- 2017-08-29 paper/article.tex
@@
-%%
-%% Copyright 2007, 2008, 2009 Elsevier Ltd
-%%
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%%
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%%
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%%
-%% Template article for Elsevier's document class `elsarticle'
-%% with harvard style bibliographic references
-%% SP 2008/03/01
+%  LaTeX support: latex@mdpi.com 
+%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
 
-\documentclass[final,3p,times,twocolumn]{elsarticle}
+% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.
 
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-%% please give \usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
+%=================================================================
+\documentclass[sensors,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi} 
+%
+%--------------------
+% Class Options:
+%--------------------
+% journal
+%----------
+% Choose between the following MDPI journals:
+% actuators, admsci, aerospace, agriculture, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, atmosphere, atoms, axioms, batteries, bdcc, behavsci, beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci, buildings, carbon, cancers, catalysts, cells, challenges, chemengineering, chemosensors, children, chromatography, climate, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, data, dentistry, designs, diagnostics, diseases, diversity, econometrics, economies, education, electrochemistry, electronics, energies, entropy, environments, epigenomes, fermentation, fibers, fishes, fluids, foods, forests, fractalfract, futureinternet, galaxies, games, gastrointestdisord, gels, genealogy, genes, geosciences, geriatrics, healthcare, horticulturae, humanities, hydrology, informatics, information, infrastructures, inorganics, insects, instruments, ijerph, ijfs, ijms, ijgi, ijtpp, inventions, jcdd, jcm, jcs, jdb, jfb, jfmk, jimaging, jof, jintelligence, jlpea, jmmp, jmse, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, mti, medsci, medicines, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, molbank, molecules, mps, nanomaterials, ncrna, neonatalscreening, nitrogen, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, plants, polymers, proceedings, processes, proteomes, publications, quaternary, qubs, recycling, religions, remotesensing, resources, risks, robotics, safety, scipharm, sensors, separations, sexes, sinusitis, socsci, societies, soilprocesses, soils, sports, standards, strdrugs, surgeries, sustainability, symmetry, systems, technologies, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vetsci, viruses, vision, water, wem
+%---------
+% article
+%---------
+% The default type of manuscript is article, but can be replaced by: 
+% addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferenceproceedings, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, newbookreceived, opinion, obituary, projectreport, reply, reprint, retraction, review, perspective, preprints, protocol, shortnote, supfile, technicalnote, viewpoint
+% supfile = supplementary materials
+% protocol: If you are preparing a "Protocol" paper, please refer to http://www.mdpi.com/journal/mps/instructions for details on its expected structure and content.
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g.
+the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. If eps figure are used, remove the option pdftex and use LaTeX and dvi2pdf.
 \usepackage{amssymb}
@@
 
-%% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
-\journal{Applied Acoustics}
-
+%=================================================================
 \newcommand{\ml}[1]{\textcolor{blue}{ Mathieu: #1}}
@@
 
-\begin{document}
+\firstpage{1} 
+\makeatletter 
+\setcounter{page}{\@firstpage} 
+\makeatother 
+\articlenumber{x}
+\doinum{10.3390/------}
+\pubvolume{xx}
+\pubyear{2017}
+\copyrightyear{2017}
+\history{Received: date; Accepted: date; Published: date}
 
-\begin{frontmatter}
+%------------------------------------------------------------------
+% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
+%\pdfoutput=1
 
-%% Title, authors and addresses
+%=================================================================
+% Add packages and commands here.
+The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz
 
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
+%=================================================================
+%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
+%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
 
-\title{A sensor grid approach for large scale acoustic monitoring}
+%=================================================================
+% Full title of the paper (Capitalized)
+\Title{A sensor grid approach for large scale acoustic monitoring}
 
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
+% If this is an expanded version of a conference paper, please cite it here: enter the full citation of your conference paper, and add $^\dagger$ in the end of the title of this article.
+%\conference{Title}
 
-\author{F\'elix Gontier, Mathieu Lagrange, Pierre Aumond, Arnaud Can, Catherine Lavandier}
+% Authors, for the paper (add full first names)
+\Author{F\'elix Gontier $^{1}$, Mathieu Lagrange $^{1}$, Pierre Aumond $^{2}$, Arnaud Can $^{2}$ and Catherine Lavandier $^{3}$}
 
-\address{felix.gontier@reseau.eseo.fr}
+% Authors, for metadata in PDF
+\AuthorNames{F\'elix Gontier, Mathieu Lagrange, Pierre Aumond, Arnaud Can and Catherine Lavandier}
 
-\begin{abstract}
-%% Text of abstract
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+$^{1}$ \quad LS2N\\
+$^{2}$ \quad IFSTTAR\\
+$^{3}$ \quad Universit\'e de Cergy-Pontoise}
 
-The spreading of urban areas and the growth of human population worldwide raised societal and environmental concerns.
+% Contact information of the corresponding author
+\corres{Correspondence: felix.gontier@reseau-eseo.fr}
+
+% Simple summary
+%\simplesumm{}
+
+% Abstract (Do not use inserted blank lines, i.e. \\) 
+\abstract{The spreading of urban areas and the growth of human population worldwide raised societal and environmental concerns.
 To better address those, the monitoring of the acoustic environment in urban but also rural or wilderness areas is among other monitoring efforts an important matter.
 Fostering on the recent development of low cost hardware acoustic sensors, we propose in this paper to consider a sensor grid approach to tackle this issue.
-
 In this kind of approach, the crucial question is the nature of the data that is transmitted from the sensors to the processing and archival servers.
@@
 The former is useful to provide quantitative information about the acoustic environment, while the latter is useful to gather qualitative information and build perceptually motivated indicators using for example the emergence of a given sound source.
-The coding scheme is also demonstrated to transmit spectrally encoded data that, reverted to the time domain using state of the art techniques, is not intelligible, thus protecting the privacy of citizens.
+The coding scheme is also demonstrated to transmit spectrally encoded data that, reverted to the time domain using state of the art techniques, is not intelligible, thus protecting the privacy of citizens.}
 
-\end{abstract}
+% Keywords
+\keyword{acoustic monitoring; audio encoding}
 
-\begin{keyword}
+% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
+%\PACS{J0101}
+%\MSC{}
+%\JEL{}
 
-acoustic monitoring \sep audio encoding \sep
-%% keywords here, in the form: keyword \sep keyword
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for journal Applied Sciences:
+%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%% PACS codes here, in the form: \PACS code \sep code
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Only for the journal Data:
+%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
+If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
+In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
 
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
+%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
 
-\end{keyword}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% For Conference Proceedings Papers:
+%\conferencetitle{Add the conference title here}
 
-\end{frontmatter}
+%\setcounter{secnumdepth}{4}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%% \linenumbers
-\clearpage
-%% main text
+\begin{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Only for the journal Gels: Please place the Experimental Section after the Conclusions
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
@@
 
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{figures/censeCoder}
-\vspace{-0.15in}
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\textwidth]{figures/censeCoder}
 \caption{Alternative implementations of the sensor grid approach for the monitoring of the acoustic environment.
@@
 	\centering
-		\includegraphics[width=\columnwidth]{figures/tob_imp.eps}
+		\includegraphics[width=0.5\textwidth]{figures/tob_imp.eps}
 	\caption{Comparison of Couvreur's and Antoni's implementations of third-octave filters. Frequency-weighting allows for arbitrary transfer functions and thus more accurate gains as standards impose.}
@@
 	\centering
-		\includegraphics[width=\columnwidth]{figures/dict_comp.eps}
+		\includegraphics[width=0.5\textwidth]{figures/dict_comp.eps}
 	\caption{Performance comparison of locally and globally generated Huffman dictionaries.
@@
 	\centering
-		\includegraphics[width=\columnwidth]{figures/freq.png}
+		\includegraphics[width=0.5\textwidth]{figures/freq.png}
 	\caption{Third-octave bands analysis and approximate inverse transformation effects on energy location.
@@
 	\centering
-		\includegraphics[width=\columnwidth]{figures/bitrate_qall.eps}
+		\includegraphics[width=0.5\textwidth]{figures/bitrate_qall.eps}
 	\caption{Coder output bitrate as a function of quantization for third-octave and Mel bands with 8 frames per second.}
@@
 	\centering
-		\includegraphics[width=\columnwidth]{figures/bitrate_mel_avg.eps}
+		\includegraphics[width=0.5\textwidth]{figures/bitrate_mel_avg.eps}
 	\caption{Impact of representation resolution on the encoded data bitrate.}
@@
     \centering
-    \includegraphics[width=\columnwidth]{figures/err_m_n.eps}
+    \includegraphics[width=0.5\textwidth]{figures/err_m_n.eps}
     \caption{Measurement error of third-octave bands over two-seconds white noise extracts, with rectangular window and no overlap.
@@
         \centering
-        \includegraphics[width=\linewidth]{figures/err_m_u_f_r.eps}
+        \includegraphics[width=1\textwidth]{figures/err_m_u_f_r.eps}
         \caption{Fast analysis, rectangular window, no overlap}
@@
         \centering
-        \includegraphics[width=\linewidth]{figures/err_m_u_f_h.eps}
+        \includegraphics[width=1\textwidth]{figures/err_m_u_f_h.eps}
         \caption{Fast analysis, Hann window, 66\% overlap}
@@
         \centering
-        \includegraphics[width=\linewidth]{figures/err_m_u_s_r.eps}
+        \includegraphics[width=1\textwidth]{figures/err_m_u_s_r.eps}
         \caption{Slow analysis, rectangular window, 50\% overlap}
@@
         \centering
-        \includegraphics[width=\linewidth]{figures/err_m_u_s_h.eps}
+        \includegraphics[width=1\textwidth]{figures/err_m_u_s_h.eps}
         \caption{Slow analysis, Hann window, 66\% overlap}
@@
 	\centering
-		\includegraphics[width=\columnwidth]{figures/error_qall.eps}
+		\includegraphics[width=0.5\textwidth]{figures/error_qall.eps}
 	\caption{Measurement error induced by encoding for different quantization resolutions.}
@@
 	\centering
-		\includegraphics[width=\columnwidth]{figures/class_mel_q.eps}
+		\includegraphics[width=0.5\textwidth]{figures/class_mel_q.eps}
 	\caption{Classification accuracy as a function of word size before encoding. The baseline on the right is computed without quantizing the representation.}
@@
 	\centering
-		\includegraphics[width=\columnwidth]{figures/class_tob_q.eps}
+		\includegraphics[width=0.5\textwidth]{figures/class_tob_q.eps}
 	\caption{Classification accuracy with third-octave bands and varying word size.}
@@
 	\centering
-		\includegraphics[width=\columnwidth]{figures/subj_int.eps}
+		\includegraphics[width=0.5\textwidth]{figures/subj_int.eps}
 	\caption{Average intellibility score (AIS) given by the subjects and the inteligibility ratio (IR) as a function of the frame rate.
@@
 
-\clearpage
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
-
-%% If you have bibdatabase file and want bibtex to generate the
-%% bibitems, please use
-%%
-%%  \bibliographystyle{elsarticle-harv}
-%%  \bibliography{<your bibdatabase>}
-
-%% else use the following coding to input the bibitems directly in the
-%% TeX file.
-
-\bibliographystyle{plain}
+%=====================================
+% References, variant B: external bibliography
+%=====================================
+\externalbibliography{yes}
+%\bibliography{your_external_BibTeX_file}
 \bibliography{biblio}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \end{document}
-
-\endinput
-%%
-%% End of file `elsarticle-template-harv.tex'.

### 2017-08-29 paper/article.tex
proofread intro

@@
-%%
-%% Copyright 2007, 2008, 2009 Elsevier Ltd
-%%
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%%
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%%
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%%
-%% Template article for Elsevier's document class `elsarticle'
-%% with harvard style bibliographic references
-%% SP 2008/03/01
+%  LaTeX support: latex@mdpi.com
+%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
 
-\documentclass[final,3p,times,twocolumn]{elsarticle}
+% You need to save the "mdpi.cls" and "mdpi.bst" files into the same folder as this template file.
 
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
+%=================================================================
+\documentclass[sensors,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
+%
+%--------------------
+% Class Options:
+%--------------------
+% journal
+%----------
 
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
-%% for a journal layout:
-%% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
-%% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
-%% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-%% please give \usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
+% article
+%---------
+% The default type of manuscript is article, but can be replaced by:
+% addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, correction, conferenceproceedings, conferencereport, expressionofconcern, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, newbookreceived, opinion, obituary, projectreport, reply, reprint, retraction, review, perspective, preprints, protocol, shortnote, supfile, technicalnote, viewpoint
+% supfile = supplementary materials
+% protocol: If you are preparing a "Protocol" paper, please refer to http://www.mdpi.com/journal/mps/instructions for details on its expected structure and content.
+%----------
+% submit
+%----------
+% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
+This will only make changes to the frontpage (e.g.
+the logo of the journal will get visible), the headings, and the copyright information.
+Also, line numbering will be removed.
+Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+%------------------
+% moreauthors
+%------------------
+% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+%---------
+% pdftex
+%---------
+% The option pdftex is for use with pdfLaTeX. If eps figure are used, remove the option pdftex and use LaTeX and dvi2pdf.
 \usepackage{amssymb}
@@
 
-\begin{document}
+\firstpage{1}
+\makeatletter
+\setcounter{page}{\@firstpage}
+\makeatother
+\articlenumber{x}
+\doinum{10.3390/------}
+\pubvolume{xx}
+\pubyear{2017}
+\copyrightyear{2017}
+\history{Received: date; Accepted: date; Published: date}
 
-\begin{frontmatter}
+%------------------------------------------------------------------
+% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
+%\pdfoutput=1
 
-%% Title, authors and addresses
+%=================================================================
+% Add packages and commands here.
+The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz
 
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
+%=================================================================
+%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
+%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
 
-\title{A sensor grid approach for large scale acoustic monitoring}
+%=================================================================
+% Full title of the paper (Capitalized)
+\Title{An efficient audio coding scheme  for quantitative and qualitative large scale acoustic monitoring using the sensor grid approach}
 
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
+% If this is an expanded version of a conference paper, please cite it here: enter the full citation of your conference paper, and add $^\dagger$ in the end of the title of this article.
+%\conference{Title}
 
-\author{F\'elix Gontier, Mathieu Lagrange, Pierre Aumond, Arnaud Can, Catherine Lavandier}
+% Authors, for the paper (add full first names)
+\Author{F\'elix Gontier $^{1}$, Mathieu Lagrange $^{1}$, Pierre Aumond $^{2}$, Arnaud Can $^{2}$ and Catherine Lavandier $^{3}$}
 
-\address{felix.gontier@reseau.eseo.fr}
+% Authors, for metadata in PDF
+\AuthorNames{F\'elix Gontier, Mathieu Lagrange, Pierre Aumond, Arnaud Can and Catherine Lavandier}
 
-\begin{abstract}
-%% Text of abstract
+% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+\address{%
+$^{1}$ \quad LS2N\\
+$^{2}$ \quad IFSTTAR\\
+$^{3}$ \quad Universit\'e de Cergy-Pontoise}
 
-The spreading of urban areas and the growth of human population worldwide raised societal and environmental concerns.
-To better address those, the monitoring of the acoustic environment in urban but also rural or wilderness areas is among other monitoring efforts an important matter.
+% Contact information of the corresponding author
+\corres{Correspondence: mathieu.lagrange@cnrs.fr}
+
+% Simple summary
+%\simplesumm{}
+
+% Abstract (Do not use inserted blank lines, i.e. \\)
+\abstract{The spreading of urban areas and the growth of human population worldwide raised societal and environmental concerns.
+To better address those, the monitoring of the acoustic environment in urban but also rural or wilderness areas is an important matter.
 Fostering on the recent development of low cost hardware acoustic sensors, we propose in this paper to consider a sensor grid approach to tackle this issue.
-
 In this kind of approach, the crucial question is the nature of the data that is transmitted from the sensors to the processing and archival servers.
@@
 The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc\footnote{\url{htttp://wp.nyu.edu/sonyc}} \cite{mydlarz2017implementation} and cense\footnote{\url{htttp://cense.ifsttar.fr}} \cite{picault2017} projects.
-
 To do so, considering the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} has several advantages.
@@
 
-In our application setting, the requirements are the following.
-First,  the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, \textit{i.e.} the approach shall be scalable.
+In such approach,  the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, \textit{i.e.} the approach shall be scalable.
 Second, the nodes shall be energy efficient, ideally autonomous, in order to ease the deployment of the sensors grid to the desired topology.
 Third, the encoding scheme used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to ensure the privacy of the citizen.
-Though, the data stored shall remain as rich as possible while maintaining a low bitrate for efficient transmission and storage.
+At the same time, the data stored shall remain as rich as possible while maintaining a low bitrate for efficient transmission and storage.
 
-The data of interest is first acoustic indicators (LAeq, ...) and second the presence of sound sources of interest (bird calls, sirens, ...).
+In the case of acoustic monitoring, the data of interest can be quantitative such as standard acoustic indicators (LAeq, ...) or qualitative such as the presence of sound sources of interest (bird calls, sirens, ...).
 The latter allows us to better assess the human perception of the urban sound environment in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}.
@@
 
-Online detection is efficient in terms of data storage as only the detection events are transmitted and is thus currently considered in several approaches \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
-Though, it requires the availability of computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware do not allow them to be autonomous using power sources like decent size solar panels.
-Furthermore, the detection is done once and cannot be recomputed during posterior analyses.
+Performing the detection online is in case B of Figure \ref{fig:codingScheme} is efficient in terms of data storage as only the detected events are transmitted.
+This approach is thus currently considered in several approaches in the literature \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
+Though, it requires the availability of decent computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware do not allow them to be autonomous using power sources like decent size solar panels.
+Furthermore, the detection is done once and cannot be recomputed during offline posterior analyses.
 
-The alternative scheme has several benefits.
-First, the sensor task is much simpler and can thus be implemented on low energy consumption processors, potentially being autonomous in terms of energy.
-This will ease the deployment of the network.
-Second, it allows researchers to gather large amount of data that can be post processed and studied further offline.
-Data can be re analyzed following newer classification schemes or using new indicators.
+Performing the detection offline has several benefits.
+First, the sensor task is much simpler and can thus be implemented on low energy consumption processors, potentially being autonomous in terms of energy, which greatly ease the deployment of the network.
+Second, it allows researchers to gather large amount of data that can be post-processed and studied further offline.
+Data can be re-analyzed following newer classification schemes or using new indicators.
 
-Transmitting the raw audio through the network has several disadvantages, in terms of required bandwidth, storage capabilities and privacy.
+Though transmitting the raw audio  through the network (case A of Figure \ref{fig:codingScheme}) has several disadvantages, in terms of required bandwidth, storage capabilities and privacy.
 Thus, for transmission from the sensors to the storage unit, the data shall be encoded in a more efficient way than lossy audio encoding standards \cite{pan1995tutorial}.
@@
 
-We thus propose in this paper an audio coding scheme specifically tailored for use in a sensor grid which has the following features.
+We thus propose in this paper an audio coding scheme specifically tailored for use in a sensor grid (case C of Figure \ref{fig:codingScheme}) which has the following features.
 It is of low bitrate but still allows the computation of most of the standard acoustics indicators with controllable precision.
@@
 
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{figures/censeCoder}
-\vspace{-0.15in}
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.5\textwidth]{figures/censeCoder}
 \caption{Alternative implementations of the sensor grid approach for the monitoring of the acoustic environment.
 In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation.
-Thickness of arrows roughly indicate bandwidth and thickness of boxes roughly indicates the level of computation or storage required.}
+Thickness of arrows indicates bandwidth and thickness of boxes indicates the level of computation or storage required.}
 \label{fig:codingScheme}

### 2017-08-30 paper/article.tex
up to validation

@@
 
-The present work is constrained to allow both acoustic monitoring and sound event recognition in urban sound environment.
+The main contribution of this paper is to present an acoustic data encoding scheme that allow both acoustic monitoring and sound event recognition in urban sound environment.
 Here we briefly review state-of-the-art methods in both subjects in order to better motivate our design choices.
@@
 Studies have been conducted to select relevant subsets of descriptors in sound environment characterization \cite{can2015, brocolini2013, nilsson2007}.
-The mentionned $L_{eq}$ features are measured at periods of 0.125~ms or 1~s, respectively fast and slow as a convention.
+The mentionned $L_{eq}$ features are measured at periods of 0.125~ms or 1~s, respectively termed as "fast" and "slow" as a convention.
 
-Most measured or derived indicators describe the global urban soundscape and lack information on its composition.
-Sound sources recognition enables a more efficient understanding of soundscape properties.
-For instance, a bird song and traffic noise with the same energy can be perceived very differently.
+Most measured or derived indicators describe the global urban acoustic environment and lack information on its composition.
+Sound sources recognition enables a more comprehensive understanding of the properties of the acoustic environment.
+For instance, a bird song and traffic noise with the same energy are perceived very differently.
 The analysis of sources within a sound environment is generally linked with spectral content \cite{ishiyama2000} and high temporal measurement resolutions.
-Other indicators can correlate with specific sound environment content \cite{aumond2017} but do not achieve the same performances as a source detection scheme in characterizing soundscapes.
-
-A solution is the calculation of spectral energetic indicators such as the 31 third-octave bands within the human audition range 20~Hz - 20~kHz.\\ Slow or fast third-octave bands measurement appears suitable for this work's purpose: in addition to being a relevant descriptor \cite{torija2013} for urban sound environment assessment, it allows for the computation of most cited indicators while representing reasonably small, fixed amounts of data to be transmitted.
-It additionnaly contains spectral information that can be used for source recognition tasks.
-However, as a tradeoff other representations such as Mel or Bark spectrograms, as well as psychoacoustical indicators cannot be precisely estimated.
+Other indicators can correlate with specific sound environment content \cite{aumond2017} but do not achieve the level of performances of a good source detection scheme in characterizing acoustic environments.
 
@@
 
-As discussed in the previous section, the recognition of sources of interest is of importance to fully model the studied soundscapes.
-As far as the encoding scheme is concerned, it is thus primordial that the encoded data allows us to compute the above cited indicators but also to detect the different sound sources with state of the art methods.
+As discussed in the previous section, the recognition of sources of interest is of importance to fully model the studied acoustic environments.
+As far as the encoding scheme is concerned, it is thus important that the encoded data allows us to compute the above cited indicators but also to detect the different sound sources with state of the art methods.
 
@@
 For instance, \cite{cai2006} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domain features.
-Another promising solution is feature engineering via unsupervised learning, which \cite{salamon2015-2} implements with a k-means clustering technique.
+Another promising solution is feature engineering via unsupervised learning, which \cite{salamon2015-2} implements with a clustering technique.
 Alternative data representations such as the scattering transform \cite{bauge2013} show good results in environmental sound classification tasks \cite{salamon2015}.\\
@@
 
-The technical constraints of size inherent to the studied setup as well as privacy concerns make it impossible to transmit raw audio recordings.
+We thus need to provide data that allows both the computation of previously described indicators and the recognition of sound events.
+To do so, we propose to consider the calculation of spectral energetic indicators such as the 31 third-octave bands within the human audition range 20~Hz - 20~kHz.\\ Slow or fast third-octave bands measurement appears suitable for this work's purpose: in addition to being a relevant descriptor \cite{torija2013} for urban sound environment assessment, it allows for the computation of most cited indicators while representing reasonably small, fixed amounts of data to be transmitted.
+It additionnaly contains spectral information that can be used for source recognition tasks as it is close to the Mel spectral representation, being just another filterbank transform with logarithmic frequency scaling.\\ %However, as a tradeoff other representations such as Mel or Bark spectrograms, as well as psychoacoustical indicators cannot be precisely estimated.
+
+%The technical constraints of size inherent to the studied setup as well as privacy concerns make it impossible to transmit raw audio recordings.
 Following the considerations briefly exposed in the previous section, we conclude that third-octave bands are a reasonable choice.
-As mentioned, they provide advantages in both acoustic monitoring quality and reduced data volume per measurement period.
+
+%As mentioned, they provide advantages in both acoustic monitoring quality and reduced data volume per measurement period.
 The resulting representation is also close to that of Mel spectrograms, being just another filterbank transform with logarithmic frequency scaling.\\
@@
 The weights matrix design procedure complies with both ANSI S1.1-1986 \cite{citeulike:9580295} and IEC 61260-1:2014 \cite{iec-norm} standards.
-It also respects the partition of unity principle over all frequency bins in the relevant range.
+It also meet the partition of unity principle over all frequency bins in the relevant range.
 Resulting filters for different parameter $l$ values are compared with Couvreur's implementation \cite{couvreur} of the time-domain filtering, as shown in Figure~\ref{fig:freq_filt}.
-The major difference is that gains at cutoff frequencies are fixed at the optimal -3dB by design.\\
+The major difference is that gains at cutoff frequencies are fixed at the optimal -3dB value by design.\\
 
@@
 	\centering
-		\includegraphics[width=0.5\textwidth]{figures/tob_imp.eps}
+		\includegraphics[width=0.8\textwidth]{figures/tob_imp.eps}
 	\caption{Comparison of Couvreur's and Antoni's implementations of third-octave filters. Frequency-weighting allows for arbitrary transfer functions and thus more accurate gains as standards impose.}
@@
 \end{figure}
+
+\ml{Pourquoi parler ici des parametrages alors qu'ils vont bouger dans les expes ? on ne parle que du fast sans fenetrage ici}
 
@@
 
+\ml{pas sur que cela soit utile de parler des mel ici.}
+
 Alternatively, we also implement the Mel filterbank for comparison purposes, as the Mel filterbank is the root representation of many state of the art classification algorithms.
@@
 
-As the Mel representation is not bounded by constraints such as conservation of energy, specific framing parameters or fixed resolution, it also offers a more flexible tool to study intelligibility alteration and coder performance, both of which we take interest in.
+As the Mel representation is not bounded by constraints for conservation of energy, or by specific framing parameters or fixed resolution, it also offers a more flexible tool to study intelligibility alteration and coder performance, both of which we take interest in.
 
@@
 By defining symbols as the possible values taken by the data, a discrete probability density function (PDF) can be expressed and estimated.
-The Shannon entropy then specifies the minimum average obtainable output data rate for this given distribution, or average information content.
-The Huffman algorithm is an entropy coding scheme, as it uses the PDF to assign an code to each symbol so that the average output rate is the closest to the entropy.
+The Shannon entropy then specifies the minimum average achievable output data rate for this given distribution, or average information content.
+The Huffman algorithm is an entropy coding scheme, as it uses the PDF to assign a code to each symbol so that the average output rate is the closest to the entropy.
 The resulting mapping function is called a Huffman dictionary.
@@
 %\fg{Schéma}
-Considering an estimated PDF for our data as shown in Figure~\ref{fig:pdf}a, immediately applying a linear quantization clearly results in most of the information being lost.
+Considering an estimated PDF for our data as shown in Figure~\ref{fig:pdf}.a, immediately applying a linear quantization clearly results in most of the information being lost.
 We therefore spread the PDF by taking the logarithm of the representation.
-A linear quantization is then applied with $2^{q-1}-1$ output values to obtain Figure~\ref{fig:pdf}b.
+A linear quantization is then applied with $2^{q-1}-1$ output values to obtain Figure~\ref{fig:pdf}.b.
 Finally, we use a $\Delta$-encoding algorithm along the time dimension to reduce redundancies.
-This also effectively concentrates higher probabilities on symbols around zero (Figure~\ref{fig:pdf}c).
-This yields a higher amount of symbols at $2^q-1$ but a nevertheless smaller entropy.
+This also effectively concentrates higher probabilities on symbols around zero (Figure~\ref{fig:pdf}.c).
+This yields a higher amount of symbols at $2^q-1$ but nevertheless a smaller entropy.
 
 In the example shown here, the former is $H_{log} = 6.24~sh$ and the latter $H_{\Delta} = 3.54~sh$.
-Huffman encoding is then computed with either a frame-specific symbol-code dictionary or a constant one generated from an entire dataset.
+Huffman encoding is then computed with either a frame-specific symbol-code dictionary or a fixed dictionary generated using a learning dataset.
 A comparison of both methods is shown in Figure~\ref{fig:dict_comp}.
-For most short texture frame duration, we found the local Huffman algorithm to be much faster.
-In fact, encoding complexity is function of the amount of dictionary elements.
+For most short texture frame durations, the local Huffman algorithm is found to be much faster.
+In fact, encoding complexity is a function of the amount of dictionary elements.
 If it is specific to a given data packet, then it does not need to contain every possible value.
@@
 
+\ml{ce n'est pas clair ici si on parle de complexite de calcul, taille memoire pour le calcul, ou bitrate resultant.
+Je me focaliserai sur le bitrate en etant bien explicite.
+Reprends la caption de la figure qui elle est claire.}
+
 \begin{figure}[htbp]
 	\centering
-		\includegraphics[width=0.5\textwidth]{figures/pdf.eps}
+		\includegraphics[width=0.8\textwidth]{figures/pdf.eps}
 	\caption{Example of estimated probability density functions of the data throughout the encoding step.
@@
 	\centering
-		\includegraphics[width=0.5\textwidth]{figures/dict_comp.eps}
+		\includegraphics[width=0.8\textwidth]{figures/dict_comp.eps}
 	\caption{Performance comparison of locally and globally generated Huffman dictionaries.
@@
 	\centering
-		\includegraphics[width=1\textwidth]{figures/scheme.pdf}
+		\includegraphics[width=.9\textwidth]{figures/scheme.pdf}
 	\caption{Overview of the coder process.}
@@
 
-We now compare the efficiency of third-octave bands at characterizing urban soundscapes to that of Mel spectrograms.
+We now compare the efficiency of third-octave bands at characterizing urban acoustic environments to that of Mel spectrograms.
 Following the previous discussions, the classification task is run on corresponding cepstra with a fixed 8 frames per second and 31 bands.

### 2017-08-30 paper/article.tex
up to results

@@
 
-A set of metrics is computed to assess the efficiency of the proposed coder scheme and to determine the impact of the degrees of freedom of the proposed algorithm.
+A set of metrics is computed to assess the efficiency of the proposed coder scheme and to determine the impact of the degrees of freedom given by the parameters of the proposed algorithm.
 Those parameters are as follow: 1) the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, and 2) the number of coefficients between 10 and 40 (only for Mel bands).
-We also study the effect of time averaging analysis frames: to force a fixed amount of frames per second lesser than the average speech rate in phonemes per second is a possible way to alter intelligibility at the cost of temporal information resolution.
+We also study the effect of time averaging analysis frames on intelligibility.
+To enforce a fixed amount of frames per second that is lower than the average speech rate in terms of phonemes per second is a possible way to alter intelligibility at the cost of temporal information resolution.
 
@@
 We study both "fast" computation with 125~ms windows and "slow" 1~s analysis to assess the impact of time integration.
-Third-octave bands are computed using the proposed method as well as the \textit{ita\_toolbox} in the same conditions, then averaged over time and compared to the toolbox's measurements on longer extracts.
+Third-octave bands are computed using the proposed method as well as the \textit{ita\_toolbox} in the same experimental conditions, then averaged over time and compared to the toolbox's measurements on longer extracts.
 In all experiments the sound dataset is the same and is composed of 2~s extracts.
@@
 For this reason we evaluate the effect of the use of windowing functions on each band measurement error in order to mitigate this loss of precision.
-To provide relevant statistics, these quantities are estimated for about 4500 extracts obtained from the UrbanSound8k dataset \cite{salamon2014} and 4500 \textit{iid.} noise sequences.
+To provide relevant statistics, these quantities are estimated with data from the 4500 audio recordings of the UrbanSound8k dataset \cite{salamon2014} described in the next section and 4500 \textit{iid.} noise sequences.
 
@@
 
-Intelligibility in decoded and reconstructed audio is also an important concern of this study.
-It is indeed important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data is transmitted over the network and potentially stored, the level of intelligibility of the decoded stream should be as low as possible.
+It is important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data is transmitted over the network and potentially stored, the level of intelligibility of potenital speech utterances present in the decoded stream should be as low as possible.
+Thus, intelligibility in decoded and reconstructed audio is also an important concern of this study.
 
-The use of an audio recording as an evidence is considered by the forensic phonetics \cite{baldwin1990forensic} domain.
-That being said, the readers shall be aware that even recorded with a good quality, such recording remains a weak biometrical indicator \cite{boe2000forensic}.
+The use of an audio recording as an evidence is considered by the forensic phonetics \cite{baldwin1990forensic} field.
+The readers shall be aware that even recorded with a good quality, such recording remains a weak biometrical indicator \cite{boe2000forensic}.
 Still, even if the identity of the speaker cannot be asserted, one can attempt to transcribe the spoken utterances.
@@
 If some speech is detected, the data is not transmitted.
-This approach is however prone to failure of the detector and will lead to unavailability of data during speech time periods which might compromise the computation of some indicators.
+This approach is however prone to failure of the detector and will lead to unavailability of data during speech time periods which might compromise the relevance of some indicators.
 
-Second, as the speech is mostly concentrated at a given frequency region, a band pass filter from 1 kHz to $~$4-5 kHz could be considered in order to remove the formant information \cite{kent1992acoustic}.
+Second, as the speech is mostly concentrated at a given frequency region, a band-pass filter from 1 kHz to $~$4-5 kHz could be considered in order to remove the formant information \cite{kent1992acoustic}.
 However, as some frequency bands are no longer available, the computation of standard acoustic indicators is no longer possible.
@@
 A third approach is to wisely choose the frame rate.
-Since a phoneme is about 100ms to 200ms long \cite{kuwabara1996acoustic} \cite{rosen1992temporal} a frame rate lower than 4 Hz should therefore dramatically reduce intelligibility.
+Since a phoneme is about 100ms to 200ms long \cite{kuwabara1996acoustic} \cite{rosen1992temporal}, a frame rate lower than 4 Hz should therefore dramatically reduce intelligibility.
 
@@
 To do so, a linearly-scaled spectrogram from the band-focused representations is estimated.
-This estimation can be achieved by multiplying by the scaled transpose of the forward transformation matrix.
+This estimation can be achieved by multiplying the spectral representation by the scaled transpose of the forward transformation matrix.
 A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
-Signal phase is then approximated by either white noise spectrogram scaling or the Griffin \& Lim algorithm \cite{griffin1984}.
+Signal phase is then approximated by either white noise spectrogram scaling or the Griffin \& Lim algorithm \cite{griffin1984} in hte case of overlapping frames.
 The signal is then retrieved using concatenation or overlap-add depending on the overlap setting.

### 2017-08-30 paper/article.tex
ml proof read done

@@
 Because we use the most common parameters, namely 23.2~ms window with 50\% overlap, the closest achievable rate considering simple averaging is 7.74 frames per second.
-Third-octave representation on 31 bands yielded an overall higher size than their Mel equivalent, here estimated for 30 bands.
+Third-octave representation on 31 bands yields an overall higher size than their Mel equivalent, here estimated for 30 bands.
 It however compares with the 40-Mel bands representation which is the most used features in literature.
@@
 	\centering
-		\includegraphics[width=0.5\textwidth]{figures/bitrate_qall.eps}
+		\includegraphics[width=0.8\textwidth]{figures/bitrate_qall.eps}
 	\caption{Coder output bitrate as a function of quantization for third-octave and Mel bands with 8 frames per second.}
@@
 A second set of parameters influences directly the time-frequency resolution of the analysis.
-By choosing a frame rate and number of bands, one can effectively control the size of periodically transmitted data.
+By choosing a frame rate and number of bands, one can effectively control the size of the periodically transmitted data.
 We evaluate the bitrate for 10 to 40 Mel bands and a frame rate from 2 to 10 per second, with fixed $q = 8$.
@@
 
-This experiment aims at an initial assessment of potential tradeoffs between bitrate and preservation of valuable information.
-As such, it will be further discussed in the \textit{Event recognition} subsection.\\
+This experiment aims at an initial assessment of potential tradeoffs between bitrate and preservation of valuable information which will be further discussed in Section \ref{sec:eventRec}.\\
 
-The measurement error is computed for third-octave bands.
+The measurement error is now computed for third-octave bands.
 Results are displayed in Figure~\ref{fig:errormn} for white noise extracts and in Figure~\ref{fig:errormu} for environmental sounds.
-Only full-octave bands are shown for visibility.
-When computing the slow analysis, we found that applying overlap attenuated the error.
-This was not observed for fast analysis where the error was similar or higher with the use of overlapping frames.
+Only full-octave bands are shown for the sake of visibility.
+When computing the slow analysis, we find that applying overlap attenuated the error.
+This is not observed for fast analysis where the error is similar or higher with the use of overlapping frames.
 
@@
 Its mean over the testing samples is close to zero and its standard deviation increases in low frequencies, confirming the above-mentioned considerations.
-This effectiveness does not translate well to environmental sounds analysis.
-A factor of this phenomenon is the sound level disparities absent in the first case but omnipresent in the second.
-In fact, spectral leakage induces a correlation between close frequency components.
-In lower frequencies, large differences between adjacent frequency bins can cause important errors on third-octave bands computations.
+This effectiveness does not translate well to environmental sounds analysis, most likely mainly due to the sound level disparities absent in the former case but omnipresent in the latter.
+Spectral leakage induces a correlation between close frequency components.
+In lower frequencies, large differences between adjacent frequency bins can thus cause important errors on third-octave bands computations.
 This issue is however not specific to Fourier transform based schemes as it is also encountered with a time domain filtering approach.
@@
 To mitigate this phenomenon, the choice of the window function shall be studied further.
-For a fast analysis with no overlap, the rectangular window seems a reasonable choice at first with its energy conservation qualities.
+For a fast analysis with no overlap, the rectangular window seems a reasonable choice at first because of its energy conservation qualities.
 While it yields the lowest error in high frequency bands, its high spectral leakage effect makes it unprecise for lower frequency regions.
@@
 The use of overlap then results in better estimates at the cost of an increased data size.
-For slow measurements, the rectangular window impact is less harmful to band analysis due to an increased frequency resolution.
+For slow measurements, considering the rectangular window impact is less harmful to band analysis due to an increased frequency resolution.
 
-Comparing the error to that of third-octave bands estimated by a time-filtering algorithm results in important similarities being found.
+The comparison of the error achieved by the proposed scheme to that of third-octave bands estimated by a reference time-filtering algorithm is now considered.
+It results in important similarities.
 For fast measurements and a rectangular window (Figure~\ref{fig:errormu}a), a student t-test ($p<0.05$) shows that the errors are not significantly different between 125~Hz and 12~kHz bands.
@@
     \caption{Measurement error of third-octave bands over two-seconds white noise extracts, with rectangular window and no overlap.
-The analysis of short frames has an effect on energy estimation at low frequencies that is corrected as the frequency resolution increases.\label{fig:errormn}}
+The analysis of short frames has an effect on energy estimation at low frequencies that is of lower importance as the frequency resolution increases.\label{fig:errormn}}
 \end{figure}
@@
     \end{subfigure}
-    \caption{Measurement error of third-octave bands over two-seconds environmental sounds recordings (US8k database).
+    \caption{Measurement error of third-octave bands over two-seconds environmental sounds recordings (US8k dataset).
 For most settings the FFT-based method yields similar errors to the time-domain filtering reference.
@@
 In both cases, the mean and standard deviation seem to decrease by a factor of 2 as $q$ increases.
-To explain this phenomenon, let us model $x$ as a uniform distribution such as $x\sim \textit{U}\{0, \Delta_x\}$.
+To better understand this phenomenon, let us model $x$ as a uniform distribution such as $x\sim \textit{U}\{0, \Delta_x\}$.
 While this is not exact it matches our objective when using a logarithm to flatten given PDFs.
@@
 
-\subsection{Event recognition}
+\subsection{Event recognition} \label{sec:eventRec}
 
@@
 The performance of the decision tree classifier is a good example of this behavior, with best performances for 10 Mel bands only and a 4\% lower accuracy for 40.
-The latter result may be due to the low ability of the decision tree classifier to handle hugh dimensional features.
 Even if the difference is small, all other models perform best with 30 or 40 Mel bands as a representation.
-Time decimation cn also be considered, as the original representation can be averaged and consistently yield a good classification accuracy.
+Time decimation can also be considered, as the original representation can be averaged and consistently yield a good classification accuracy.
 The loss of information can be considered negligible for FPS values as low as 20 or 10 depending on the method.
@@
 \caption{Classification accuracy in percentage for different classifiers: SVMs (a), Random Forests (b), Decision Trees (c), and Nearest Neigbors (d) with respect to varying representation resolutions.
-Numbers in red indicate best performance and numbers in bold indicate statistical equivalent results compared to the best performing setting.}
+Numbers in red indicate best performance and numbers in bold indicate that no statisticaly significant difference is found when comparing to the best performing setting ($p<.05$).}
 \label{T2}
@@
 
+\ml{on avait dit que l'on enlevait les metriques, non ?}
+
 Subjective intelligibility metrics are then computed for the encoder's settings under evaluation and compared to the results of the perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/}}.
@@
 
-Perceptual test results confirm the qualitative evaluation of speech properties discussed in Section \ref{sec:inintelligibility}.
+The results of the perceptual test confirm the qualitative evaluation of speech properties discussed in Section \ref{sec:inintelligibility}.
 Phonemes separation is indeed mandatory in order to ensure good intelligibility of speech.
@@
 It has been designed to transfer data from acoustic sensors to processing and storage servers in an efficient and effective manner.
-It relies on a lossy audio coding scheme designed to the ensure privacy of citizens while retaining the needed amount of acoustic precision to compute standard acoustic descriptors and to allow the recognition of events of interest at a state of the art level of recognition accuracy.
+It relies on a lossy audio coding scheme designed to the guaranty the privacy of the citizens while retaining the needed amount of acoustic precision to compute standard acoustic descriptors and to allow the recognition of events of interest at a state of the art level of recognition accuracy.
 
@@
 	- do not impact the quality of the acoustics indicators.
-	- permits to perform the sound recognition with the same quality than directly from the spectrogram.
+	- enable the sound recognition with the same quality than directly from the spectrogram.
 	\item efficiency: for fast and slow modes, the bitrate is respectively about 1.4~kbps and 0.4~kbps for the high precision mode
@@
 
-The encoding scheme is designed to be simple to use and to lead to an efficient data format for storage and sharing acroos the research community.
+The encoding scheme is designed to be easy to implement and to lead to an efficient data format for storage and sharing across the research community.
 To encourage its use for other research projects, an open source Matlab implementation of the coder is available.
@@
 
-Future work will focus on the use of such a sensor grid approach as part of the cense project where its effectiveness will be assessed in filed conditions.
+Future work will focus on the use of such a sensor grid approach as part of the cense project where its effectiveness will be assessed in field conditions.
 The usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency should also be studied.

### 2017-08-31 paper/article.tex
FG final corrections

@@
 \newcommand{\cl}[1]{\textcolor{red}{ Catherine: #1}}
-
 \firstpage{1}
@@
 
-\ml{Pourquoi parler ici des parametrages alors qu'ils vont bouger dans les expes ? on ne parle que du fast sans fenetrage ici}
-
 The first step is to represent the signal in the frequency domain using a short-term Fourier transform (STFT).
-The continuously sampled audio is segmented into 125~ms frames to provide "fast" acoustic measurements.
+The continuously sampled audio is segmented into either 125~ms or 1~s frames to provide "fast" or "slow" acoustic measurements.
 The data is zero-padded to the next power of two to improve computational efficiency.
-No overlap is used.
-A rectangular windowing function is applied to ensure energy conservation in a given analysis frame.
+The other parameters such as windowing functions and frame overlap are dependant on the specific constraints, and discussed in section \label{sec:protocol}.
 The phase is discarded as it is not meaningful for third-octave analysis.
@@
 center frequencies $f_i$ ranging from $20~Hz$ to $20~kHz$ with $f_0 = 1~kHz$.
-The representation is thus composed of 31 values sampled every 125~ms.
-
-\ml{pas sur que cela soit utile de parler des mel ici.}
-
-Alternatively, we also implement the Mel filterbank for comparison purposes, as the Mel filterbank is the root representation of many state of the art classification algorithms.
-Mel spectrograms can thus be used as a baseline method to evaluate the relative performance of third-octave bands in sound event recognition.
-
-As the Mel representation is not bounded by constraints for conservation of energy, or by specific framing parameters or fixed resolution, it also offers a more flexible tool to study intelligibility alteration and coder performance, both of which we take interest in.
-
-Mel spectrograms are computed with the \textit{rastamat} library \cite{ellis2005}.
-STFT analysis frames are obtained by applying a Hann window on 23.2~ms of signal with 50\% (11.6~ms) overlap to allow for efficient phase recovery in further tests.
+The representation is thus composed of 31 values.
 
@@
 For most short texture frame durations, the local Huffman algorithm is found to be much faster.
-In fact, encoding complexity is a function of the amount of dictionary elements.
-If it is specific to a given data packet, then it does not need to contain every possible value.
-This gain seems to outweight the additional complexity induced by the need to transmit the result of the tree generation algorithm.
-Alternatively, short texture frames or single analysis windows can be encoded using one general dictionary to improve bitrate.
-Choosing between those two approaches is the result of a balance between requirements in terms of size and complexity.\\
-
-\ml{ce n'est pas clair ici si on parle de complexite de calcul, taille memoire pour le calcul, ou bitrate resultant.
-Je me focaliserai sur le bitrate en etant bien explicite.
-Reprends la caption de la figure qui elle est claire.}
+In fact, the encoding computational complexity is a function of the number of dictionary elements.
+A frame-specific dictionnary only contains the symbols found in a given data packet, while a fixed dictionnary must contain every possible symbol as it does not depend on the present data.
+The output bitrate is found to be close for both methods, as sending an optimal local dictionnary balances the suboptimality of globally generated symbol-code pairs.\\
 
@@
 A set of metrics is computed to assess the efficiency of the proposed coder scheme and to determine the impact of the degrees of freedom given by the parameters of the proposed algorithm.
-Those parameters are as follow: 1) the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, and 2) the number of coefficients between 10 and 40 (only for Mel bands).
-We also study the effect of time averaging analysis frames on intelligibility.
-To enforce a fixed amount of frames per second that is lower than the average speech rate in terms of phonemes per second is a possible way to alter intelligibility at the cost of temporal information resolution.
+Those parameters are as follow: 1) the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, 2) the number of considered bands, and 3) the STFT parameters including frame duration, overlap and windowing function usage.
 
@@
 
+Mel spectrograms are computed with the \textit{rastamat} library \cite{ellis2005} to assess the relative performance of third-octave bands.
+STFT analysis frames are obtained by applying a Hann window on 23.2~ms of signal with 50\% (11.6~ms) overlap to allow for efficient phase recovery in further tests.
+
 We evaluate the global loss of information induced by the coder by implementing the four classification models proposed in \cite{salamon2014}: a support vector machine with a radial basis function kernel, a random forest classifier with 500 trees, a decision tree and a k-nearest neighbors classifier with $k = 5$.
 Values for the SVM parameter $C$ and RBF kernel variance $\sigma^2$ are found with a grid search.
-We optionally apply a discrete cosine transform to the critical band signal representation to obtain cepstra (known as Mel Frequency Cepstrum Coefficients or MFCC in the first case) of which we conserve the 25 first coefficients, and summarize along time with the mean, variance, skewness, kurtosis, minimum, maximum, median, derivative mean and variance, second order derivative mean and variance.
+We optionally apply a discrete cosine transform to the critical band signal representation to obtain cepstra, known as Mel Frequency Cepstrum Coefficients or MFCC in the case of Mel spectrograms.
+The 25 first coefficients are conserved, and summarized along time with the mean, variance, skewness, kurtosis, minimum, maximum, median, derivative mean and variance, second order derivative mean and variance operators.
 The feature vector is thus comprised of 275 values to reproduce available results and compare with the data produced by the proposed coding scheme.
@@
 Figure~\ref{fig:bitrate_q} shows estimations of the output bitrate for different values of $q$.
-To match third-octave bands computation principle where a 125~ms analysis is mandatory, we averaged Mel frames over time.
+To match third-octave bands computation principle where a 125~ms analysis is mandatory, Mel frames are averaged over time.
 Because we use the most common parameters, namely 23.2~ms window with 50\% overlap, the closest achievable rate considering simple averaging is 7.74 frames per second.

### 2017-10-02 paper/article.tex
Paper update

@@
 To do so, considering the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} has several advantages.
-The sensor grid approach put the focus on a) a distributed system of data acquisition with a large set of sensors, b) the production and storage of a large dataset, and c) its availability for intensive and open data analysis computation.
+The sensor grid approach puts the focus on a) a distributed system of data acquisition with a large set of sensors, b) the production and storage of a large dataset, and c) its availability for intensive and open data analysis computation.
 
 In such approach,  the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, \textit{i.e.} the approach shall be scalable.
-Second, the nodes shall be energy efficient, ideally autonomous, in order to ease the deployment of the sensors grid to the desired topology.
-Third, the encoding scheme used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to ensure the privacy of the citizen.
+Second, the nodes shall be energy efficient, ideally autonomous, in order to ease the deployment of the sensor grid to the desired topology.
+Third, the encoding scheme used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to ensure the privacy of the citizens.
 At the same time, the data stored shall remain as rich as possible while maintaining a low bitrate for efficient transmission and storage.
@@
 The latter allows us to better assess the human perception of the urban sound environment in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}.
-This detection step can respectively be operated online (on the sensors) or offline (on the data servers) leading to different grid designs, see Figure \ref{fig:codingScheme}.
+This detection step can respectively be operated online (on the sensors) or offline (on the data servers) leading to different grid designs (Figure \ref{fig:codingScheme}).
 
-Performing the detection online is in case B of Figure \ref{fig:codingScheme} is efficient in terms of data storage as only the detected events are transmitted.
+Performing the detection online (case B of Figure \ref{fig:codingScheme}) is efficient in terms of data storage as only the detected events are transmitted.
 This approach is thus currently considered in several approaches in the literature \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
-Though, it requires the availability of decent computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware do not allow them to be autonomous using power sources like decent size solar panels.
+Though, it requires the availability of decent computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware does not allow them to be autonomous using power sources like decent size solar panels.
 Furthermore, the detection is done once and cannot be recomputed during offline posterior analyses.
@@
 To do so, we propose to consider the calculation of spectral energetic indicators such as the 31 third-octave bands within the human audition range 20~Hz - 20~kHz.\\ Slow or fast third-octave bands measurement appears suitable for this work's purpose: in addition to being a relevant descriptor \cite{torija2013} for urban sound environment assessment, it allows for the computation of most cited indicators while representing reasonably small, fixed amounts of data to be transmitted.
-It additionnaly contains spectral information that can be used for source recognition tasks as it is close to the Mel spectral representation, being just another filterbank transform with logarithmic frequency scaling.\\ %However, as a tradeoff other representations such as Mel or Bark spectrograms, as well as psychoacoustical indicators cannot be precisely estimated.
-
-%The technical constraints of size inherent to the studied setup as well as privacy concerns make it impossible to transmit raw audio recordings.
-Following the considerations briefly exposed in the previous section, we conclude that third-octave bands are a reasonable choice.
-
-%As mentioned, they provide advantages in both acoustic monitoring quality and reduced data volume per measurement period.
-The resulting representation is also close to that of Mel spectrograms, being just another filterbank transform with logarithmic frequency scaling.\\
+It additionnaly contains spectral information that can be used for source recognition tasks as it is close to the Mel spectral representation, being just another filterbank transform with logarithmic frequency scaling.
 
@@
 The data is zero-padded to the next power of two to improve computational efficiency.
-The other parameters such as windowing functions and frame overlap are dependant on the specific constraints, and discussed in section \label{sec:protocol}.
+The other parameters such as windowing functions and frame overlap are dependant on the specific constraints, and discussed in section \ref{sec:protocol}.
 The phase is discarded as it is not meaningful for third-octave analysis.
@@
 
-A Huffman coding scheme \cite{huffman1952} is an efficient method to further reduce data rate.
+A Huffman coding scheme \cite{huffman1952} is an efficient method to further reduce data rate while keeping the underlying information.
 At this point of the processing chain, the data takes the form of a spectrogram with amplitude values represented on an arbitrary data type.
@@
 The efficiency of the coding step thus directly depends on the entropy of the transmitted data.
-It is defined as $H = -\sum\limits_i p_ilog_n(p_i)$, where $p_i$ is the probability of appearance of a given symbol and $n$ the numerical base in which the output code is represented.
+It is defined as $H = -\sum\limits_i p_ilog_n(p_i)$, where $p_i$ is the probability of appearance of a given symbol $i$ and $n$ the numerical base in which the output code is represented.
 A lower entropy can be obtained with two factors.
@@
 
-%The algorithm concepts are summarized in Figure~\ref{fig:huffalg}.
-%\fg{Schéma}
-Considering an estimated PDF for our data as shown in Figure~\ref{fig:pdf}.a, immediately applying a linear quantization clearly results in most of the information being lost.
-We therefore spread the PDF by taking the logarithm of the representation.
-A linear quantization is then applied with $2^{q-1}-1$ output values to obtain Figure~\ref{fig:pdf}.b.
-Finally, we use a $\Delta$-encoding algorithm along the time dimension to reduce redundancies.
-This also effectively concentrates higher probabilities on symbols around zero (Figure~\ref{fig:pdf}.c).
-This yields a higher amount of symbols at $2^q-1$ but nevertheless a smaller entropy.
+Considering an estimated PDF for our data as shown in Figure~\ref{fig:pdf} (top-left), immediately applying a linear quantization is clearly suboptimal, as the data mostly consists of very low values and a direct quantization results in most of the information being lost.
+We therefore flatten the PDF by taking the logarithm of the representation (top-right).
+This allows to better use the available range of symbols.
+A linear quantization is then applied with $2^{q-1}-1$ output values to obtain Figure~\ref{fig:pdf} (bottom-left).
+Finally, we use a $\Delta$-encoding algorithm along the time dimension to reduce redundancies between consecutive frames.
+This effectively concentrates higher probabilities on symbols around zero (Figure~\ref{fig:pdf} bottom-right), yielding a higher amount of symbols at $2^q-1$ but nevertheless a smaller entropy.
+In the example shown here, the entropy before $\Delta$-compression is $H_{log} = 6.24~sh$ which is reduced to $H_{\Delta} = 3.54~sh$.
 
-In the example shown here, the former is $H_{log} = 6.24~sh$ and the latter $H_{\Delta} = 3.54~sh$.
 Huffman encoding is then computed with either a frame-specific symbol-code dictionary or a fixed dictionary generated using a learning dataset.
@@
 	\caption{Example of estimated probability density functions of the data throughout the encoding step.
-Unchanged output of the representation step (left), concentrated towards very low values.
-PDF "flattening" effect induced by logarithm application (middle).
-Here values are mapped to the range $[0, 2^7-1]$ and rounded to perform quantization.
-Output of the $\Delta$ compression (right) -, with desirable probabilities as the input to a Huffman algorithm.}
+Unchanged output of the representation step (top-left), concentrated towards very low values.
+PDF "flattening" effect induced by logarithm application (top-right).
+Here values are mapped to the range $[0, 2^7-1] (q=8)$ and rounded to perform quantization (bottom-left).
+Output of the $\Delta$ compression (bottom-right), with desirable probabilities as the input to a Huffman algorithm.}
 	\label{fig:pdf}
@@
 It is used in all the following experiments with the exception of intelligibility computation for which a small dataset of high-quality voice recordings is preferred.
-Audio files are resampled at 44.1~kHz, normalized and reduced to a single channel.
+Audio files are resampled at 44.1~kHz, normalized and a single channel is considered.
 
@@
 To do so, a perceptual test is conducted.
-For the evaluation, a dataset of clean speech recordings made of 9 french sentences enunciated by 3 male and 3 female speakers, for a total of 216 audio excerpts.
-The recorded sentences are encoded using the proposed approach with analysis frame rates of respectively 50~Hz, 16~Hz, 8~Hz and 4~Hz.
+For the evaluation, a dataset of clean speech recordings made of 9 french sentences enunciated by 3 male and 3 female speakers.
+The recorded sentences are encoded using the proposed approach with 4 analysis frame rate parameters of respectively 50~Hz, 16~Hz, 8~Hz and 4~Hz.
+As a result, 216 audio excerpts with a duration of about 2 seconds are tested in total.
 
 For the perceptual test, each subject is presented with sentences and asked both to transcribe the utterances and rate the global intelligibility from 1 (not intelligible) to 5 (intelligible).
-Due to the low number of sentences, each sentence is tested twice for the same subject but under different encoding setting and speaker identity.
+Due to the low number of sentences, each sentence is tested twice for the same subject but under different encoding setting and speaker identity, resulting in each subject evaluating 18 extracts.
 12 subjects of age ranging from 17 to 60 which reported normal hearing participated to the listening test.
@@
 Its mean over the testing samples is close to zero and its standard deviation increases in low frequencies, confirming the above-mentioned considerations.
-This effectiveness does not translate well to environmental sounds analysis, most likely mainly due to the sound level disparities absent in the former case but omnipresent in the latter.
+This effectiveness does not translate well to environmental sound analysis, most likely mainly due to the sound level disparities absent in the former case but omnipresent in the latter.
 Spectral leakage induces a correlation between close frequency components.
@@
 
-\ml{on avait dit que l'on enlevait les metriques, non ?}
+The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
 
-Subjective intelligibility metrics are then computed for the encoder's settings under evaluation and compared to the results of the perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/}}.
-The results of the perceptual test is evaluated using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
-Figure~\ref{fig:subj_int} presents the results of the perceptual test for the same encoder's settings.
-
-The results of the perceptual test confirm the qualitative evaluation of speech properties discussed in Section \ref{sec:inintelligibility}.
+The results of the perceptual test visible in Figure~\ref{fig:subj_int} confirm the qualitative evaluation of speech properties discussed in Section \ref{sec:inintelligibility}.
 Phonemes separation is indeed mandatory in order to ensure good intelligibility of speech.
@@
 		\includegraphics[width=0.5\textwidth]{figures/subj_int.eps}
-	\caption{Average intellibility score (AIS) given by the subjects and the inteligibility ratio (IR) as a function of the frame rate.
+	\caption{Normalized Average intellibility score (AIS) given by the subjects and the inteligibility ratio (IR) as a function of the frame rate.
 Inintelligibility appears at around 10~Hz, corresponding to the average duration of a phoneme.}
@@
 \section{Conclusion}
-\pa{Je repasserais un coup sur la conclusion en fonction des changements apportés}
 

### 2017-10-09 paper/article.tex
Paper corrections

@@
 % Authors, for the paper (add full first names)
-\Author{F\'elix Gontier $^{1}$, Mathieu Lagrange $^{1}$, Pierre Aumond $^{2}$, Arnaud Can $^{2}$ and Catherine Lavandier $^{3}$}
+\Author{F\'elix Gontier $^{1}$, Mathieu Lagrange $^{1}$, Pierre Aumond $^{2,3}$, Arnaud Can $^{2}$ and Catherine Lavandier $^{3}$}
 
@@
 $^{1}$ \quad LS2N\\
-$^{2}$ \quad IFSTTAR\\
+$^{2}$ \quad IFSTTAR, AME, LAE\\
 $^{3}$ \quad Universit\'e de Cergy-Pontoise}
@@
 Performing the detection offline has several benefits.
-First, the sensor task is much simpler and can thus be implemented on low energy consumption processors, potentially being autonomous in terms of energy, which greatly ease the deployment of the network.
+First, the sensor task is much simpler and can thus be implemented on low energy consumption processors, potentially being autonomous in terms of energy, which greatly eases the deployment of the network.
 Second, it allows researchers to gather large amount of data that can be post-processed and studied further offline.
 Data can be re-analyzed following newer classification schemes or using new indicators.
-
-Though transmitting the raw audio  through the network (case A of Figure \ref{fig:codingScheme}) has several disadvantages, in terms of required bandwidth, storage capabilities and privacy.
+Though, transmitting the raw audio  through the network (case A of Figure \ref{fig:codingScheme}) has several disadvantages, in terms of required bandwidth, storage capabilities and privacy.
 Thus, for transmission from the sensors to the storage unit, the data shall be encoded in a more efficient way than lossy audio encoding standards \cite{pan1995tutorial}.
@@
 It is of low bitrate but still allows the computation of most of the standard acoustics indicators with controllable precision.
-As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data at production level rates.
+As far as acoustic event detection is concerned, we report equivalent performance of several state-of-the-art classification schemes from features computed using raw audio data and encoded data at production level rates.
 Finally, according to a perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
@@
 In order to promote reproducible research, the coder as well as the experiments needed to generate the figures is available to the community\footnote{\url{https://github.com/felixgontier/cense-coder}}.
-The remaining of the paper is organized as follows: Section \ref{sec:background} reviews the types of data that needs to be estimated using the transmitted data and Section \ref{sec:coder} describes the proposed encoding scheme.
+The remaining of the paper is organized as follows: Section \ref{sec:background} reviews the types of data that need to be estimated using the transmitted data and Section \ref{sec:coder} describes the proposed encoding scheme.
 The experimental protocol designed to validate the proposed approach is described in Section \ref{sec:protocol} and results are discussed in Section \ref{sec:results}.
@@
 
-The main contribution of this paper is to present an acoustic data encoding scheme that allow both acoustic monitoring and sound event recognition in urban sound environment.
+The main contribution of this paper is to present an acoustic data encoding scheme that allows both acoustic monitoring and sound event recognition in urban sound environment.
 Here we briefly review state-of-the-art methods in both subjects in order to better motivate our design choices.
@@
 
-The considered sensor network primarily aims at monitoring urban sound environment, that is, continuously assessing their content and impact on the population.
+The considered sensor network primarily aims at monitoring urban sound environments, that is, continuously assessing their content and impact on the population.
 In the literature, this is typically performed by measuring energetic acoustic indicators such as the equivalent sound pressure level $L_{eq}$ in dB SPL or its A-weighted equivalent $L_{Aeq}$ in dBA.
@@
 While parameters are empirical and vary in the literature, a reference implementation includes 23.2~ms analysis and a 40 Mel bands resolution.
-The resulting representations are generally more precise in time and frequency than in acoustic monitoring applications because it is a primordial factor for classification whereas acoustic indicators must be computed more accurately.
+The resulting representations are generally more precise in time and frequency than in acoustic monitoring applications because it is a primordial factor for classification whereas acoustic indicators must be computed more accurately.\fg{ref Jean-R\'emy?}
 
@@
 The weights matrix design procedure complies with both ANSI S1.1-1986 \cite{citeulike:9580295} and IEC 61260-1:2014 \cite{iec-norm} standards.
-It also meet the partition of unity principle over all frequency bins in the relevant range.
-Resulting filters for different parameter $l$ values are compared with Couvreur's implementation \cite{couvreur} of the time-domain filtering, as shown in Figure~\ref{fig:freq_filt}.
+It also meets the partition of unity principle over all frequency bins in the relevant range.
+Resulting filters for different parameter $l$ values are compared with Couvreur's implementation \cite{couvreur} with $2^{nd}$ order Butterworth time-domain filters, as shown in Figure~\ref{fig:freq_filt}.
 The major difference is that gains at cutoff frequencies are fixed at the optimal -3dB value by design.\\
@@
 Similarly, negative frequency components contain the same information as positive ones because the input signal is real.
-We then compute third-octave bands from the squared spectral magnitude by matrix multiplication with the frequency weights proposed in \cite{antoni2010} for $l = 2$\footnote{When implementing said method, we found that squaring the $\phi_l(p), l \geq 1$ intermediate function (p.
+We then compute third-octave bands from the squared spectral magnitude by matrix multiplication with the frequency weights proposed in \cite{antoni2010} for $l = 2$ \footnote{When implementing said method, we found that squaring the $\phi_l(p), l \geq 1$ intermediate function (p.
 887) was the correct approach to meet cutoff frequencies requirements, and we believe this was the author's original intention.}.
@@
 In fact, the encoding computational complexity is a function of the number of dictionary elements.
-A frame-specific dictionnary only contains the symbols found in a given data packet, while a fixed dictionnary must contain every possible symbol as it does not depend on the present data.
-The output bitrate is found to be close for both methods, as sending an optimal local dictionnary balances the suboptimality of globally generated symbol-code pairs.\\
+A frame-specific dictionary only contains the symbols found in a given data packet, while a fixed dictionary must contain every possible symbol as it does not depend on the present data.
+The output bitrate is found to be close for both methods, as sending an optimal local dictionary balances the suboptimality of globally generated symbol-code pairs.\\
 
@@
 
-Second, as the speech is mostly concentrated at a given frequency region, a band-pass filter from 1 kHz to $~$4-5 kHz could be considered in order to remove the formant information \cite{kent1992acoustic}.
-However, as some frequency bands are no longer available, the computation of standard acoustic indicators is no longer possible.
-
-A third approach is to wisely choose the frame rate.
+A second approach is to wisely choose the frame rate.
 Since a phoneme is about 100ms to 200ms long \cite{kuwabara1996acoustic} \cite{rosen1992temporal}, a frame rate lower than 4 Hz should therefore dramatically reduce intelligibility.
@@
 To do so, a perceptual test is conducted.
-For the evaluation, a dataset of clean speech recordings made of 9 french sentences enunciated by 3 male and 3 female speakers.
-The recorded sentences are encoded using the proposed approach with 4 analysis frame rate parameters of respectively 50~Hz, 16~Hz, 8~Hz and 4~Hz.
-As a result, 216 audio excerpts with a duration of about 2 seconds are tested in total.
+For the evaluation, a dataset of clean speech utterances recorded in studio conditions is used.
+The dataset is made of 9 french sentences enunciated by 3 male and 3 female speakers.
+The sentences have an mean duration of $2~s$ and are composed of 5 to 12 words, averaging at 8.
+The 54 extracts are encoded using the proposed approach with 4 analysis frame rate parameters of respectively 50~Hz, 16~Hz, 8~Hz and 4~Hz leading to 216 audio excerpts being tested in total.
+However, as the recording conditions are the same for all extracts the speaker identity is considered as a source of variability rather than as a necessary factor in the test statistics.
+As a result the objective is primarily to evaluate the 9 sentences with 4 encoding frame rates, \textit{i.e.} 36 parameters.
 
-For the perceptual test, each subject is presented with sentences and asked both to transcribe the utterances and rate the global intelligibility from 1 (not intelligible) to 5 (intelligible).
-Due to the low number of sentences, each sentence is tested twice for the same subject but under different encoding setting and speaker identity, resulting in each subject evaluating 18 extracts.
+For the perceptual test, each subject is presented with sentences and asked after listening to each sentence to both transcribe the utterances and rate the global intelligibility from 1 (not intelligible) to 5 (intelligible).
+Due to the low number of sentences, each one is tested twice by the same subject but under different encoding setting and speaker identity.
+As a result each subject evaluates 18 extracts evenly distributed over the 4 frame rate parameters.
 12 subjects of age ranging from 17 to 60 which reported normal hearing participated to the listening test.
@@
 The output level was set by the experimenter at the same level for all subjects.
+The mean duration of the test was about 8 minutes.
 
@@
 A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
-Signal phase is then approximated by either white noise spectrogram scaling or the Griffin \& Lim algorithm \cite{griffin1984} in hte case of overlapping frames.
+Signal phase is then approximated by either white noise spectrogram scaling or the Griffin \& Lim algorithm \cite{griffin1984} in the case of overlapping frames.
 The signal is then retrieved using concatenation or overlap-add depending on the overlap setting.
@@
 Third-octave representation on 31 bands yields an overall higher size than their Mel equivalent, here estimated for 30 bands.
-It however compares with the 40-Mel bands representation which is the most used features in literature.
+It however compares with the 40-Mel bands representation which is the most used in sound event recognition literature.
 This higher bitrate is likely due to the distribution observed by the data prior to Huffman encoding.
@@
 We evaluate the bitrate for 10 to 40 Mel bands and a frame rate from 2 to 10 per second, with fixed $q = 8$.
-Results are shown in Figure~\ref{fig:bitrate_mel_avg}.
-As expected, the bitrate for a given word size $q$ can be modeled as a linear function of the representation dimensions for one second of analysis.
+As can be expected, the bitrate for a given word size $q$ can be approximated as a linear function of the representation dimensions for one second of analysis.
 Small variations are induced by data distributions on a per-frame level and their impact on the Huffman algorithm.
 
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=0.5\textwidth]{figures/bitrate_mel_avg.eps}
-	\caption{Impact of representation resolution on the encoded data bitrate.}
-	\label{fig:bitrate_mel_avg}
-\end{figure}
+%\begin{figure}[htbp]
+%	\centering
+%		\includegraphics[width=0.5\textwidth]{figures/bitrate_mel_avg.eps}
+%	\caption{Impact of representation resolution on the encoded data bitrate.}
+%	\label{fig:bitrate_mel_avg}
+%\end{figure}
 
@@
 We now compare the efficiency of third-octave bands at characterizing urban acoustic environments to that of Mel spectrograms.
-Following the previous discussions, the classification task is run on corresponding cepstra with a fixed 8 frames per second and 31 bands.
+Following the previous discussions, the classification task is run on corresponding cepstrum coefficients, computed with the following parameters: 125~ms analysis frames with rectangular windowing and no overlap are used to perform the STFT, and 31 third-octave bands (20~Hz - 20~kHz) are considered.
 Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps Mel spectrograms seen in Table~\ref{T2} for all classification schemes.
@@
 The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
+Given the test conditions presented in Section\ref{sec:inintelligibility} and the number of subjects, the mean and standard deviation are computed on an average of 54 results per frame rate parameter: 12 subjects evaluating each analysis resolution 4.5 times on average.
 
-The results of the perceptual test visible in Figure~\ref{fig:subj_int} confirm the qualitative evaluation of speech properties discussed in Section \ref{sec:inintelligibility}.
+The results of the perceptual test, visible in Figure~\ref{fig:subj_int}, confirm the qualitative evaluation of speech properties discussed in Section \ref{sec:inintelligibility}.
 Phonemes separation is indeed mandatory in order to ensure good intelligibility of speech.
@@
 		\includegraphics[width=0.5\textwidth]{figures/subj_int.eps}
-	\caption{Normalized Average intellibility score (AIS) given by the subjects and the inteligibility ratio (IR) as a function of the frame rate.
-Inintelligibility appears at around 10~Hz, corresponding to the average duration of a phoneme.}
+	\caption{Mean and standard deviation of the Normalized Average intellibility score (AIS) given by the subjects and the inteligibility ratio (IR) as a function of the frame rate.
+Inintelligibility appears at around 10~Hz\fg{ref metrics<->intelligibility}, corresponding to the average duration of a phoneme.}
 	\label{fig:subj_int}
@@
 	\item precision: the impact of the quantization step for 8 bits codewords is found to be very small (< 0.5dB) and thus:
-	- do not impact the quality of the acoustics indicators.
-	- enable the sound recognition with the same quality than directly from the spectrogram.
-	\item efficiency: for fast and slow modes, the bitrate is respectively about 1.4~kbps and 0.4~kbps for the high precision mode
+	- does not impact the quality of the acoustics indicators.
+	- enables the sound recognition with the same quality than directly from the spectrogram.
+	\item efficiency: using the high precision parameters, the bitrate is about 1.4~kbps and 0.4~kbps for fast and slow modes respectively.
 	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible according to a perceputal test.
@@
 
-Future work will focus on the use of such a sensor grid approach as part of the cense project where its effectiveness will be assessed in field conditions.
+Future work will focus on the use of such a sensor grid approach as part of the Cense project where its effectiveness will be assessed in field conditions.
 The usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency should also be studied.

### 2017-10-09 embedded/matlab/cense_enc.m

@@ -128,7 +128,7 @@ if ~imp_ver
 
     % w = hanning(l_frame, 'periodic');
     w = rectwin(l_frame);
-    fft_norm = sum(w.^2)*(l_frame/2+1)/(l_frame^2);
+    fft_norm = sum(w.^2)/l_frame;
     
     %% STFT
     n_win = floor(1+(length(x)-l_frame)/l_hop); % Number of windows
@@ -153,7 +153,7 @@ if ~imp_ver
     
     X_tob(X_tob == 0) = eps; % Should never happen on real data
     X_tob = 10*log10(X_tob); % dB scale
-
+    
     %% Quantization
     q_norm(1) = min(min(X_tob));
     X_tob = X_tob-q_norm(1); % Everything has to be positive
@@ -195,9 +195,9 @@ else
         X = fft(x((ind_frame-1)*l_hop+1:(ind_frame-1)*l_hop+l_frame).*w); % FFT of current frame
 
         %% Magnitude spectrogram
+        X = X(1:end/2+1); % Only keep the first half
         X = abs(X).^2; % Squared magnitude
         X = X/fft_norm; % Normalize to conserve the energy of x
-        X = X(1:end/2+1); % Only keep the first half
 
         fwrite(res_file, ['// RFFT + Magnitude Spectrum (Frame' num2str(ind_frame) ')' 10]);
         fwrite(res_file, ['double X_' num2str(ind_frame) '[' num2str(length(X)) '] = {']);
@@ -224,6 +224,7 @@ else
         X_tob(X_tob == 0) = eps; % Avoid -Inf, Should never happen on real data
         X_tob(:, f_cnt) = 10*log10(X_tob(:, f_cnt)); % dB scale
 
+        plot(X_tob)
         fwrite(res_file, ['// Third Octave Analysis + log10 (Frame' num2str(ind_frame) ')' 10]);
         fwrite(res_file, ['double X_tob' num2str(ind_frame) '[' num2str(size(X_tob, 1)) '] = {']);
         n_line = 0;

### 2017-10-09 paper/article.tex

@@
 
-As discussed in the previous section, the recognition of sources of interest is of importance to fully model the studied acoustic environments.
+As discussed in the previous section, the recognition and the estimation of the level of contribution of sources of interest is of importance to fully model the studied acoustic environments, see for example \cite{alsina2016design, app7020146, gloaguen2016estimating}.
 As far as the encoding scheme is concerned, it is thus important that the encoded data allows us to compute the above cited indicators but also to detect the different sound sources with state of the art methods.

### 2017-10-09 paper/article.tex
ml proof read until validation protocol

--- 2017-10-02 paper/article.tex
@@
 The latter allows us to better assess the human perception of the urban sound environment in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}.
-This detection step can respectively be operated online (on the sensors) or offline (on the data servers) leading to different grid designs (Figure \ref{fig:codingScheme}).
+This detection step can respectively be operated online (on the sensors) or offline (on the data servers) leading to different network grid designs (Figure \ref{fig:codingScheme}).
 
@@
 This approach is thus currently considered in several approaches in the literature \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
-Though, it requires the availability of decent computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware does not allow them to be autonomous using power sources like decent size solar panels.
+Though, it requires the availability of decent computing resources on the sensors in order to perform the detection step, which as of today's efficiency of hardware does not allow them to be autonomous using power sources like reasonable size solar panels.
 Furthermore, the detection is done once and cannot be recomputed during offline posterior analyses.
@@
 Second, it allows researchers to gather large amount of data that can be post-processed and studied further offline.
-Data can be re-analyzed following newer classification schemes or using new indicators.
+Data can be re-analyzed following newer classification schemes or using new indicators if needed at a later stage.
 
-Though transmitting the raw audio  through the network (case A of Figure \ref{fig:codingScheme}) has several disadvantages, in terms of required bandwidth, storage capabilities and privacy.
+Though, transmitting the raw audio through the network (case A of Figure \ref{fig:codingScheme}) has several disadvantages, in terms of required bandwidth, storage capabilities and privacy.
 Thus, for transmission from the sensors to the storage unit, the data shall be encoded in a more efficient way than lossy audio encoding standards \cite{pan1995tutorial}.
 Indeed, the audio signal is not mandatory for the computation of the acoustic indicators and the features needed for event recognition.
-Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.
+Also, in order to ensure the privacy of the citizens since the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process.
 
@@
 As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data at production level rates.
-Finally, according to a perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
+Finally, according to a perceptual evaluation of intelligibility, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
 
-In order to promote reproducible research, the coder as well as the experiments needed to generate the figures is available to the community\footnote{\url{https://github.com/felixgontier/cense-coder}}.
+In order to promote reproducible research, the coder as well as the experiments needed to generate the figures is available\footnote{\url{https://github.com/felixgontier/cense-coder}}.
 The remaining of the paper is organized as follows: Section \ref{sec:background} reviews the types of data that needs to be estimated using the transmitted data and Section \ref{sec:coder} describes the proposed encoding scheme.
@@
 In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation.
+The latter is the proposed approach.
 Thickness of arrows indicates bandwidth and thickness of boxes indicates the level of computation or storage required.}
@@
 
-As discussed in the previous section, the recognition of sources of interest is of importance to fully model the studied acoustic environments.
-As far as the encoding scheme is concerned, it is thus important that the encoded data allows us to compute the above cited indicators but also to detect the different sound sources with state of the art methods.
+The recognition and the estimation of the level of contribution of sources of interest is thus of great importance to fully model the studied acoustic environments, see for example \cite{alsina2016design, app7020146, gloaguen2016estimating}.
+As far as the encoding scheme is concerned, it is therefore important that the encoded data allows us to compute the above cited indicators but also preserve an sufficient amount of information to reliably detect the different sound sources of interest.
 
-The recognition of sources of interest from audio streams has been the subject of extensive research in the past on speech \cite{anusuya2009}, music \cite{tzanetakis2002}, and lately more complex scenes in which the current work falls.
+The recognition of sound sources from audio streams has been the subject of extensive research in the past on speech \cite{anusuya2009}, music \cite{tzanetakis2002}, and lately  environmental scenes in which the current work falls.
 Studied classification methods are diverse, ranging from time-dependant modeling with hidden markov models \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}.
@@
 However, the selection of relevant features is still an open debate.
-The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal.
+That bein said, the most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal.
 Among them, Mel spectrograms and their cepstral-domain derivation, the Mel-frequency cepstrum coefficients (MFCC), are the most recurrent.

### 2017-10-09 paper/article.tex
ml proof read until validation protocol

@@
 The latter allows us to better assess the human perception of the urban sound environment in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}.
-This detection step can respectively be operated online (on the sensors) or offline (on the data servers) leading to different network grid designs (Figure \ref{fig:codingScheme}).
+This detection step can respectively be operated online (on the sensors) or offline (on the data servers) leading to different grid designs (Figure \ref{fig:codingScheme}).
 
@@
 This approach is thus currently considered in several approaches in the literature \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
-Though, it requires the availability of decent computing resources on the sensors in order to perform the detection step, which as of today's efficiency of hardware does not allow them to be autonomous using power sources like reasonable size solar panels.
+Though, it requires the availability of decent computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware does not allow them to be autonomous using power sources like decent size solar panels.
 Furthermore, the detection is done once and cannot be recomputed during offline posterior analyses.
@@
 Second, it allows researchers to gather large amount of data that can be post-processed and studied further offline.
-Data can be re-analyzed following newer classification schemes or using new indicators if needed at a later stage.
+Data can be re-analyzed following newer classification schemes or using new indicators.
 
-Though, transmitting the raw audio through the network (case A of Figure \ref{fig:codingScheme}) has several disadvantages, in terms of required bandwidth, storage capabilities and privacy.
+Though transmitting the raw audio  through the network (case A of Figure \ref{fig:codingScheme}) has several disadvantages, in terms of required bandwidth, storage capabilities and privacy.
 Thus, for transmission from the sensors to the storage unit, the data shall be encoded in a more efficient way than lossy audio encoding standards \cite{pan1995tutorial}.
 Indeed, the audio signal is not mandatory for the computation of the acoustic indicators and the features needed for event recognition.
-Also, in order to ensure the privacy of the citizens since the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process.
+Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.
 
@@
 As far as acoustic event detection is concerned, we report equivalent performance of several state of the art classification schemes from features computed using raw audio data and encoded data at production level rates.
-Finally, according to a perceptual evaluation of intelligibility, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
+Finally, according to a perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
 
-In order to promote reproducible research, the coder as well as the experiments needed to generate the figures is available\footnote{\url{https://github.com/felixgontier/cense-coder}}.
+In order to promote reproducible research, the coder as well as the experiments needed to generate the figures is available to the community\footnote{\url{https://github.com/felixgontier/cense-coder}}.
 The remaining of the paper is organized as follows: Section \ref{sec:background} reviews the types of data that needs to be estimated using the transmitted data and Section \ref{sec:coder} describes the proposed encoding scheme.
@@
 In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation.
-The latter is the proposed approach.
 Thickness of arrows indicates bandwidth and thickness of boxes indicates the level of computation or storage required.}
@@
 
-The recognition and the estimation of the level of contribution of sources of interest is thus of great importance to fully model the studied acoustic environments, see for example \cite{alsina2016design, app7020146, gloaguen2016estimating}.
-As far as the encoding scheme is concerned, it is therefore important that the encoded data allows us to compute the above cited indicators but also preserve an sufficient amount of information to reliably detect the different sound sources of interest.
+As discussed in the previous section, the recognition and the estimation of the level of contribution of sources of interest is of importance to fully model the studied acoustic environments, see for example \cite{alsina2016design, app7020146, gloaguen2016estimating}.
+As far as the encoding scheme is concerned, it is thus important that the encoded data allows us to compute the above cited indicators but also to detect the different sound sources with state of the art methods.
 
-The recognition of sound sources from audio streams has been the subject of extensive research in the past on speech \cite{anusuya2009}, music \cite{tzanetakis2002}, and lately  environmental scenes in which the current work falls.
+The recognition of sources of interest from audio streams has been the subject of extensive research in the past on speech \cite{anusuya2009}, music \cite{tzanetakis2002}, and lately more complex scenes in which the current work falls.
 Studied classification methods are diverse, ranging from time-dependant modeling with hidden markov models \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}.
@@
 However, the selection of relevant features is still an open debate.
-That bein said, the most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal.
+The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal.
 Among them, Mel spectrograms and their cepstral-domain derivation, the Mel-frequency cepstrum coefficients (MFCC), are the most recurrent.

### 2017-10-09 paper/article.tex
ml proof read until validation protocol

--- 2017-10-09 paper/article.tex
@@
 
-As discussed in the previous section, the recognition and the estimation of the level of contribution of sources of interest is of importance to fully model the studied acoustic environments, see for example \cite{alsina2016design, app7020146, gloaguen2016estimating}.
-As far as the encoding scheme is concerned, it is thus important that the encoded data allows us to compute the above cited indicators but also to detect the different sound sources with state of the art methods.
+The recognition and the estimation of the level of contribution of sources of interest is thus of great importance to fully model the studied acoustic environments, see for example \cite{alsina2016design, app7020146, gloaguen2016estimating}.
+As far as the encoding scheme is concerned, it is therefore important that the encoded data allows us to compute the above cited indicators but also preserve an sufficient amount of information to reliably detect the different sound sources of interest.
 

### 2017-10-10 paper/article.tex
ml proof read up to background

@@
 Second, the nodes shall be energy efficient, ideally autonomous, in order to ease the deployment of the sensor grid to the desired topology.
-Third, the encoding scheme used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to ensure the privacy of the citizens.
+Third, the encoding scheme used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to guarantee the privacy of the citizens.
 At the same time, the data stored shall remain as rich as possible while maintaining a low bitrate for efficient transmission and storage.
@@
 Performing the detection offline has several benefits.
-First, the sensor task is much simpler and can thus be implemented on low energy consumption processors, potentially being autonomous in terms of energy, which greatly eases the deployment of the network.
+First, the sensor task is much simpler and can thus be implemented on low energy consumption processors.
+This means that the sensors can be autonomous in terms of energy, which greatly eases the deployment of the network.
 Second, it allows researchers to gather large amount of data that can be post-processed and studied further offline.
@@
 Indeed, the audio signal is not mandatory for the computation of the acoustic indicators and the features needed for event recognition.
-Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to ensure the privacy of the citizens.
+Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to guarantee the privacy of the citizens.
 
-We thus propose in this paper an audio coding scheme specifically tailored for use in a sensor grid (case C of Figure \ref{fig:codingScheme}) which has the following features.
-It is of low bitrate but still allows the computation of most of the standard acoustics indicators with controllable precision.
+We thus propose in this paper an audio coding scheme specifically tailored for use in a sensor grid (case C of Figure \ref{fig:codingScheme}).
+It has the following features: it is of low bitrate but still allows the computation of most of the standard acoustics indicators with controllable precision.
 As far as acoustic event detection is concerned, we report equivalent performance of several state-of-the-art classification schemes from features computed using raw audio data and encoded data at production level rates.
@@
 
-In order to promote reproducible research, the coder as well as the experiments needed to generate the figures is available to the community\footnote{\url{https://github.com/felixgontier/cense-coder}}.
+In order to promote reproducible research, the coder as well as the experiments needed to generate the figures is available to the research community\footnote{\url{https://github.com/felixgontier/cense-coder}}.
 The remaining of the paper is organized as follows: Section \ref{sec:background} reviews the types of data that need to be estimated using the transmitted data and Section \ref{sec:coder} describes the proposed encoding scheme.
@@
 \includegraphics[width=0.5\textwidth]{figures/censeCoder}
-\caption{Alternative implementations of the sensor grid approach for the monitoring of the acoustic environment.
+\caption{Three alternative implementations of the sensor grid approach for the monitoring of the acoustic environment.
 In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation.

### 2017-10-10 paper/article.tex
ml proof read up to validation

@@
 The recognition and the estimation of the level of contribution of sources of interest is thus of great importance to fully model the studied acoustic environments, see for example \cite{alsina2016design, app7020146, gloaguen2016estimating}.
-As far as the encoding scheme is concerned, it is therefore important that the encoded data allows us to compute the above cited indicators but also preserve an sufficient amount of information to reliably detect the different sound sources of interest.
+As far as the encoding scheme is concerned, it is therefore important that the encoded data allows us to compute the above cited indicators but also preserve a sufficient amount of information to reliably detect the different sound sources of interest.
 
-The recognition of sources of interest from audio streams has been the subject of extensive research in the past on speech \cite{anusuya2009}, music \cite{tzanetakis2002}, and lately more complex scenes in which the current work falls.
+The identification of those sources from audio streams has been the subject of extensive research in the past for speech data \cite{anusuya2009}, music data \cite{tzanetakis2002}, and lately environmental data in which the current work falls.
 Studied classification methods are diverse, ranging from time-dependant modeling with hidden markov models \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}.
 Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, Gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}.
-However, the selection of relevant features is still an open debate.
+Also, several type of features are considered to feed those classifiers.
 The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal.
-Among them, Mel spectrograms and their cepstral-domain derivation, the Mel-frequency cepstrum coefficients (MFCC), are the most recurrent.
+Among them, Mel spectrograms and their cepstral-domain derivation, the Mel-frequency cepstrum coefficients (MFCC), arethe most widely used as of today.
 These representations effectively model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale.
 While parameters are empirical and vary in the literature, a reference implementation includes 23.2~ms analysis and a 40 Mel bands resolution.
-The resulting representations are generally more precise in time and frequency than in acoustic monitoring applications because it is a primordial factor for classification whereas acoustic indicators must be computed more accurately.\fg{ref Jean-R\'emy?}
+The resulting representations are generally more densely sampled in time and frequency than in acoustic monitoring applications since acoustic indicators focus more scarce but very accurate measurements.
 

### 2017-10-10 paper/article.tex
ml proof read up to conclusion

@@
 The coder's output bitrate as well as measurement error is computed for both data representations.
-This metric is composed of band analysis error and the additional loss yielded by quantization before the encoding process.
+This metric is composed of \ml{spectral ?} band analysis error and the additional loss yielded by quantization before the encoding process.
 
@@
 As the analysis frames are of short duration, poor frequency resolution and spectral leakage are expected, particularly in the lower frequencies bands.
-For this reason we evaluate the effect of the use of windowing functions on each band measurement error in order to mitigate this loss of precision.
+For this reason we evaluate the effect of the use of windowing functions on each band measurement error in order to potentially mitigate this loss of precision.
 To provide relevant statistics, these quantities are estimated with data from the 4500 audio recordings of the UrbanSound8k dataset \cite{salamon2014} described in the next section and 4500 \textit{iid.} noise sequences.
@@
 In order to ensure that the proposed scheme allows the recognition of events using state of the art methods, we consider the results achieved by several recognition systems on the UrbanSound8k dataset\cite{salamon2014}.
-It features about 9 hours of urban environmental sounds recordings separated in 8732 wave files ranging from 1 to 4 seconds each.
+It features about 9 hours of urban environmental sounds recordings separated in 8732 audio files ranging from 1 to 4 seconds each.
 The recordings are labeled in 10 classes (air conditioner, car horn, children playing, dog bark, drilling, engine idling, gun shot, jackhammer, siren, street music), and distributed in 10 independent folds.
@@
 It is used in all the following experiments with the exception of intelligibility computation for which a small dataset of high-quality voice recordings is preferred.
-Audio files are resampled at 44.1~kHz, normalized and a single channel is considered.
+Audio files are resampled at 44.1~kHz, normalized and only the \ml{left} channel is considered for further analysis.
 
@@
 We evaluate the global loss of information induced by the coder by implementing the four classification models proposed in \cite{salamon2014}: a support vector machine with a radial basis function kernel, a random forest classifier with 500 trees, a decision tree and a k-nearest neighbors classifier with $k = 5$.
-Values for the SVM parameter $C$ and RBF kernel variance $\sigma^2$ are found with a grid search.
+Values for the SVM parameter $C$ and RBF kernel variance $\sigma^2$ are determined using a grid search.
 We optionally apply a discrete cosine transform to the critical band signal representation to obtain cepstra, known as Mel Frequency Cepstrum Coefficients or MFCC in the case of Mel spectrograms.
-The 25 first coefficients are conserved, and summarized along time with the mean, variance, skewness, kurtosis, minimum, maximum, median, derivative mean and variance, second order derivative mean and variance operators.
+The 25 first coefficients are kept, and summarized along time with several statistics such as the mean, variance, skewness, kurtosis, minimum, maximum, median, derivative mean and variance, second order derivative mean and variance operators.
 The feature vector is thus comprised of 275 values to reproduce available results and compare with the data produced by the proposed coding scheme.
@@
 
-It is important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data is transmitted over the network and potentially stored, the level of intelligibility of potenital speech utterances present in the decoded stream should be as low as possible.
+It is important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data is transmitted over the network and potentially stored, the level of intelligibility of  speech utterances potentially captured in the decoded stream should be as low as possible.
 Thus, intelligibility in decoded and reconstructed audio is also an important concern of this study.
@@
 
-This test requires an estimate of the time-domain signal.
+This test requires an implementation of the inverse operation of the coding process to provide the listener with an estimate of the time-domain signal.
 To do so, a linearly-scaled spectrogram from the band-focused representations is estimated.
@@
 When using overlap to compute third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.
+
+\ml{tu parles de plein d'approches alternatives et on ne sait pas de quoi tu te sers pour les resultats. Ne presente que ce que tu utilises !!}
 
@@
 
-As can be expected when performing a short time analysis, high errors appear in low frequency bands where precision is poor.
+As can be expected when performing a short time analysis, strong errors appear in low frequency bands where precision is poor.
 The slow analysis yields better estimations as it provides a globally better resolution and thus also reduces the impact of spectral leakage effects in this region.
-When considering white noise the error is low on the whole spectrum.
+When considering white noise the error is low on the whole frequency range.
 Its mean over the testing samples is close to zero and its standard deviation increases in low frequencies, confirming the above-mentioned considerations.
@@
 For fast measurements and a rectangular window (Figure~\ref{fig:errormu}a), a student t-test ($p<0.05$) shows that the errors are not significantly different between 125~Hz and 12~kHz bands.
-For the first bands, the two methods yield different error distributions but of similar importance.
-Using a Hann window function results in lower error in low frequencies but adds a bias to the previously accurate band measurements.
+For the lower frequency bands, the two methods yield different error distributions but of similar importance.
+Using a Hann window function results in lower error in the low frequency range but adds a bias to the previously accurate band measurements.
 Again comparing the two computation methods shows a significant difference in the bands below 100~Hz only.
@@
 
-We also examine the additional error caused by the encoding steps after obtaining the desired data representation.
+The additional error caused by the encoding steps after obtaining the desired data representation is now studied.
 The only lossy operation applied is quantization, which is defined by an output word size $q$ in bits.
@@
 		\includegraphics[width=0.5\textwidth]{figures/class_mel_q.eps}
-	\caption{Classification accuracy as a function of word size before encoding. The baseline on the right is computed without quantizing the representation.}
+	\caption{Classification accuracy as a function of word size before encoding. The baseline plotted on the right is computed without quantizing the representation.}
 	\label{fig:class_mel_q}
@@
 We thus compute these metrics for the SVM classifier, with predictions accumulated over the ten folds in test configuration.
-The analogous natures of the two descriptors is highlighted by close one-versus-one differentiation performances, with a slightly lower accuracy for third-octave bands on average.
+The analogous designs of the two descriptors is highlighted by close one-versus-one differentiation performances, with a slightly lower accuracy for third-octave bands on average.
 Both representations yield best results for the \textit{Gun shot} class with 88.2\% for third-octave cepstra and 86.6\% for Mel cepstra.
@@
 
-The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
+The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \ml{la page est terminée ?} \url{https://felixgontier.github.io/cense-coder/web/examples.html}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
 Given the test conditions presented in Section\ref{sec:inintelligibility} and the number of subjects, the mean and standard deviation are computed on an average of 54 results per frame rate parameter: 12 subjects evaluating each analysis resolution 4.5 times on average.
@@
 	\item efficiency: using the high precision parameters, the bitrate is about 1.4~kbps and 0.4~kbps for fast and slow modes respectively.
-	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible according to a perceputal test.
+	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible according to a perceputal test done using clean speech recorded at very low background level.
+The sensors being typically hanged at 4 meters high in a usually very noisy environment, we believe that the intelligibility risk is negligible.
 \end{itemize}

### 2017-10-10 paper/article.tex
ml proof read done

@@
 The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \ml{la page est terminée ?} \url{https://felixgontier.github.io/cense-coder/web/examples.html}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
-Given the test conditions presented in Section\ref{sec:inintelligibility} and the number of subjects, the mean and standard deviation are computed on an average of 54 results per frame rate parameter: 12 subjects evaluating each analysis resolution 4.5 times on average.
+Given the test conditions presented in Section~\ref{sec:inintelligibility} and the number of subjects, the mean and standard deviation are computed on an average of 54 results per frame rate parameter: 12 subjects evaluating each analysis resolution 4.5 times on average.
 
 The results of the perceptual test, visible in Figure~\ref{fig:subj_int}, confirm the qualitative evaluation of speech properties discussed in Section \ref{sec:inintelligibility}.
-Phonemes separation is indeed mandatory in order to ensure good intelligibility of speech.
+Phonemes separation is indeed mandatory in order to have a good intelligibility of speech.
 This implies an analysis frame rate significantly larger than the phonemes rate the considered language.
-A limit of about 10~Hz corresponding to a frame duration of 100~ms is observed, as the studied 8~Hz setting is found to be almost completely inintelligible.
-Very few words are understood correctly.
-We assume that the correctly identified words are a result of coincidentally adequate frame timings, \textit{i.e.} analysis frames matching the location of phoneme utterances for a short duration.
+A limit at about 10~Hz corresponding to a frame duration of 100~ms is observed, as the studied 8~Hz setting is found to be almost completely inintelligible as very few words are understood correctly at this rate.
+We assume that the correctly identified words are a result of coincidentally adequate frame timings, \textit{i.e.} analysis frames matching the precise location of phoneme utterances for a short duration.
 Similarly, framing effects induced by the proposed processing scheme yielded errors for higher frame rates transcriptions and a globally lower perceptual intelligibility.\\
+
+\ml{encore une fois c'est pas bien clair si il y a de l'overlap ou pas. Si il n'y en a pas il faut enlever griffin and lim}
 
@@
 It has been designed to transfer data from acoustic sensors to processing and storage servers in an efficient and effective manner.
-It relies on a lossy audio coding scheme designed to the guaranty the privacy of the citizens while retaining the needed amount of acoustic precision to compute standard acoustic descriptors and to allow the recognition of events of interest at a state of the art level of recognition accuracy.
+It relies on a lossy audio coding scheme designed to preserve the privacy of the citizens while retaining the needed amount of acoustic precision to compute standard acoustic descriptors and to allow the recognition of events of interest at a state of the art level of recognition accuracy.
 
@@
 	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible according to a perceputal test done using clean speech recorded at very low background level.
-The sensors being typically hanged at 4 meters high in a usually very noisy environment, we believe that the intelligibility risk is negligible.
+Additionaly, the sensors being typically hanged at 4 meters high in a usually very noisy environment, we believe that the intelligibility risk of the proposed approach is negligible.
 \end{itemize}
@@
 The encoding scheme is designed to be easy to implement and to lead to an efficient data format for storage and sharing across the research community.
-To encourage its use for other research projects, an open source Matlab implementation of the coder is available.
+To encourage its use for other research projects, an open source Matlab and Python implementations of the coder are available.
 
@@
 The usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency should also be studied.
-Also, a more thorough investigation shall be performed on the inversion methods used to recover audio data from encoded data in order to ensure that the inintelligibility constraint is indeed not violated for fast settings.
+%Also, a more thorough investigation shall be performed on the inversion methods used to recover audio data from encoded data in order to ensure that the inintelligibility constraint is indeed not violated for fast settings.
 

### 2017-10-17 paper/article.tex
Paper corrections

@@
 The coder's output bitrate as well as measurement error is computed for both data representations.
-This metric is composed of \ml{spectral ?} band analysis error and the additional loss yielded by quantization before the encoding process.
+This metric is composed of the spectral third-octave band analysis error and the additional loss yielded by quantization before the encoding process.
 
@@
 It is used in all the following experiments with the exception of intelligibility computation for which a small dataset of high-quality voice recordings is preferred.
-Audio files are resampled at 44.1~kHz, normalized and only the \ml{left} channel is considered for further analysis.
+Audio files are resampled at 44.1~kHz, normalized and only the left channel is considered for further analysis.
 
@@
 To do so, a linearly-scaled spectrogram from the band-focused representations is estimated.
-This estimation can be achieved by multiplying the spectral representation by the scaled transpose of the forward transformation matrix.
+This estimation is achieved by multiplying the spectral representation by the scaled transpose of the forward transformation matrix.
 A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
-Signal phase is then approximated by either white noise spectrogram scaling or the Griffin \& Lim algorithm \cite{griffin1984} in the case of overlapping frames.
-The signal is then retrieved using concatenation or overlap-add depending on the overlap setting.
-When using overlap to compute third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.
-
-\ml{tu parles de plein d'approches alternatives et on ne sait pas de quoi tu te sers pour les resultats. Ne presente que ce que tu utilises !!}
+The signal phase is recovered with the Griffin \& Lim algorithm \cite{griffin1984} if analysis overlap is used and white noise spectrogram scaling if not.
+The time-domain signal is then retrieved using the overlap-add method.
+When using overlap to compute third-octave bands, framing effects produced by rectangular windowing are reduced by convoluting the signal with a Hann windowing function prior to inverse-STFT computation.
 
@@
 
-The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \ml{la page est terminée ?} \url{https://felixgontier.github.io/cense-coder/web/examples.html}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
+The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/web/examples.html}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
 Given the test conditions presented in Section~\ref{sec:inintelligibility} and the number of subjects, the mean and standard deviation are computed on an average of 54 results per frame rate parameter: 12 subjects evaluating each analysis resolution 4.5 times on average.
@@
 
-\ml{encore une fois c'est pas bien clair si il y a de l'overlap ou pas. Si il n'y en a pas il faut enlever griffin and lim}
-
 \begin{figure}[htbp]
@@
 	\caption{Mean and standard deviation of the Normalized Average intellibility score (AIS) given by the subjects and the inteligibility ratio (IR) as a function of the frame rate.
-Inintelligibility appears at around 10~Hz\fg{ref metrics<->intelligibility}, corresponding to the average duration of a phoneme.}
+Inintelligibility appears at around 10~Hz, corresponding to the average duration of a phoneme.}
 	\label{fig:subj_int}

### 2017-10-17 paper/article.tex
References update

@@
 The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal.
-Among them, Mel spectrograms and their cepstral-domain derivation, the Mel-frequency cepstrum coefficients (MFCC), arethe most widely used as of today.
+Among them, Mel spectrograms and their cepstral-domain derivation, the Mel-frequency cepstrum coefficients (MFCC), are the most widely used as of today.
 These representations effectively model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale.
-While parameters are empirical and vary in the literature, a reference implementation includes 23.2~ms analysis and a 40 Mel bands resolution.
-The resulting representations are generally more densely sampled in time and frequency than in acoustic monitoring applications since acoustic indicators focus more scarce but very accurate measurements.
+The resulting representations are generally more densely sampled in time and frequency than in acoustic monitoring applications since acoustic indicators focus on more scarce but very accurate measurements.
 

### 2017-10-17 censeCoder/cecoReport.m
Minor changes

@@ -49,7 +49,7 @@ if nargin==0, censeCoder('report', 'r'); return; end%censeCoder('report', 'rhv')
 %%% Class
 % Fixed: -
 % Varying: Quant - All
-% config = expExpose(config, 'p', 'mask', {-1, -1, 0, -1, -1, -1, 2, 0, -1, 2, -1, 2}, 'obs', 'cv_acc', 'save', 'tob_class', 'step', 4, 'expand', 'quant');
+config = expExpose(config, 'p', 'mask', {-1, -1, 0, -1, -1, -1, 2, 0, -1, 2, -1, 2, 6}, 'obs', 'cv_acc', 'save', 'tob_class', 'step', 4, 'expand', 'quant');
 
 %%% Intel
 % Fixed: -
@@ -95,6 +95,6 @@ if nargin==0, censeCoder('report', 'r'); return; end%censeCoder('report', 'rhv')
 % config = expExpose(config, 'p', 'mask', {-1, -1, 6, 1, 2, 10, 1, -1, 1, 2, 1, 2, 1:4}, 'obs', 'csii', 'save', 'tob_csii_len', 'step', 4);
 % config = expExpose(config, 'p', 'mask', {-1, -1, 6, 1, 2, 10, 1, -1, 1, 2, 2, 2, 1:4}, 'obs', 'fwSNRseg', 'save', 'tob_fwSNRseg_len', 'step', 4);
 
-config = expExpose(config, 'p', 'mask', {-1, -1, 6, 1, 2, 10, 2, 0, -1, 2, -1, 1, 6}, 'obs', 'fwSNRseg', 'save', 'tob_fwSNRseg_len', 'step', 4);
+% config = expExpose(config, 'p', 'mask', {-1, -1, 6, 1, 2, 10, 2, 0, -1, 2, -1, 1, 6}, 'obs', 'fwSNRseg', 'save', 'tob_fwSNRseg_len', 'step', 4);
 
 

### 2017-10-17 censeCoder/run_script.m

@@ -26,12 +26,12 @@ clear all, close all, clc;
 %%% Intel indicators - All mel settings, 8 bit
 % censeCoder('do', [1 2 3 4], 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, 0, -1});
 % censeCoder('do', [4], 'mask', {4, 4, 6, 1, 2, 10, 2, 1, -1, 0, -1, 2});
- 
+
 % censeCoder('do', [1 2 3], 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, -1, -1});
 % censeCoder('do', [3], 'mask', {0, 0, 6, 1, 2, 10, 1, -1, 1, 1, -1, -1});
 % censeCoder('do', [1 2 3], 'mask', {-1, -1, 0, 1, 2, 10, 1, -1, 1, 2, -1, 1});
 % censeCoder('do', [1 2 3], 'mask', {-1, -1, 0, 1, 2, 10, 1, -1, 1, 2, -1, 2});
 % censeCoder('do', [1 2 3], 'mask', {-1, -1, 6, 1, 2, 10, 3, -1, 2, 2, -1, 1, 1:4});
 % censeCoder('do', [1 2], 'mask', {-1, -1, 6, 2, 2, 10, 2, -1, -1, 2, -1, 2, 3});
-censeCoder('do', [1 4], 'mask', {-1, -1, 6, 1, 2, 10, 2, 4, -1, 2, -1, 3, 6});
+censeCoder('do', [4], 'mask', {-1, -1, 1, -1, -1, -1, 2, 1:3, -1, 2, -1, 2, 3});
 

### 2017-10-17 tobError/run_script.m

@@ -37,25 +37,26 @@
 % tobError('do', [3], 'mask', {[17], [3], 2, 6, 2, 3, 2});
 % tobError('do', [3], 'mask', {[17], [3], 2, 6, 2, 3, 2});
 %% DONE
-
-
-% 125ms - No overlap - Hann
-% tobError('do', [4], 'mask', {2, 3, 1, 6, 2, 3, 0});
-% 1s - 50% overlap - Hann
-% tobError('do', [4], 'mask', {2, 3, 2, 6, 2, 2, 0});
-% 1s - 66% overlap - Hann
-% tobError('do', [1 3 4], 'mask', {2, 3, 2, 6, 2, 4, 0});
-% 125ms - 66% overlap - Hann
-% tobError('do', [1 3 4], 'mask', {2, 3, 1, 6, 2, 4, 0});
-
 %% Not used
 % 125ms - 66% overlap - Rect
 % tobError('do', [4], 'mask', {17, 3, 1, 6, 2, 4, 0});
 % 1s - 66% overlap - Rect
 % tobError('do', [4], 'mask', {17, 3, 2, 6, 2, 4, 0});
+% 125ms - No overlap - Hann
+% tobError('do', [4], 'mask', {2, 3, 1, 6, 2, 3, 0});
+% 1s - 50% overlap - Hann
+% tobError('do', [4], 'mask', {2, 3, 2, 6, 2, 2, 0});
 
 %% Used
 % 125ms - No overlap - Rect
+% tobError('do', [1], 'mask', {17, 3, 1, 6, 2, 3, 1});
 % tobError('do', [4], 'mask', {17, 3, 1, 6, 2, 3, 0});
 % 1s - 50% overlap - Rect
+% tobError('do', [1], 'mask', {17, 3, 2, 6, 2, 2, 1});
 % tobError('do', [4], 'mask', {17, 3, 2, 6, 2, 2, 0});
+% 1s - 66% overlap - Hann
+% tobError('do', [1], 'mask', {2, 3, 2, 6, 2, 4, 1});
+% tobError('do', [4], 'mask', {2, 3, 2, 6, 2, 4, 0});
+% 125ms - 66% overlap - Hann
+tobError('do', [1], 'mask', {2, 3, 1, 6, 2, 4, 1});
+tobError('do', [4], 'mask', {2, 3, 1, 6, 2, 4, 0});

### 2017-10-17 paper/article.tex
web update

@@
 
-The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/web/examples.html}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
+The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
 Given the test conditions presented in Section~\ref{sec:inintelligibility} and the number of subjects, the mean and standard deviation are computed on an average of 54 results per frame rate parameter: 12 subjects evaluating each analysis resolution 4.5 times on average.

### 2017-10-18 embedded/stm/audio_analyzer/acoustic_indicators.h
code structure for unit test

@@ -1,0 +1,5 @@
+#ifndef ACOUSTIC_INDICATORS_H_
+#define ACOUSTIC_INDICATORS_H_
+
+
+#endif

### 2017-10-18 embedded/stm/tests/test_acoustic_indicators.c

@@ -1,0 +1,15 @@
+#include "audio_analyzer/acoustic_indicators.h"
+#include <stdio.h>
+#include <stdlib.h>
+
+/**
+ * Read raw audio signal file
+ */
+int main(int argc, char **argv) {
+	char *filename;
+	filename = (char*) malloc(sizeof(char) * 1024);
+	if (filename == NULL) {
+		printf("Error in malloc\n");
+		exit(1);		
+	}
+}

### 2017-11-10 paper/sensors/articleV1.tex
moving to v2 of paper

--- 2017-10-17 paper/article.tex
@@
 The coder's output bitrate as well as measurement error is computed for both data representations.
-This metric is composed of the spectral third-octave band analysis error and the additional loss yielded by quantization before the encoding process.
+This metric is composed of \ml{spectral ?} band analysis error and the additional loss yielded by quantization before the encoding process.
 
@@
 It is used in all the following experiments with the exception of intelligibility computation for which a small dataset of high-quality voice recordings is preferred.
-Audio files are resampled at 44.1~kHz, normalized and only the left channel is considered for further analysis.
+Audio files are resampled at 44.1~kHz, normalized and only the \ml{left} channel is considered for further analysis.
 
@@
 To do so, a linearly-scaled spectrogram from the band-focused representations is estimated.
-This estimation is achieved by multiplying the spectral representation by the scaled transpose of the forward transformation matrix.
+This estimation can be achieved by multiplying the spectral representation by the scaled transpose of the forward transformation matrix.
 A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
-The signal phase is recovered with the Griffin \& Lim algorithm \cite{griffin1984} if analysis overlap is used and white noise spectrogram scaling if not.
-The time-domain signal is then retrieved using the overlap-add method.
-When using overlap to compute third-octave bands, framing effects produced by rectangular windowing are reduced by convoluting the signal with a Hann windowing function prior to inverse-STFT computation.
+Signal phase is then approximated by either white noise spectrogram scaling or the Griffin \& Lim algorithm \cite{griffin1984} in the case of overlapping frames.
+The signal is then retrieved using concatenation or overlap-add depending on the overlap setting.
+When using overlap to compute third-octave bands, one can also avoid framing effects produced by rectangular windowing by convoluting the signal with another windowing function prior to inverse-STFT computation.
+
+\ml{tu parles de plein d'approches alternatives et on ne sait pas de quoi tu te sers pour les resultats. Ne presente que ce que tu utilises !!}
 
@@
 
-The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/web/examples.html}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
+The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \ml{la page est terminée ?} \url{https://felixgontier.github.io/cense-coder/web/examples.html}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
 Given the test conditions presented in Section~\ref{sec:inintelligibility} and the number of subjects, the mean and standard deviation are computed on an average of 54 results per frame rate parameter: 12 subjects evaluating each analysis resolution 4.5 times on average.
@@
 Similarly, framing effects induced by the proposed processing scheme yielded errors for higher frame rates transcriptions and a globally lower perceptual intelligibility.\\
+
+\ml{encore une fois c'est pas bien clair si il y a de l'overlap ou pas. Si il n'y en a pas il faut enlever griffin and lim}
 

### 2017-11-14 paper/sensors/articleV1.tex
paper V2

--- 2017-10-17 paper/article.tex
@@
 %=================================================================
-\newcommand{\ml}[1]{\textcolor{blue}{ Mathieu: #1}}
-\newcommand{\fg}[1]{\textcolor{red}{ Felix: #1}}
-\newcommand{\ac}[1]{\textcolor{red}{ Arnaud: #1}}
-\newcommand{\pa}[1]{\textcolor{red}{ Pierre: #1}}
-\newcommand{\cl}[1]{\textcolor{red}{ Catherine: #1}}
 \firstpage{1}
@@
 \Title{An efficient audio coding scheme  for quantitative and qualitative large scale acoustic monitoring using the sensor grid approach}
-
-% If this is an expanded version of a conference paper, please cite it here: enter the full citation of your conference paper, and add $^\dagger$ in the end of the title of this article.
-%\conference{Title}
 
@@
 
-The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the sonyc\footnote{\url{htttp://wp.nyu.edu/sonyc}} \cite{mydlarz2017implementation} and cense\footnote{\url{htttp://cense.ifsttar.fr}} \cite{picault2017} projects.
+The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the SONYC\footnote{\url{htttp://wp.nyu.edu/sonyc}} \cite{mydlarz2017implementation} and CENSE\footnote{\url{htttp://cense.ifsttar.fr}} \cite{picault2017} projects.
 To do so, considering the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} has several advantages.
@@
 
-%\begin{figure}[htbp]
-%	\centering
-%		\includegraphics[width=0.5\textwidth]{figures/bitrate_mel_avg.eps}
-%	\caption{Impact of representation resolution on the encoded data bitrate.}
-%	\label{fig:bitrate_mel_avg}
-%\end{figure}
-
 This experiment aims at an initial assessment of potential tradeoffs between bitrate and preservation of valuable information which will be further discussed in Section \ref{sec:eventRec}.\\
@@
 
-%As those constraints are to some extent orthogonal, the proposed approach is flexible enough to balance rapidly between several modes of operations by changing a few parameters in an intuitive manner.
-
 Future work will focus on the use of such a sensor grid approach as part of the Cense project where its effectiveness will be assessed in field conditions.
 The usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency should also be studied.
-%Also, a more thorough investigation shall be performed on the inversion methods used to recover audio data from encoded data in order to ensure that the inintelligibility constraint is indeed not violated for fast settings.
 

### 2017-11-14 paper/sensors/coverLetter.tex
paper V2

\documentclass[10pt]{article}

\title{Reply to reviewers concerning submission sensors-238686: "An efficient audio coding scheme  for quantitative and qualitative large scale acoustic monitoring using the sensor grid approach"}

\begin{document}

\maketitle

As a preamble, we would like to thank the editor and the reviewer for their comments and suggestions. Following these comments, we made several changes to the article, which are summarized here. The next sections list our answers to each of the reviewer’s comments, with references to the revised manuscript (page, column, and paragraph) where appropriate.

\section{Answers to Reviewer I}

\begin{enumerate}

\item \emph{It is recommended to discuss about noise annoying and loudness monitoring and evaluation with sensor network.}

$\rightarrow$

\item \emph{Is it possible to achieve a two channel coding and transmission with this proposed scheme?}

$\rightarrow$

\item \emph{Typos:\\
- Small English typos.\\
- Use of "we" too often. It is recommended using third person writting.\\
- Equation numeration}

$\rightarrow$

\end{enumerate}

\section{Answers to Reviewer II}

\begin{enumerate}

\item \emph{The Introduction is a bit shaky and needs to be reworked in my opinion. This section should: a) provide a literature review of the state of the art on acoustic sensors’ networks; b) identify a methodological gap in current practice; c) explain why it is important to fill it; and d) give a glimpse about how the proposed research aimed to do so. The current structure is confusing to me, with Section 2 coming a bit out of the blue (I feel it should be reported earlier in the Introduction).}

$\rightarrow$

\item \emph{Please, also note that not all readers are likely to be familiar with ASC and AED protocols, so it would be nice if the authors could provide some more details about the general steps; i.e., feature extraction (parametrisation) stage, classification stage, etc.}

$\rightarrow$

\item \emph{The Validation protocol (Section 4) is not very convincing. In particular, the subjective validation of Section 4.3 does not look rigorous at all.}

$\rightarrow$

\item \emph{In general, a strange aspect for me is that, this paper being submitted to the journal Sensors, there is no actual description of the sensors’ network architecture and/or hardware components proposed for the current study.}

$\rightarrow$

\item \emph{The overall structure of the paper should be re-thought in my opinion, as the reader struggles to orientate himself between the different sections of the manuscript. When I read the conclusions, it is hard to track back the discourse in the methodological and results sections.}

$\rightarrow$

\end{enumerate}

\section{Answers to Reviewer III}

\begin{enumerate}

\item \emph{It would be nice if the authors could add the following information to their work: Motivation for using the third octave band spectral representation.}

$\rightarrow$

\item \emph{Clearly state the novel points of this work in the introduction.}

$\rightarrow$

\item \emph{Why did you select these classification schemes? There many approaches in the literature exploiting that; for example "A novel holistic modeling approach for generalized sound recognition". In addition to that, the authors should justify why the did not employ deep learning (for both feature extraction and pattern recognition).}

$\rightarrow$

\item \emph{Another point regarding detection would be to relate this work with other operating in real unrestricted environments, such as "Acoustic detection of human activities in natural environments" and how the proposed method could boost the existing ones.}

$\rightarrow$

\item \emph{Since the authors use the UrbanSound8k dataset, it is not clear how the sensor grid approach is applied. Is there a grid of sensors included?}

$\rightarrow$

\item \emph{The authors should compare their system with other existing in the related literature to understand its merits and limitations. This should be done in many levels, i.e. coding, recognition, detection, etc.}

$\rightarrow$

\item \emph{Regarding intelligibility, it would be nice if the authors gave more information on the used metric. Moreover they should use standard metrics used for that which are similar to those used in the speech enhancement field. See paper "Objective comparison of speech enhancement algorithms under real world conditions" for more details.}

$\rightarrow$

\end{enumerate}

\end{document}

### 2017-11-14 paper/sensors/coverLetterTemplate.tex
paper V2

\documentclass[10pt]{article}

\title{Reply to reviewers concerning submission sensors-238686: "An efficient audio coding scheme  for quantitative and qualitative large scale acoustic monitoring using the sensor grid approach"}

\begin{document}

\maketitle

As a preamble, we would like to thank the editor and the reviewer for their comments and suggestions. Following these comments, we made several changes to the article, which are summarized here. The next sections list our answers to each of the reviewer’s comments, with references to the revised manuscript (page, column, and paragraph) where appropriate.

\section{Answers to Academic Editor}

\begin{enumerate}

\item \emph{The manuscript requires to address all the points raised in the reviewers' reports, mainly technical issues about the proposed technique, but also English writing mistakes which make it difficult to understand the paper.}

$\rightarrow$ We made our best to fix all the issues raised by the reviewers and to improve the readability of the paper.

\item \emph{
We are quite skeptical about the real significance of the contribution, since most of the ideas have already been accounted for in the (old) literature.}

$\rightarrow$ Our contribution lies in the uses of two concepts which have been long standing. We completely agree on that point. Though, we are unaware of previous contributions explicitly presenting the algorithm we propose together with detailed complexity analysis, memory requirements, experimentations, etc.

Many people from the machine learning community uses the kernel kmeans on arbitrary similarity matrices, eventhough the convergence is in this case not guaranteed. We believe, that our proposal is, in the case of arbitrary similarity matrices considered as input, a good alternative that provides guaranteed convergence, similar clustering performance, this for lower cpu and memory requirements.

\end{enumerate}

\section{Answers to Reviewer I}

\begin{enumerate}

\item \emph{Some points are not clear, and there are many English mistakes. For example,
(1) an maximization of : a maximization of (abstract)
(2) relaxing the conditions : what are "the conditions" here? (abstract)
(3) our simple non-quadratic updates makes : make (Section 4)
(4) times series : time series (Section 7)}

$\rightarrow$ The typos have been corrected and the whole manuscript have been carefully scrutinized. We clarified (2) by providing an example.

\item \emph{The contribution of this manuscript is not clear (or not sufficient). It is a well-known fact that minimizing the sum of squared distances between a data point and its cluster center can be converted into a form of maximizing the within-cluster similarity as noted in Duda et al. (Chapter 10.7). Also, considering the actual change of the objective function leads to a natural extension of the batch k-means as described in Duda et al. (Chapter 10.8). These two well-known ideas seem to be the main ideas of the proposed algorithm.}

$\rightarrow$ Those properties are indeed well known and clearly stated early in the manuscript. The main contribution of the paper is to demonstrate that the combination of those 2 properties lead an algorithm, that is to the best of our knowledge, new or at least whose properties in terms of convergence for arbitrary similarity measures, convergence and efficiency do not have been studied extensively in the literature.

We added a paragraph at the end of the introduction to more clearly state the contributions of the paper.

\item \emph{In Section 7, the proposed algorithm has been compared with only one baseline method (kernel k-means). Since there are a number of clustering algorithms, other state-of-the-art clustering algorithms also should be compared with the proposed algorithm to show the usefulness of the method. Also, in Section 7.3, the run time of the methods should be presented.}

$\rightarrow$ Following this comment and the comment of Reviewer II, we added the results for the spectral clustering technique, which is also widely used for dealing with proximity measures.

\item \emph{in Section 7.3, the run time of the methods should be presented.}

$\rightarrow$ We made a new section (section 7.4) dedicated to a runtime comparison of the different algorithms.

\end{enumerate}

\section{Answers to Reviewer II}

\begin{enumerate}

\item \emph{The flexibility to use arbitrary similarity measures is a novel contribution.\\ Exploiting only points that change cluster membership is a clever idea and leads to lower complexity.}

$\rightarrow$ Those are indeed the main contributions of the paper. Hopefully the manuscript now stresses more those contributions.

\item \emph{Convergence Issues: Permitting arbitrary similarity measures raises questions about convergence. In case of kernel k-means, the similarity measure is obtained using a positive definite kernel. Such a kernel implicitly assumes a Hilbert space, where Euclidean distances can be computed by virtue of inner products. Such a mapping through kernel functions is the premise for convergence of the basic iterative MSE procedure described in Duda \& Hart Ch 10.8. As arbitrary similarity measures are permitted, it is not clear how the convergence properties are impacted. Intuitively and empirically (based on Fig. 1) it seems that convergence should happen, [...]. Do arbitrary similarity measures always converge?}

$\rightarrow$ The k-average algorithm converge by design, see Section 3.2: "To ensure global convergence, we need to compute the impact on the global objective function of moving one object from one class to another. Using such formulation and performing only reallocation that have a positive impact, the convergence of such an iterative algorithm is guaranteed."

\item \emph{however, unfortunately the paper does not discuss the similarity measure that is used for experiments in Fig. 1}

$\rightarrow$ The similarity measure is the Dynamic Time Warping (DTW) has it was found to be the best performing measure for those datasets as described in the beginning of Section 7. The caption of Fig. 1 have been extended to provide this information.

\item \emph{Sensitivity to clustering performance:
Duda \& Hart (in Ch. 10.8) point out that the iterative optimization scheme is more susceptible to local minimum. I expect this effect to be exacerbated when arbitrary similarity measures are used. However, this has not been thoroughly investigated.}

$\rightarrow$ This is indeed a concern. We found experimentally that the k-average algorithm is, at least experimentally, not more susceptible to local minima than the other studied approaches, see comment below and discussion in Section 7.3.

\item \emph{Initialization of the algorithm:
In Alg. 3, the initialization 'L', i.e., the initial point-cluster assignment is done randomly. This is not the case in kernel k-means. It is surprising that despite the random initialization, the performance of k-average clustering matches the kernel k-means in many cases. As in the case of k-means and its iterative version, I would expect that the final solution depends on the initialization. Randomly initializing cluster labels ignores any notion of similarity between points, and are likely to lead to local poor minima in the overall optimization. This fact has been completely ignored and not investigated at all in the paper.}

$\rightarrow$ As stated in Section 7.2, all the algorithms are given the same initialization: "clustering is done by requesting a number of clusters equal to the actual number of classes in the dataset, and repeated 200 times with varying initial conditions, each algorithm being run with the exact same initial assignments."

That is, for each run, each object is given a label from 1 to $C$, $C$ being the number of classes. This labeling is used to initialize the k-average, kernel k-means and kmeans algorithm used in the spectral clustering technique.

There indeed exist strategies to better initialize the iterative scheme, but we believe that this matter is out of the scope of the paper which is about comparing the behaviors of the studied clustering methods.

In order to evaluate the influence of the initialization, we no longer consider the nmi of the best performing run in terms of objective function, but the mean and variance of the nmi obtained for each dataset. As now discussed in the paper in Section ??, the variance is comparable for each methods meaning that the k-average method

\item \emph{Writing and Grammar: The paper is very poorly written. There are several grammatical mistakes (e.g., 'an maximization' in the abstract. There are several more throughout the paper).}

$\rightarrow$ Several typos have been corrected and the whole manuscript have been carefully improve for better readability.

\item \emph{in (1), the notation used for vector multiplication (inner and outer products) is incorrect.}

$\rightarrow$ Equation 1 have been rewritten. Vector orientation and notation are also better introduced in the preceding paragraph.

\item \emph{On page 7, the statement that $\mathcal{Q}$ is strictly equivalent to the average point to centroid similarity' is not true in general, but only in case when the similarity can be interpreted as an inner product. If this is not the case, I suppose a proof to back this statement up is necessary.}

$\rightarrow$ We removed this sentence as it would indeed require more detailed explanations that we believe are out of the scope of this section.

\item \emph{$\delta_o$ in (9) is not introduced.}

$\rightarrow$ Introduction is now provided.

\item \emph{I would expect that comparisons with spectral clustering in terms of quality of clustering should also be included. Spectral clustering also permits arbitrary similarity measures and thus is directly relevant to the proposed work.}

$\rightarrow$ We added the spectral clustering technique to the reference set and discussed the matter. The main issue with the spectral clustering techniques is that it requires a diagonalization of a $N^2$ matrix with $N$ being the number of objects, making it difficult to scale to very large datasets.

\end{enumerate}

\end{document}

### 2017-11-14 paper/articleV2.tex
moving files in paper

--- 2017-11-14 paper/sensors/articleV1.tex
@@
 In this kind of approach, the crucial question is the nature of the data that is transmitted from the sensors to the processing and archival servers.
-To this end, we propose an efficient audio coding scheme based on third octave band spectral representation that allows 1) the estimation of standard acoustic indicators and 2) the recognition of acoustic events at state of the art performance rate.
+To this end, we propose an efficient audio coding scheme based on third octave band spectral representation that allows 1) the estimation of standard acoustic indicators and 2) the recognition of acoustic events at state-of-the-art performance rate.
 The former is useful to provide quantitative information about the acoustic environment, while the latter is useful to gather qualitative information and build perceptually motivated indicators using for example the emergence of a given sound source.
-The coding scheme is also demonstrated to transmit spectrally encoded data that, reverted to the time domain using state of the art techniques, is not intelligible, thus protecting the privacy of citizens.}
+The coding scheme is also demonstrated to transmit spectrally encoded data that, reverted to the time domain using state-of-the-art techniques, is not intelligible, thus protecting the privacy of citizens.}
 
@@
 
-In the case of acoustic monitoring, the data of interest can be quantitative such as standard acoustic indicators (LAeq, ...) or qualitative such as the presence of sound sources of interest (bird calls, sirens, ...).
-The latter allows us to better assess the human perception of the urban sound environment in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}.
-This detection step can respectively be operated online (on the sensors) or offline (on the data servers) leading to different grid designs (Figure \ref{fig:codingScheme}).
+In the case of urban acoustic monitoring, the data of interest typically rely on standardized high-quality measurements of energetic indicators such as the equivalent sound level $L_{eq}$ in dB SPL or its A-weighted counterpart $L_{Aeq}$ in dBA.
+However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe urban sound environments \cite{rychtarikova2013}.
+Many other variables can be derived to better account for previously implicit properties \cite{can2016} including percentile values or time dynamics.
+Studies have been conducted to select relevant subsets of descriptors in sound environment characterization \cite{can2015, brocolini2013, nilsson2007}.
+
+In addition, considering sound sources allows to better assess the human perception of the urban sound environment in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}.
+For instance, a bird song and traffic noise with the same energy are perceived very differently.
+Most acoustic indicators used in current sound maps describe the global sound environment and lack information on its composition.
+The recognition and the estimation of the level of contribution of sources of interest is thus of great importance to fully model the studied acoustic environments, see for example \cite{alsina2016design, app7020146, gloaguen2016estimating}.
+Other indicators have been found to correlate with specific sound environment content \cite{aumond2017} but do not achieve the level of performances of a well-designed source detection scheme in characterizing acoustic environments.
+This source detection step can respectively be operated online (on the sensors) or offline (on the data servers) leading to different grid designs (Figure \ref{fig:codingScheme}).
 
 Performing the detection online (case B of Figure \ref{fig:codingScheme}) is efficient in terms of data storage as only the detected events are transmitted.
-This approach is thus currently considered in several approaches in the literature \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
-Though, it requires the availability of decent computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware does not allow them to be autonomous using power sources like decent size solar panels.
+This approach is thus currently considered in several applications in the literature \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
+Though, it requires the availability of decent computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware does not allow them to be autonomous using power sources like solar panels.
 Furthermore, the detection is done once and cannot be recomputed during offline posterior analyses.
@@
 
-We thus propose in this paper an audio coding scheme specifically tailored for use in a sensor grid (case C of Figure \ref{fig:codingScheme}).
-It has the following features: it is of low bitrate but still allows the computation of most of the standard acoustics indicators with controllable precision.
-As far as acoustic event detection is concerned, we report equivalent performance of several state-of-the-art classification schemes from features computed using raw audio data and encoded data at production level rates.
+The analysis of sources within a sound environment is generally linked with spectral content \cite{ishiyama2000} and high temporal resolutions while acoustic indicators focus on more scarce but highly accurate measurements.
+To the extent of our knowledge, no implementation of large-scale sensor network consider both applications using in a single measurement.
+We thus present in this paper an audio coding scheme specifically tailored for use in a sensor grid (case C of Figure \ref{fig:codingScheme}).
+The proposed method computes and encodes third-octave bands $L_{eq}$ with controllable precision, enabling low bitrate transmissions while allowing both the derivation of other acoustic indicators and the implementation of offline audio event detection schemes.
+We report equivalent performance of several state-of-the-art classification models from features computed using raw audio data and encoded data at production level rates.
 Finally, according to a perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
@@
 In order to promote reproducible research, the coder as well as the experiments needed to generate the figures is available to the research community\footnote{\url{https://github.com/felixgontier/cense-coder}}.
-The remaining of the paper is organized as follows: Section \ref{sec:background} reviews the types of data that need to be estimated using the transmitted data and Section \ref{sec:coder} describes the proposed encoding scheme.
+The remaining of the paper is organized as follows: Section \ref{sec:coder} describes the proposed encoding scheme.
 The experimental protocol designed to validate the proposed approach is described in Section \ref{sec:protocol} and results are discussed in Section \ref{sec:results}.
@@
 
-\section{Background} \label{sec:background}
+\section{Encoding scheme} \label{sec:coder}
 
-The main contribution of this paper is to present an acoustic data encoding scheme that allows both acoustic monitoring and sound event recognition in urban sound environment.
-Here we briefly review state-of-the-art methods in both subjects in order to better motivate our design choices.
+\subsection{Data content}
 
-\subsection{Acoustic monitoring}
-
-The considered sensor network primarily aims at monitoring urban sound environments, that is, continuously assessing their content and impact on the population.
-In the literature, this is typically performed by measuring energetic acoustic indicators such as the equivalent sound pressure level $L_{eq}$ in dB SPL or its A-weighted equivalent $L_{Aeq}$ in dBA.
-However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe urban sound environments \cite{rychtarikova2013}.
-Many other variables can be derived to better account for previously implicit properties \cite{can2016} including percentile values or time dynamics.
-Studies have been conducted to select relevant subsets of descriptors in sound environment characterization \cite{can2015, brocolini2013, nilsson2007}.
-The mentionned $L_{eq}$ features are measured at periods of 0.125~ms or 1~s, respectively termed as "fast" and "slow" as a convention.
-
-Most measured or derived indicators describe the global urban acoustic environment and lack information on its composition.
-Sound sources recognition enables a more comprehensive understanding of the properties of the acoustic environment.
-For instance, a bird song and traffic noise with the same energy are perceived very differently.
-The analysis of sources within a sound environment is generally linked with spectral content \cite{ishiyama2000} and high temporal measurement resolutions.
-Other indicators can correlate with specific sound environment content \cite{aumond2017} but do not achieve the level of performances of a good source detection scheme in characterizing acoustic environments.
-
-\subsection{Event detection}
-
-The recognition and the estimation of the level of contribution of sources of interest is thus of great importance to fully model the studied acoustic environments, see for example \cite{alsina2016design, app7020146, gloaguen2016estimating}.
-As far as the encoding scheme is concerned, it is therefore important that the encoded data allows us to compute the above cited indicators but also preserve a sufficient amount of information to reliably detect the different sound sources of interest.
-
-The identification of those sources from audio streams has been the subject of extensive research in the past for speech data \cite{anusuya2009}, music data \cite{tzanetakis2002}, and lately environmental data in which the current work falls.
-Studied classification methods are diverse, ranging from time-dependant modeling with hidden markov models \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}.
+The identification of sources from audio streams has been the subject of extensive research in the past for speech data \cite{anusuya2009}, music data \cite{tzanetakis2002}, and lately environmental data in which the current work falls.
+Studied classification methods are diverse, ranging from time-dependant modeling with hidden Markov models \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}.
 Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, Gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}.
@@
 These representations effectively model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale.
-The resulting representations are generally more densely sampled in time and frequency than in acoustic monitoring applications since acoustic indicators focus on more scarce but very accurate measurements.
-
-They may also be exploited together with features computed in other domains to better model signal properties.
+Features can also be computed in other domains to better model signal properties.
 For instance, \cite{cai2006} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domain features.
 Another promising solution is feature engineering via unsupervised learning, which \cite{salamon2015-2} implements with a clustering technique.
-Alternative data representations such as the scattering transform \cite{bauge2013} show good results in environmental sound classification tasks \cite{salamon2015}.\\
+Alternative data representations such as the scattering transform \cite{bauge2013} show good results in environmental sound classification tasks \cite{salamon2015}.
 A more detailed review of used methods is available in \cite{chachada2013}.
 
-\section{Encoding scheme} \label{sec:coder}
+In the acoustic monitoring field, the measurement of energetic indicators is mandatory to the development of noise maps.
+The third-octave bands $L_{eq}$ appears suitable for this work's purpose: in addition to being a relevant descriptor \cite{torija2013} for urban sound environment assessment, it allows for the computation of most cited indicators while representing reasonably small, fixed amounts of data to be transmitted.
+Interestingly, third-octave bands are closely related to MFCC as they both are logarithmic-scaled spectral representations of the audio signal and diverge only in their motivation, mathematical and perceptive respectively.
 
-We thus need to provide data that allows both the computation of previously described indicators and the recognition of sound events.
-To do so, we propose to consider the calculation of spectral energetic indicators such as the 31 third-octave bands within the human audition range 20~Hz - 20~kHz.\\ Slow or fast third-octave bands measurement appears suitable for this work's purpose: in addition to being a relevant descriptor \cite{torija2013} for urban sound environment assessment, it allows for the computation of most cited indicators while representing reasonably small, fixed amounts of data to be transmitted.
-It additionnaly contains spectral information that can be used for source recognition tasks as it is close to the Mel spectral representation, being just another filterbank transform with logarithmic frequency scaling.
+We therefore consider the calculation of spectral energetic indicators such as the 31 third-octave bands within the human audition range 20~Hz - 20~kHz.
+"Fast" measurements of third-octave bands with an integration time of 125~ms are preferred to suit the temporal resolution needs of AED schemes, although "slow", 1~s measurements are also considered to further study the effect on our application's constraints.
+
+\subsection{Signal analysis}
 
 A common way to implement third-octave analysis is to first design the highest octave three filters, and use them on progressively time-decimated versions of the input signal \cite{davis1986}.
-Antoni et al.
 \cite{antoni2010} presents an alternative analysis method based on direct frequency weighting, which yields a lower computational complexity as opposed to time filtering.
@@
 
-\subsection{Data Encoding}
+\subsection{Data Encoding} \label{sec:dataenc}
 
@@
 Those parameters are as follow: 1) the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, 2) the number of considered bands, and 3) the STFT parameters including frame duration, overlap and windowing function usage.
+This section details experimental protocols for the validation of bitrate, measurement error, audio event recognition and intelligibility developped to best suit the corresponding constraints.
 
-\subsection{Efficiency}
+\subsection{Efficiency} \label{sec:efficiency_p}
 
@@
 
-To evaluate the analysis error, we consider the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017} as a reference.
+Regarding the analysis error, we consider the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017} as a reference, with less than $0.1~dB$ error when compared to a class 1 sound level meter on 2~s third-octave bands measurements.
 We study both "fast" computation with 125~ms windows and "slow" 1~s analysis to assess the impact of time integration.
-Third-octave bands are computed using the proposed method as well as the \textit{ita\_toolbox} in the same experimental conditions, then averaged over time and compared to the toolbox's measurements on longer extracts.
-In all experiments the sound dataset is the same and is composed of 2~s extracts.
-The experiment is run for white noise as well as urban environmental recordings.
-As the analysis frames are of short duration, poor frequency resolution and spectral leakage are expected, particularly in the lower frequencies bands.
-For this reason we evaluate the effect of the use of windowing functions on each band measurement error in order to potentially mitigate this loss of precision.
-To provide relevant statistics, these quantities are estimated with data from the 4500 audio recordings of the UrbanSound8k dataset \cite{salamon2014} described in the next section and 4500 \textit{iid.} noise sequences.
+Third-octave bands are computed using the proposed method as well as the \textit{ita\_toolbox} in the same experimental conditions, then averaged over time and compared to the toolbox's measurements on longer 2~s extracts.
+The experiment is run for Gaussian white noise as well as urban environmental recordings: the former allows direct estimation bias evaluation, while the latter provides a simulation of real operating conditions.
+As the analysis frames are of short duration, poor frequency resolution and spectral leakage are expected when performing the STFT, particularly in the lower frequencies bands.
+For this reason we evaluate the impact of windowing functions on each band measurement error in order to potentially mitigate this loss of precision.
 
-\subsection{Event recognition}
+To provide relevant statistics, these quantities are estimated with data from the 4500 audio recordings of the UrbanSound8k dataset \cite{salamon2014} described in the next section and 4500 \textit{iid.} Gaussian noise sequences.
 
-In order to ensure that the proposed scheme allows the recognition of events using state of the art methods, we consider the results achieved by several recognition systems on the UrbanSound8k dataset\cite{salamon2014}.
+\subsection{Event recognition} \label{sec:event_p}
+
+In order to ensure that the proposed scheme allows the recognition of events using state-of-the-art methods, we consider the results achieved by several recognition systems on the UrbanSound8k dataset\cite{salamon2014}.
 It features about 9 hours of urban environmental sounds recordings separated in 8732 audio files ranging from 1 to 4 seconds each.
@@
 A method and baseline results are also provided for the classification task.
-It is used in all the following experiments with the exception of intelligibility computation for which a small dataset of high-quality voice recordings is preferred.
-Audio files are resampled at 44.1~kHz, normalized and only the left channel is considered for further analysis.
+In this study, audio files are resampled at 44.1~kHz, normalized and only the left channel is considered for further analysis.
 
-Mel spectrograms are computed with the \textit{rastamat} library \cite{ellis2005} to assess the relative performance of third-octave bands.
-STFT analysis frames are obtained by applying a Hann window on 23.2~ms of signal with 50\% (11.6~ms) overlap to allow for efficient phase recovery in further tests.
+The aim of this experiment is two-fold: to evaluate the global loss of information induced by the coding process, and to evaluate the adequacy of third-octave bands indicators for classification.
+As studying the best performing classical models \citep{ntalampiras2013}, deep learning approaches \citep{salamon2017} or unsupervised feature learning is beyond the scope of this paper, we choose to replicate the baseline models and results proposed in \cite{salamon2014}.
 
-We evaluate the global loss of information induced by the coder by implementing the four classification models proposed in \cite{salamon2014}: a support vector machine with a radial basis function kernel, a random forest classifier with 500 trees, a decision tree and a k-nearest neighbors classifier with $k = 5$.
+The four classification models are as follow: a support vector machine with a radial basis function kernel, a random forest classifier with 500 trees, a decision tree and a k-nearest neighbors classifier with $k = 5$.
 Values for the SVM parameter $C$ and RBF kernel variance $\sigma^2$ are determined using a grid search.
@@
 Models are trained for each setup using the 10-fold cross validation method provided by the authors of \cite{salamon2014}, that is, every combination of testing one fold on models trained with the other nine.
+A summary of the considered classification process is shown in Figure~\ref{fig:class_flwc}.
 
-\subsection{Inintelligibility} \label{sec:inintelligibility}
+\begin{figure*}[htbp]
+	\centering
+		\includegraphics[width=.9\textwidth]{figures/class.pdf}
+	\caption{Classification process flowchart.
+Here third-octave bands are obtained by reversing the operations in Section~\ref{sec:dataenc}.
+Cepstral coefficients are then computed before training the model.
+Cross-validation is achieved by independantly training and testing the models with each of the 10 combination of a 90\%-10\% training-validation dataset separation.
+Accuracy results are considered only for validation (not encountered during training) data.}
+	\label{fig:class_flwc}
+\end{figure*}
+
+Mel spectrograms are also computed with the \textit{rastamat} library \cite{ellis2005} to assess the relative performance of third-octave bands.
+STFT analysis frames are obtained by applying a Hann window on 23.2~ms of signal with 50\% (11.6~ms) overlap to allow for efficient phase recovery in further tests.
+
+\subsection{Inintelligibility} \label{sec:inintelligibility_p}
 
@@
 For the evaluation, a dataset of clean speech utterances recorded in studio conditions is used.
-The dataset is made of 9 french sentences enunciated by 3 male and 3 female speakers.
+The dataset is composed of 9 french sentences enunciated by 3 male and 3 female speakers.
 The sentences have an mean duration of $2~s$ and are composed of 5 to 12 words, averaging at 8.
@@
 
-For the perceptual test, each subject is presented with sentences and asked after listening to each sentence to both transcribe the utterances and rate the global intelligibility from 1 (not intelligible) to 5 (intelligible).
-Due to the low number of sentences, each one is tested twice by the same subject but under different encoding setting and speaker identity.
-As a result each subject evaluates 18 extracts evenly distributed over the 4 frame rate parameters.
+For the perceptual test, 18 different sentences evenly distributed over the 4 frame rate parameters are selected for each subject.
+For each sentence the participant first listens to the extract and is then asked to transcribe the utterance and to rate the perceived intelligibility from 1 (not intelligible) to 5 (intelligible).
+The first metric is computed as the ratio of correctly transcribed words and will be referred as the intelligibility ratio (IR) in this paper.
+The second metric is directly the score attributed by the listener, referred as the intelligibility score (IS), which is assimilable to the OVRL metric proposed in \cite{itup835}.
+The other two metrics in this standard relative to the signal only (SIG) and background noise only (BAK), which are often used to evaluate speech enhancement schemes \citep{ntalampiras2008}, are not suitable for this test due to the background and signal being mixed with uncontrollable SNR by the coding process.
+As decoding the transmitted audio induces a framing effect unevenly distorting the input utterance, the computation of the IR appears adequate as an additional metric.
+
 12 subjects of age ranging from 17 to 60 which reported normal hearing participated to the listening test.
@@
 
-\subsection{Coder efficiency}
+\subsection{Coder efficiency} \label{sec:efficiency_r}
 
@@
 Figure~\ref{fig:bitrate_q} shows estimations of the output bitrate for different values of $q$.
-To match third-octave bands computation principle where a 125~ms analysis is mandatory, Mel frames are averaged over time.
+To match third-octave bands computation principle where a 125~ms (fast) or 1~s (slow) analysis is standardized, Mel frames are averaged over time.
 Because we use the most common parameters, namely 23.2~ms window with 50\% overlap, the closest achievable rate considering simple averaging is 7.74 frames per second.
@@
 
-This experiment aims at an initial assessment of potential tradeoffs between bitrate and preservation of valuable information which will be further discussed in Section \ref{sec:eventRec}.\\
+This experiment aims at an initial assessment of potential tradeoffs between bitrate and preservation of valuable information which will be further discussed in Section \ref{sec:event_r}.\\
 
@@
 Only full-octave bands are shown for the sake of visibility.
-When computing the slow analysis, we find that applying overlap attenuated the error.
+When computing the slow analysis, we find that applying overlap attenuates the error.
 This is not observed for fast analysis where the error is similar or higher with the use of overlapping frames.
 
-As can be expected when performing a short time analysis, strong errors appear in low frequency bands where precision is poor.
+When performing a short time analysis, strong errors appear in low frequency bands where the precision of the DFT is poor.
 The slow analysis yields better estimations as it provides a globally better resolution and thus also reduces the impact of spectral leakage effects in this region.
@@
 Its mean over the testing samples is close to zero and its standard deviation increases in low frequencies, confirming the above-mentioned considerations.
-This effectiveness does not translate well to environmental sound analysis, most likely mainly due to the sound level disparities absent in the former case but omnipresent in the latter.
+This effectiveness does not translate well to environmental sound analysis, most likely due to the sound level disparities absent in the former case but omnipresent in the latter.
 Spectral leakage induces a correlation between close frequency components.
-In lower frequencies, large differences between adjacent frequency bins can thus cause important errors on third-octave bands computations.
-This issue is however not specific to Fourier transform based schemes as it is also encountered with a time domain filtering approach.
+In lower frequencies, large differences between adjacent frequency bins can therefore cause important errors on the third-octave bands computation.
+This issue is however not specific to Fourier transform-based schemes as it is also encountered with a time domain filtering approach.
 
@@
 For a fast analysis with no overlap, the rectangular window seems a reasonable choice at first because of its energy conservation qualities.
-While it yields the lowest error in high frequency bands, its high spectral leakage effect makes it unprecise for lower frequency regions.
+While it yields the lowest error in high frequency bands, its important spectral leakage effect makes it unprecise in lower frequency regions.
 Non-flat windows better account for this issue but require assuming that the signal is stationary in a given frame.
 The use of overlap then results in better estimates at the cost of an increased data size.
-For slow measurements, considering the rectangular window impact is less harmful to band analysis due to an increased frequency resolution.
+For slow measurements, considering the rectangular window is less harmful to band analysis due to an increased frequency resolution.
 
@@
     \caption{Measurement error of third-octave bands over two-seconds environmental sounds recordings (US8k dataset).
-For most settings the FFT-based method yields similar errors to the time-domain filtering reference.
+For most settings the FFT-based method yields similar errors compared to the time-domain filtering reference.
 \label{fig:errormu}}
@@
 However, it corresponds to the word size \textit{after} $\Delta$-compression, meaning that the data is in fact quantized on $2^{q-1}$ values.
-Since these measurements are already expressed in dB, the error $\varepsilon$ is:
+Since these measurements are already expressed in dB, the error $\varepsilon$ is computed as:
 \begin{equation*}
@@
 
-\subsection{Event recognition} \label{sec:eventRec}
+\subsection{Event recognition} \label{sec:event_r}
 
-The same set of parameters as in bitrate evaluation is used to study the impact of their tuning to the sound event recognition performance.
-We thus aim at finding ways to further reduce the encoded data size without strongly affecting recognition performance.
-Results of the four presented classification methods are provided for the sake of completeness.\\
+The same set of parameters as in bitrate evaluation is used to study the impact of their tuning on sound event recognition performance.
+This experiment aims at finding ways to further reduce the encoded data size without strongly affecting detection performance.
+Results of the four presented classification methods \ref{sec:event_p} are provided for the sake of completeness.
 
 First, we observe the impact of quantization on classification accuracy.
-The models are trained on the most complete implemented representation, ie.
-40 Mel bands, 23.2~ms, 50\% overlap and no time averaging (85 frames per second).
-Figure~\ref{fig:class_mel_q} shows that this process yields equivalent accuracy for higher resolutions.\\
+The models are trained on the most complete implemented representation to replicate the results of \citep{salamon2014}, ie.
+40 Mel bands, 23.2~ms, 50\% overlap analysis and no time averaging (85 frames per second).
+Figure~\ref{fig:class_mel_q} shows that equivalent accuracies are obtained for all considered values of the quantization parameter $q$ down to 5 bits.\\
 
@@
 
-The effect of changing the time-frequency resolution of the representation is presented in Table~\ref{T2}.
-Similarly to baseline results, the random forest and SVM classifiers are the higher performing systems at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively.
-However, we find that given our setup, reducing the number of analysis bands up to a given level most often does not induce a strong drop of performance.
-The performance of the decision tree classifier is a good example of this behavior, with best performances for 10 Mel bands only and a 4\% lower accuracy for 40.
-Even if the difference is small, all other models perform best with 30 or 40 Mel bands as a representation.
+The effect of changing the time-frequency resolution of the representation is presented in Table~\ref{T1}.
+In this table, equivalence of performance with respect to the best performing setting (in red) is depicted with a bold font evaluated using the following procedure.
+The null hypothesis that the subtraction of the two compared distribution (the distribution of the setting we consider minus the distribution of the best performing one) comes from a normal distribution with mean equal to zero and unknown variance is evaluated using the paired-sample t-test at the 0.05 significance level.
+If the null hypothesis is not rejected, the setting is considered as equivalent in terms of performance to the best performing one.
+
+Similarly to baseline results, the random forest and SVM classifiers are the best performing systems at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively.
+However, we find that given our setup, reducing the number of analysis bands up to a given level often does not induce a severe drop of performance.
+The accuracy of the decision tree classifier is a good example of this behavior, with best performances for 10 Mel bands only and a 4\% lower accuracy for 40.
+Other models trained with 20 to 40 Mel bands as a representation show no significant performance difference.
 Time decimation can also be considered, as the original representation can be averaged and consistently yield a good classification accuracy.
-The loss of information can be considered negligible for FPS values as low as 20 or 10 depending on the method.
-Even below, classification accuracy only drops by one or a few percents.
+The loss of information can be considered negligible for frame-per-second values as low as 20~Hz or 10~Hz depending on the method.
+Even below, the classification accuracy only drops by one to a few percents.
 This means that we can effectively divide the data size by a factor of at most 10 without strongly affecting sound event recognition performance.
-It also provides us with a preliminary confirmation of the possibility for "fast"-sampled third-octave bands cepstra to match  MFCC performances.\\
+It also provides us with a preliminary confirmation of the possibility for "fast", 8~Hz third-octave bands cepstra to match MFCC performances.\\
 
@@
 \centering
-\caption{Classification accuracy in percentage for different classifiers: SVMs (a), Random Forests (b), Decision Trees (c), and Nearest Neigbors (d) with respect to varying representation resolutions.
-Numbers in red indicate best performance and numbers in bold indicate that no statisticaly significant difference is found when comparing to the best performing setting ($p<.05$).}
-\label{T2}
+\caption{Classification accuracy in percentage for different models: SVMs (a), Random Forests (b), Decision Trees (c), and Nearest Neigbors (d) with respect to varying representation resolutions.
+Numbers in red indicate best performance and numbers in bold indicate that no statistically significant difference is found when comparing to the best performing setting ($p<.05$).}
+\label{T1}
 (a)\\
@@
 
-\subsection{Third-octave bands as base descriptors}
+\subsection{Third-octave bands as base descriptors} \label{sec:tob_r}
 
-We now compare the efficiency of third-octave bands at characterizing urban acoustic environments to that of Mel spectrograms.
+We now compare the efficiency of third-octave bands at differenciating sound sources in urban acoustic environments to that of Mel spectrograms.
 Following the previous discussions, the classification task is run on corresponding cepstrum coefficients, computed with the following parameters: 125~ms analysis frames with rectangular windowing and no overlap are used to perform the STFT, and 31 third-octave bands (20~Hz - 20~kHz) are considered.
-Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps Mel spectrograms seen in Table~\ref{T2} for all classification schemes.
-In this table, equivalence of performance with respect to the best performing setting (in red) is depicted with a bold font evaluated using the following procedure.
-The null hypothesis that the subtraction of the two compared distribution (the distribution of the setting we consider minus the distribution of the best performing one) comes from a normal distribution with mean equal to zero and unknown variance is evaluated using the paired-sample t-test at the 0.05 significance level.
-If the null hypothesis is not rejected, the setting is considered as equivalent in terms of performance to the best performing one.
-\\
+Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps Mel spectrograms seen in Table~\ref{T1} for all classification schemes.\\
 
@@
 These sounds involve important low-frequency information which can generally differentiate them, leading third-octave descriptors to perform better.
-Conversely, using Mel-based cepstra improves globally \textit{Air conditioning} recognition as most of its defining components are situated in higher frequencies.\\
+Conversely, using Mel-based cepstra improves globally \textit{Air conditioning} recognition as most of its defining components are situated in higher frequencies.
 
@@
 
-\subsection{Inintelligibility}
+\subsection{Inintelligibility} \label{sec:inintelligibility_r}
 
 The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
-Given the test conditions presented in Section~\ref{sec:inintelligibility} and the number of subjects, the mean and standard deviation are computed on an average of 54 results per frame rate parameter: 12 subjects evaluating each analysis resolution 4.5 times on average.
+Given the test conditions presented in Section~\ref{sec:inintelligibility_p} and the number of subjects, the mean and standard deviation are computed on an average of 54 results per frame rate parameter: 12 subjects evaluating each analysis resolution 4.5 times on average.
 
-The results of the perceptual test, visible in Figure~\ref{fig:subj_int}, confirm the qualitative evaluation of speech properties discussed in Section \ref{sec:inintelligibility}.
+The results of the perceptual test, visible in Figure~\ref{fig:subj_int}, confirm the qualitative evaluation of speech properties discussed in Section \ref{sec:inintelligibility_p}.
 Phonemes separation is indeed mandatory in order to have a good intelligibility of speech.
@@
 It has been designed to transfer data from acoustic sensors to processing and storage servers in an efficient and effective manner.
-It relies on a lossy audio coding scheme designed to preserve the privacy of the citizens while retaining the needed amount of acoustic precision to compute standard acoustic descriptors and to allow the recognition of events of interest at a state of the art level of recognition accuracy.
+It relies on a lossy audio coding scheme designed to preserve the privacy of the citizens while retaining the needed amount of acoustic precision to compute standard acoustic descriptors and to allow the recognition of events of interest at a state-of-the-art level of recognition accuracy.
 
@@
 \begin{itemize}
-	\item precision: the impact of the quantization step for 8 bits codewords is found to be very small (< 0.5dB) and thus:
-	- does not impact the quality of the acoustics indicators.
-	- enables the sound recognition with the same quality than directly from the spectrogram.
-	\item efficiency: using the high precision parameters, the bitrate is about 1.4~kbps and 0.4~kbps for fast and slow modes respectively.
+	\item precision: the impact of the quantization step for 8 bits codewords is found to be very small (< 0.2dB) and thus:\\
+	- does not impact the quality of the acoustics indicators (Sections~\ref{sec:efficiency_p}, \ref{sec:efficiency_r}).\\
+	- enables the sound recognition with the same quality than directly from the spectrogram (Sections~\ref{sec:event_p}, \ref{sec:event_r} and \ref{sec:tob_r}).
+	\item efficiency: using the high precision parameters, the bitrate is about 1.4~kbps and 0.4~kbps for fast and slow modes respectively (Section~\ref{sec:efficiency_r}).
 	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible according to a perceputal test done using clean speech recorded at very low background level.
-Additionaly, the sensors being typically hanged at 4 meters high in a usually very noisy environment, we believe that the intelligibility risk of the proposed approach is negligible.
+Additionaly, the sensors being typically hanged at 4 meters high in a usually very noisy environment, we believe that the intelligibility risk of the proposed approach is negligible (Sections~\ref{sec:inintelligibility_p}, \ref{sec:inintelligibility_r}).
 \end{itemize}
@@
 
-Future work will focus on the use of such a sensor grid approach as part of the Cense project where its effectiveness will be assessed in field conditions.
+Future work will focus on the use of such a sensor grid approach as part of the CENSE project where its effectiveness will be assessed in field conditions.
 The usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency should also be studied.
@@
 
-The authors would like to thank Christophe d'Alessandro for fruitful discussion on speech intelligibilty.
+The authors would like to thank Christophe d'Alessandro for fruitful discussion on speech intelligibility.
 

### 2017-11-15 paper/articleV2.tex
acticle revision

@@
 
-In the case of urban acoustic monitoring, the data of interest typically rely on standardized high-quality measurements of energetic indicators such as the equivalent sound level $L_{eq}$ in dB SPL or its A-weighted counterpart $L_{Aeq}$ in dBA.
+In the case of urban acoustic monitoring, the data of interest typically consists of standardized high-quality measurements of energetic indicators such as the equivalent sound level $L_{eq}$ in dB SPL or its A-weighted counterpart $L_{Aeq}$ in dBA.
 However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe urban sound environments \cite{rychtarikova2013}.
@@
 The analysis of sources within a sound environment is generally linked with spectral content \cite{ishiyama2000} and high temporal resolutions while acoustic indicators focus on more scarce but highly accurate measurements.
-To the extent of our knowledge, no implementation of large-scale sensor network consider both applications using in a single measurement.
+To the best of our knowledge, no efficient coding scheme has been proposed for large-scale sensor network.
 We thus present in this paper an audio coding scheme specifically tailored for use in a sensor grid (case C of Figure \ref{fig:codingScheme}).
@@
 
-\section{Encoding scheme} \label{sec:coder}
+\section{Proposed encoding scheme} \label{sec:coder}
 
-\subsection{Data content}
+\subsection{Data representation}
 
@@
 
-Regarding the analysis error, we consider the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017} as a reference, with less than $0.1~dB$ error when compared to a class 1 sound level meter on 2~s third-octave bands measurements.
+In order to assess the quality of the propoposed scheme's spectral measurement precision, we compare it to a widely used reference: the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017}.
+This toolbox's implementation shows less than $0.1~dB$ error on all bands when compared to a class 1 sound level meter on 2~s third-octave bands measurements.
 We study both "fast" computation with 125~ms windows and "slow" 1~s analysis to assess the impact of time integration.
@@
 Mel spectrograms are also computed with the \textit{rastamat} library \cite{ellis2005} to assess the relative performance of third-octave bands.
-STFT analysis frames are obtained by applying a Hann window on 23.2~ms of signal with 50\% (11.6~ms) overlap to allow for efficient phase recovery in further tests.
+STFT analysis frames are obtained by applying a Hann window on 23.2~ms of signal with 50\% (11.6~ms) overlap to allow for efficient phase recovery.
 
@@
 
+Several subjective intelligibility metrics are standardized in the literature such as the system proposed in \cite{itup835}.
+However, metrics regarding the signal only (SIG) or background noise only (BAK) which are often used to evaluate speech enhancement schemes \citep{ntalampiras2008}, are not suitable for this test due to the background and signal being mixed with an uncontrollable SNR by the encoding process.
+Given these conditions a subjective score on the whole signal is used similarly to the OVRL score.
+As decoding the transmitted audio induces a framing effect unevenly distorting the input utterance, a second metric is designed to assess the comprehension of words.
 For the perceptual test, 18 different sentences evenly distributed over the 4 frame rate parameters are selected for each subject.
 For each sentence the participant first listens to the extract and is then asked to transcribe the utterance and to rate the perceived intelligibility from 1 (not intelligible) to 5 (intelligible).
-The first metric is computed as the ratio of correctly transcribed words and will be referred as the intelligibility ratio (IR) in this paper.
-The second metric is directly the score attributed by the listener, referred as the intelligibility score (IS), which is assimilable to the OVRL metric proposed in \cite{itup835}.
-The other two metrics in this standard relative to the signal only (SIG) and background noise only (BAK), which are often used to evaluate speech enhancement schemes \citep{ntalampiras2008}, are not suitable for this test due to the background and signal being mixed with uncontrollable SNR by the coding process.
-As decoding the transmitted audio induces a framing effect unevenly distorting the input utterance, the computation of the IR appears adequate as an additional metric.
+The first metric is directly the score attributed by the listener, referred as the intelligibility score (IS).
+The second metric is computed as the ratio of correctly transcribed words and will be referred as the intelligibility ratio (IR) in this paper.
 
@@
 Future work will focus on the use of such a sensor grid approach as part of the CENSE project where its effectiveness will be assessed in field conditions.
-The usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency should also be studied.
+The usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency should also be studied, as well as the effect of multiple channel coding and its interest in sensor grids applications.
 

### 2017-11-15 paper/sensors/coverLetter.tex
acticle revision

@@
 
-$\rightarrow$
+$\rightarrow$ This is now more clearly dscussed in the introduction as well as in the conclusion where a dedicated paragraph has been added.
 
@@
 
-$\rightarrow$
+$\rightarrow$ While a single audio channel was selected for this study, a multiple channel encoding can be performed by applying the Delta compression along both the time and channels dimensions.
+As the transmitted data primarily consists of energetic measurements, additional channels are likely to be encoded very efficiently due to the redundance of information already contained in the first channel.
 
@@
 
-$\rightarrow$
+$\rightarrow$ The typos have been corrected and the whole manuscript has been carefully scrutinized.
+The use of "we" has also been reduced to favor third-person writing.
+The equation numeration has been corrected throughout the document.
 
@@
 
-$\rightarrow$
+$\rightarrow$ Following this comment as well as the comment of Reviewer III, we reworked the introduction to match this format.
+The considerations on acoustic monitoring and event detection in urban sound environments previously discussed in Section 2 have also been moved earlier in the introduction.
+A new section (Section 2.1) was added to discuss the choice of data representation.
 
@@
 
-$\rightarrow$
+$\rightarrow$ We added a new figure (Figure 6) to clarify the applied classification process.
 
@@
 
-$\rightarrow$
+$\rightarrow$ Our coding scheme must observe several constraints, namely low bitrate, measurement accuracy for monitoring purposes, the ability to perform event classification on the transmitted data and inintelligibility for privacy concerns.
+For each of these required properties we designed a validation procedure using urban environmental sound recordings.
+We acknowledge that the listening test is somewhat informal, as our goal is more to provide insights about why the transmitted data will not lead to intelligible speech content than to fully prove it which would be out of the scope of this paper.
 
@@
 
-$\rightarrow$
+$\rightarrow$ The main contribution of this work, which is now more clearly shown in the introduction, is about the definition of a coding scheme that will be used (as stated in the conclusion) in a sensor network.
+But prior to this usage, several properties needed to be validated, motivating this work.
 
@@
 
-$\rightarrow$
+$\rightarrow$ We added more references bewteen sections to facilitate the reader's orientation in the manuscript.
 
@@
 
-$\rightarrow$
+$\rightarrow$ A new section (Section 2.1) has been added to motivate the use of third-octave bands for both acoustic monitoring and audio event detection.
 
@@
 
-$\rightarrow$
+$\rightarrow$ The contribution is now more clearly stated in the introduction.
 
@@
 
-$\rightarrow$
+$\rightarrow$ As is now explained in Section 3.2, we do not aim at achieving the best classification performance but 1) to prove that third-octave bands match the most commonly used descriptors for the classification task, and 2) to discuss the effect of encoding parameters on the recognition accuracy to select the most appropriate.
+To this aim we chose to replicate the baseline results for the considered dataset on these four schemes.
+The study of more advanced classification schemes and of deep learning for AED will however be of particular interest in future related work.
 
@@
 
-$\rightarrow$
+$\rightarrow$ This would be a very interesting avenue of research that could be considered for future work.
 
@@
 
-$\rightarrow$
+$\rightarrow$ As stated in the introduction and conclusion, the proposed scheme will be applied to a sensor grid as part of the CENSE project.
+However, as this sensor grid is not yet implemented, the UrbanSound8k dataset provides both a decent amount of audio data with similar content (urban environmental sounds) and classification methods and results that can be used as a baseline for our work.
 
@@
 
-$\rightarrow$
+$\rightarrow$ The contribution of this work is on the coding only.
+To the best of our knowledge the proposed approach is the only scheme where the data transmitted is not the detected events nor the raw audio but an intermediate spectral based format, specifically designed for acoustic monitoring and AED.
 
@@
 
-$\rightarrow$
+$\rightarrow$ While we are aware that standardized metrics exist such as the ITU protocols, we believe that they are not adapted to the evaluation of intelligibility in this application.
+The encoding process distorts the signal in a very non-linear way, so that we have no control over the background and signal elements.
+A five-point score on the overall intelligibility is however used, and a second metric (the transcription ratio) is designed to account for the typical distortions induced by linearly scaled spectrogram and phase recoveries.
+Motivation and insight concerning the used metrics are now added in Section 3.3.
 

### 2017-11-15 paper/sensors/coverLetter.tex
cover letter proof read

@@
 $\rightarrow$ While a single audio channel was selected for this study, a multiple channel encoding can be performed by applying the Delta compression along both the time and channels dimensions.
-As the transmitted data primarily consists of energetic measurements, additional channels are likely to be encoded very efficiently due to the redundance of information already contained in the first channel.
+As the transmitted data primarily consists of energetic measurements, additional channels are likely to be encoded very efficiently due to the redundancy of information already contained in the first channel.
+
+FELIX : reference to where the article has been modified.
 
@@
 
-$\rightarrow$ Following this comment as well as the comment of Reviewer III, we reworked the introduction to match this format.
-The considerations on acoustic monitoring and event detection in urban sound environments previously discussed in Section 2 have also been moved earlier in the introduction.
+$\rightarrow$ Following your comment as well as the comment of Reviewer III, we have rewritten the introduction to better highlight the contributions of the paper.
+The considerations on acoustic monitoring and event detection in urban sound environments previously discussed in Section 2 have also been moved earlier in the introduction to better frame those contributions.
 A new section (Section 2.1) was added to discuss the choice of data representation.
@@
 
-$\rightarrow$ The main contribution of this work, which is now more clearly shown in the introduction, is about the definition of a coding scheme that will be used (as stated in the conclusion) in a sensor network.
+$\rightarrow$ The main contribution of this work, which is now more clearly shown in the introduction, is about the definition of a coding scheme that will be used (as stated in the conclusion) in a sensor network that will be implemented in a near future.
 But prior to this usage, several properties needed to be validated, motivating this work.
@@
 
-$\rightarrow$ We added more references bewteen sections to facilitate the reader's orientation in the manuscript.
+$\rightarrow$ We added more references between sections to facilitate the reader's orientation in the manuscript.
 
@@
 To this aim we chose to replicate the baseline results for the considered dataset on these four schemes.
-The study of more advanced classification schemes and of deep learning for AED will however be of particular interest in future related work.
+The study of more advanced classification schemes and of deep learning for AED is very interesting and will be of particular interest in future work.
 
@@
 
+FELIX give ref to where you discuss this the paper.
+
 \item \emph{Since the authors use the UrbanSound8k dataset, it is not clear how the sensor grid approach is applied. Is there a grid of sensors included?}
 
-$\rightarrow$ As stated in the introduction and conclusion, the proposed scheme will be applied to a sensor grid as part of the CENSE project.
+$\rightarrow$ As now more clearly stated in the introduction and conclusion, the proposed scheme will be applied to a sensor grid as part of the CENSE project.
 However, as this sensor grid is not yet implemented, the UrbanSound8k dataset provides both a decent amount of audio data with similar content (urban environmental sounds) and classification methods and results that can be used as a baseline for our work.
@@
 $\rightarrow$ The contribution of this work is on the coding only.
-To the best of our knowledge the proposed approach is the only scheme where the data transmitted is not the detected events nor the raw audio but an intermediate spectral based format, specifically designed for acoustic monitoring and AED.
+As discussed in the introduction, to the best of our knowledge the proposed approach is the only scheme where the data transmitted is not the detected events nor the raw audio but an intermediate spectral based format, specifically designed for acoustic monitoring and AED, thus motivating this paper.
 
@@
 
-$\rightarrow$ While we are aware that standardized metrics exist such as the ITU protocols, we believe that they are not adapted to the evaluation of intelligibility in this application.
+$\rightarrow$ While we are aware that standardized metrics exist such as the ITU protocols, we found that they are not adapted to the evaluation of intelligibility in this application.
 The encoding process distorts the signal in a very non-linear way, so that we have no control over the background and signal elements.
-A five-point score on the overall intelligibility is however used, and a second metric (the transcription ratio) is designed to account for the typical distortions induced by linearly scaled spectrogram and phase recoveries.
-Motivation and insight concerning the used metrics are now added in Section 3.3.
+A five-point score on the overall intelligibility is still used however, and a second metric (the transcription ratio) is designed to account for the typical distortions induced by linearly scaled spectrogram and phase recoveries.
+Motivation and insights concerning the used metrics as well as this discussion are now added in Section 3.3.
 

### 2017-11-16 paper/sensors/coverLetter.tex
done with proof read

@@
 
+FELIX : fig 3 xlabel coupé, réduire la figure ou la refaire pour avoir la bonne taille de fonte
+
+section 3.2 Preserving event recognition performance at low bitrate.
+
+Fig 6 en haut de page caption trop longue
+
+Fig 7 convertir en noir et blanc et expliciter le niveau de gris dans la caption. On ne fait pas le lien avec la figure. Raccourci et explicite la figure avant.
+
+Fig 12 et 13 agrandir presque pleine page
+
 \end{document}

### 2017-11-16 paper/articleV2.tex
paper revision

@@
 For instance, \cite{cai2006} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domain features.
+Alternative data representations such as the scattering transform \cite{bauge2013} show good results in environmental sound classification tasks \cite{salamon2015}.
 Another promising solution is feature engineering via unsupervised learning, which \cite{salamon2015-2} implements with a clustering technique.
-Alternative data representations such as the scattering transform \cite{bauge2013} show good results in environmental sound classification tasks \cite{salamon2015}.
+More complex systems using multiple-domain data representation as well as unsupervised models have been found to handle unrestricted environments suche as urban acoustic scenes efficiently \citep{ntalampiras2012}.
 A more detailed review of used methods is available in \cite{chachada2013}.
@@
 		\includegraphics[width=.9\textwidth]{figures/scheme.pdf}
-	\caption{Overview of the coder process.}
+	\caption{Overview of the encoding process.}
 	\label{fig:scheme}
@@
 
-\subsection{Event recognition} \label{sec:event_p}
+\subsection{Preserving event recognition performance at low bitrate} \label{sec:event_p}
 
@@
 
-\begin{figure*}[htbp]
+\begin{figure*}[t]
 	\centering
@@
 	\caption{Classification process flowchart.
-Here third-octave bands are obtained by reversing the operations in Section~\ref{sec:dataenc}.
-Cepstral coefficients are then computed before training the model.
-Cross-validation is achieved by independantly training and testing the models with each of the 10 combination of a 90\%-10\% training-validation dataset separation.
-Accuracy results are considered only for validation (not encountered during training) data.}
+Here third-octave bands are obtained by reversing the operations in Section~\ref{sec:dataenc} and cepstral coefficients are computed before training the model.
+Cross-validation is achieved by independantly training and testing the models with each of the 10 combination of a 90\%-10\% training-validation dataset separation.}
 	\label{fig:class_flwc}
@@
 A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
+In fact, each white square can be interpreted as the filter applied to obtain a single third-octave band.
+The filtering process will average the energy content of the signal over the corresponding band.
+As a result the energy located at a specific frequency is impossible to recover and the best inverse approximation is to split the third-octave band's observed energy into all the corresponding frequency bins with the same proportions as during analysis.
+This leads to the phenomenon seen on Figure~\ref{fig:freq} where part of the energy of a frequency bin in the original signal is found in all other bins of the same band at reconstruction, in almost equal proportions.
 The signal phase is recovered with the Griffin \& Lim algorithm \cite{griffin1984} if analysis overlap is used and white noise spectrogram scaling if not.
@@
 	\caption{Third-octave bands analysis and approximate inverse transformation effects on energy location.
+Here a brighter gray indicates that part of the energy contained at the corresponding frequency of the original signal is transferred to the reconstructed signal at the indicated frequency.
 This process yields an important and heterogeneous loss in resolution, particularly at higher frequency points.}
@@
 	\centering
-		\includegraphics[width=0.5\textwidth]{figures/class_mel_q.eps}
+		\includegraphics[width=0.8\textwidth]{figures/class_mel_q.eps}
 	\caption{Classification accuracy as a function of word size before encoding. The baseline plotted on the right is computed without quantizing the representation.}
@@
 	\centering
-		\includegraphics[width=0.5\textwidth]{figures/class_tob_q.eps}
+		\includegraphics[width=0.8\textwidth]{figures/class_tob_q.eps}
 	\caption{Classification accuracy with third-octave bands and varying word size.}

### 2017-11-16 paper/sensors/coverLetter.tex
paper revision

--- 2017-11-15 paper/sensors/coverLetter.tex
@@
 
+CATHERINE: Est-il possible de dédier un petit paragraphe à la question dans la conclusion?
+
 \item \emph{Is it possible to achieve a two channel coding and transmission with this proposed scheme?}
@@
 As the transmitted data primarily consists of energetic measurements, additional channels are likely to be encoded very efficiently due to the redundancy of information already contained in the first channel.
-
-FELIX : reference to where the article has been modified.
+Future work using this idea in a sensor grid is now discussed in the conclusion.
 
@@
 $\rightarrow$ This would be a very interesting avenue of research that could be considered for future work.
-
-FELIX give ref to where you discuss this the paper.
+The discussion on data representations and models used in environmental audio event recognition (Section 2.1) has been extended to include related works.
 

### 2017-11-20 paper/articleV2.tex
anr funding

@@
 
-The authors would like to thank Christophe d'Alessandro for fruitful discussion on speech intelligibility.
+The authors would like to acknowledge partial funding from the ANR under project reference ANR-16-CE22-0012 and to thank Christophe d'Alessandro for fruitful discussion on speech intelligibility.
 

### 2017-11-20 paper/articleV2.tex
paper update

@@
 $^{2}$ \quad IFSTTAR, AME, LAE\\
-$^{3}$ \quad Universit\'e de Cergy-Pontoise}
+$^{3}$ \quad ETIS, UMR 8051, Universit\'e Paris Seine, Universit\'e Cergy-Pontoise, ENSEA, CNRS, F-95000 Cergy-Pontoise.}
 
@@
 The analysis of sources within a sound environment is generally linked with spectral content \cite{ishiyama2000} and high temporal resolutions while acoustic indicators focus on more scarce but highly accurate measurements.
-To the best of our knowledge, no efficient coding scheme has been proposed for large-scale sensor network.
 We thus present in this paper an audio coding scheme specifically tailored for use in a sensor grid (case C of Figure \ref{fig:codingScheme}).
@@
 
-In order to assess the quality of the propoposed scheme's spectral measurement precision, we compare it to a widely used reference: the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017}.
-This toolbox's implementation shows less than $0.1~dB$ error on all bands when compared to a class 1 sound level meter on 2~s third-octave bands measurements.
+In order to assess the quality of the propoposed scheme's spectral measurement precision, we compare it to a known reference: the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017}.
+This toolbox's implementation shows less than $0.1~dB$ error on all bands when compared to a class 1 sound level meter software on 2~s third-octave bands measurements.
 We study both "fast" computation with 125~ms windows and "slow" 1~s analysis to assess the impact of time integration.
@@
 The dataset is composed of 9 french sentences enunciated by 3 male and 3 female speakers.
-The sentences have an mean duration of $2~s$ and are composed of 5 to 12 words, averaging at 8.
+The sentences have a mean duration of $2~s$ and are composed of 5 to 12 words, averaging at 8.
 The 54 extracts are encoded using the proposed approach with 4 analysis frame rate parameters of respectively 50~Hz, 16~Hz, 8~Hz and 4~Hz leading to 216 audio excerpts being tested in total.
@@
 However, metrics regarding the signal only (SIG) or background noise only (BAK) which are often used to evaluate speech enhancement schemes \citep{ntalampiras2008}, are not suitable for this test due to the background and signal being mixed with an uncontrollable SNR by the encoding process.
-Given these conditions a subjective score on the whole signal is used similarly to the OVRL score.
+Given these conditions a subjective score on the whole signal is used similarly to the OVRL score in \cite{itup835}.
 As decoding the transmitted audio induces a framing effect unevenly distorting the input utterance, a second metric is designed to assess the comprehension of words.
@@
 For each sentence the participant first listens to the extract and is then asked to transcribe the utterance and to rate the perceived intelligibility from 1 (not intelligible) to 5 (intelligible).
-The first metric is directly the score attributed by the listener, referred as the intelligibility score (IS).
-The second metric is computed as the ratio of correctly transcribed words and will be referred as the intelligibility ratio (IR) in this paper.
+The first metric is computed as the ratio of correctly transcribed words and will be referred as the intelligibility ratio (IR) in this paper.
+The second metric is directly the score attributed by the listener, referred as the intelligibility score (IS).
 
@@
 A loss of resolution increasing with frequency is induced due to the shape of the transformation, as illustrated by Figure~\ref{fig:freq}.
-In fact, each white square can be interpreted as the filter applied to obtain a single third-octave band.
+Each white square can be interpreted as the filter applied to obtain a single third-octave band.
 The filtering process will average the energy content of the signal over the corresponding band.
@@
 
+This scheme will be implemented with a large-scale sensor grid as part of the CENSE project, where sensors are designed to be low-cost and energy efficient.
+The aim of the project is to create noise maps by linking standard acoustic measurements with novel perceptually motivated metrics.
+The presented coding scheme will enable a thorough study of the correlation between sound sources and context with pleasantness as perceived by the citizens to better understand the composition of acoustic scenes in urban environments.
+
 Future work will focus on the use of such a sensor grid approach as part of the CENSE project where its effectiveness will be assessed in field conditions.

### 2017-11-20 paper/sensors/coverLetter.tex
paper update

@@
 
-$\rightarrow$ This is now more clearly dscussed in the introduction as well as in the conclusion where a dedicated paragraph has been added.
-
-CATHERINE: Est-il possible de dédier un petit paragraphe à la question dans la conclusion?
+$\rightarrow$ This is now more clearly discussed in the introduction as well as in the conclusion where a dedicated paragraph has been added on the use of this scheme as part of the current project.
 

### 2017-11-20 paper/articleV2.tex
polish conclusion

@@
 The aim of the project is to create noise maps by linking standard acoustic measurements with novel perceptually motivated metrics.
-The presented coding scheme will enable a thorough study of the correlation between sound sources and context with pleasantness as perceived by the citizens to better understand the composition of acoustic scenes in urban environments.
+The presented coding scheme will enable a thorough study of the correlation between sound sources and context with pleasantness as perceived by the citizens to better understand the content of urban acoustic scenes and its perception by city dwellers.
 
-Future work will focus on the use of such a sensor grid approach as part of the CENSE project where its effectiveness will be assessed in field conditions.
-The usefulness of more sophisticated encoding paradigms in order to further improve bitrate efficiency should also be studied, as well as the effect of multiple channel coding and its interest in sensor grids applications.
+To do so, future work will focus on the use of such data encoder in a sensor grid approach as part of the CENSE project where its effectiveness will be assessed in field conditions.
+As far as the proposed encoding scheme is concerned, the usefulness of more sophisticated encoding paradigms should also be studied in order to further improve bitrate efficiency, as well as the effect of multiple channel coding and its interest in sensor grids applications.
 

### 2017-11-27 paper/articleV3.tex
added article v3

--- 2017-11-20 paper/articleV2.tex
@@
 %=================================================================
-\documentclass[sensors,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}
+\documentclass[sensors,article,accept,moreauthors,pdftex,10pt,a4paper]{mdpi}
 %
@@
 \usepackage{multirow}
-\usepackage{subcaption}
+\usepackage[labelformat=simple]{subcaption}
+\renewcommand\thesubfigure{\alph{subfigure}}
+\DeclareCaptionLabelFormat{subcaptionlabel}{\normalfont(\textbf{#2}\normalfont)}
+\captionsetup[subfigure]{labelformat=subcaptionlabel}
+
+\DeclareRobustCommand{\fg}[1]{{\sethlcolor{cyan}\hl{#1}}}
+
+\usepackage{microtype}
 
@@
 \doinum{10.3390/------}
-\pubvolume{xx}
+\pubvolume{17}
 \pubyear{2017}
 \copyrightyear{2017}
-\history{Received: date; Accepted: date; Published: date}
+%\externaleditor{Academic Editor: name}
+\history{Received: 17 October 2017; Accepted: 20 November 2017; Published: date}
 
@@
 % Full title of the paper (Capitalized)
-\Title{An efficient audio coding scheme  for quantitative and qualitative large scale acoustic monitoring using the sensor grid approach}
+\Title{An Efficient Audio Coding Scheme  for Quantitative and Qualitative Large Scale Acoustic Monitoring Using the Sensor Grid Approach}
 
 % Authors, for the paper (add full first names)
-\Author{F\'elix Gontier $^{1}$, Mathieu Lagrange $^{1}$, Pierre Aumond $^{2,3}$, Arnaud Can $^{2}$ and Catherine Lavandier $^{3}$}
+\Author{\hl{F\'elix Gontier} $^{1}$, Mathieu Lagrange $^{1,}$\hl{*}, Pierre Aumond $^{2,3}$, Arnaud Can $^{2}$ and Catherine Lavandier $^{3}$}%Please carefully check the accuracy of names and affiliations.
+Changes will not be possible after proofreading.
+and  ``*'' is newly added, please confirm.
+%R:confirmed that M.L.
+is the corresponding author
 
@@
 \address{%
-$^{1}$ \quad LS2N\\
-$^{2}$ \quad IFSTTAR, AME, LAE\\
-$^{3}$ \quad ETIS, UMR 8051, Universit\'e Paris Seine, Universit\'e Cergy-Pontoise, ENSEA, CNRS, F-95000 Cergy-Pontoise.}
+$^{1}$ \quad \hl{LS2N}\fg{, UMR 6004, CNRS, \'Ecole Centrale de Nantes, 44300 Nantes}, France; felix.gontier@ls2n.fr\\%please add the complete location and add it's zip code. %R: done
+$^{2}$ \quad \hl{IFSTTAR, AME, LAE}\fg{, 44340 Bouguenais, France}; pierre.aumond@ifsttar.fr (P.A.); arnaud.can@ifsttar.fr (A.C.)\\%please add the complete location and add it's zip code. %R: done
+$^{3}$ \quad \hl{ETIS, UMR 8051}%please add the complete location and add it's zip code. 
+, Universit\'e Paris Seine, Universit\'e de Cergy-Pontoise, ENSEA, CNRS, F-95000 \hl{Cergy-Pontoise}; %please add the city. %R: done
+ catherine.lavandier@u-cergy.fr}
 
@@
 % Abstract (Do not use inserted blank lines, i.e. \\)
-\abstract{The spreading of urban areas and the growth of human population worldwide raised societal and environmental concerns.
-To better address those, the monitoring of the acoustic environment in urban but also rural or wilderness areas is an important matter.
-Fostering on the recent development of low cost hardware acoustic sensors, we propose in this paper to consider a sensor grid approach to tackle this issue.
-In this kind of approach, the crucial question is the nature of the data that is transmitted from the sensors to the processing and archival servers.
-To this end, we propose an efficient audio coding scheme based on third octave band spectral representation that allows 1) the estimation of standard acoustic indicators and 2) the recognition of acoustic events at state-of-the-art performance rate.
+\abstract{The spreading of urban areas and the growth of human population worldwide \highlight{raise} societal and environmental concerns.
+To better address \highlight{these concerns}, the monitoring of the acoustic environment in urban \highlight{as well as} rural or wilderness areas is an important matter.
+\highlight{Building} on the recent development of low cost hardware acoustic sensors, we propose in this paper to consider a sensor grid approach to tackle this issue.
+In this kind of approach, the crucial question is the nature of the data that \highlight{are} transmitted from the sensors to the processing and archival servers.
+To this end, we propose an efficient audio coding scheme based on third octave band spectral representation that \highlight{allows:} (1) the estimation of standard acoustic \highlight{indicators;} and (2) the recognition of acoustic events at state-of-the-art performance rate.
 The former is useful to provide quantitative information about the acoustic environment, while the latter is useful to gather qualitative information and build perceptually motivated indicators using for example the emergence of a given sound source.
-The coding scheme is also demonstrated to transmit spectrally encoded data that, reverted to the time domain using state-of-the-art techniques, is not intelligible, thus protecting the privacy of citizens.}
+The coding scheme is also demonstrated to transmit spectrally encoded data that, reverted to the time domain using state-of-the-art techniques, \highlight{are} not intelligible, thus protecting the privacy of citizens.}
 
@@
 
-The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the SONYC\footnote{\url{htttp://wp.nyu.edu/sonyc}} \cite{mydlarz2017implementation} and CENSE\footnote{\url{htttp://cense.ifsttar.fr}} \cite{picault2017} projects.
-To do so, considering the so-called "sensor grid" approach  \cite{lim2005sensor,tham2005sensorgrid} has several advantages.
-The sensor grid approach puts the focus on a) a distributed system of data acquisition with a large set of sensors, b) the production and storage of a large dataset, and c) its availability for intensive and open data analysis computation.
+The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the \hl{SONYC} ({\url{htttp://wp.nyu.edu/sonyc}}) \cite{mydlarz2017implementation} and %Footnote are not allowed, pls conrfim.
+%R: ok
+ \hl{CENSE} ({\url{htttp://cense.ifsttar.fr}}) \cite{picault2017} projects.
+To do so, considering the so-called ``sensor grid'' approach  \cite{lim2005sensor,tham2005sensorgrid} has several advantages.
+The sensor grid approach puts the focus \highlight{on:} (a) a distributed system of data acquisition with a large set of sensors; (b) the production and storage of a large dataset; and (c) its availability for intensive and open data analysis computation.
 
-In such approach, the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, \textit{i.e.} the approach shall be scalable.
-Second, the nodes shall be energy efficient, ideally autonomous, in order to ease the deployment of the sensor grid to the desired topology.
+In such approach, the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, i.e., the approach shall be scalable.
+Second, the nodes shall be energy efficient, \highlight{and,  ideally,} autonomous, \highlight{to} ease the deployment of the sensor grid to the desired topology.
 Third, the encoding scheme used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to guarantee the privacy of the citizens.
-At the same time, the data stored shall remain as rich as possible while maintaining a low bitrate for efficient transmission and storage.
+At the same time, the data stored shall remain as rich as \highlight{possible,} while maintaining a low bitrate for efficient transmission and storage.
 
-In the case of urban acoustic monitoring, the data of interest typically consists of standardized high-quality measurements of energetic indicators such as the equivalent sound level $L_{eq}$ in dB SPL or its A-weighted counterpart $L_{Aeq}$ in dBA.
+In the case of urban acoustic monitoring, the data of interest typically \highlight{consist} of standardized high-quality measurements of energetic indicators such as the equivalent sound level $L_{eq}$ in dB SPL or its A-weighted counterpart $L_{Aeq}$ in dBA.
 However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe urban sound environments \cite{rychtarikova2013}.
@@
 
-In addition, considering sound sources allows to better assess the human perception of the urban sound environment in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017modeling}.
-For instance, a bird song and traffic noise with the same energy are perceived very differently.
+In addition, considering sound sources allows \highlight{better assessing} the human perception of the urban sound environment in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017}.
+For instance, \highlight{bird song} and traffic noise with the same energy are perceived very differently.
 Most acoustic indicators used in current sound maps describe the global sound environment and lack information on its composition.
-The recognition and the estimation of the level of contribution of sources of interest is thus of great importance to fully model the studied acoustic environments, see for example \cite{alsina2016design, app7020146, gloaguen2016estimating}.
+The recognition and the estimation of the level of contribution of sources of interest is thus of great importance to fully model the studied acoustic environments\highlight{ (see for example \cite{alsina2016design, app7020146, gloaguen2016estimating})}.
 Other indicators have been found to correlate with specific sound environment content \cite{aumond2017} but do not achieve the level of performances of a well-designed source detection scheme in characterizing acoustic environments.
-This source detection step can respectively be operated online (on the sensors) or offline (on the data servers) leading to different grid designs (Figure \ref{fig:codingScheme}).
+This source detection step can\highlight{ be} operated online (on the sensors) or offline \highlight{(on the data servers),} leading to different grid designs (Figure \ref{fig:codingScheme}).
 
@@
 This approach is thus currently considered in several applications in the literature \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
-Though, it requires the availability of decent computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware does not allow them to be autonomous using power sources like solar panels.
+\highlight{However}, it requires the availability of decent computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware does not allow them to be autonomous using power sources like solar panels.
 Furthermore, the detection is done once and cannot be recomputed during offline posterior analyses.
@@
 Indeed, the audio signal is not mandatory for the computation of the acoustic indicators and the features needed for event recognition.
-Also, as the data is transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to guarantee the privacy of the citizens.
+\highlight{In addition, as the data are} transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to guarantee the privacy of the citizens.
 
-The analysis of sources within a sound environment is generally linked with spectral content \cite{ishiyama2000} and high temporal resolutions while acoustic indicators focus on more scarce but highly accurate measurements.
+The analysis of sources within a sound environment is generally linked with spectral content~\cite{ishiyama2000} and high temporal resolutions while acoustic indicators focus on more scarce but highly accurate measurements.
 We thus present in this paper an audio coding scheme specifically tailored for use in a sensor grid (case C of Figure \ref{fig:codingScheme}).
@@
 We report equivalent performance of several state-of-the-art classification models from features computed using raw audio data and encoded data at production level rates.
-Finally, according to a perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring citizen privacy.
+Finally, according to a perceptual evaluation, the proposed coding scheme very strongly degrades the intelligibility, thus ensuring\mbox{ citizen privacy.}
 
-In order to promote reproducible research, the coder as well as the experiments needed to generate the figures is available to the research community\footnote{\url{https://github.com/felixgontier/cense-coder}}.
-The remaining of the paper is organized as follows: Section \ref{sec:coder} describes the proposed encoding scheme.
-The experimental protocol designed to validate the proposed approach is described in Section \ref{sec:protocol} and results are discussed in Section \ref{sec:results}.
+\highlight{To} promote reproducible research, the coder as well as the experiments needed to generate the figures is available to the research \hl{community} ({\url{https://github.com/felixgontier/cense-coder}}).
+The remaining of the paper is organized as follows: Section \ref{sec:coder} describes the proposed encoding \highlight{scheme;} the experimental protocol designed to validate the proposed approach is described in \highlight{Section \ref{sec:protocol};} and results are discussed in Section \ref{sec:results}.
 
-\begin{figure}[h]
+\begin{figure}[H]
 \centering
-\includegraphics[width=0.5\textwidth]{figures/censeCoder}
-\caption{Three alternative implementations of the sensor grid approach for the monitoring of the acoustic environment.
-In A) the raw audio is transmitted, in B) only the detected events, and in C) a compressed spectral representation.
+\includegraphics[width=0.7\textwidth]{figures/censeCoder}
+\caption{Three alternative implementations of the sensor grid approach for the monitoring of the acoustic \highlight{environment:} in (\textbf{A}) the raw audio is transmitted; in (\textbf{B}) only the detected events; and in (\textbf{C}) a compressed spectral representation.
 Thickness of arrows indicates bandwidth and thickness of boxes indicates the level of computation or storage required.}
@@
 
-\section{Proposed encoding scheme} \label{sec:coder}
+\section{Proposed Encoding Scheme} \label{sec:coder}
+\vspace{-6pt}
 
-\subsection{Data representation}
+\subsection{Data Representation}
 
-The identification of sources from audio streams has been the subject of extensive research in the past for speech data \cite{anusuya2009}, music data \cite{tzanetakis2002}, and lately environmental data in which the current work falls.
-Studied classification methods are diverse, ranging from time-dependant modeling with hidden Markov models \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}.
+The identification of sources from audio streams has been the subject of extensive research in the past for speech data \cite{anusuya2009}, music data \cite{tzanetakis2002}, and lately environmental \highlight{data,} in which the current work falls.
+Studied classification methods are diverse, ranging from time-dependant modeling with hidden Markov models \cite{ntalampiras2014} to ``bag-of-frames'' approaches \cite{aucouturier2007, foggia2015}.
 Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, Gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}.
-Also, several type of features are considered to feed those classifiers.
+\highlight{In addition}, several type of features are considered to feed those classifiers.
 The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal.
@@
 Features can also be computed in other domains to better model signal properties.
-For instance, \cite{cai2006} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domain features.
+\mbox{For \highlight{instance,} \fg{Cai et al.} \cite{cai2006}} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domain features.
 Alternative data representations such as the scattering transform \cite{bauge2013} show good results in environmental sound classification tasks \cite{salamon2015}.
-Another promising solution is feature engineering via unsupervised learning, which \cite{salamon2015-2} implements with a clustering technique.
-More complex systems using multiple-domain data representation as well as unsupervised models have been found to handle unrestricted environments suche as urban acoustic scenes efficiently \citep{ntalampiras2012}.
-A more detailed review of used methods is available in \cite{chachada2013}.
+Another promising solution is feature engineering via unsupervised learning, \highlight{which} \fg{Salamon et al.} \cite{salamon2015-2} implements with a clustering technique.
+More complex systems using multiple-domain data representation as well as unsupervised models have been found to handle unrestricted environments such as urban acoustic scenes \mbox{efficiently \citep{ntalampiras2012}.
+}A~more detailed review of used methods is available in \cite{chachada2013}.
+%NOTE: Please add author names so that references are not subjects: "Smith et al. [ref] add..."
 
@@
 
-We therefore consider the calculation of spectral energetic indicators such as the 31 third-octave bands within the human audition range 20~Hz - 20~kHz.
-"Fast" measurements of third-octave bands with an integration time of 125~ms are preferred to suit the temporal resolution needs of AED schemes, although "slow", 1~s measurements are also considered to further study the effect on our application's constraints.
+We therefore consider the calculation of spectral energetic indicators such as the 31 third-octave bands within the human audition range 20~Hz--20~kHz.
+``Fast'' measurements of third-octave bands with an integration time of 125~ms are preferred to suit the temporal resolution needs of AED schemes, although ``slow'', 1~s measurements are also considered to further study the effect on our \mbox{application's constraints.}
 
-\subsection{Signal analysis}
+\subsection{Signal Analysis}
 
 A common way to implement third-octave analysis is to first design the highest octave three filters, and use them on progressively time-decimated versions of the input signal \cite{davis1986}.
-\cite{antoni2010} presents an alternative analysis method based on direct frequency weighting, which yields a lower computational complexity as opposed to time filtering.
+\fg{Antoni} %newly added information, please confirm.
+ \cite{antoni2010} \highlight{presents} an alternative analysis method based on direct frequency weighting, which yields a lower computational complexity as opposed to time filtering.
 The weights matrix design procedure complies with both ANSI S1.1-1986 \cite{citeulike:9580295} and IEC 61260-1:2014 \cite{iec-norm} standards.
 It also meets the partition of unity principle over all frequency bins in the relevant range.
-Resulting filters for different parameter $l$ values are compared with Couvreur's implementation \cite{couvreur} with $2^{nd}$ order Butterworth time-domain filters, as shown in Figure~\ref{fig:freq_filt}.
-The major difference is that gains at cutoff frequencies are fixed at the optimal -3dB value by design.\\
+Resulting filters for different parameter $l$ values are compared with Couvreur's implementation \cite{couvreur} with 2nd order Butterworth time-domain filters, as shown in Figure~\ref{fig:freq_filt}.
+The major difference is that gains at cutoff frequencies are fixed at the optimal $-3$~dB value by design.
+\vspace{-6pt}
 
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
-		\includegraphics[width=0.8\textwidth]{figures/tob_imp.eps}
-	\caption{Comparison of Couvreur's and Antoni's implementations of third-octave filters. Frequency-weighting allows for arbitrary transfer functions and thus more accurate gains as standards impose.}
+		\includegraphics[width=0.7\textwidth]{figures/tob_imp.eps}
+	\caption{Comparison of Couvreur's and Antoni's implementations of third-octave filters.
+Frequency- weighting allows for arbitrary transfer functions and thus more accurate gains {as standards impose.}}
 	\label{fig:freq_filt}
@@
 The first step is to represent the signal in the frequency domain using a short-term Fourier transform (STFT).
-The continuously sampled audio is segmented into either 125~ms or 1~s frames to provide "fast" or "slow" acoustic measurements.
-The data is zero-padded to the next power of two to improve computational efficiency.
-The other parameters such as windowing functions and frame overlap are dependant on the specific constraints, and discussed in section \ref{sec:protocol}.
+The continuously sampled audio is segmented into either 125~ms or 1~s frames to provide ``fast'' or ``slow'' acoustic measurements.
+The data \highlight{are} zero-padded to the next power of two to improve computational efficiency.
+The other parameters such as windowing functions and frame overlap are dependant on the specific constraints, and discussed in Section \ref{sec:protocol}.
 The phase is discarded as it is not meaningful for third-octave analysis.
 Similarly, negative frequency components contain the same information as positive ones because the input signal is real.
-We then compute third-octave bands from the squared spectral magnitude by matrix multiplication with the frequency weights proposed in \cite{antoni2010} for $l = 2$ \footnote{When implementing said method, we found that squaring the $\phi_l(p), l \geq 1$ intermediate function (p.
-887) was the correct approach to meet cutoff frequencies requirements, and we believe this was the author's original intention.}.
-We include analysis for bands $i$ from -17 to 13, ie.
-center frequencies $f_i$ ranging from $20~Hz$ to $20~kHz$ with $f_0 = 1~kHz$.
+We then compute third-octave bands from the squared spectral magnitude by matrix multiplication with the frequency weights proposed in~\cite{antoni2010} for $l = 2$ ({\highlight{when} implementing said method, we found that squaring the $\phi_l(p), l \geq 1$ intermediate function (p.
+887) was the correct approach to meet cutoff frequencies requirements, and we believe this was the author's original \highlight{intention).}} We include analysis for bands $i$ from $-17$ to 13, i.e., center frequencies $f_i$ ranging from $20$~Hz to $20$~kHz with $f_0 = 1$~kHz.
 The representation is thus composed of 31 values.
@@
 A Huffman coding scheme \cite{huffman1952} is an efficient method to further reduce data rate while keeping the underlying information.
-At this point of the processing chain, the data takes the form of a spectrogram with amplitude values represented on an arbitrary data type.
+At this point of the processing chain, the data \highlight{take} the form of a spectrogram with amplitude values represented on an arbitrary data type.
 It is therefore assimilable to a discrete distribution.
@@
 The efficiency of the coding step thus directly depends on the entropy of the transmitted data.
-It is defined as $H = -\sum\limits_i p_ilog_n(p_i)$, where $p_i$ is the probability of appearance of a given symbol $i$ and $n$ the numerical base in which the output code is represented.
+It~is defined as $H = -\sum\limits_i p_ilog_n(p_i)$, where $p_i$ is the probability of appearance of a given symbol $i$ and $n$ \highlight{is} the numerical base in which the output code is represented.
 A lower entropy can be obtained with two factors.
-First, the dictionary size \textit{i.e.} the number of symbols must be kept low.
+First, the dictionary \highlight{size,} i.e., the number of symbols must be kept low.
 This implies performing a quantization on the data resulting in a loss of precision.
@@
 
-Considering an estimated PDF for our data as shown in Figure~\ref{fig:pdf} (top-left), immediately applying a linear quantization is clearly suboptimal, as the data mostly consists of very low values and a direct quantization results in most of the information being lost.
+Considering an estimated PDF for our \highlight{data,} as shown in Figure~\ref{fig:pdf} (top-left), immediately applying a linear quantization is clearly suboptimal, as the data mostly \highlight{consist} of very low values and a direct quantization results in most of the information being lost.
 We therefore flatten the PDF by taking the logarithm of the representation (top-right).
@@
 This effectively concentrates higher probabilities on symbols around zero (Figure~\ref{fig:pdf} bottom-right), yielding a higher amount of symbols at $2^q-1$ but nevertheless a smaller entropy.
-In the example shown here, the entropy before $\Delta$-compression is $H_{log} = 6.24~sh$ which is reduced to $H_{\Delta} = 3.54~sh$.
+In~the example shown here, the entropy before $\Delta$-compression is $H_{log} = 6.24~sh$ which is reduced to $H_{\Delta} = 3.54~sh$.
+\vspace{-6pt}
+
+\begin{figure}[H]
+	\centering
+		\includegraphics[width=0.78\textwidth]{figures/pdf.eps}
+	\caption{Example of estimated probability density functions of the data throughout the encoding step.
+Unchanged output of the representation step (\textbf{top}-\textbf{left}), concentrated towards very low values.
+PDF ``flattening'' effect induced by logarithm application (\textbf{top}-\textbf{right}).
+\highlight{Here,} values are mapped to the range $[0, 2^7-1] (q=8)$ and rounded to perform quantization (\textbf{bottom}-\textbf{left}).
+Output of the $\Delta$ compression  (\textbf{bottom}-\textbf{right}), with desirable probabilities as the input to a Huffman algorithm.}
+	\label{fig:pdf}
+\end{figure}
 
@@
 A frame-specific dictionary only contains the symbols found in a given data packet, while a fixed dictionary must contain every possible symbol as it does not depend on the present data.
-The output bitrate is found to be close for both methods, as sending an optimal local dictionary balances the suboptimality of globally generated symbol-code pairs.\\
+The output bitrate is found to be close for both methods, as sending an optimal local dictionary balances the suboptimality of globally generated symbol-code pairs.
 
-\begin{figure}[htbp]
+The decoding process is quite straightforward, as both Huffman and $\Delta$ compressions are lossless and directly invertible. The entire coder scheme is summarized in Figure~\ref{fig:scheme}.
+\vspace{-12pt}
+
+\begin{figure}[H]
 	\centering
-		\includegraphics[width=0.8\textwidth]{figures/pdf.eps}
-	\caption{Example of estimated probability density functions of the data throughout the encoding step.
-Unchanged output of the representation step (top-left), concentrated towards very low values.
-PDF "flattening" effect induced by logarithm application (top-right).
-Here values are mapped to the range $[0, 2^7-1] (q=8)$ and rounded to perform quantization (bottom-left).
-Output of the $\Delta$ compression (bottom-right), with desirable probabilities as the input to a Huffman algorithm.}
-	\label{fig:pdf}
+		\includegraphics[width=0.65\textwidth]{figures/dict_comp.eps}
+	\caption{Performance comparison of locally and globally generated Huffman dictionaries.
+(\textbf{top}) The mean execution time ratio favors the use of frame-specific dictionaries for tested texture frame lengths.
+(\textbf{bottom}) The mean output bitrate is close for both algorithms, showing that the necessity of sending symbol-code pairs mostly compensates for their optimality.}
+	\label{fig:dict_comp}
+\end{figure}
+\unskip
+\begin{figure}[H]
+	\centering
+		\includegraphics[width=0.85\textwidth]{figures/scheme.pdf}
+	\caption{Overview of the encoding process.}
+	\label{fig:scheme}
 \end{figure}
 
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=0.8\textwidth]{figures/dict_comp.eps}
-	\caption{Performance comparison of locally and globally generated Huffman dictionaries.
-(top) The mean execution time ratio favors the use of frame-specific dictionaries for tested texture frame lengths.
-(bottom) The mean output bitrate is close for both algorithms, showing that the necessity of sending symbol-code pairs mostly compensates for their optimality.}
-	\label{fig:dict_comp}
-\end{figure}
-
-The decoding process is quite straightforward, as both Huffman and $\Delta$ compressions are lossless and directly invertible. The entire coder scheme is summarized in Figure~\ref{fig:scheme}.
-
-\begin{figure*}[htbp]
-	\centering
-		\includegraphics[width=.9\textwidth]{figures/scheme.pdf}
-	\caption{Overview of the encoding process.}
-	\label{fig:scheme}
-\end{figure*}
-
-\section{Validation protocol} \label{sec:protocol}
+\section{Validation Protocol} \label{sec:protocol}
 
 A set of metrics is computed to assess the efficiency of the proposed coder scheme and to determine the impact of the degrees of freedom given by the parameters of the proposed algorithm.
-Those parameters are as follow: 1) the desired word size prior to Huffman encoding, set by quantization for both signal representation choices, 2) the number of considered bands, and 3) the STFT parameters including frame duration, overlap and windowing function usage.
+Those parameters are as follow: (1) the desired word size prior to Huffman encoding, set by quantization for both signal representation choices; (2) the number of considered bands; and (3) the STFT parameters including frame duration, overlap and windowing function usage.
 This section details experimental protocols for the validation of bitrate, measurement error, audio event recognition and intelligibility developped to best suit the corresponding constraints.
@@
 
-In order to assess the quality of the propoposed scheme's spectral measurement precision, we compare it to a known reference: the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017}.
-This toolbox's implementation shows less than $0.1~dB$ error on all bands when compared to a class 1 sound level meter software on 2~s third-octave bands measurements.
-We study both "fast" computation with 125~ms windows and "slow" 1~s analysis to assess the impact of time integration.
+\highlight{To} assess the quality of the propoposed scheme's spectral measurement precision, we compare it to a known reference: the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017}.
+This toolbox's implementation shows less than $0.1$~dB error on all bands when compared to a class 1 sound level meter software on 2~s third-octave bands measurements.
+We study both ``fast'' computation with 125~ms windows and ``slow'' 1~s analysis to assess the impact of time integration.
 Third-octave bands are computed using the proposed method as well as the \textit{ita\_toolbox} in the same experimental conditions, then averaged over time and compared to the toolbox's measurements on longer 2~s extracts.
@@
 As the analysis frames are of short duration, poor frequency resolution and spectral leakage are expected when performing the STFT, particularly in the lower frequencies bands.
-For this reason we evaluate the impact of windowing functions on each band measurement error in order to potentially mitigate this loss of precision.
+For this \highlight{reason,} we evaluate the impact of windowing functions on each band measurement error in order to potentially mitigate this loss of precision.
 
-To provide relevant statistics, these quantities are estimated with data from the 4500 audio recordings of the UrbanSound8k dataset \cite{salamon2014} described in the next section and 4500 \textit{iid.} Gaussian noise sequences.
+To provide relevant statistics, these quantities are estimated with data from the 4500 audio recordings of the UrbanSound8k dataset \cite{salamon2014} described in the next section and 4500 \textit{iid.} Gaussian \mbox{noise sequences.}
 
-\subsection{Preserving event recognition performance at low bitrate} \label{sec:event_p}
+\subsection{Preserving Event Recognition Performance at Low Bitrate} \label{sec:event_p}
 
-In order to ensure that the proposed scheme allows the recognition of events using state-of-the-art methods, we consider the results achieved by several recognition systems on the UrbanSound8k dataset\cite{salamon2014}.
-It features about 9 hours of urban environmental sounds recordings separated in 8732 audio files ranging from 1 to 4 seconds each.
-The recordings are labeled in 10 classes (air conditioner, car horn, children playing, dog bark, drilling, engine idling, gun shot, jackhammer, siren, street music), and distributed in 10 independent folds.
+\highlight{To} ensure that the proposed scheme allows the recognition of events using state-of-the-art methods, we consider the results achieved by several recognition systems on the UrbanSound8k dataset~\cite{salamon2014}.
+It features about 9 h of urban environmental sounds recordings separated in 8732 audio files ranging from 1 to 4 s each.
+The recordings are labeled in 10 classes (air conditioner, car horn, children playing, dog bark, drilling, engine idling, gun shot, jackhammer, siren,\highlight{ and} street music), and distributed in 10 independent folds.
 A method and baseline results are also provided for the classification task.
@@
 The aim of this experiment is two-fold: to evaluate the global loss of information induced by the coding process, and to evaluate the adequacy of third-octave bands indicators for classification.
-As studying the best performing classical models \citep{ntalampiras2013}, deep learning approaches \citep{salamon2017} or unsupervised feature learning is beyond the scope of this paper, we choose to replicate the baseline models and results proposed in \cite{salamon2014}.
+As~studying the best performing classical \hl{models} \citep{ntalampiras2013}, %Reference [49] is cited after [47] directly, which is out of order.
+Please confirm.
+deep learning approaches \citep{salamon2017} or unsupervised feature learning is beyond the scope of this paper, we choose to replicate the baseline models and results proposed in \cite{salamon2014}.
 
@@
 The feature vector is thus comprised of 275 values to reproduce available results and compare with the data produced by the proposed coding scheme.
-Models are trained for each setup using the 10-fold cross validation method provided by the authors of \cite{salamon2014}, that is, every combination of testing one fold on models trained with the other nine.
+Models are trained for each setup using the 10-fold cross validation method provided by the authors \mbox{of \cite{salamon2014},} that is, every combination of testing one fold on models trained with the other nine.
 A summary of the considered classification process is shown in Figure~\ref{fig:class_flwc}.
 
-\begin{figure*}[t]
+\begin{figure}[H]
 	\centering
-		\includegraphics[width=.9\textwidth]{figures/class.pdf}
+		\includegraphics[width=0.8\textwidth]{figures/class.pdf}
 	\caption{Classification process flowchart.
 Here third-octave bands are obtained by reversing the operations in Section~\ref{sec:dataenc} and cepstral coefficients are computed before training the model.
-Cross-validation is achieved by independantly training and testing the models with each of the 10 combination of a 90\%-10\% training-validation dataset separation.}
+Cross-validation is achieved by independantly training and testing the models with each of the 10 combinations of a 90--\hl{10}\% training\highlight{--}validation dataset separation.}% changed from ``10'' to ``100'', please confirm.
+%NOTE: 90%/10%?
+%R: 90% of the dataset used for training, the remaining 10% for validation
 	\label{fig:class_flwc}
-\end{figure*}
+\end{figure}
 
@@
 
-It is important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data is transmitted over the network and potentially stored, the level of intelligibility of  speech utterances potentially captured in the decoded stream should be as low as possible.
+It is important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data \highlight{are} transmitted over the network and potentially stored, the level of intelligibility of  speech utterances potentially captured in the decoded stream should be as low as possible.
 Thus, intelligibility in decoded and reconstructed audio is also an important concern of this study.
@@
 The readers shall be aware that even recorded with a good quality, such recording remains a weak biometrical indicator \cite{boe2000forensic}.
-Still, even if the identity of the speaker cannot be asserted, one can attempt to transcribe the spoken utterances.
-As such, we believe that it is important to demonstrate that the proposed encoding scheme do not allow such thing.
+\highlight{However}, even if the identity of the speaker cannot be asserted, one can attempt to transcribe the spoken utterances.
+\highlight{Thus}, we believe that it is important to demonstrate that the proposed encoding scheme do not allow such thing.
 
-In order to decrease the intelligibility, several approaches can be considered.
+\highlight{To} decrease the intelligibility, several approaches can be considered.
 First, a speech versus non speech detector can be implemented on the sensor.
-If some speech is detected, the data is not transmitted.
-This approach is however prone to failure of the detector and will lead to unavailability of data during speech time periods which might compromise the relevance of some indicators.
+If some speech is detected, the data \highlight{are} not transmitted.
+This approach is however prone to failure of the detector and will lead to unavailability of data during speech time \highlight{periods,} which might compromise the relevance of some indicators.
 
 A second approach is to wisely choose the frame rate.
-Since a phoneme is about 100ms to 200ms long \cite{kuwabara1996acoustic} \cite{rosen1992temporal}, a frame rate lower than 4 Hz should therefore dramatically reduce intelligibility.
+Since a phoneme is about 100 ms to 200 ms long \cite{kuwabara1996acoustic,rosen1992temporal}, a frame rate lower than 4 Hz should therefore dramatically reduce intelligibility.
 
@@
 For the evaluation, a dataset of clean speech utterances recorded in studio conditions is used.
-The dataset is composed of 9 french sentences enunciated by 3 male and 3 female speakers.
-The sentences have a mean duration of $2~s$ and are composed of 5 to 12 words, averaging at 8.
-The 54 extracts are encoded using the proposed approach with 4 analysis frame rate parameters of respectively 50~Hz, 16~Hz, 8~Hz and 4~Hz leading to 216 audio excerpts being tested in total.
+The dataset is composed of \highlight{nine} french sentences enunciated by \highlight{three} male and \highlight{three} female speakers.
+The sentences have a mean duration of $2$~s and are composed of \highlight{5--12} words, averaging \highlight{eight words}.
+The 54 extracts are encoded using the proposed approach with \highlight{four} analysis frame rate parameters \highlight{of,  respectively,} 50~Hz, 16~Hz, 8~Hz and 4~Hz leading to 216 audio excerpts being tested in total.
 However, as the recording conditions are the same for all extracts the speaker identity is considered as a source of variability rather than as a necessary factor in the test statistics.
-As a result the objective is primarily to evaluate the 9 sentences with 4 encoding frame rates, \textit{i.e.} 36 parameters.
+As a \highlight{result,} the objective is primarily to evaluate the \highlight{nine} sentences with \highlight{four} encoding frame rates, i.e., 36 parameters.
 
@@
 Given these conditions a subjective score on the whole signal is used similarly to the OVRL score in \cite{itup835}.
-As decoding the transmitted audio induces a framing effect unevenly distorting the input utterance, a second metric is designed to assess the comprehension of words.
-For the perceptual test, 18 different sentences evenly distributed over the 4 frame rate parameters are selected for each subject.
-For each sentence the participant first listens to the extract and is then asked to transcribe the utterance and to rate the perceived intelligibility from 1 (not intelligible) to 5 (intelligible).
+As~decoding the transmitted audio induces a framing effect unevenly distorting the input utterance, a~second metric is designed to assess the comprehension of words.
+For the perceptual test, 18 different sentences evenly distributed over the \highlight{four} frame rate parameters are selected for each subject.
+For each \highlight{sentence,} the participant first listens to the extract and is then asked to transcribe the utterance and to rate the perceived intelligibility from 1 (not intelligible) to 5 (intelligible).
 The first metric is computed as the ratio of correctly transcribed words and will be referred as the intelligibility ratio (IR) in this paper.
@@
 
-12 subjects of age ranging from 17 to 60 which reported normal hearing participated to the listening test.
+\highlight{Twelve} subjects of age ranging from 17 to 60 which reported normal hearing participated to the listening test.
 The test was conducted using a Matlab interface displayed with a desktop computer and audio was played through \textit{Beyerdynamics DT 770} headphones.
 The output level was set by the experimenter at the same level for all subjects.
-The mean duration of the test was about 8 minutes.
+The mean duration of the test was about 8 min.
 
@@
 As a result the energy located at a specific frequency is impossible to recover and the best inverse approximation is to split the third-octave band's observed energy into all the corresponding frequency bins with the same proportions as during analysis.
-This leads to the phenomenon seen on Figure~\ref{fig:freq} where part of the energy of a frequency bin in the original signal is found in all other bins of the same band at reconstruction, in almost equal proportions.
-The signal phase is recovered with the Griffin \& Lim algorithm \cite{griffin1984} if analysis overlap is used and white noise spectrogram scaling if not.
+This leads to the phenomenon seen \highlight{in} Figure~\ref{fig:freq} where part of the energy of a frequency bin in the original signal is found in all other bins of the same band at reconstruction, in almost equal proportions.
+The signal phase is recovered with the \fg{Griffin--Lim} algorithm \cite{griffin1984} if analysis overlap is used and white noise spectrogram scaling if not.
 The time-domain signal is then retrieved using the overlap-add method.
 When using overlap to compute third-octave bands, framing effects produced by rectangular windowing are reduced by convoluting the signal with a Hann windowing function prior to inverse-STFT computation.
+%NOTE: Or "Griffin--Lim"? %R: Changed to "Griffin--Lim"
 
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
-		\includegraphics[width=0.5\textwidth]{figures/freq.png}
+		\includegraphics[width=0.6\textwidth]{figures/freq.png}
 	\caption{Third-octave bands analysis and approximate inverse transformation effects on energy location.
-Here a brighter gray indicates that part of the energy contained at the corresponding frequency of the original signal is transferred to the reconstructed signal at the indicated frequency.
+\highlight{Here,} a brighter gray indicates that part of the energy contained at the corresponding frequency of the original signal is transferred to the reconstructed signal at the indicated frequency.
 This process yields an important and heterogeneous loss in resolution, particularly at higher frequency points.}
@@
 \section{Results} \label{sec:results}
+\vspace{-6pt}
 
-\subsection{Coder efficiency} \label{sec:efficiency_r}
+\subsection{Coder Efficiency} \label{sec:efficiency_r}
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
-		\includegraphics[width=0.8\textwidth]{figures/bitrate_qall.eps}
-	\caption{Coder output bitrate as a function of quantization for third-octave and Mel bands with 8 frames per second.}
+		\includegraphics[width=0.6\textwidth]{figures/bitrate_qall.eps}
+	\caption{Coder output bitrate as a function of quantization for third-octave and Mel bands with 8~frames per second.}
 	\label{fig:bitrate_q}
@@
 A second set of parameters influences directly the time-frequency resolution of the analysis.
-By choosing a frame rate and number of bands, one can effectively control the size of the periodically transmitted data.
+By~choosing a frame rate and number of bands, one can effectively control the size of the periodically transmitted data.
 We evaluate the bitrate for 10 to 40 Mel bands and a frame rate from 2 to 10 per second, with fixed $q = 8$.
@@
 
-This experiment aims at an initial assessment of potential tradeoffs between bitrate and preservation of valuable information which will be further discussed in Section \ref{sec:event_r}.\\
+This experiment aims at an initial assessment of potential tradeoffs between bitrate and preservation of valuable information which will be further discussed in Section \ref{sec:event_r}.
 
@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.65\textwidth]{figures/err_m_n.eps}
+    \caption{Measurement error of third-octave bands over two-seconds white noise extracts, with rectangular window and no overlap.
+The analysis of short frames has an effect on energy estimation at low frequencies that is of lower importance as the frequency resolution increases.\label{fig:errormn}}
+\end{figure}
+
 To mitigate this phenomenon, the choice of the window function shall be studied further.
@@
 It results in important similarities.
-For fast measurements and a rectangular window (Figure~\ref{fig:errormu}a), a student t-test ($p<0.05$) shows that the errors are not significantly different between 125~Hz and 12~kHz bands.
+For fast measurements and a rectangular window (Figure~\ref{fig:errormu}a), a student \emph{t}-test ($p<0.05$) shows that the errors are not significantly different between 125~Hz and 12~kHz bands.
 For the lower frequency bands, the two methods yield different error distributions but of similar importance.
@@
 Again comparing the two computation methods shows a significant difference in the bands below 100~Hz only.
-A slow analysis results in statistically equivalent errors between the two methods apart from the very low frequencies: $p = 0.011$ with the rectangular window (Figure~\ref{fig:errormu}c), $p = 0.003$ at 20~Hz and $p = 0.021$ at 25~Hz for the Hann window and 66\% overlap (Figure~\ref{fig:errormu}d).\\
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.5\textwidth]{figures/err_m_n.eps}
-    \caption{Measurement error of third-octave bands over two-seconds white noise extracts, with rectangular window and no overlap.
-The analysis of short frames has an effect on energy estimation at low frequencies that is of lower importance as the frequency resolution increases.\label{fig:errormn}}
-\end{figure}
-
-\begin{figure*}[h!]
-    \centering
-    \begin{subfigure}[h]{0.45\textwidth}
-        \centering
-        \includegraphics[width=1\textwidth]{figures/err_m_u_f_r.eps}
-        \caption{Fast analysis, rectangular window, no overlap}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[h]{0.45\textwidth}
-        \centering
-        \includegraphics[width=1\textwidth]{figures/err_m_u_f_h.eps}
-        \caption{Fast analysis, Hann window, 66\% overlap}
-    \end{subfigure}
-	\begin{subfigure}[h]{0.45\textwidth}
-        \centering
-        \includegraphics[width=1\textwidth]{figures/err_m_u_s_r.eps}
-        \caption{Slow analysis, rectangular window, 50\% overlap}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[h]{0.45\textwidth}
-        \centering
-        \includegraphics[width=1\textwidth]{figures/err_m_u_s_h.eps}
-        \caption{Slow analysis, Hann window, 66\% overlap}
-    \end{subfigure}
-    \caption{Measurement error of third-octave bands over two-seconds environmental sounds recordings (US8k dataset).
-For most settings the FFT-based method yields similar errors compared to the time-domain filtering reference.
-\label{fig:errormu}}
-\end{figure*}
+A slow analysis results in statistically equivalent errors between the two methods apart from the very low frequencies: $p = 0.011$ with the rectangular window (Figure~\ref{fig:errormu}c), $p = 0.003$ at 20~Hz and $p = 0.021$ at 25~Hz for the Hann window and 66\% overlap (Figure~\ref{fig:errormu}d).
 
@@
 The only lossy operation applied is quantization, which is defined by an output word size $q$ in bits.
-However, it corresponds to the word size \textit{after} $\Delta$-compression, meaning that the data is in fact quantized on $2^{q-1}$ values.
+However, it corresponds to the word size \textit{after} $\Delta$-compression, meaning that the data \highlight{are} in fact quantized on $2^{q-1}$ values.
 Since these measurements are already expressed in dB, the error $\varepsilon$ is computed as:
@@
 \end{equation*}
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}[H]{0.47\textwidth}
+        \centering
+       \includegraphics[width=1\textwidth]{figures/err_m_u_f_r.eps}
+        \caption{Fast analysis, rectangular window, no overlap}
+    \end{subfigure}
+    \begin{subfigure}[H]{0.47\textwidth}
+        \centering
+        \includegraphics[width=1\textwidth]{figures/err_m_u_f_h.eps}
+        \caption{Fast analysis, Hann window, 66\% overlap}
+    \end{subfigure}
+	\begin{subfigure}[H]{0.47\textwidth}
+        \centering
+        \includegraphics[width=1\textwidth]{figures/err_m_u_s_r.eps}
+        \caption{Slow analysis, rectangular window, 50\% overlap}
+    \end{subfigure}
+    \begin{subfigure}[H]{0.475\textwidth}
+        \centering
+        \includegraphics[width=1\textwidth]{figures/err_m_u_s_h.eps}
+        \caption{Slow analysis, Hann window, 66\% overlap}
+    \end{subfigure}
+    \vspace{-10pt}
+    \caption{Measurement error of third-octave bands over two-seconds environmental sounds recordings (US8k dataset).
+For most \highlight{settings,} the FFT-based method yields similar errors compared to the time-domain filtering reference.
+\label{fig:errormu}}
+\end{figure}
+
 Figure~\ref{fig:error_q} shows an estimation of $\varepsilon$ as a function of $q$ for third-octave and Mel bands.
@@
 To better understand this phenomenon, let us model $x$ as a uniform distribution such as $x\sim \textit{U}\{0, \Delta_x\}$.
-While this is not exact it matches our objective when using a logarithm to flatten given PDFs.
+While this is not \highlight{exact,} it matches our objective when using a logarithm to flatten given PDFs.
 The error $\varepsilon$ will follow a uniform distribution $U\sim \{0, \frac{\Delta_x}{2\times (2^{q-1}-1)}\}$.
@@
 
-\begin{figure}[htbp]
+As $\Delta_x$ is sampled for each analysis frame in our implementation, the error has the same statistics across all bands.
+It is to be added to the measurement error discussed in the same section before comparing to the values specified in the IEC 61672-1:2013 \cite{iec-norm2} standard on class 1 and 2 sound \mbox{level meters.}
+
+\begin{figure}[H]
 	\centering
-		\includegraphics[width=0.5\textwidth]{figures/error_qall.eps}
+		\includegraphics[width=0.65\textwidth]{figures/error_qall.eps}
 	\caption{Measurement error induced by encoding for different quantization resolutions.}
@@
 
-As $\Delta_x$ is sampled for each analysis frame in our implementation, the error has the same statistics across all bands.
-It is to be added to the measurement error discussed in the same section before comparing to the values specified in the IEC 61672-1:2013 \cite{iec-norm2} standard on class 1 and 2 sound level meters.
-
-\subsection{Event recognition} \label{sec:event_r}
+\subsection{Event Recognition} \label{sec:event_r}
 
@@
 This experiment aims at finding ways to further reduce the encoded data size without strongly affecting detection performance.
-Results of the four presented classification methods \ref{sec:event_p} are provided for the sake of completeness.
+Results of the four presented classification methods (\hl{Section} \ref{sec:event_p}) are provided for the sake of completeness.% newly added information, please confirm.
+R:correct
 
-First, we observe the impact of quantization on classification accuracy.
-The models are trained on the most complete implemented representation to replicate the results of \citep{salamon2014}, ie.
-40 Mel bands, 23.2~ms, 50\% overlap analysis and no time averaging (85 frames per second).
-Figure~\ref{fig:class_mel_q} shows that equivalent accuracies are obtained for all considered values of the quantization parameter $q$ down to 5 bits.\\
+\textls[-5]{First, we observe the impact of quantization on classification accuracy.
+The models are trained on the most complete implemented representation to replicate the results of \citep{salamon2014}, i.e., 40 Mel bands, 23.2~ms, 50\% overlap analysis and no time averaging (85 frames per second).
+Figure~\ref{fig:class_mel_q} shows that equivalent accuracies are obtained for all considered values of the quantization parameter $q$ down to 5~bits.}
+The effect of changing the time-frequency resolution of the representation is presented in Table~\ref{T1}.
+In this table, equivalence of performance with respect to the best performing setting (in red) is depicted with a bold font evaluated using the following procedure.
+The null hypothesis that the subtraction of the two compared distribution (the distribution of the setting we consider minus the distribution of the best performing one) comes from a normal distribution with mean equal to zero and unknown variance is evaluated using the paired-sample \emph{t}-test at the 0.05 significance level.
+If the null hypothesis is not rejected, the setting is considered as equivalent in terms of performance to the best \mbox{performing one.}
 
-\begin{figure}[htbp]
+\begin{figure}[H]
 	\centering
-		\includegraphics[width=0.8\textwidth]{figures/class_mel_q.eps}
+		\includegraphics[width=0.65\textwidth]{figures/class_mel_q.eps}
 	\caption{Classification accuracy as a function of word size before encoding. The baseline plotted on the right is computed without quantizing the representation.}
@@
 
-The effect of changing the time-frequency resolution of the representation is presented in Table~\ref{T1}.
-In this table, equivalence of performance with respect to the best performing setting (in red) is depicted with a bold font evaluated using the following procedure.
-The null hypothesis that the subtraction of the two compared distribution (the distribution of the setting we consider minus the distribution of the best performing one) comes from a normal distribution with mean equal to zero and unknown variance is evaluated using the paired-sample t-test at the 0.05 significance level.
-If the null hypothesis is not rejected, the setting is considered as equivalent in terms of performance to the best performing one.
-
-Similarly to baseline results, the random forest and SVM classifiers are the best performing systems at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively.
+\textls[-5]{Similar\highlight{ to} baseline results, the random forest and SVM classifiers are the best performing systems at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively.
 However, we find that given our setup, reducing the number of analysis bands up to a given level often does not induce a severe drop of performance.
@@
 This means that we can effectively divide the data size by a factor of at most 10 without strongly affecting sound event recognition performance.
-It also provides us with a preliminary confirmation of the possibility for "fast", 8~Hz third-octave bands cepstra to match MFCC performances.\\
+It also provides us with a preliminary confirmation of the possibility for ``fast'', 8~Hz third-octave bands cepstra to match MFCC performances.\\}
 
-\begin{table*}[h]
+\begin{table}[H]
 \centering
-\caption{Classification accuracy in percentage for different models: SVMs (a), Random Forests (b), Decision Trees (c), and Nearest Neigbors (d) with respect to varying representation resolutions.
-Numbers in red indicate best performance and numbers in bold indicate that no statistically significant difference is found when comparing to the best performing setting ($p<.05$).}
+\tablesize{\footnotesize} 
+\caption{Classification accuracy in percentage for different models: SVMs (\textbf{a}); Random \mbox{Forests (\textbf{b});} Decision Trees (\textbf{c}); and Nearest Neigbors (\textbf{d}) with respect to varying representation resolutions.
+Numbers in red indicate best performance and numbers in bold indicate that no statistically significant difference is found when comparing to the best performing setting ($p<0.05$).}
 \label{T1}
-(a)\\
-\begin{tabular}{ll|c|c|c|c|c|c|c|}
-\cline{3-9}
-\multicolumn{2}{c}{\multirow{2}{*}{SVM}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
- & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9}
-\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} & 55$\pm$3 & 60$\pm$3 & 61$\pm$4 & 62$\pm$3 & 62$\pm$4 & \textbf{63$\pm$6} & \textbf{65$\pm$6} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & 58$\pm$4 & 62$\pm$4 & 63$\pm$4 & 64$\pm$4 & 63$\pm$4 & \textbf{65$\pm$5} & \textbf{67$\pm$6} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & 60$\pm$3 & 64$\pm$4 & 64$\pm$4 & \textbf{65$\pm$4} & \textbf{65$\pm$3} & \textbf{67$\pm$4} & \textbf{\textcolor{red}{68$\pm$4}} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & 60$\pm$3 & 63$\pm$4 & \textbf{64$\pm$4} & 64$\pm$4 & \textbf{64$\pm$4} & \textbf{66$\pm$4} & \textbf{68$\pm$5} \\ \cline{1-9}
-\end{tabular}
-\\(b)\\
-\begin{tabular}{ll|c|c|c|c|c|c|c|}
-\cline{3-9}
-\multicolumn{2}{c}{\multirow{2}{*}{RF-500}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
- & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9}
-\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} & 60$\pm$3 & 62$\pm$3 & 62$\pm$3 & 63$\pm$3 & 63$\pm$3 & \textbf{65$\pm$4} & \textbf{67$\pm$5} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & 61$\pm$4 & 63$\pm$3 & 64$\pm$3 & 64$\pm$3 & 64$\pm$4 & \textbf{66$\pm$6} & \textbf{69$\pm$6} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & 62$\pm$3 & 63$\pm$3 & 64$\pm$3 & 64$\pm$3 & 64$\pm$4 & \textbf{67$\pm$5} & \textbf{\textcolor{red}{69$\pm$6}} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & 62$\pm$4 & 63$\pm$4 & 63$\pm$4 & 64$\pm$4 & 63$\pm$4 & \textbf{67$\pm$6} & \textbf{68$\pm$6} \\ \cline{1-9}
-\end{tabular}
-\\(c)\\
-\begin{tabular}{ll|c|c|c|c|c|c|c|}
-\cline{3-9}
-\multicolumn{2}{c}{\multirow{2}{*}{DT}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
- & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9}
-\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} & 42$\pm$3 & \textbf{46$\pm$4} & 46$\pm$2 & 44$\pm$3 & 45$\pm$3 & \textbf{46$\pm$5} & \textbf{\textcolor{red}{49$\pm$3}} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & 43$\pm$5 & 43$\pm$3 & 43$\pm$2 & 44$\pm$3 & 45$\pm$3 & 45$\pm$5 & \textbf{47$\pm$5} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & 42$\pm$4 & 43$\pm$2 & 44$\pm$3 & 45$\pm$5 & 43$\pm$3 & 43$\pm$4 & \textbf{45$\pm$5} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & 42$\pm$6 & 43$\pm$3 & 43$\pm$3 & 42$\pm$3 & 44$\pm$3 & 46$\pm$3 & \textbf{46$\pm$4} \\ \cline{1-9}
-\end{tabular}
-\\(d)\\
-\begin{tabular}{ll|c|c|c|c|c|c|c|}
-\cline{3-9}
-\multicolumn{2}{c}{\multirow{2}{*}{KNN-5}} & \multicolumn{7}{|c|}{Frames per second}\\ \cline{3-9}
- & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ \cline{1-9}
-\multicolumn{1}{|c}{\multirow{4}{*}{Mel bands}}
- & \multicolumn{1}{|c|}{10} &43$\pm$2 & 51$\pm$4 & 53$\pm$4 & 53$\pm$5 & 53$\pm$4 & 54$\pm$4 & \textbf{56$\pm$3} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{20} & 44$\pm$3 & 52$\pm$4 & 53$\pm$3 & 54$\pm$4 & \textbf{54$\pm$4} & \textbf{55$\pm$4} & \textbf{\textcolor{red}{58$\pm$4}} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{30} & 45$\pm$4 & 54$\pm$5 & \textbf{55$\pm$5} & \textbf{55$\pm$4} & \textbf{55$\pm$4} & \textbf{56$\pm$4} & \textbf{56$\pm$4} \\ \cline{2-9}
-\multicolumn{1}{|c}{}
- & \multicolumn{1}{|c|}{40} & 46$\pm$3 & 53$\pm$5 & \textbf{55$\pm$5} & \textbf{55$\pm$4} & \textbf{55$\pm$5} & \textbf{57$\pm$4} & \textbf{57$\pm$3} \\ \cline{1-9}
+
+\begin{tabular}{ccccccccc}
+\toprule
+\multicolumn{9}{c}{(\textbf{a})}\\
+\midrule
+%\cline{3-9}
+\multicolumn{2}{c}{\multirow{2}{*}{SVM}} & \multicolumn{7}{c}{Frames per second}\\ 
+\cmidrule{2-9}
+
+ & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\ 
+\midrule
+\multicolumn{1}{c}{\multirow{4}{*}{Mel bands}}
+ & \multicolumn{1}{c}{10} & 55 $\pm$ 3 & 60 $\pm$ 3 & 61 $\pm$ 4 & 62 $\pm$ 3 & 62 $\pm$ 4 & \textbf{63 $\pm$ 6} & \textbf{65 $\pm$ 6} \\ 
+ %\cline{2-9}
+\multicolumn{1}{c}{}
+ & \multicolumn{1}{c}{20} & 58 $\pm$ 4 & 62 $\pm$ 4 & 63 $\pm$ 4 & 64 $\pm$ 4 & 63 $\pm$ 4 & \textbf{65 $\pm$ 5} & \textbf{67  $\pm$  6} \\ 
+ %\cline{2-9}
+\multicolumn{1}{c}{}
+ & \multicolumn{1}{c}{30} & 60 $\pm$ 3 & 64 $\pm$ 4 & 64 $\pm$ 4 & \textbf{65 $\pm$ 4} & \textbf{65 $\pm$ 3} & \textbf{67 $\pm$ 4} & \textbf{\textcolor{red}{68 $\pm$ 4}} \\ 
+ %\cline{2-9}
+\multicolumn{1}{c}{}
+ & \multicolumn{1}{c}{40} & 60 $\pm$ 3 & 63 $\pm$ 4 & \textbf{64 $\pm$ 4} & 64 $\pm$ 4 & \textbf{64 $\pm$ 4} & \textbf{66 $\pm$ 4} & \textbf{68 $\pm$ 5} \\
+
+\midrule
+
+\multicolumn{9}{c}{(\textbf{b})}\\
+\cmidrule{1-9}
+\multicolumn{2}{c}{\multirow{2}{*}{RF-500}} & \multicolumn{7}{c}{Frames per second}\\ 
+\cmidrule{2-9}
+
+ & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\
+
+\midrule
+
+\multicolumn{1}{c}{\multirow{4}{*}{Mel bands}}
+ & \multicolumn{1}{c}{10} & 60 $\pm$ 3 & 62 $\pm$ 3 & 62 $\pm$ 3 & 63 $\pm$ 3 & 63 $\pm$ 3 & \textbf{65 $\pm$ 4} & \textbf{67 $\pm$ 5} \\ 
+% \cline{2-9}
+\multicolumn{1}{c}{}
+ & \multicolumn{1}{c}{20} & 61 $\pm$ 4 & 63 $\pm$ 3 & 64 $\pm$ 3 & 64 $\pm$ 3 & 64 $\pm$ 4 & \textbf{66 $\pm$ 6} & \textbf{69 $\pm$ 6} \\ 
+% \cline{2-9}
+\multicolumn{1}{c}{}
+ & \multicolumn{1}{c}{30} & 62 $\pm$ 3 & 63 $\pm$ 3 & 64 $\pm$ 3 & 64 $\pm$ 3 & 64 $\pm$ 4 & \textbf{67 $\pm$ 5} & \textbf{\textcolor{red}{69 $\pm$ 6}} \\ 
+ %\cline{2-9}
+\multicolumn{1}{c}{}
+ & \multicolumn{1}{c}{40} & 62 $\pm$ 4 & 63 $\pm$ 4 & 63 $\pm$ 4 & 64 $\pm$ 4 & 63 $\pm$ 4 & \textbf{67 $\pm$ 6} & \textbf{68 $\pm$ 6} \\
+
+\midrule
+
+\multicolumn{9}{c}{(\textbf{c})}\\
+
+\midrule
+
+\multicolumn{2}{c}{\multirow{2}{*}{DT}} & \multicolumn{7}{c}{Frames per second}\\ 
+\cmidrule{2-9}
+ & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\
+
+\midrule
+
+\multicolumn{1}{c}{\multirow{4}{*}{Mel bands}}
+ & \multicolumn{1}{c}{10} & 42 $\pm$ 3 & \textbf{46 $\pm$ 4} & 46 $\pm$ 2 & 44 $\pm$ 3 & 45 $\pm$ 3 & \textbf{46 $\pm$ 5} & \textbf{\textcolor{red}{49 $\pm$ 3}} \\ 
+ %\cline{2-9}
+\multicolumn{1}{c}{}
+ & \multicolumn{1}{c}{20} & 43 $\pm$ 5 & 43 $\pm$ 3 & 43 $\pm$ 2 & 44 $\pm$ 3 & 45 $\pm$ 3 & 45 $\pm$ 5 & \textbf{47 $\pm$ 5} \\ 
+ %\cline{2-9}
+\multicolumn{1}{c}{}
+ & \multicolumn{1}{c}{30} & 42 $\pm$ 4 & 43 $\pm$ 2 & 44 $\pm$ 3 & 45 $\pm$ 5 & 43 $\pm$ 3 & 43 $\pm$ 4 & \textbf{45 $\pm$ 5} \\ 
+ %\cline{2-9}
+\multicolumn{1}{c}{}
+ & \multicolumn{1}{c}{40} & 42 $\pm$ 6 & 43 $\pm$ 3 & 43 $\pm$ 3 & 42 $\pm$ 3 & 44 $\pm$ 3 & 46 $\pm$ 3 & \textbf{46 $\pm$ 4} \\
+
+\midrule
+
+\multicolumn{9}{c}{(\textbf{d})}\\
+
+\cmidrule{1-9}
+
+\multicolumn{2}{c}{\multirow{2}{*}{KNN-5}} & \multicolumn{7}{c}{Frames per second}\\ 
+\cmidrule{2-9}
+ & & 2 & 4 (4.1) & 6 (6.1) & 8 (7.7) & 10 (9.5) & 20 (21) & 85 \\
+
+\midrule
+
+\multicolumn{1}{c}{\multirow{4}{*}{Mel bands}}
+ & \multicolumn{1}{c}{10} &43 $\pm$ 2 & 51 $\pm$ 4 & 53 $\pm$ 4 & 53 $\pm$ 5 & 53 $\pm$ 4 & 54 $\pm$ 4 & \textbf{56 $\pm$ 3} \\ 
+ %\cline{2-9}
+\multicolumn{1}{c}{}
+ & \multicolumn{1}{c}{20} & 44 $\pm$ 3 & 52 $\pm$ 4 & 53 $\pm$ 3 & 54 $\pm$ 4 & \textbf{54 $\pm$ 4} & \textbf{55 $\pm$ 4} & \textbf{\textcolor{red}{58 $\pm$ 4}} \\ 
+ %\cline{2-9}
+\multicolumn{1}{c}{}
+ & \multicolumn{1}{c}{30} & 45 $\pm$ 4 & 54 $\pm$ 5 & \textbf{55 $\pm$ 5} & \textbf{55 $\pm$ 4} & \textbf{55 $\pm$ 4} & \textbf{56 $\pm$ 4} & \textbf{56 $\pm$ 4} \\ 
+ %\cline{2-9}
+\multicolumn{1}{c}{}
+ & \multicolumn{1}{c}{40} & 46 $\pm$ 3 & 53 $\pm$ 5 & \textbf{55 $\pm$ 5} & \textbf{55 $\pm$ 4} & \textbf{55 $\pm$ 5} & \textbf{57 $\pm$ 4} & \textbf{57 $\pm$ 3} \\ 
+ %\cline{1-9}
+ \bottomrule
 \end{tabular}
 
-\end{table*}
+\end{table}
 
-\subsection{Third-octave bands as base descriptors} \label{sec:tob_r}
+\subsection{Third-Octave Bands as Base Descriptors} \label{sec:tob_r}
 
 We now compare the efficiency of third-octave bands at differenciating sound sources in urban acoustic environments to that of Mel spectrograms.
-Following the previous discussions, the classification task is run on corresponding cepstrum coefficients, computed with the following parameters: 125~ms analysis frames with rectangular windowing and no overlap are used to perform the STFT, and 31 third-octave bands (20~Hz - 20~kHz) are considered.
-Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps Mel spectrograms seen in Table~\ref{T1} for all classification schemes.\\
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=0.8\textwidth]{figures/class_tob_q.eps}
-	\caption{Classification accuracy with third-octave bands and varying word size.}
-	\label{fig:class_tob_q}
-\end{figure}
+Following the previous discussions, the classification task is run on corresponding cepstrum coefficients, computed with the following parameters: 125~ms analysis frames with rectangular windowing and no overlap are used to perform the STFT, and 31 third-octave bands (20~Hz--20~kHz) are considered.
+Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps Mel spectrograms seen in Table~\ref{T1} for all classification schemes.
 
 To further analyze both representations advantages, the confusion matrix is a reliable tool.
-It aims at providing information regarding class-by-class accuracy and misclassification rates.
+It~aims at providing information regarding class-by-class accuracy and misclassification rates.
 We thus compute these metrics for the SVM classifier, with predictions accumulated over the ten folds in test configuration.
@@
 
+\begin{figure}[H]
+	\centering
+		\includegraphics[width=0.65\textwidth]{figures/class_tob_q.eps}
+	\caption{Classification accuracy with third-octave bands and varying word size.}
+	\label{fig:class_tob_q}
+\end{figure}
+
 \subsection{Inintelligibility} \label{sec:inintelligibility_r}
 
-The perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/}} then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
+The perceptual test ({\hl{decoded speech utterances for various conditions can be listened to at} \url{https://felixgontier.github.io/cense-coder/}}) then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
 Given the test conditions presented in Section~\ref{sec:inintelligibility_p} and the number of subjects, the mean and standard deviation are computed on an average of 54 results per frame rate parameter: 12 subjects evaluating each analysis resolution 4.5 times on average.
@@
 A limit at about 10~Hz corresponding to a frame duration of 100~ms is observed, as the studied 8~Hz setting is found to be almost completely inintelligible as very few words are understood correctly at this rate.
-We assume that the correctly identified words are a result of coincidentally adequate frame timings, \textit{i.e.} analysis frames matching the precise location of phoneme utterances for a short duration.
-Similarly, framing effects induced by the proposed processing scheme yielded errors for higher frame rates transcriptions and a globally lower perceptual intelligibility.\\
-
-\begin{figure}[htbp]
+We assume that the correctly identified words are a result of coincidentally adequate frame timings, i.e., analysis frames matching the precise location of phoneme utterances for a short duration.
+Similarly, framing effects induced by the proposed processing scheme yielded errors for higher frame rates transcriptions and a globally lower perceptual intelligibility.
+\vspace{-6pt} 
+\begin{figure}[H]
 	\centering
-		\includegraphics[width=0.5\textwidth]{figures/subj_int.eps}
+		\includegraphics[width=0.6\textwidth]{figures/subj_int.eps}
 	\caption{Mean and standard deviation of the Normalized Average intellibility score (AIS) given by the subjects and the inteligibility ratio (IR) as a function of the frame rate.
@@
 
-\section{Conclusion}
+\section{Conclusions}
 
@@
 The proposed approach has the following benefits:
-\begin{itemize}
-	\item precision: the impact of the quantization step for 8 bits codewords is found to be very small (< 0.2dB) and thus:\\
-	- does not impact the quality of the acoustics indicators (Sections~\ref{sec:efficiency_p}, \ref{sec:efficiency_r}).\\
-	- enables the sound recognition with the same quality than directly from the spectrogram (Sections~\ref{sec:event_p}, \ref{sec:event_r} and \ref{sec:tob_r}).
-	\item efficiency: using the high precision parameters, the bitrate is about 1.4~kbps and 0.4~kbps for fast and slow modes respectively (Section~\ref{sec:efficiency_r}).
-	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible according to a perceputal test done using clean speech recorded at very low background level.
-Additionaly, the sensors being typically hanged at 4 meters high in a usually very noisy environment, we believe that the intelligibility risk of the proposed approach is negligible (Sections~\ref{sec:inintelligibility_p}, \ref{sec:inintelligibility_r}).
+\begin{itemize}[leftmargin=*,labelsep=5.5mm]
+	\item Precision: \highlight{The} impact of the quantization step for 8 bits codewords is found to be very small \highlight{(<~0.2 dB),} and thus:
+	\begin{itemize}[leftmargin=*,labelsep=5.6mm]
+	\item does not impact the quality of the acoustics indicators (Sections~\ref{sec:efficiency_p}  \highlight{ and \ref{sec:efficiency_r}); and}
+	\item enables sound event recognition with the same quality than directly from the spectrogram (Sections~\ref{sec:event_p}, \ref{sec:event_r} and \ref{sec:tob_r}).
 	\end{itemize}
-
+	\item Efficiency: \highlight{Using} the high precision parameters, the bitrate is about 1.4~kbps and 0.4~kbps for fast and slow modes respectively (Section~\ref{sec:efficiency_r}).
+	\item Privacy: \highlight{At} all operating modes, the reverted audio signal is found to be inintelligible according to a perceputal test done using clean speech recorded at very low background level.
+Additionaly, the sensors being typically hanged at 4 m high in a usually very noisy environment, we believe that the intelligibility risk of the proposed approach is negligible (Sections~\ref{sec:inintelligibility_p} and \ref{sec:inintelligibility_r}).
+\end{itemize}
+%NOTE: All capitalization
 The encoding scheme is designed to be easy to implement and to lead to an efficient data format for storage and sharing across the research community.
@@
 
-\section{Acknowlegments}
+\vspace{6pt} 
+\acknowledgments{The authors would like to acknowledge partial funding from the ANR under project reference ANR-16-CE22-0012 and to thank Christophe d'Alessandro for fruitful discussion on speech intelligibility.}
 
-The authors would like to acknowledge partial funding from the ANR under project reference ANR-16-CE22-0012 and to thank Christophe d'Alessandro for fruitful discussion on speech intelligibility.
+\authorcontributions{\hl{For research articles with several authors, }a short paragraph specifying their individual contributions must be provided.
+The following statements should be used “X.X.
+and Y.Y.
+conceived and designed the experiments; X.X.
+performed the experiments; X.X.
+and Y.Y.
+analyzed the data; W.W.
+contributed reagents/materials/analysis tools; Y.Y.
+wrote the paper.” Authorship must be limited to those who have contributed substantially to the work reported.}%Please add the main text in accordance with the template.
 
+\conflictsofinterest{\hl{The authors declare no conflict of interest}.}%Please disclose conflicts of interest, or add 'The authors declare no conflicts of interest'. %R: No conflicts of interest
 %=====================================
@@
 %\bibliography{your_external_BibTeX_file}
-\bibliography{biblio}
+\reftitle{References}
+\begin{thebibliography}{999}
+\providecommand{\natexlab}[1]{#1}
+
+\bibitem[Mydlarz et~al.(2017)Mydlarz, Salamon, and
+  Bello]{mydlarz2017implementation}
+Mydlarz, C.; Salamon, J.; Bello, J.
+\newblock The implementation of low-cost urban acoustic monitoring devices.
+\newblock {\em Appl.~Acoust.} {\bf 2017}, {\em 117},~207--218.
+
+\bibitem[Picaut et~al.(2017)Picaut, Can, Ardouin, Cr{\'e}peaux, Dhorne,
+  {\'E}coti{\`e}re, and Lagrange]{picault2017}
+Picaut, J.; Can, A.; Ardouin, J.; Cr{\'e}peaux, P.; Dhorne, T.;
+  {\'E}coti{\`e}re, D.; Lagrange, M.
+\newblock Characterization of urban sound environments using a comprehensive
+  approach combining open data, measurements, and modeling.
+\newblock   \emph{J. Acoust. Soc. Am. }  \textbf{2017}, \emph{141}, 3808.
+
+\bibitem[Lim et~al.(2005)Lim, Teo, Mukherjee, Lam, Wong, and
+  See]{lim2005sensor}
+Lim, H.; Teo, Y.; Mukherjee, P.; Lam, V.; Wong, W.; See, S.
+\newblock Sensor grid: Integration of wireless sensor networks and the grid.
+\newblock In Proceedings of the 2005 30th Anniversary IEEE Conference on Local Computer Networks, \hl{Sydney,  Australia, 17 November } 2005; pp. 91--99.
+ %please confirm if the added information is right. %R: Confirmed
+\bibitem[Tham and Buyya(2005)]{tham2005sensorgrid}
+Tham, C.K.; Buyya, R.
+\newblock SensorGrid: Integrating sensor networks and grid computing.
+\newblock {\em CSI Commun.} {\bf 2005}, {\em 29},~24--29.
+
+\bibitem[Rey~Gozalo et~al.(2015)Rey~Gozalo, Trujillo~Carmona,
+  Barrigon~Morillas, and Gomez~Escobar]{gozalo2015}
+Rey~Gozalo, G.; Trujillo~Carmona, J.; Barrigon~Morillas, J.; Gomez~Escobar, V.
+\newblock Relationship between objective acoustic indices and subjective
+  assessments for the quality of soundscapes.
+\newblock {\em Appl. Acoust.} {\bf 2015}, {\em 97},~1--10.
+
+\bibitem[Rychtarikova and Vermeir(2013)]{rychtarikova2013}
+Rychtarikova, M.; Vermeir, G.
+\newblock Soundscape categorization on the basis of objective acoustical
+  parameters.
+\newblock {\em Appl. Acoust.} {\bf 2013}, {\em 74},~240--247.
+
+\bibitem[Can et~al.(2016)Can, Aumond, Michel, De~Coensel, Ribeiro,
+  Botteldooren, and Lavandier]{can2016}
+Can, A.; Aumond, P.; Michel, S.; De~Coensel, B.; Ribeiro, C.; Botteldooren, D.;
+  Lavandier, C.
+\newblock Comparison of noise indicators in an urban context.
+\newblock  In Proceedings of the 45th International Congress and Exposition on Noise Control
+  Engineering, \hl{Hamburg, Germany, 21--24 August }2016; pp. 5678--5686.
+ %please confirm if the added information is right. %R: Confirmed
+\bibitem[Can and Gauvreau(2015)]{can2015}
+Can, A.; Gauvreau, B.
+\newblock Describing and classifying urban sound environments with a relevant
+  set of physical indicators.
+\newblock {\em J. Acoust. Soc. Am.} {\bf 2015}, {\em 137},~208--218.
+
+\bibitem[Brocolini et~al.(2013)Brocolini, Lavandier, Quoy, and
+  Ribeiro]{brocolini2013}
+Brocolini, L.; Lavandier, C.; Quoy, M.; Ribeiro, C.
+\newblock Measurements of acoustic environments for urban soundscapes: Choice
+  of homogeneous periods, optimization of durations, and selection of
+  indicators.
+\newblock {\em J.~Acoust. Soc. Am.} {\bf 2013}, {\em 134},~813--821.
+
+\bibitem[Nilsson et~al.(2007)Nilsson, Botteldooren, and
+  De~Coensel]{nilsson2007}
+Nilsson, M.; Botteldooren, D.; De~Coensel, B.
+\newblock Acoustic indicators of soundscape quality and noise annoyance in
+  outdoor urban areas.
+\newblock  In Proceedings of the 19th International Congress on Acoustics, \hl{Madrid, Spain, 2--7 September} 2007.
+%please confirm if the added information is right. %R: Confirmed
+\bibitem[Lavandier and Defr{\'e}ville(2006)]{lavandier2006contribution}
+Lavandier, C.; Defr{\'e}ville, B.
+\newblock The contribution of sound source characteristics in the assessment of
+  urban soundscapes.
+\newblock {\em Acta Acust. United Acust.} {\bf 2006}, {\em
+  92},~912--921.
+
+% ref 12 is the same as ref 16, please confirm. %R: Confirmed, deleted ref 12 and changed corresponding ref to 16
+\bibitem[Alsina-Pag{\`e}s et~al.(2016)Alsina-Pag{\`e}s, Hernandez-Jayo,
+  Al{\'\i}as, and Angulo]{alsina2016design}
+Alsina-Pag{\`e}s, R.; Hernandez-Jayo, U.; Al{\'\i}as, F.; Angulo, I.
+\newblock Design of a mobile low-cost sensor network using urban buses for
+  real-time ubiquitous noise monitoring.
+\newblock {\em Sensors} {\bf 2016}, {\em 17},~57.
+
+\bibitem[Alías and Socoró(2017)]{app7020146}
+Alías, F.; Socoró, J.
+\newblock Description of anomalous noise events for reliable dynamic traffic
+  noise mapping in real-life urban and suburban soundscapes.
+\newblock {\em Appl. Sci.} {\bf 2017}, {\em 7}, 146.
+
+\bibitem[Gloaguen et~al.(2016)Gloaguen, Can, Lagrange, and
+  Petiot]{gloaguen2016estimating}
+Gloaguen, J.R.; Can, A.; Lagrange, M.; Petiot, J.F.
+\newblock Estimating traffic noise levels using acoustic monitoring: A~preliminary study.
+\newblock  In Proceedings of the DCASE 2016, Detection and Classification of Acoustic Scenes and
+  Events, \hl{Budapest, Hungary, 3  September} 2016;~4p.
+%please confirm if the added information is right. %R: Confirmed
+\bibitem[Aumond et~al.(2017)Aumond, Can, De~Coensel, Botteldooren,
+  Ribeiro, and Lavandier]{aumond2017}
+\hl{Aumond, P.; Can, A.; De~Coensel, B.; Botteldooren, D.; Ribeiro, C.; Lavandier,
+  C.}
+\newblock Modeling soundscape pleasantness using perceptual assessments and
+  acoustic measurements along paths in urban context.
+\newblock {\em Acta~Acust. United Acust.} {\bf 2017}, {\em
+  103},~430--443.
+
+\bibitem[Defr{\'e}ville et~al.(2006)Defr{\'e}ville, Pachet, Rosin, and
+  Roy]{defreville2006automatic}
+Defr{\'e}ville, B.; Pachet, F.; Rosin, C.; Roy, P.
+\newblock Automatic recognition of urban sound sources.
+\newblock  In Proceedings of the Audio Engineering Society Convention 120, \fg{Paris, France, 20--23} 2006;   Audio Engineering Society: \hl{New York, NY, USA,}  2006.
+%please confirm if the added information is right. %R: Location and dates changed from convention 121 to 120
+\bibitem[Mydlarz et~al.(2015)Mydlarz, Shamoon, Baglione, and
+  Pimpinella]{mydlarz2015design}
+Mydlarz, C.; Shamoon, C.; Baglione, M.; Pimpinella, M.
+\newblock The design and calibration of low cost urban acoustic sensing
+  devices.
+\newblock  In Proceedings of the EuroNoise 2015, \hl{Maastricht, The Netherlands, 31 May--3 June} 2015.
+%please confirm if the added information is right. %R: Confirmed
+\bibitem[Pan(1995)]{pan1995tutorial}
+Pan, D.
+\newblock A tutorial on MPEG/audio compression.
+\newblock {\em IEEE Multimedia} {\bf 1995}, {\em 2},~60--74.
+
+\bibitem[Ishiyama and Hashimoto(2000)]{ishiyama2000}
+Ishiyama, T.; Hashimoto, T.
+\newblock The impact of sound quality on annoyance caused by road traffc noise:
+  An~influence of frequency spectra on annoyance.
+\newblock {\em JSAE Rev.} {\bf 2000}, {\em 21},~225--230.
+
+\bibitem[Anusuya and Katty(2009)]{anusuya2009}
+Anusuya, M.; Katty, S.
+\newblock Speech recognition by machine, a review.
+\newblock {\em Int. J. Comput. Sci. Inf. Secur.} {\bf 2009}, {\em 6},~181--205.
+
+\bibitem[Tzanztakis et~al.(2002)Tzanztakis, Essl, and
+  Cook]{tzanetakis2002}
+Tzanztakis, G.; Essl, G.; Cook, P.
+\newblock Automatic musical genre classification of audio signals.
+\newblock {\em IEEE Trans. Speech  Audio Process.} {\bf 2002},
+  {\em 10},~293--302.
+
+\bibitem[Ntalampiras(2014)]{ntalampiras2014}
+Ntalampiras, S.
+\newblock Universal background modeling for acoustic surveillance of urban
+  traffic.
+\newblock {\em Digit.~Signal~Process.} {\bf 2014}, {\em 31},~69--78.
+
+\bibitem[Aucouturier et~al.(2007)Aucouturier, Defreville, and
+  Pachet]{aucouturier2007}
+Aucouturier, J.; Defreville, B.; Pachet, F.
+\newblock The bag-of-frames approach to audio pattern recognition: A~sufficient
+  model for urban soundscapes but not for polyphonic music.
+\newblock {\em J. Acoust. Soc. Am.} {\bf 2007}, {\em 122},~881--891.
+
+\bibitem[Foggia et~al.(2015)Foggia, Petkov, Saggese, Strisciuglio, and
+  Vento]{foggia2015}
+Foggia, P.; Petkov, N.; Saggese, A.; Strisciuglio, N.; Vento, M.
+\newblock Reliable detection of audio events in highly noisy environments.
+\newblock {\em Pattern Recognit. Lett.} {\bf 2015}, {\em 65},~22--28.
+
+\bibitem[Kumar and Raj(2016)]{kumar2016}
+Kumar, A.; Raj, B.
+\newblock Features and Kernels for Audio Event Recognition. 2016. 
+\newblock Available online: \mbox{\url{https://arxiv.org/abs/1607.05765}} (\hl{accessed on}). 
+%please add accessed date.
+\bibitem[Radhakrishnan et~al.(2005)Radhakrishnan, Divakaran, and
+  Smaragdis]{radhakrishnan2005}
+Radhakrishnan, R.; Divakaran, A.; Smaragdis, P.
+\newblock Audio analysis for surveillance applications.
+\newblock  In Proceedings of the IEEE Workshop on Applications of Signal Processing to Audio and
+  Acoustics, \hl{New Paltz, NY, USA, 16 October} 2005.
+%please confirm if the added information is right. %R: Confirmed
+\bibitem[Salamon and Bello(2017)]{salamon2017}
+Salamon, J.; Bello, J.
+\newblock Deep convolutional neural networks and data augmentation for
+  environmental sound classification.
+\newblock {\em IEEE Signal Process. Lett.} {\bf 2017}, {\em 24},~279--283.
+
+\bibitem[Piczak(2015)]{piczak2015}
+Piczak, K.
+\newblock Environmental sound classification with convolutional neural
+  networks.
+\newblock  In Proceedings of the IEEE 25th International Workshop on Machine Learning for Signal
+  Processing, \hl{Boston, MA, USA, 17--20 September }2015.
+%please confirm if the added information is right.
+\bibitem[Khunarsal et~al.(2013)Khunarsal, Lursinsap, and
+  Raicharoen]{khunarsal2013}
+Khunarsal, P.; Lursinsap, C.; Raicharoen, T.
+\newblock Very short time environmental sound classification based on
+  spectrogram pattern matching.
+\newblock {\em Inf. Sci.} {\bf 2013}, {\em 243},~57--74.
+
+\bibitem[Couvreur and Laniray(2004)]{couvreur2004}
+Couvreur, L.; Laniray, M.
+\newblock Automatic noise recognition in urban environments based on artificial
+  neural networks and hidden markov models.
+\newblock  In Proceedings of the  33rd International Congress and Exposition on Noise Control
+  Engineering, \hl{Prague, Czech Republic,  22--25 August }2004.
+%please confirm if the added information is right. %R: Confirmed
+\bibitem[Cai et~al.(2006)Cai, Lu, Hanjalic, Zhang, and Cai]{cai2006}
+Cai, R.; Lu, L.; Hanjalic, A.; Zhang, H.; Cai, L.
+\newblock A flexible framewok for key audio effects detection and auditory
+  context inference.
+\newblock {\em IEEE Trans. Audio Speech Lang. Process.}
+  {\bf 2006}, {\em 14},~1026--1039.
+
+\bibitem[Chu et~al.(2009)Chu, Narayanan, and Kuo]{chu2009}
+Chu, S.; Narayanan, S.; Kuo, C.
+\newblock Environmental sound recognition with time-frequency audio features.
+\newblock {\em IEEE~Trans. Audio Speech Lang. Process.}
+  {\bf 2009}, {\em 17},~1142--1158.
+
+\bibitem[Baugé et~al.(2013)Baugé, Lagrange, Andén, and
+  Mallat]{bauge2013}
+Baugé, C.; Lagrange, M.; Andén, J.; Mallat, S.
+\newblock Representing environmental sounds using the separable scattering
+  transform.
+\newblock  In Proceedings of the 2013 IEEE International Conference on Acoustics, Speech and Signal
+  Processing, \hl{Vancouver, BC, Canada,  26--31 May } 2013.
+%please confirm if the added information is right. %R: Confirmed
+\bibitem[Salamon and Bello(2015{\natexlab{a}})]{salamon2015}
+Salamon, J.; Bello, J.
+\newblock Feature learning with deep scattering for urban sound analysis.
+\newblock  In  Proceedings of the 23rd European Signal Processing Conference,  \hl{Nice, France, 31 August--4 September }2015.
+%please confirm if the added information is right. %R: Confirmed
+\bibitem[Salamon and Bello(2015{\natexlab{b}})]{salamon2015-2}
+Salamon, J.; Bello, J.
+\newblock Unsupervised feature learning for urban sound classification.
+\newblock In Proceedings of the 2015 IEEE International Conference on Acoustics, Speech and Signal
+  Processing, \hl{Brisbane,  Australia, 19--24 April } 2015.
+%please confirm if the added information is right. %R: Confirmed
+\bibitem[Ntalampiras et~al.(2012)Ntalampiras, Potamitis, and
+  Fakotakis]{ntalampiras2012}
+Ntalampiras, S.; Potamitis, I.; Fakotakis, N.
+\newblock Acoustic detection of human activities in natural environments.
+\newblock {\em J. Audio Eng. Soc.} {\bf 2012}, {\em 60},~686--695.
+
+\bibitem[Chachada and Kuo(2013)]{chachada2013}
+Chachada, S.; Kuo, C.
+\newblock Environmental sound recognition: A survey.
+\newblock  In Proceedings of the 2013 Asia-Pacific Signal and Information Processing Association
+  Annual Summit and Conference, \hl{Kaohsiung, Taiwan, 29 October--1 November} 2013.
+%please confirm if the added information is right. %R: Confirmed
+\bibitem[Torija et~al.(2013)Torija, Ruiz, and Ramos-Ridao]{torija2013}
+Torija, A.; Ruiz, D.; Ramos-Ridao, A.
+\newblock Application of a methodology for categorizing and differentiating
+  urban soundscapes using acoustical descriptors and semantic-differential
+  attributes.
+\newblock {\em J. Acoust. Soc. Am.} {\bf 2013}, {\em 134},~791--802.
+
+\bibitem[Davis(1986)]{davis1986}
+Davis, S.
+\newblock Octave and fractional-octave band digital filtering based on the
+  proposed ANSI standard.
+\newblock  In~Proceedings of the 1986 IEEE International Conference on Acoustics, Speech and Signal
+  Processing, \hl{Tokyo, Japan, 7--11 April } 1986.
+%please confirm if the added information is right. %R: Confirmed
+\bibitem[Antoni(2010)]{antoni2010}
+Antoni, J.
+\newblock Orthogonal-like fractional-octave-band filters.
+\newblock {\em J. Acoust. Soc. Am.} {\bf 2010}, {\em 127},~884--895.
+
+\bibitem[cit(1993)]{citeulike:9580295}
+\emph{ANSI S1.1-1986, (ASA 65-1986)---Specifications for Octave-Band and
+  Fractional-Octave-Band Analog and Digital Filters}; \hl{ANSI: Washington, DC, USA,}  1993.
+%please confirm if the added information is right, and confirm if the layout  is right.
+\bibitem[iec(2014)]{iec-norm}
+\emph{IEC 61260-1:2014 ---Electroacoustics---Octave-Band and Fractional-Octave-Band
+  Filters--Part 1: Specifications}; \hl{IEC:~Geneva, Switzerland, }2014.
+%please confirm if the added information is right, and confirm if the layout  is right.
+\bibitem[Couvreur()]{couvreur}
+Couvreur, C.
+\newblock Implementation of a One-Third-Octave Filter Bank in Matlab.
+\newblock Available online: \mbox{\url{http://citeseer.ist.psu.edu/24150.html}} (\hl{accessed on} \fg{15 May 2017}).
+%please add accessed date. %R: Added accessed date
+\bibitem[Huffman(1952)]{huffman1952}
+Huffman, D.
+\newblock A method for the construction of minimum-redundancy codes.
+\newblock {\em Proc. IRE} {\bf 1952}, {\em 40},~1098--1101.
+
+\bibitem[Berzborn et~al.(2017)Berzborn, Bomhardt, Klein, Richter, and
+  Vorländer]{itatoolbox2017}
+Berzborn, M.; Bomhardt, R.; Klein, J.; Richter, J.G.; Vorländer, M.
+\newblock {T}he {ITA}-{T}oolbox: {A}n {o}pen {s}ource {MATLAB} {t}oolbox for
+  {a}coustic {m}easurements and {s}ignal {p}rocessing.
+\newblock In Proceedings of the 43th Annual German Congress on Acoustics, Kiel, Germany, 6--9 March 2017.
+
+\bibitem[Salamon et~al.(2014)Salamon, Jacoby, and Bello]{salamon2014}
+Salamon, J.; Jacoby, C.; Bello, J.
+\newblock A dataset and taxonomy for urban sound research.
+\newblock In Proceedings of the 22nd ACM international conference on Multimedia, \hl{Orlando, FL, USA, 3--7 November }2014.
+%please confirm if the added information is right. %R: Confirmed
+
+\bibitem[Ntalampiras(2013)]{ntalampiras2013}
+Ntalampiras, S.
+\newblock \hl{A novel holistic modeling acoustic approach for generalized sound
+  recognition.}
+\newblock {\em IEEE Signal Process. Lett.} {\bf 2013}, {\em 20},~185--188.
+%please confirm if ref 48 is the same as ref 55. %R: Title of ref 55 is now correct
+\bibitem[Ellis(2005)]{ellis2005}
+Ellis, D.
+\newblock {PLP} and {RASTA} (and {MFCC}, and Inversion) in {M}atlab. 2005.
+\newblock Available online: \url{http://www.ee.columbia.edu/~dpwe/resources/matlab/rastamat/} (\hl{accessed on} \fg{6 March 2017}).
+ %please add accessed date. %R: Added accessed date
+\bibitem[Baldwin and French(1990)]{baldwin1990forensic}
+Baldwin, J.; French, P.
+\newblock {\em Forensic Phonetics}; Pinter Publishers: \fg{London, }\hl{UK}, 1990.
+%please add city. %R: Added city
+\bibitem[Bo{\"e}(2000)]{boe2000forensic}
+Bo{\"e}, L.J.
+\newblock Forensic voice identification in France.
+\newblock {\em Speech Commun.} {\bf 2000}, {\em 31},~205--224.
+
+\bibitem[Kuwabara(1996)]{kuwabara1996acoustic}
+Kuwabara, H.
+\newblock Acoustic properties of phonemes in continuous speech for different
+  speaking rate.
+\newblock  In~Proceedings of the Fourth International  Conference on Spoken Language (ICSLP 96),  \hl{Philadelphia, PA, USA, 3--6 October} 1996; Volume~4, pp. 2435--2438.
+%please confirm if the added information is right. %R: Confirmed
+\bibitem[Rosen(1992)]{rosen1992temporal}
+Rosen, S.
+\newblock Temporal information in speech: Acoustic, auditory and linguistic
+  aspects.
+\newblock {\em Philos. Trans. R. Soc. Lond. B Biol. Sci.} {\bf 1992}, {\em 336},~367--373.
+
+\bibitem[itu(2003)]{itup835}
+{\em ITU-T P.835: Subjective Test Methodology for Evaluating Speech Communication
+  Systems That Include Noise Suppression Algorithm}; \hl{ITU: Geneva, Switzerland,} 2003.
+%please confirm if the added information is right, and confirm if the layout  is right.
+\bibitem[Ntalampiras et~al.(2008)Ntalampiras, Ganchev, and
+  Potamitis]{ntalampiras2008}
+Ntalampiras, S.; Ganchev, T.; Potamitis, I.
+\newblock \fg{Objective comparison of speech enhancement algorithms under real world conditions.}
+\newblock  In Proceedings of the 1st International Conference on PErvasive Technologies Related to
+  Assistive Environments, \hl{Athens, Greece, 15--19 July} 2008.
+%please confirm if the added information is right. %R: Confirmed
+\bibitem[Griffin and Lim(1984)]{griffin1984}
+Griffin, D.; Lim, J.
+\newblock Signal estimation from modified short-time fourier transform.
+\newblock {\em IEEE Trans. Acoust. Speech Signal Process.}
+  {\bf 1984}, {\em 32},~236--243.
+
+\bibitem[iec(2013)]{iec-norm2}
+{\em IEC 61672-1:2013---Electroacoustics---Sound Level Meters---Part 1:
+  Specifications}; \hl{IEC: Geneva, Switzerland,}~2013.
+%please confirm if the added information is right, and confirm if the layout  is right.
+\end{thebibliography}
 

### 2017-11-28 paper/articleV3.tex
v3pdf

@@
 
-\DeclareRobustCommand{\fg}[1]{{\sethlcolor{cyan}\hl{#1}}}
-
 \usepackage{microtype}
@@
 % Authors, for the paper (add full first names)
-\Author{\hl{F\'elix Gontier} $^{1}$, Mathieu Lagrange $^{1,}$\hl{*}, Pierre Aumond $^{2,3}$, Arnaud Can $^{2}$ and Catherine Lavandier $^{3}$}%Please carefully check the accuracy of names and affiliations.
+\Author{{F\'elix Gontier} $^{1}$, Mathieu Lagrange $^{1,}${*}, Pierre Aumond $^{2,3}$, Arnaud Can $^{2}$ and Catherine Lavandier $^{3}$}%Please carefully check the accuracy of names and affiliations.
 Changes will not be possible after proofreading.
@@
 \address{%
-$^{1}$ \quad \hl{LS2N}\fg{, UMR 6004, CNRS, \'Ecole Centrale de Nantes, 44300 Nantes}, France; felix.gontier@ls2n.fr\\%please add the complete location and add it's zip code. %R: done
-$^{2}$ \quad \hl{IFSTTAR, AME, LAE}\fg{, 44340 Bouguenais, France}; pierre.aumond@ifsttar.fr (P.A.); arnaud.can@ifsttar.fr (A.C.)\\%please add the complete location and add it's zip code. %R: done
-$^{3}$ \quad \hl{ETIS, UMR 8051}%please add the complete location and add it's zip code. 
-, Universit\'e Paris Seine, Universit\'e de Cergy-Pontoise, ENSEA, CNRS, F-95000 \hl{Cergy-Pontoise}; %please add the city. %R: done
+$^{1}$ \quad {LS2N}{, UMR 6004, CNRS, \'Ecole Centrale de Nantes, 44300 Nantes}, France; felix.gontier@ls2n.fr\\%please add the complete location and add its zip code. %R: done
+$^{2}$ \quad {IFSTTAR, AME, LAE}{, 44340 Bouguenais, France}; pierre.aumond@ifsttar.fr (P.A.); arnaud.can@ifsttar.fr (A.C.)\\%please add the complete location and add it's zip code. %R: done
+$^{3}$ \quad {ETIS, UMR 8051}%please add the complete location and add it's zip code.
+, Universit\'e Paris Seine, Universit\'e de Cergy-Pontoise, ENSEA, CNRS, F-95000 {Cergy-Pontoise}; %please add the city. %R: done
  catherine.lavandier@u-cergy.fr}
@@
 % Abstract (Do not use inserted blank lines, i.e. \\)
-\abstract{The spreading of urban areas and the growth of human population worldwide \highlight{raise} societal and environmental concerns.
-To better address \highlight{these concerns}, the monitoring of the acoustic environment in urban \highlight{as well as} rural or wilderness areas is an important matter.
-\highlight{Building} on the recent development of low cost hardware acoustic sensors, we propose in this paper to consider a sensor grid approach to tackle this issue.
-In this kind of approach, the crucial question is the nature of the data that \highlight{are} transmitted from the sensors to the processing and archival servers.
-To this end, we propose an efficient audio coding scheme based on third octave band spectral representation that \highlight{allows:} (1) the estimation of standard acoustic \highlight{indicators;} and (2) the recognition of acoustic events at state-of-the-art performance rate.
+\abstract{The spreading of urban areas and the growth of human population worldwide {raise} societal and environmental concerns.
+To better address {these concerns}, the monitoring of the acoustic environment in urban {as well as} rural or wilderness areas is an important matter.
+{Building} on the recent development of low cost hardware acoustic sensors, we propose in this paper to consider a sensor grid approach to tackle this issue.
+In this kind of approach, the crucial question is the nature of the data that {are} transmitted from the sensors to the processing and archival servers.
+To this end, we propose an efficient audio coding scheme based on third octave band spectral representation that {allows:} (1) the estimation of standard acoustic {indicators;} and (2) the recognition of acoustic events at state-of-the-art performance rate.
 The former is useful to provide quantitative information about the acoustic environment, while the latter is useful to gather qualitative information and build perceptually motivated indicators using for example the emergence of a given sound source.
-The coding scheme is also demonstrated to transmit spectrally encoded data that, reverted to the time domain using state-of-the-art techniques, \highlight{are} not intelligible, thus protecting the privacy of citizens.}
+The coding scheme is also demonstrated to transmit spectrally encoded data that, reverted to the time domain using state-of-the-art techniques, {are} not intelligible, thus protecting the privacy of citizens.}
 
@@
 
-The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the \hl{SONYC} ({\url{htttp://wp.nyu.edu/sonyc}}) \cite{mydlarz2017implementation} and %Footnote are not allowed, pls conrfim.
+The advent of low cost acoustic sensors together with the need to better monitor and comprehend the acoustic environment of urban and wilderness areas give rise to the deployment of experimental sensor networks such as the {SONYC} ({\url{htttp://wp.nyu.edu/sonyc}}) \cite{mydlarz2017implementation} and %Footnote are not allowed, pls conrfim.
 %R: ok
- \hl{CENSE} ({\url{htttp://cense.ifsttar.fr}}) \cite{picault2017} projects.
+ {CENSE} ({\url{htttp://cense.ifsttar.fr}}) \cite{picault2017} projects.
 To do so, considering the so-called ``sensor grid'' approach  \cite{lim2005sensor,tham2005sensorgrid} has several advantages.
-The sensor grid approach puts the focus \highlight{on:} (a) a distributed system of data acquisition with a large set of sensors; (b) the production and storage of a large dataset; and (c) its availability for intensive and open data analysis computation.
+The sensor grid approach puts the focus {on:} (a) a distributed system of data acquisition with a large set of sensors; (b) the production and storage of a large dataset; and (c) its availability for intensive and open data analysis computation.
 
 In such approach, the number of sensor nodes shall be extended as needed without having to change the hardware and software architecture, i.e., the approach shall be scalable.
-Second, the nodes shall be energy efficient, \highlight{and,  ideally,} autonomous, \highlight{to} ease the deployment of the sensor grid to the desired topology.
+Second, the nodes shall be energy efficient, {and,  ideally,} autonomous, {to} ease the deployment of the sensor grid to the desired topology.
 Third, the encoding scheme used to transmit the data from the sensor to the storage and processing servers shall be designed with care in order to guarantee the privacy of the citizens.
-At the same time, the data stored shall remain as rich as \highlight{possible,} while maintaining a low bitrate for efficient transmission and storage.
-
-In the case of urban acoustic monitoring, the data of interest typically \highlight{consist} of standardized high-quality measurements of energetic indicators such as the equivalent sound level $L_{eq}$ in dB SPL or its A-weighted counterpart $L_{Aeq}$ in dBA.
+At the same time, the data stored shall remain as rich as {possible,} while maintaining a low bitrate for efficient transmission and storage.
+
+In the case of urban acoustic monitoring, the data of interest typically {consist} of standardized high-quality measurements of energetic indicators such as the equivalent sound level $L_{eq}$ in dB SPL or its A-weighted counterpart $L_{Aeq}$ in dBA.
 However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe urban sound environments \cite{rychtarikova2013}.
@@
 
-In addition, considering sound sources allows \highlight{better assessing} the human perception of the urban sound environment in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017}.
-For instance, \highlight{bird song} and traffic noise with the same energy are perceived very differently.
+In addition, considering sound sources allows {better assessing} the human perception of the urban sound environment in terms of pleasantness and other perceptual indicators \cite{lavandier2006contribution, aumond2017}.
+For instance, {bird song} and traffic noise with the same energy are perceived very differently.
 Most acoustic indicators used in current sound maps describe the global sound environment and lack information on its composition.
-The recognition and the estimation of the level of contribution of sources of interest is thus of great importance to fully model the studied acoustic environments\highlight{ (see for example \cite{alsina2016design, app7020146, gloaguen2016estimating})}.
+The recognition and the estimation of the level of contribution of sources of interest is thus of great importance to fully model the studied acoustic environments{ (see for example \cite{alsina2016design, app7020146, gloaguen2016estimating})}.
 Other indicators have been found to correlate with specific sound environment content \cite{aumond2017} but do not achieve the level of performances of a well-designed source detection scheme in characterizing acoustic environments.
-This source detection step can\highlight{ be} operated online (on the sensors) or offline \highlight{(on the data servers),} leading to different grid designs (Figure \ref{fig:codingScheme}).
+This source detection step can{ be} operated online (on the sensors) or offline {(on the data servers),} leading to different grid designs (Figure \ref{fig:codingScheme}).
 
@@
 This approach is thus currently considered in several applications in the literature \cite{defreville2006automatic, mydlarz2017implementation, mydlarz2015design}.
-\highlight{However}, it requires the availability of decent computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware does not allow them to be autonomous using power sources like solar panels.
+{However}, it requires the availability of decent computing resources on the sensors in order to perform the detection step which as of today's efficiency of hardware does not allow them to be autonomous using power sources like solar panels.
 Furthermore, the detection is done once and cannot be recomputed during offline posterior analyses.
@@
 Indeed, the audio signal is not mandatory for the computation of the acoustic indicators and the features needed for event recognition.
-\highlight{In addition, as the data are} transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to guarantee the privacy of the citizens.
+{In addition, as the data are} transmitted using the network and stored, one must ensure that the intelligibility of potential speech utterances is lost during the coding process, in order to guarantee the privacy of the citizens.
 
@@
 
-\highlight{To} promote reproducible research, the coder as well as the experiments needed to generate the figures is available to the research \hl{community} ({\url{https://github.com/felixgontier/cense-coder}}).
-The remaining of the paper is organized as follows: Section \ref{sec:coder} describes the proposed encoding \highlight{scheme;} the experimental protocol designed to validate the proposed approach is described in \highlight{Section \ref{sec:protocol};} and results are discussed in Section \ref{sec:results}.
+{To} promote reproducible research, the coder as well as the experiments needed to generate the figures is available to the research {community} ({\url{https://github.com/felixgontier/cense-coder}}).
+The remaining of the paper is organized as follows: Section \ref{sec:coder} describes the proposed encoding {scheme;} the experimental protocol designed to validate the proposed approach is described in {Section \ref{sec:protocol};} and results are discussed in Section \ref{sec:results}.
 
@@
 \includegraphics[width=0.7\textwidth]{figures/censeCoder}
-\caption{Three alternative implementations of the sensor grid approach for the monitoring of the acoustic \highlight{environment:} in (\textbf{A}) the raw audio is transmitted; in (\textbf{B}) only the detected events; and in (\textbf{C}) a compressed spectral representation.
+\caption{Three alternative implementations of the sensor grid approach for the monitoring of the acoustic {environment:} in (\textbf{A}) the raw audio is transmitted; in (\textbf{B}) only the detected events; and in (\textbf{C}) a compressed spectral representation.
 Thickness of arrows indicates bandwidth and thickness of boxes indicates the level of computation or storage required.}
@@
 
-The identification of sources from audio streams has been the subject of extensive research in the past for speech data \cite{anusuya2009}, music data \cite{tzanetakis2002}, and lately environmental \highlight{data,} in which the current work falls.
+The identification of sources from audio streams has been the subject of extensive research in the past for speech data \cite{anusuya2009}, music data \cite{tzanetakis2002}, and lately environmental {data,} in which the current work falls.
 Studied classification methods are diverse, ranging from time-dependant modeling with hidden Markov models \cite{ntalampiras2014} to ``bag-of-frames'' approaches \cite{aucouturier2007, foggia2015}.
 Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, Gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}.
-\highlight{In addition}, several type of features are considered to feed those classifiers.
+{In addition}, several type of features are considered to feed those classifiers.
 The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal.
@@
 Features can also be computed in other domains to better model signal properties.
-\mbox{For \highlight{instance,} \fg{Cai et al.} \cite{cai2006}} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domain features.
+\mbox{For {instance,} {Cai et al.} \cite{cai2006}} adds spectral features related to harmonicity and salient frequencies, and \cite{chu2009} uses a matching pursuit (MP) algorithm to deduce time-domain features.
 Alternative data representations such as the scattering transform \cite{bauge2013} show good results in environmental sound classification tasks \cite{salamon2015}.
-Another promising solution is feature engineering via unsupervised learning, \highlight{which} \fg{Salamon et al.} \cite{salamon2015-2} implements with a clustering technique.
+Another promising solution is feature engineering via unsupervised learning, {which} {Salamon et al.} \cite{salamon2015-2} implements with a clustering technique.
 More complex systems using multiple-domain data representation as well as unsupervised models have been found to handle unrestricted environments such as urban acoustic scenes \mbox{efficiently \citep{ntalampiras2012}.
@@
 A common way to implement third-octave analysis is to first design the highest octave three filters, and use them on progressively time-decimated versions of the input signal \cite{davis1986}.
-\fg{Antoni} %newly added information, please confirm.
- \cite{antoni2010} \highlight{presents} an alternative analysis method based on direct frequency weighting, which yields a lower computational complexity as opposed to time filtering.
+{Antoni} %newly added information, please confirm.
+ \cite{antoni2010} {presents} an alternative analysis method based on direct frequency weighting, which yields a lower computational complexity as opposed to time filtering.
 The weights matrix design procedure complies with both ANSI S1.1-1986 \cite{citeulike:9580295} and IEC 61260-1:2014 \cite{iec-norm} standards.
@@
 The continuously sampled audio is segmented into either 125~ms or 1~s frames to provide ``fast'' or ``slow'' acoustic measurements.
-The data \highlight{are} zero-padded to the next power of two to improve computational efficiency.
+The data {are} zero-padded to the next power of two to improve computational efficiency.
 The other parameters such as windowing functions and frame overlap are dependant on the specific constraints, and discussed in Section \ref{sec:protocol}.
@@
 Similarly, negative frequency components contain the same information as positive ones because the input signal is real.
-We then compute third-octave bands from the squared spectral magnitude by matrix multiplication with the frequency weights proposed in~\cite{antoni2010} for $l = 2$ ({\highlight{when} implementing said method, we found that squaring the $\phi_l(p), l \geq 1$ intermediate function (p.
-887) was the correct approach to meet cutoff frequencies requirements, and we believe this was the author's original \highlight{intention).}} We include analysis for bands $i$ from $-17$ to 13, i.e., center frequencies $f_i$ ranging from $20$~Hz to $20$~kHz with $f_0 = 1$~kHz.
+We then compute third-octave bands from the squared spectral magnitude by matrix multiplication with the frequency weights proposed in~\cite{antoni2010} for $l = 2$ ({{when} implementing said method, we found that squaring the $\phi_l(p), l \geq 1$ intermediate function (p.
+887) was the correct approach to meet cutoff frequencies requirements, and we believe this was the author's original {intention).}} We include analysis for bands $i$ from $-17$ to 13, i.e., center frequencies $f_i$ ranging from $20$~Hz to $20$~kHz with $f_0 = 1$~kHz.
 The representation is thus composed of 31 values.
@@
 A Huffman coding scheme \cite{huffman1952} is an efficient method to further reduce data rate while keeping the underlying information.
-At this point of the processing chain, the data \highlight{take} the form of a spectrogram with amplitude values represented on an arbitrary data type.
+At this point of the processing chain, the data {take} the form of a spectrogram with amplitude values represented on an arbitrary data type.
 It is therefore assimilable to a discrete distribution.
@@
 The efficiency of the coding step thus directly depends on the entropy of the transmitted data.
-It~is defined as $H = -\sum\limits_i p_ilog_n(p_i)$, where $p_i$ is the probability of appearance of a given symbol $i$ and $n$ \highlight{is} the numerical base in which the output code is represented.
+It~is defined as $H = -\sum\limits_i p_ilog_n(p_i)$, where $p_i$ is the probability of appearance of a given symbol $i$ and $n$ {is} the numerical base in which the output code is represented.
 A lower entropy can be obtained with two factors.
-First, the dictionary \highlight{size,} i.e., the number of symbols must be kept low.
+First, the dictionary {size,} i.e., the number of symbols must be kept low.
 This implies performing a quantization on the data resulting in a loss of precision.
@@
 
-Considering an estimated PDF for our \highlight{data,} as shown in Figure~\ref{fig:pdf} (top-left), immediately applying a linear quantization is clearly suboptimal, as the data mostly \highlight{consist} of very low values and a direct quantization results in most of the information being lost.
+Considering an estimated PDF for our {data,} as shown in Figure~\ref{fig:pdf} (top-left), immediately applying a linear quantization is clearly suboptimal, as the data mostly {consist} of very low values and a direct quantization results in most of the information being lost.
 We therefore flatten the PDF by taking the logarithm of the representation (top-right).
@@
 PDF ``flattening'' effect induced by logarithm application (\textbf{top}-\textbf{right}).
-\highlight{Here,} values are mapped to the range $[0, 2^7-1] (q=8)$ and rounded to perform quantization (\textbf{bottom}-\textbf{left}).
+{Here,} values are mapped to the range $[0, 2^7-1] (q=8)$ and rounded to perform quantization (\textbf{bottom}-\textbf{left}).
 Output of the $\Delta$ compression  (\textbf{bottom}-\textbf{right}), with desirable probabilities as the input to a Huffman algorithm.}
@@
 
-\highlight{To} assess the quality of the propoposed scheme's spectral measurement precision, we compare it to a known reference: the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017}.
+{To} assess the quality of the propoposed scheme's spectral measurement precision, we compare it to a known reference: the Matlab \textit{ita\_toolbox} implementation \cite{itatoolbox2017}.
 This toolbox's implementation shows less than $0.1$~dB error on all bands when compared to a class 1 sound level meter software on 2~s third-octave bands measurements.
@@
 As the analysis frames are of short duration, poor frequency resolution and spectral leakage are expected when performing the STFT, particularly in the lower frequencies bands.
-For this \highlight{reason,} we evaluate the impact of windowing functions on each band measurement error in order to potentially mitigate this loss of precision.
+For this {reason,} we evaluate the impact of windowing functions on each band measurement error in order to potentially mitigate this loss of precision.
 
@@
 
-\highlight{To} ensure that the proposed scheme allows the recognition of events using state-of-the-art methods, we consider the results achieved by several recognition systems on the UrbanSound8k dataset~\cite{salamon2014}.
+{To} ensure that the proposed scheme allows the recognition of events using state-of-the-art methods, we consider the results achieved by several recognition systems on the UrbanSound8k dataset~\cite{salamon2014}.
 It features about 9 h of urban environmental sounds recordings separated in 8732 audio files ranging from 1 to 4 s each.
-The recordings are labeled in 10 classes (air conditioner, car horn, children playing, dog bark, drilling, engine idling, gun shot, jackhammer, siren,\highlight{ and} street music), and distributed in 10 independent folds.
+The recordings are labeled in 10 classes (air conditioner, car horn, children playing, dog bark, drilling, engine idling, gun shot, jackhammer, siren,{ and} street music), and distributed in 10 independent folds.
 A method and baseline results are also provided for the classification task.
@@
 The aim of this experiment is two-fold: to evaluate the global loss of information induced by the coding process, and to evaluate the adequacy of third-octave bands indicators for classification.
-As~studying the best performing classical \hl{models} \citep{ntalampiras2013}, %Reference [49] is cited after [47] directly, which is out of order.
+As~studying the best performing classical {models} \citep{ntalampiras2013}, %Reference [49] is cited after [47] directly, which is out of order.
 Please confirm.
@@
 Here third-octave bands are obtained by reversing the operations in Section~\ref{sec:dataenc} and cepstral coefficients are computed before training the model.
-Cross-validation is achieved by independantly training and testing the models with each of the 10 combinations of a 90--\hl{10}\% training\highlight{--}validation dataset separation.}% changed from ``10'' to ``100'', please confirm.
+Cross-validation is achieved by independantly training and testing the models with each of the 10 combinations of a 90--{10}\% training{--}validation dataset separation.}% changed from ``10'' to ``100'', please confirm.
 %NOTE: 90%/10%?
@@
 
-It is important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data \highlight{are} transmitted over the network and potentially stored, the level of intelligibility of  speech utterances potentially captured in the decoded stream should be as low as possible.
+It is important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data {are} transmitted over the network and potentially stored, the level of intelligibility of  speech utterances potentially captured in the decoded stream should be as low as possible.
 Thus, intelligibility in decoded and reconstructed audio is also an important concern of this study.
@@
 The readers shall be aware that even recorded with a good quality, such recording remains a weak biometrical indicator \cite{boe2000forensic}.
-\highlight{However}, even if the identity of the speaker cannot be asserted, one can attempt to transcribe the spoken utterances.
-\highlight{Thus}, we believe that it is important to demonstrate that the proposed encoding scheme do not allow such thing.
-
-\highlight{To} decrease the intelligibility, several approaches can be considered.
+{However}, even if the identity of the speaker cannot be asserted, one can attempt to transcribe the spoken utterances.
+{Thus}, we believe that it is important to demonstrate that the proposed encoding scheme do not allow such thing.
+
+{To} decrease the intelligibility, several approaches can be considered.
 First, a speech versus non speech detector can be implemented on the sensor.
-If some speech is detected, the data \highlight{are} not transmitted.
-This approach is however prone to failure of the detector and will lead to unavailability of data during speech time \highlight{periods,} which might compromise the relevance of some indicators.
+If some speech is detected, the data {are} not transmitted.
+This approach is however prone to failure of the detector and will lead to unavailability of data during speech time {periods,} which might compromise the relevance of some indicators.
 
@@
 For the evaluation, a dataset of clean speech utterances recorded in studio conditions is used.
-The dataset is composed of \highlight{nine} french sentences enunciated by \highlight{three} male and \highlight{three} female speakers.
-The sentences have a mean duration of $2$~s and are composed of \highlight{5--12} words, averaging \highlight{eight words}.
-The 54 extracts are encoded using the proposed approach with \highlight{four} analysis frame rate parameters \highlight{of,  respectively,} 50~Hz, 16~Hz, 8~Hz and 4~Hz leading to 216 audio excerpts being tested in total.
+The dataset is composed of {nine} french sentences enunciated by {three} male and {three} female speakers.
+The sentences have a mean duration of $2$~s and are composed of {5--12} words, averaging {eight words}.
+The 54 extracts are encoded using the proposed approach with {four} analysis frame rate parameters {of,  respectively,} 50~Hz, 16~Hz, 8~Hz and 4~Hz leading to 216 audio excerpts being tested in total.
 However, as the recording conditions are the same for all extracts the speaker identity is considered as a source of variability rather than as a necessary factor in the test statistics.
-As a \highlight{result,} the objective is primarily to evaluate the \highlight{nine} sentences with \highlight{four} encoding frame rates, i.e., 36 parameters.
+As a {result,} the objective is primarily to evaluate the {nine} sentences with {four} encoding frame rates, i.e., 36 parameters.
 
@@
 As~decoding the transmitted audio induces a framing effect unevenly distorting the input utterance, a~second metric is designed to assess the comprehension of words.
-For the perceptual test, 18 different sentences evenly distributed over the \highlight{four} frame rate parameters are selected for each subject.
-For each \highlight{sentence,} the participant first listens to the extract and is then asked to transcribe the utterance and to rate the perceived intelligibility from 1 (not intelligible) to 5 (intelligible).
+For the perceptual test, 18 different sentences evenly distributed over the {four} frame rate parameters are selected for each subject.
+For each {sentence,} the participant first listens to the extract and is then asked to transcribe the utterance and to rate the perceived intelligibility from 1 (not intelligible) to 5 (intelligible).
 The first metric is computed as the ratio of correctly transcribed words and will be referred as the intelligibility ratio (IR) in this paper.
@@
 
-\highlight{Twelve} subjects of age ranging from 17 to 60 which reported normal hearing participated to the listening test.
+{Twelve} subjects of age ranging from 17 to 60 which reported normal hearing participated to the listening test.
 The test was conducted using a Matlab interface displayed with a desktop computer and audio was played through \textit{Beyerdynamics DT 770} headphones.
@@
 As a result the energy located at a specific frequency is impossible to recover and the best inverse approximation is to split the third-octave band's observed energy into all the corresponding frequency bins with the same proportions as during analysis.
-This leads to the phenomenon seen \highlight{in} Figure~\ref{fig:freq} where part of the energy of a frequency bin in the original signal is found in all other bins of the same band at reconstruction, in almost equal proportions.
-The signal phase is recovered with the \fg{Griffin--Lim} algorithm \cite{griffin1984} if analysis overlap is used and white noise spectrogram scaling if not.
+This leads to the phenomenon seen {in} Figure~\ref{fig:freq} where part of the energy of a frequency bin in the original signal is found in all other bins of the same band at reconstruction, in almost equal proportions.
+The signal phase is recovered with the {Griffin--Lim} algorithm \cite{griffin1984} if analysis overlap is used and white noise spectrogram scaling if not.
 The time-domain signal is then retrieved using the overlap-add method.
@@
 	\caption{Third-octave bands analysis and approximate inverse transformation effects on energy location.
-\highlight{Here,} a brighter gray indicates that part of the energy contained at the corresponding frequency of the original signal is transferred to the reconstructed signal at the indicated frequency.
+{Here,} a brighter gray indicates that part of the energy contained at the corresponding frequency of the original signal is transferred to the reconstructed signal at the indicated frequency.
 This process yields an important and heterogeneous loss in resolution, particularly at higher frequency points.}
@@
 The only lossy operation applied is quantization, which is defined by an output word size $q$ in bits.
-However, it corresponds to the word size \textit{after} $\Delta$-compression, meaning that the data \highlight{are} in fact quantized on $2^{q-1}$ values.
+However, it corresponds to the word size \textit{after} $\Delta$-compression, meaning that the data {are} in fact quantized on $2^{q-1}$ values.
 Since these measurements are already expressed in dB, the error $\varepsilon$ is computed as:
@@
     \caption{Measurement error of third-octave bands over two-seconds environmental sounds recordings (US8k dataset).
-For most \highlight{settings,} the FFT-based method yields similar errors compared to the time-domain filtering reference.
+For most {settings,} the FFT-based method yields similar errors compared to the time-domain filtering reference.
 \label{fig:errormu}}
@@
 To better understand this phenomenon, let us model $x$ as a uniform distribution such as $x\sim \textit{U}\{0, \Delta_x\}$.
-While this is not \highlight{exact,} it matches our objective when using a logarithm to flatten given PDFs.
+While this is not {exact,} it matches our objective when using a logarithm to flatten given PDFs.
 The error $\varepsilon$ will follow a uniform distribution $U\sim \{0, \frac{\Delta_x}{2\times (2^{q-1}-1)}\}$.
@@
 This experiment aims at finding ways to further reduce the encoded data size without strongly affecting detection performance.
-Results of the four presented classification methods (\hl{Section} \ref{sec:event_p}) are provided for the sake of completeness.% newly added information, please confirm.
+Results of the four presented classification methods ({Section} \ref{sec:event_p}) are provided for the sake of completeness.% newly added information, please confirm.
 R:correct
@@
 
-\textls[-5]{Similar\highlight{ to} baseline results, the random forest and SVM classifiers are the best performing systems at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively.
+\textls[-5]{Similar{ to} baseline results, the random forest and SVM classifiers are the best performing systems at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively.
 However, we find that given our setup, reducing the number of analysis bands up to a given level often does not induce a severe drop of performance.
@@
 
-The perceptual test ({\hl{decoded speech utterances for various conditions can be listened to at} \url{https://felixgontier.github.io/cense-coder/}}) then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
+The perceptual test ({{decoded speech utterances for various conditions can be listened to at} \url{https://felixgontier.github.io/cense-coder/}}) then evaluates the impact of analysis frame rate on intelligibility using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance.
 Given the test conditions presented in Section~\ref{sec:inintelligibility_p} and the number of subjects, the mean and standard deviation are computed on an average of 54 results per frame rate parameter: 12 subjects evaluating each analysis resolution 4.5 times on average.
@@
 \begin{itemize}[leftmargin=*,labelsep=5.5mm]
-	\item Precision: \highlight{The} impact of the quantization step for 8 bits codewords is found to be very small \highlight{(<~0.2 dB),} and thus:
+	\item Precision: {The} impact of the quantization step for 8 bits codewords is found to be very small {(<~0.2 dB),} and thus:
 	\begin{itemize}[leftmargin=*,labelsep=5.6mm]
-	\item does not impact the quality of the acoustics indicators (Sections~\ref{sec:efficiency_p}  \highlight{ and \ref{sec:efficiency_r}); and}
+	\item does not impact the quality of the acoustics indicators (Sections~\ref{sec:efficiency_p}  { and \ref{sec:efficiency_r}); and}
 	\item enables sound event recognition with the same quality than directly from the spectrogram (Sections~\ref{sec:event_p}, \ref{sec:event_r} and \ref{sec:tob_r}).
 	\end{itemize}
-	\item Efficiency: \highlight{Using} the high precision parameters, the bitrate is about 1.4~kbps and 0.4~kbps for fast and slow modes respectively (Section~\ref{sec:efficiency_r}).
-	\item Privacy: \highlight{At} all operating modes, the reverted audio signal is found to be inintelligible according to a perceputal test done using clean speech recorded at very low background level.
+	\item Efficiency: {Using} the high precision parameters, the bitrate is about 1.4~kbps and 0.4~kbps for fast and slow modes respectively (Section~\ref{sec:efficiency_r}).
+	\item Privacy: {At} all operating modes, the reverted audio signal is found to be inintelligible according to a perceputal test done using clean speech recorded at very low background level.
 Additionaly, the sensors being typically hanged at 4 m high in a usually very noisy environment, we believe that the intelligibility risk of the proposed approach is negligible (Sections~\ref{sec:inintelligibility_p} and \ref{sec:inintelligibility_r}).
@@
 
-\authorcontributions{\hl{For research articles with several authors, }a short paragraph specifying their individual contributions must be provided.
+%\authorcontributions{{For research articles with several authors, }a short paragraph specifying their individual contributions must be provided.
 The following statements should be used “X.X.
@@
 wrote the paper.” Authorship must be limited to those who have contributed substantially to the work reported.}%Please add the main text in accordance with the template.
-
-\conflictsofinterest{\hl{The authors declare no conflict of interest}.}%Please disclose conflicts of interest, or add 'The authors declare no conflicts of interest'. %R: No conflicts of interest
+\authorcontributions{F.
+Gontier and M.
+Lagrange conceived and designed the experiments; F.
+Gontier performed the experiments; F.
+Gontier, M.
+Lagrange, P.
+Aumond, A.
+Can and C.
+Lavandier analyzed the data; P.
+Aumond contributed analysis tools; F.
+Gontier, M.
+Lagrange, P.
+Aumond, A.
+Can and C.
+Lavandier wrote the paper.}
+
+\conflictsofinterest{The authors declare no conflict of interest.}%Please disclose conflicts of interest, or add 'The authors declare no conflicts of interest'. %R: No conflicts of interest
 %=====================================
@@
 %\bibliography{your_external_BibTeX_file}
-\reftitle{References}
+\section{References}
 \begin{thebibliography}{999}
@@
 \newblock Sensor grid: Integration of wireless sensor networks and the grid.
-\newblock In Proceedings of the 2005 30th Anniversary IEEE Conference on Local Computer Networks, \hl{Sydney,  Australia, 17 November } 2005; pp. 91--99.
+\newblock In Proceedings of the 2005 30th Anniversary IEEE Conference on Local Computer Networks, {Sydney,  Australia, 17 November } 2005; pp. 91--99.
  %please confirm if the added information is right. %R: Confirmed
@@
 \newblock  In Proceedings of the 45th International Congress and Exposition on Noise Control
-  Engineering, \hl{Hamburg, Germany, 21--24 August }2016; pp. 5678--5686.
+  Engineering, {Hamburg, Germany, 21--24 August }2016; pp. 5678--5686.
  %please confirm if the added information is right. %R: Confirmed
@@
   outdoor urban areas.
-\newblock  In Proceedings of the 19th International Congress on Acoustics, \hl{Madrid, Spain, 2--7 September} 2007.
+\newblock  In Proceedings of the 19th International Congress on Acoustics, {Madrid, Spain, 2--7 September} 2007.
 %please confirm if the added information is right. %R: Confirmed
@@
 \newblock  In Proceedings of the DCASE 2016, Detection and Classification of Acoustic Scenes and
-  Events, \hl{Budapest, Hungary, 3  September} 2016;~4p.
+  Events, {Budapest, Hungary, 3  September} 2016;~4p.
 %please confirm if the added information is right. %R: Confirmed
@@
   Ribeiro, and Lavandier]{aumond2017}
-\hl{Aumond, P.; Can, A.; De~Coensel, B.; Botteldooren, D.; Ribeiro, C.; Lavandier,
+{Aumond, P.; Can, A.; De~Coensel, B.; Botteldooren, D.; Ribeiro, C.; Lavandier,
   C.}
@@
 \newblock Automatic recognition of urban sound sources.
-\newblock  In Proceedings of the Audio Engineering Society Convention 120, \fg{Paris, France, 20--23} 2006;   Audio Engineering Society: \hl{New York, NY, USA,}  2006.
+\newblock  In Proceedings of the Audio Engineering Society Convention 120, {Paris, France, 20--23} 2006;   Audio Engineering Society: {New York, NY, USA,}  2006.
 %please confirm if the added information is right. %R: Location and dates changed from convention 121 to 120
@@
   devices.
-\newblock  In Proceedings of the EuroNoise 2015, \hl{Maastricht, The Netherlands, 31 May--3 June} 2015.
+\newblock  In Proceedings of the EuroNoise 2015, {Maastricht, The Netherlands, 31 May--3 June} 2015.
 %please confirm if the added information is right. %R: Confirmed
@@
 \newblock Features and Kernels for Audio Event Recognition. 2016.
-\newblock Available online: \mbox{\url{https://arxiv.org/abs/1607.05765}} (\hl{accessed on}). 
+\newblock Available online: \mbox{\url{https://arxiv.org/abs/1607.05765}} ({accessed on}).
 %please add accessed date.
@@
 \newblock  In Proceedings of the IEEE Workshop on Applications of Signal Processing to Audio and
-  Acoustics, \hl{New Paltz, NY, USA, 16 October} 2005.
+  Acoustics, {New Paltz, NY, USA, 16 October} 2005.
 %please confirm if the added information is right. %R: Confirmed
@@
 \newblock  In Proceedings of the IEEE 25th International Workshop on Machine Learning for Signal
-  Processing, \hl{Boston, MA, USA, 17--20 September }2015.
+  Processing, {Boston, MA, USA, 17--20 September }2015.
 %please confirm if the added information is right.
@@
 \newblock  In Proceedings of the  33rd International Congress and Exposition on Noise Control
-  Engineering, \hl{Prague, Czech Republic,  22--25 August }2004.
+  Engineering, {Prague, Czech Republic,  22--25 August }2004.
 %please confirm if the added information is right. %R: Confirmed
@@
 \newblock  In Proceedings of the 2013 IEEE International Conference on Acoustics, Speech and Signal
-  Processing, \hl{Vancouver, BC, Canada,  26--31 May } 2013.
+  Processing, {Vancouver, BC, Canada,  26--31 May } 2013.
 %please confirm if the added information is right. %R: Confirmed
@@
 \newblock Feature learning with deep scattering for urban sound analysis.
-\newblock  In  Proceedings of the 23rd European Signal Processing Conference,  \hl{Nice, France, 31 August--4 September }2015.
+\newblock  In  Proceedings of the 23rd European Signal Processing Conference,  {Nice, France, 31 August--4 September }2015.
 %please confirm if the added information is right. %R: Confirmed
@@
 \newblock In Proceedings of the 2015 IEEE International Conference on Acoustics, Speech and Signal
-  Processing, \hl{Brisbane,  Australia, 19--24 April } 2015.
+  Processing, {Brisbane,  Australia, 19--24 April } 2015.
 %please confirm if the added information is right. %R: Confirmed
@@
 \newblock  In Proceedings of the 2013 Asia-Pacific Signal and Information Processing Association
-  Annual Summit and Conference, \hl{Kaohsiung, Taiwan, 29 October--1 November} 2013.
+  Annual Summit and Conference, {Kaohsiung, Taiwan, 29 October--1 November} 2013.
 %please confirm if the added information is right. %R: Confirmed
@@
 \newblock  In~Proceedings of the 1986 IEEE International Conference on Acoustics, Speech and Signal
-  Processing, \hl{Tokyo, Japan, 7--11 April } 1986.
+  Processing, {Tokyo, Japan, 7--11 April } 1986.
 %please confirm if the added information is right. %R: Confirmed
@@
 \emph{ANSI S1.1-1986, (ASA 65-1986)---Specifications for Octave-Band and
-  Fractional-Octave-Band Analog and Digital Filters}; \hl{ANSI: Washington, DC, USA,}  1993.
+  Fractional-Octave-Band Analog and Digital Filters}; {ANSI: Washington, DC, USA,}  1993.
 %please confirm if the added information is right, and confirm if the layout  is right.
@@
 \emph{IEC 61260-1:2014 ---Electroacoustics---Octave-Band and Fractional-Octave-Band
-  Filters--Part 1: Specifications}; \hl{IEC:~Geneva, Switzerland, }2014.
+  Filters--Part 1: Specifications}; {IEC:~Geneva, Switzerland, }2014.
 %please confirm if the added information is right, and confirm if the layout  is right.
@@
 \newblock Implementation of a One-Third-Octave Filter Bank in Matlab.
-\newblock Available online: \mbox{\url{http://citeseer.ist.psu.edu/24150.html}} (\hl{accessed on} \fg{15 May 2017}).
+\newblock Available online: \mbox{\url{http://citeseer.ist.psu.edu/24150.html}} ({accessed on} {15 May 2017}).
 %please add accessed date. %R: Added accessed date
@@
 \newblock A dataset and taxonomy for urban sound research.
-\newblock In Proceedings of the 22nd ACM international conference on Multimedia, \hl{Orlando, FL, USA, 3--7 November }2014.
+\newblock In Proceedings of the 22nd ACM international conference on Multimedia, {Orlando, FL, USA, 3--7 November }2014.
 %please confirm if the added information is right. %R: Confirmed
@@
 Ntalampiras, S.
-\newblock \hl{A novel holistic modeling acoustic approach for generalized sound
+\newblock {A novel holistic modeling acoustic approach for generalized sound
   recognition.}
@@
 \newblock {PLP} and {RASTA} (and {MFCC}, and Inversion) in {M}atlab. 2005.
-\newblock Available online: \url{http://www.ee.columbia.edu/~dpwe/resources/matlab/rastamat/} (\hl{accessed on} \fg{6 March 2017}).
+\newblock Available online: \url{http://www.ee.columbia.edu/~dpwe/resources/matlab/rastamat/} ({accessed on} {6 March 2017}).
  %please add accessed date. %R: Added accessed date
@@
 Baldwin, J.; French, P.
-\newblock {\em Forensic Phonetics}; Pinter Publishers: \fg{London, }\hl{UK}, 1990.
+\newblock {\em Forensic Phonetics}; Pinter Publishers: {London, }{UK}, 1990.
 %please add city. %R: Added city
@@
   speaking rate.
-\newblock  In~Proceedings of the Fourth International  Conference on Spoken Language (ICSLP 96),  \hl{Philadelphia, PA, USA, 3--6 October} 1996; Volume~4, pp. 2435--2438.
+\newblock  In~Proceedings of the Fourth International  Conference on Spoken Language (ICSLP 96),  {Philadelphia, PA, USA, 3--6 October} 1996; Volume~4, pp. 2435--2438.
 %please confirm if the added information is right. %R: Confirmed
@@
 {\em ITU-T P.835: Subjective Test Methodology for Evaluating Speech Communication
-  Systems That Include Noise Suppression Algorithm}; \hl{ITU: Geneva, Switzerland,} 2003.
+  Systems That Include Noise Suppression Algorithm}; {ITU: Geneva, Switzerland,} 2003.
 %please confirm if the added information is right, and confirm if the layout  is right.
@@
 Ntalampiras, S.; Ganchev, T.; Potamitis, I.
-\newblock \fg{Objective comparison of speech enhancement algorithms under real world conditions.}
+\newblock {Objective comparison of speech enhancement algorithms under real world conditions.}
 \newblock  In Proceedings of the 1st International Conference on PErvasive Technologies Related to
-  Assistive Environments, \hl{Athens, Greece, 15--19 July} 2008.
+  Assistive Environments, {Athens, Greece, 15--19 July} 2008.
 %please confirm if the added information is right. %R: Confirmed
@@
 {\em IEC 61672-1:2013---Electroacoustics---Sound Level Meters---Part 1:
-  Specifications}; \hl{IEC: Geneva, Switzerland,}~2013.
+  Specifications}; {IEC: Geneva, Switzerland,}~2013.
 %please confirm if the added information is right, and confirm if the layout  is right.

### 2018-12-05 paper/articleV3.tex
Add correct python implementation

@@
 \address{%
-$^{1}$ \quad {LS2N}{, UMR 6004, CNRS, \'Ecole Centrale de Nantes, 44300 Nantes}, France; felix.gontier@ls2n.fr\\%please add the complete location and add its zip code. %R: done
-$^{2}$ \quad {IFSTTAR, AME, LAE}{, 44340 Bouguenais, France}; pierre.aumond@ifsttar.fr (P.A.); arnaud.can@ifsttar.fr (A.C.)\\%please add the complete location and add it's zip code. %R: done
-$^{3}$ \quad {ETIS, UMR 8051}%please add the complete location and add it's zip code.
-, Universit\'e Paris Seine, Universit\'e de Cergy-Pontoise, ENSEA, CNRS, F-95000 {Cergy-Pontoise}; %please add the city. %R: done
+$^{1}$ \quad {LS2N, UMR 6004, \'Ecole Centrale de Nantes, 44300 Nantes, France}, France; felix.gontier@ls2n.fr\\%please add the complete location and add its zip code. %R: done
+$^{2}$ \quad {LAE, AME, IFSTTAR, 44340 Bouguenais, France}; pierre.aumond@ifsttar.fr (P.A.); arnaud.can@ifsttar.fr (A.C.)\\%please add the complete location and add it's zip code. %R: done
+$^{3}$ \quad {ETIS, UMR 8051, Université Paris Seine, Université de Cergy-Pontoise, ENSEA, CNRS, 95000 Cergy-Pontoise, France}; %please add the city. %R: done
  catherine.lavandier@u-cergy.fr}
@@
 %\bibliography{your_external_BibTeX_file}
-\section{References}
+\reftitle{References}
 \begin{thebibliography}{999}

### 2018-12-05 embedded/matlab/cense_dec.m

@@ -40,7 +40,7 @@ iH(isnan(iH)) = 0; % Some frequencies are outside analysis range, ie we divide b
 %% Huffman dictionnary
 load dict;
 
-imp_ver = 0;
+imp_ver = 1;
 % ----- END - Matlab ----- %
 
 if ~imp_ver

### 2018-12-05 embedded/matlab/cense_enc.m

@@ -27,8 +27,8 @@ x = resample(x(:, 1), sr, sr_temp); % Resample to 32kHz
 
 sig_type = 'White noise';
 sig_type = 'Sweep';
-sig_type = 'Sine_440';
-sig_type = 'Sine_440_emb';
+%sig_type = 'Sine_440';
+%sig_type = 'Sine_440_emb';
 
 switch sig_type
     case 'White noise'

### 2018-12-05 embedded/python/cense_dec.py

@@ -1,8 +1,9 @@
 import sys
 import numpy as np
 # from librosa import core
-import matplotlib.pyplot as plt
-import soundfile as sf
+#import matplotlib.pyplot as plt
+#import soundfile as sf
+import librosa as lr
 
 # Constants: process parameters
 sr = 32000
@@ -45,7 +46,11 @@ for line in c_file: # Texture frames
 	q_norm[0] = float(c_temp[0])
 	q_norm[1] = float(c_temp[1])
 	X_huff_l = int(c_temp[2])
-	X_huff = c_temp[3]
+	X_huffh = c_temp[3]
+	
+	X_huff = ""
+	for ind_byte in range(int(len(X_huffh)/2)):
+		X_huff = X_huff+bin(int(X_huffh[ind_byte*2:(ind_byte+1)*2], 16))[2:].zfill(8)
 	# Huffman
 	X_delta = []
 
@@ -64,7 +69,6 @@ for line in c_file: # Texture frames
 
 	X_delta = [int(i) for i in X_delta]
 	X_delta = np.reshape(X_delta,(-1,iH.shape[1])).transpose()
-	print(X_delta)
 	# Delta
 	X_tob = np.zeros(X_delta.shape)
 	X_tob[:,0] = X_delta[:,0]
@@ -72,8 +76,6 @@ for line in c_file: # Texture frames
 		X_tob[:,ind_f_tf] = X_delta[:,ind_f_tf]+X_tob[:,ind_f_tf-1]
 	# Normalisation + Quantization
 	X_tob = q_norm[1]*X_tob/(np.power(2,q-1)-1)+q_norm[0]
-
-	print(X_tob)
 
 	# Third-octave bands to spectrogram
 	X_tob = np.power(10,X_tob/10) # Linear amplitude
@@ -113,10 +115,5 @@ x = x_temp/np.absolute(x_temp).max()
 # Save resulting audio
 np.savetxt("".join((d_filename,"_dec.txt")), x, fmt='%.18e', delimiter=',', newline='\n', header='', footer='', comments='# ')
 
+lr.output.write_wav('sinus_440_emb_dec.wav', x, sr)
 
-sf.write('sinus_440_emb_dec.ogg', x, sr)
-
-
-t = np.linspace(0,x_temp.shape[0]/sr, num=x_temp.shape[0])
-plt.plot(t, x_temp)
-plt.show()

### 2018-12-05 embedded/python/cense_enc.py

@@ -27,10 +27,10 @@ with open("tob_4096.txt") as w_file:
 		f_temp = line.split(',')
 		# Weight array (variable length)
 		f_temp = [float(i) for i in f_temp]
-		H.append(f_temp[4:])
+		H.append(f_temp[2:])
 		# Beginning and end indices
 		f_temp = [int(i) for i in f_temp]
-		f.append(f_temp[:4])
+		f.append(f_temp[:2])
 
 # Load Huffman dictionary
 d_sym = []
@@ -57,9 +57,6 @@ X_tob = np.zeros((len(f), l_tf))
 X_tob2 = np.zeros((len(f), l_tf))
 
 
-# Open a code file
-c_file = open("".join((d_filename,"_enc.txt")), 'w')
-
 # Process
 for ind_frame in range(1,n_frames+1):
 	# Squared magnitude of RFFT
@@ -67,17 +64,7 @@ for ind_frame in range(1,n_frames+1):
 	X = np.square(np.absolute(X))/fft_norm
 	# Third-octave band analysis
 	for ind_band in range(0,len(f)):
-		# ----- Add where weights equal 1 version -----
-		X_tob2[ind_band, ind_f] = 0
-		if f[ind_band][1] != 0: # 0 if there is no 1 part
-			# f[][0]: first nonzero weight, increasing part - f[][1]: last non-1 weight, increasing part - f[][2]: first nonzero weight, increasing part - f[][3]: last non-1 weight, increasing part
-			X_tob2[ind_band, ind_f] = X_tob2[ind_band, ind_f] + np.dot(X[f[ind_band][0]-1:f[ind_band][1]], H[ind_band][:f[ind_band][1]-f[ind_band][0]+1]) # Increasing part
-			X_tob2[ind_band, ind_f] = X_tob2[ind_band, ind_f] + X[f[ind_band][1]:f[ind_band][2]-1] # 1 part
-			X_tob2[ind_band, ind_f] = X_tob2[ind_band, ind_f] + np.dot(X[f[ind_band][2]-1:f[ind_band][3]], H[ind_band][f[ind_band][1]-f[ind_band][0]+1:]) # Decreasing part
-		else
-			X_tob2[ind_band, ind_f] = X_tob2[ind_band, ind_f] + np.dot(X[f[ind_band][0]-1:f[ind_band][3]], H[ind_band])
-		# ----- END -----
[…]
